---
title: "Estimate structural parameters"
author: "Katsuhiro Komatsu"
date: "`r Sys.Date()`"
output: 
  html_document
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 4, fig.width = 8)

library(magrittr)
library(ggplot2)
library(kableExtra)
library(Dispatching)
```

```{css, echo = FALSE}

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

```

```{r}
result_dist_IV <- readRDS(here::here("output/estimate_structural_parameters/result_distance_IV.RDS"))
result_dist_IV_selected <- readRDS(here::here("output/estimate_structural_parameters/result_distance_IV_selected.RDS"))
result_rivals_IV <- readRDS(here::here("output/estimate_structural_parameters/result_rivals_IV.RDS"))
equilibrium_dist_IV <- readRDS(here::here("output/estimate_structural_parameters/equilibrium_data_distance_IV.RDS"))
equilibrium_dist_IV_selected <- readRDS(here::here("output/estimate_structural_parameters/equilibrium_data_distance_IV_selected.RDS"))
equilibrium_rivals_IV <- readRDS(here::here("output/estimate_structural_parameters/equilibrium_data_rivals_IV.RDS"))
share_data <- readRDS(here::here("output/share_data_small_markets.RDS"))
```

```{r}
equilibrium_iv_dist <- readRDS(here::here("output/estimate_model/equilibrium_iv_dist.rds"))
equilibrium_iv_dist_selected <- readRDS(here::here("output/estimate_model/equilibrium_iv_dist_selected.rds"))
equilibrium_iv_rivals <- readRDS(here::here("output/estimate_model/equilibrium_iv_rivals.rds"))
```


- For parameters of the matching function, use $\alpha = 0.566$ and $\beta=0.360$.

### Distribution of match efficiency
```{r}

# mp <- equilibrium_iv_dist$parameters$matching_params
# mu <- share_data$Q / (share_data$D_W ^ mp[1] * share_data$D_F ^ mp[2])
mu <- equilibrium_iv_dist$dataframe$mu

data.frame(mu = mu) %>% 
  ggplot(
    aes(
      x = log(mu),
      fill = "all"
    )
  ) +
  geom_histogram() +
  scale_fill_viridis_d() +
  theme_classic() +
  labs(
    x = "log of match efficiency"
  ) +
  theme(
    legend.position = "none"
  )


```


# Parameters {.tabset}

## Distance IV

### Demand parameters

```{r}
result_table <- make_coefficient_table_demand_side(equilibrium_iv_dist)

result_table %>%
  kbl() %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/parameters_demand_dist_IV.tex"))
```


### Cost parameters

```{r}

result_table <- make_coefficient_table_supply_side(equilibrium_iv_dist)

result_table %>%
  kbl() %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/parameters_cost_dist_IV.tex"))
```


### Converted to reduced-form


```{r}
result_table <- make_coefficient_table_demand_side_converted_to_reduced_form(equilibrium_iv_dist)

result_table %>%
  kbl() %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/parameters_demand_side_converted_to_reduced_form_dist_IV.tex"))
```


### Decompose network effects

```{r}
result_table <- make_elasticity_table_detailed(equilibrium_iv_dist)

result_table %>%
  kbl() %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/elasticity_decomposition_dist_IV.tex"))
```


## Distance IV (selected)

### Demand parameters

```{r}
result_table <- make_coefficient_table_demand_side(equilibrium_iv_dist_selected)

result_table %>%
  kbl() %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/parameters_demand_dist_IV_selected.tex"))
```


### Cost parameters

```{r}

result_table <- make_coefficient_table_supply_side(equilibrium_iv_dist_selected)

result_table %>%
  kbl() %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/parameters_cost_dist_IV_selected.tex"))
```


### Converted to reduced-form


```{r}
result_table <- make_coefficient_table_demand_side_converted_to_reduced_form(equilibrium_iv_dist_selected)

result_table %>%
  kbl() %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/parameters_demand_side_converted_to_reduced_form_dist_IV_selected.tex"))
```


### Decompose network effects

```{r}
result_table <- make_elasticity_table_detailed(equilibrium_iv_dist_selected)

result_table %>%
  kbl() %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/elasticity_decomposition_dist_IV_selected.tex"))
```




## Num rivals IV


### Demand parameters

```{r}
result_table <- make_coefficient_table_demand_side(equilibrium_iv_rivals)

result_table %>%
  kbl() %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/parameters_demand_rivals_IV.tex"))
```


### Cost parameters

```{r}

result_table <- make_coefficient_table_supply_side(equilibrium_iv_rivals)

result_table %>%
  kbl() %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  add_header_above(
    c(
      "",
      "Worker" = 2,
      "Client firm" = 2
    ) 
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/parameters_cost_rivals_IV.tex"))
```


### Converted to reduced-form


```{r}
result_table <- make_coefficient_table_demand_side_converted_to_reduced_form(equilibrium_iv_rivals)

result_table %>%
  kbl() %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/parameters_demand_side_converted_to_reduced_form_rivals_IV.tex"))
```


### Decompose network effects

```{r}
result_table <- make_elasticity_table_detailed(equilibrium_iv_rivals)

result_table %>%
  kbl() %>%
  kable_classic()

result_table %>%
  kbl(
    escape = FALSE,
    align = rep("r", ncol(result_table)),
    linesep = "",
    format = "latex",
    booktabs = TRUE
  ) %>%
  save_kable(table, file = here::here("figuretable/estimate_structural_parameters/elasticity_decomposition_rivals_IV.tex"))
```
