---
title: "Counterfactual: Margin constraint"
author: "Katsuhiro Komatsu"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F)

library("magrittr")
library("ggplot2")
library("foreach")
library("Dispatching")

```


```{r}
equilibrium <- readRDS(here::here("output/estimate_structural_parameters/equilibrium_data_distance_IV.RDS"))
result_hypo <- readRDS(here::here("output/simulate_margin_constraint/result_hypothetical_market.RDS"))
result_act <- readRDS(here::here("output/simulate_margin_constraint/result_actual_market.RDS"))
```


```{r}

data <- result_hypo$data_cf

margin_ranking <- result_hypo$equilibrium_original %>% 
  dplyr::mutate(margin = log(fee) - log(wage))%>%
  dplyr::arrange(-margin) %>% 
  dplyr::select(id_unique)

margin_ranking$ranking <- 1:dim(margin_ranking)[1]

data <- data %>% 
  dplyr::left_join(margin_ranking, by = "id_unique")


```




```{r}
surplus_list <- list()
outcome_list <- list()

# Loop over constraints
for (j in 1:length(result_act$equilibrium)){

  surplus_j <- result_act$surplus[[j]] %>% as.data.frame()
  surplus_j$margin_constraint <- result_act$margin_constraint[j]
  surplus_list[[j]] <- surplus_j
  
  eq_j <- result_act$equilibrium[[j]]$endogenous %>% 
    do.call("rbind", .) %>% 
    as.data.frame() %>% 
    na.omit()
  
  outcome_list[[j]] <- eq_j %>% 
    dplyr::summarise(
      wage = mean(wage),
      fee = mean(fee),
      s_W = mean(s_W),
      s_F = mean(s_F),
      negative_profit = mean(profit < 0)
    ) %>% 
    dplyr::mutate(margin_constraint = result_act$margin_constraint[j])
  
}

surplus_all <- do.call("rbind", surplus_list)

# surplus_baseline <- compute_surplus(equilibrium) %>% as.data.frame()
surplus_baseline <- surplus_list[[1]] %>% dplyr::select(-margin_constraint)

surplus_all <- surplus_all %>% 
  dplyr::left_join(surplus_baseline, by = c("year", "cz")) %>% 
  dplyr::mutate(
    WS = WS.x - WS.y,
    FS = FS.x - FS.y,
    profit = profit.x - profit.y
  ) %>% 
  dplyr::select(cz, year, margin_constraint, WS, FS, profit)


outcome_mean <- do.call("rbind", outcome_list)


```


```{r}
# Margin constraint vs. fraction of establishments with binding constraint
margin <- equilibrium$generate_dataframe() %>% 
  dplyr::mutate(margin = log(fee) - log(wage)) %>% 
  dplyr::pull(margin)
frac <- rep(0, 5)

frac[1] <- mean(margin >= 0.1)
frac[2] <- mean(margin >= 0.2)
frac[3] <- mean(margin >= 0.3)
frac[4] <- mean(margin >= 0.4)
frac[5] <- mean(margin >= 0.5)

frac_constrained <- data.frame(margin_constraint = pracma::linspace(0.1, 0.5, 5),
                               frac = frac)

```





# Simulation in a hypothetical market
- Construct a hypothetical market with two establishments.
  - One has $a^W$ that is at +1 s.d. of the empirical distribution. The other has $a^W$ that is at -1 s.d.
  
```{r}
limits <- c(0, 0)
limits[1] <- max(data$margin_constraint)
limits[2] <- min(data$margin_constraint)
height <- 3
width <- 4

color <- "#440154FF"

```




:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px; "}

::: {}

## Wage

```{r}
data %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = wage,
      linetype = factor(ranking),
      shape = factor(ranking)
    )
  ) + 
  ggrepel::geom_text_repel(aes(label = round(wage, 2), y = wage - 0.1), size = 3, color = color) +
  geom_line(color = color) +
  geom_point(color = color) +
  scale_linetype_discrete(name = "Baseline margin rank") +
  scale_shape_discrete(name = "Baseline margin rank") +
  scale_x_reverse(limits = limits) +
  labs(
    x = "Margin constraint",
    y = "Wage (10K Yen / Day)"
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/wage.png"),
  width = width,
  height = height
)


```



:::

::: {}

## Fee
```{r}
data %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = fee,
      linetype = factor(ranking),
      shape = factor(ranking)
    )
  ) + 
  ggrepel::geom_text_repel(aes(label = round(fee, 2), y = fee - 0.15), size = 3, color = color) +
  geom_line(color = color) +
  geom_point(color = color) +
  scale_linetype_discrete(name = "Baseline margin rank") +
  scale_shape_discrete(name = "Baseline margin rank") +
  scale_x_reverse(limits = limits) +
  labs(
    x = "Margin constraint",
    y = "Fee (10K Yen / Day)"
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/fee.png"),
  width = width,
  height = height
)

```


:::

::::

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px; "}

::: {}

## Worker share
```{r}
data %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = s_W,
      color = "all",
      linetype = factor(ranking),
      shape = factor(ranking)
    )
  ) + 
  ggrepel::geom_text_repel(aes(label = round(s_W, 4), y = s_W * 1.1), size = 3, color = color) +
  geom_line(color = color) +
  geom_point(color = color) +
  scale_linetype_discrete(name = "Baseline margin rank") +
  scale_shape_discrete(name = "Baseline margin rank") +
  scale_x_reverse(limits = limits) +
  labs(
    x = "Margin constraint",
    y = "Worker shares"
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/worker_share.png"),
  width = width,
  height = height
)

```

:::

::: {}

## Firm share
```{r}
data %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = s_F,
      color = "all",
      linetype = factor(ranking),
      shape = factor(ranking)
    )
  ) + 
  ggrepel::geom_text_repel(aes(label = round(s_F, 6), y = s_F * 0.9), size = 3, color = color) +
  geom_line(color = color) +
  geom_point(color = color) +
  scale_linetype_discrete(name = "Baseline margin rank") +
  scale_shape_discrete(name = "Baseline margin rank") +
  scale_x_reverse(limits = limits) +
  labs(
    x = "Margin constraint",
    y = "Client firm shares"
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/firm_share.png"),
  width = width,
  height = height
)
```

:::

::::



## Match

```{r}
data %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = Q,
      color = "all",
      linetype = factor(ranking),
      shape = factor(ranking)
    )
  ) + 
  ggrepel::geom_text_repel(aes(label = round(Q, 5), y = Q * 0.9), size = 3, color = color) +
  geom_line(color = color) +
  geom_point(color = color) +
  scale_linetype_discrete(name = "Baseline margin rank") +
  scale_shape_discrete(name = "Baseline margin rank") +
  scale_x_reverse(limits = limits) +
  labs(
    x = "Margin constraint",
    y = "Matches"
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/match.png"),
  width = width,
  height = height
)

```


## Margin

```{r, out.width = "60%"}
data %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = log(fee) - log(wage),
      color = "all",
      linetype = factor(ranking),
      shape = factor(ranking)
    )
  ) + 
  ggrepel::geom_text_repel(aes(label = round(log(fee) - log(wage), 2), y = log(fee) - log(wage) - 0.05), size = 3, color = color) +
  geom_line(color = color) +
  geom_point(color = color) +
  scale_linetype_discrete(name = "Baseline margin rank") +
  scale_shape_discrete(name = "Baseline margin rank") +
  scale_x_reverse(limits = limits) +
  labs(
    x = "Margin constraint",
    y = "Margin"
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom"
  )

ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/margin.png"),
  width = width,
  height = height
)
```


## Profit

```{r}
data %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = profit,
      color = "all",
      linetype = factor(ranking),
      shape = factor(ranking)
    )
  ) + 
  ggrepel::geom_text_repel(aes(label = round(profit, 4), y = profit  * 0.9), size = 3, color = color) +
  geom_line(color = color) +
  geom_point(color = color) +
  scale_linetype_discrete(name = "Baseline margin rank") +
  scale_shape_discrete(name = "Baseline margin rank") +
  scale_x_reverse(limits = limits) +
  labs(
    x = "Margin constraint",
    y = "Profit"
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/profit.png"),
  width = width,
  height = height
)

```



# Simulation in actual markets

## Fraction of constrained establishments

```{r}
frac_constrained %>% 
  dplyr::mutate(group = "all") %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = frac,
      color = "all"
    )
  ) +
  geom_point() + 
  geom_text(aes(label = round(frac, 2), y = frac - 0.05), size = 3) +
  geom_line() +
  ylim(0, 1) +
  scale_x_reverse() +
  labs(
    x = "Margin",
    y = "Fraction of establishments"
  ) +
  scale_color_viridis_d() +
  theme_classic() +
  theme(
    legend.position = "none"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/constrained_fraction.png"),
  width = width,
  height = height
)

```



## Average outcomes

### Wage
```{r}
outcome_mean %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = wage,
      color = "all"
    )
  ) +
  geom_text(aes(label = round(wage, 2), y = wage * 0.98), size = 3) +
  geom_line() +
  geom_point() +
  scale_color_viridis_d() +
  scale_x_reverse() +
  labs(
    x = "Margin constraint",
    y = "Wage (10K Yen / Day)"
  ) +
  theme_classic() +
  theme(
    legend.position = "none"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/wage_actual_market.png"),
  width = width,
  height = height
)  


```

### Fee
```{r}
outcome_mean %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = fee,
      color = "all"
    )
  ) +
  geom_text(aes(label = round(fee, 2), y = fee * 0.98), size = 3) +
  geom_line() +
  geom_point() +
  scale_color_viridis_d() +
  scale_x_reverse() +
  labs(
    x = "Margin constraint",
    y = "Fee (10K Yen / Day)"
  ) +
  theme_classic() +
  theme(
    legend.position = "none"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/fee_actual_market.png"),
  width = width,
  height = height
)  


```


### Worker share

```{r}
outcome_mean %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = s_W,
      color = "all"
    )
  ) +
  geom_text(aes(label = round(s_W, 4), y = s_W * 1.05), size = 3) +
  geom_line() +
  geom_point() +
  scale_color_viridis_d() +
  scale_x_reverse() +
  labs(
    x = "Margin constraint",
    y = "Worker share"
  ) +
  theme_classic() +
  theme(
    legend.position = "none"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/worker_share_actual_market.png"),
  width = width,
  height = height
)  


```


### Firm share

```{r}
outcome_mean %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = s_F,
      color = "all"
    )
  ) +
  geom_text(aes(label = round(s_F, 6), y = s_F * 1.05), size = 3) +
  geom_line() +
  geom_point() +
  scale_color_viridis_d() +
  scale_x_reverse() +
  scale_y_continuous(labels = scales::comma) +
  labs(
    x = "Margin constraint",
    y = "Client firm share"
  ) +
  theme_classic() +
  theme(
    legend.position = "none"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/firm_share_actual_market.png"),
  width = width,
  height = height
)  


```


### Fraction of establishments with negative profits

```{r}
outcome_mean %>% 
  ggplot(
    aes(
      x = margin_constraint,
      y = negative_profit,
      color = "all"
    )
  ) +
  geom_text(aes(label = round(negative_profit, 4), y = negative_profit + 0.005), size = 3) +
  geom_line() +
  geom_point() +
  scale_color_viridis_d() +
  scale_x_reverse() +
  scale_y_continuous(labels = scales::comma) +
  labs(
    x = "Margin constraint",
    y = "Fraction of establishments \n with negative profits"
  ) +
  theme_classic() +
  theme(
    legend.position = "none"
  )


ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/fraction_negative_profits.png"),
  width = width,
  height = height
)  


```



## Surplus

### Median

```{r}
surplus_all %>% 
  dplyr::group_by(margin_constraint) %>% 
  dplyr::summarise(
    WS = median(WS),
    FS = median(FS),
    profit = median(profit),
    total = median(WS + FS + profit)
  ) %>% 
  dplyr::ungroup() %>% 
  tidyr::pivot_longer(cols = WS:total) %>%
  dplyr::mutate(
    name = dplyr::case_when(
      name == "WS" ~ "Worker",
      name == "FS" ~ "Client firm",
      name == "profit" ~ "THS",
      name == "total" ~ "Total"
    )
  ) %>%  
  ggplot(
    aes(
      x = margin_constraint,
      y = value,
      color = name,
      linetype = name
    )
  ) + 
  geom_line() +
  geom_point() +
  scale_color_viridis_d() +
  scale_x_reverse(limits = c(0.5, 0.2)) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    x = "Margin constraint",
    y = "Median Surplus (10K Yen / Day)"
  ) +
  theme_classic() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  )

ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/surplus_median.png"),
  width = width,
  height = height
)
```


### Mean

```{r}
surplus_all %>% 
  dplyr::group_by(margin_constraint) %>% 
  dplyr::summarise(
    WS = mean(WS),
    FS = mean(FS),
    profit = mean(profit),
    total = mean(WS + FS + profit)
  ) %>% 
  dplyr::ungroup() %>% 
  tidyr::pivot_longer(cols = WS:total) %>%
  dplyr::mutate(
    name = dplyr::case_when(
      name == "WS" ~ "Worker",
      name == "FS" ~ "Client firm",
      name == "profit" ~ "THS",
      name == "total" ~ "Total"
    )
  ) %>%  
  ggplot(
    aes(
      x = margin_constraint,
      y = value,
      color = name,
      linetype = name
    )
  ) + 
  geom_line() +
  geom_point() +
  scale_color_viridis_d() +
  scale_x_reverse(limits = c(0.5, 0.2)) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    x = "Margin constraint",
    y = "Mean Surplus (10K Yen / Day)"
  ) +
  theme_classic() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  )

ggsave(
  filename = here::here("figuretable/simulate_margin_constraint/surplus_mean.png"),
  width = width,
  height = height
)
```



