---
title: "report_reduced_form_analysis"
author: "Daisy Dan Song"
date: "2026-01-06"
output: html_document
---

# initialize
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )
rm(list = ls())
library(Dispatching)
library(foreach)
library(magrittr)
library(codetools)
library(ggplot2)
library(kableExtra)
library(purrr)
library(dplyr)
library(tidyr)
library(fixest)
library(broom)
library(glue)
library(patchwork)
library(here)
```

# load data
```{r}
# load data --------------------------------------------------------------
data_establishment <- 
  readRDS(
    file = "cleaned/data_establishments.RDS" %>%
    here::here()
  )
data_zipcode <- 
  readRDS(
   file =  "cleaned/data_zipcode.RDS" %>%
    here::here()
  )
data_area <- 
  readRDS(
   file =  "cleaned/data_area.RDS" %>%
    here::here()
  )
data_pref_year_minimum_wage <- 
  readRDS(
   file =  "cleaned/data_pref_year_minimum_wage.RDS" %>%
    here::here()
  )
data_year <- 
  readRDS(
   file =  "cleaned/data_year.RDS" %>%
    here::here()
  )
data_area_year_num_parttemp <-
  readRDS(
   file =  "cleaned/data_area_year_num_parttemp.RDS" %>%
    here::here()
  )
data_area_year_num_firm <-
  readRDS(
   file =  "cleaned/data_area_year_num_firms.RDS" %>%
    here::here()
  )
data_area_year_num_labor <-
  readRDS(
    file = "cleaned/data_area_year_num_labor.RDS" %>%
    here::here()
  )
data_area_year_partwage <-
  readRDS(
   file =  "cleaned/data_area_year_partwage.RDS" %>%
    here::here()
  )
out_dir <- here::here("draft/figuretable/descriptives/aggregate/cross_section")
```

# replication of daiji result 

```{r daiji-data-construction}
daiji_df <-
  data_establishment %>%
  inner_join(data_zipcode, by = "zipcode") %>%
  inner_join(data_area, by = "area_code") %>%
  inner_join(data_pref_year_minimum_wage, by = c("pref", "year")) %>%
  inner_join(
    readRDS(here::here("cleaned/data_pref_year_partwage.RDS")),
    by = c("pref", "year")
  ) %>%
  inner_join(data_year, by = "year") %>%
  mutate(
    temptot = tempperm + tempfixed
  ) %>%
  group_by(year, cz) %>%
  mutate(
    n_cz = n(),
    n_cz_10000 = n_cz / 10000
  ) %>%
  ungroup() %>%
  mutate(
    tot = perm + fixed,
    staffperm = ifelse(perm - tempperm < 0, NA_real_, perm - tempperm),
    stafffixed = ifelse(fixed - tempfixed < 0, NA_real_, fixed - tempfixed),
    margin = ifelse((fee - wage) / fee < 0, NA_real_, (fee - wage) / fee),
    lfee = log(fee),
    lwage = log(wage),
    lfee_wage = lfee - lwage
  ) %>%
  filter(
    year != 2015,
    temptot > 5,
    !is.na(staffperm),
    !is.na(stafffixed),
    !is.na(wage), !is.na(fee),
    wage <= fee,
    !(is.na(wagedaily) & !is.na(feedaily)),
    !(!is.na(wagedaily) & is.na(feedaily)),
    is.na(wagedaily) | wagedaily <= feedaily
  )

cat("Daiji replication sample size:", nrow(daiji_df), "\n")
```

```{r daiji-regression}
reg_fee <- feols(lfee ~ n_cz_10000 | cz + year, data = daiji_df, cluster = ~cz)
reg_wage <- feols(lwage ~ n_cz_10000 | cz + year, data = daiji_df, cluster = ~cz)
reg_margin <- feols(lfee_wage ~ n_cz_10000 | cz + year, data = daiji_df, cluster = ~cz)

# Recover a reported constant from the equivalent dummy-variable
# representation of the same FE specification.
reg_fee_const <-
  feols(lfee ~ n_cz_10000 + factor(cz) + factor(year), data = daiji_df, cluster = ~cz)
reg_wage_const <-
  feols(lwage ~ n_cz_10000 + factor(cz) + factor(year), data = daiji_df, cluster = ~cz)
reg_margin_const <-
  feols(
    lfee_wage ~ n_cz_10000 + factor(cz) + factor(year),
    data = daiji_df,
    cluster = ~cz
  )

etable(
  reg_fee, reg_wage, reg_margin,
  headers = c("ln(fee)", "ln(wage)", "ln(fee) - ln(wage)"),
  se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  fitstat = ~ n + r2
)

```

```{r daiji-binscatter, fig.width=10, fig.height=3.5}
residualize_fe <- function(var_name, data) {
  model <- feols(
    stats::as.formula(paste0(var_name, " ~ 1 | cz + year")),
    data = data
  )
  stats::residuals(model)
}

make_daiji_binscatter_df <- function(y_var, x_var, label, data) {
  data_clean <-
    data %>%
    filter(!is.na(.data[[y_var]]), !is.na(.data[[x_var]]))

  x_mean <- mean(data_clean[[x_var]], na.rm = TRUE)
  y_mean <- mean(data_clean[[y_var]], na.rm = TRUE)

  data_clean$x_resid <- residualize_fe(x_var, data_clean)
  data_clean$y_resid <- residualize_fe(y_var, data_clean)

  data_clean %>%
    mutate(bin = ntile(x_resid, 50)) %>%
    group_by(bin) %>%
    summarise(
      x = mean(x_resid, na.rm = TRUE) + x_mean,
      y = mean(y_resid, na.rm = TRUE) + y_mean,
      .groups = "drop"
    ) %>%
    mutate(panel = label)
}

plot_df <- bind_rows(
  make_daiji_binscatter_df("lfee", "n_cz_10000", "ln(fee)", daiji_df),
  make_daiji_binscatter_df("lwage", "n_cz_10000", "ln(wage)", daiji_df),
  make_daiji_binscatter_df("lfee_wage", "n_cz_10000", "ln(fee) - ln(wage)", daiji_df)
) %>%
  mutate(
    panel = factor(
      panel,
      levels = c("ln(fee)", "ln(wage)", "ln(fee) - ln(wage)")
    )
  )

line_df <-
  tibble(
    panel = factor(
      c("ln(fee)", "ln(wage)", "ln(fee) - ln(wage)"),
      levels = c("ln(fee)", "ln(wage)", "ln(fee) - ln(wage)")
    ),
    slope = c(
      unname(stats::coef(reg_fee)["n_cz_10000"]),
      unname(stats::coef(reg_wage)["n_cz_10000"]),
      unname(stats::coef(reg_margin)["n_cz_10000"])
    ),
    intercept = c(
      mean(daiji_df$lfee[!is.na(daiji_df$lfee)], na.rm = TRUE) -
        unname(stats::coef(reg_fee)["n_cz_10000"]) *
        mean(daiji_df$n_cz_10000[!is.na(daiji_df$lfee)], na.rm = TRUE),
      mean(daiji_df$lwage[!is.na(daiji_df$lwage)], na.rm = TRUE) -
        unname(stats::coef(reg_wage)["n_cz_10000"]) *
        mean(daiji_df$n_cz_10000[!is.na(daiji_df$lwage)], na.rm = TRUE),
      mean(daiji_df$lfee_wage[!is.na(daiji_df$lfee_wage)], na.rm = TRUE) -
        unname(stats::coef(reg_margin)["n_cz_10000"]) *
        mean(daiji_df$n_cz_10000[!is.na(daiji_df$lfee_wage)], na.rm = TRUE)
    )
  )

p_binscatter <-
  ggplot(plot_df, aes(x = x, y = y)) +
  geom_point(shape = 16, color = "#123b5d", size = 2.7, alpha = 0.95) +
  geom_abline(
    data = line_df,
    aes(slope = slope, intercept = intercept),
    color = "#b22222",
    linewidth = 1.05
  ) +
  facet_wrap(~ panel, scales = "free_y", strip.position = "left") +
  labs(
    x = "Number of establishments in CZ in 10,000",
    y = NULL
  ) +
  theme_bw(base_size = 11, base_family = "Times") +
  theme(
    panel.grid = element_blank(),
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text = element_text(face = "plain"),
    strip.text.y.left = element_text(angle = 90, face = "plain"),
    axis.title.x = element_text(margin = margin(t = 10)),
    legend.position = "none"
  )

ggsave(
  filename = here::here(
    "draft/figuretable/descriptives/aggregate/cross_section/combined_graph_daisy_replication.pdf"
  ),
  plot = p_binscatter,
  width = 10,
  height = 3.5,
  device = grDevices::pdf
)

p_binscatter
```

# make data base
```{r}
data_base <-
  make_data_base(
    data_establishment = data_establishment,
    data_zipcode = data_zipcode,
    data_area = data_area,
    data_pref_year_minimum_wage = data_pref_year_minimum_wage,
    data_year = data_year,
    data_area_year_num_parttemp = data_area_year_num_parttemp,
    data_area_year_num_firm = data_area_year_num_firm,
    data_area_year_num_labor = data_area_year_num_labor,
    data_area_year_partwage = data_area_year_partwage
  ) 

data_base_top5 <- 
  make_data_base_nationwide_top5(
    data_base = data_base
  )

data_base_fringe <-
  make_data_base_fringe_ths(
    data_base = data_base,
    data_base_top5 = data_base_top5
  ) 

data_base_all <- 
  rbind(
    data_base_top5,
    data_base_fringe
  )

make_binscatter_long <-
  function(
    df,
    x_var,
    y_vars = c("ln_f", "ln_w", "ln_m"),
    y_labels = c("Log fee", "Log wage", "Log margin"),
    n_bins = 20
  ) {
    df$x_bin_value <- df[[x_var]]
    df$bin_id <- dplyr::ntile(df$x_bin_value, n_bins)
    
    out <-
      df %>%
      dplyr::group_by(.data$bin_id) %>%
      dplyr::summarise(
        x_bin = mean(.data$x_bin_value, na.rm = TRUE),
        dplyr::across(
          dplyr::all_of(y_vars),
          function(z) mean(z, na.rm = TRUE)
        ),
        .groups = "drop"
      ) %>%
      tidyr::pivot_longer(
        cols = dplyr::all_of(y_vars),
        names_to = "var",
        values_to = "value"
      ) %>%
      dplyr::mutate(
        var = factor(
          var,
          levels = y_vars,
          labels = y_labels
        )
      )
    
    names(out)[names(out) == "x_bin"] <- x_var
    
    return(out)
  }
```



# reduced form analysis
## top5 data with number of ths
```{r}
# build top5 regression sample directly from data_base_top5
panel_df_top5 <-
  data_base_top5 %>%
  dplyr::group_by(
    year,
    cz
  ) %>%
  dplyr::mutate(
    n_ths = dplyr::n(),
    n_firms = dplyr::n_distinct(firm_id)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f = log(f),
    ln_w = log(w),
    ln_m = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_ths),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  ) %>%
  dplyr::select(
    year,
    cz,
    firm_id,
    n_ths,
    n_firms,
    w,
    f,
    margin,
    ln_f,
    ln_w,
    ln_m
  )
summary(panel_df_top5)
```

```{r}
# two-way FE regressions: log fee, log wage, log margin on number of Establishments
reg_fee <- feols(ln_f ~ n_ths | cz + year, data = panel_df_top5)
reg_w   <- feols(ln_w ~ n_ths | cz + year, data = panel_df_top5)
reg_m   <- feols(ln_m ~ n_ths | cz + year, data = panel_df_top5)

reg_table <-
  list(
    "Log fee"    = reg_fee,
    "Log wage"   = reg_w,
    "Log margin" = reg_m
  )
```

```{r fig.width=12, fig.height=8}
# bin-scatter style plot mirroring main.tex figure
plot_df <-
  make_binscatter_long(
    df = panel_df_top5,
    x_var = "n_ths"
  )

p_breaks <- pretty(plot_df$n_ths, n = 5)


p_fee <-
  ggplot(
    dplyr::filter(plot_df, .data$var == "Log fee"),
    aes(x = .data$n_ths, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = unname(stats::coef(reg_fee)["n_ths"]),
    intercept = mean(panel_df_top5$ln_f, na.rm = TRUE) -
      unname(stats::coef(reg_fee)["n_ths"]) * mean(panel_df_top5$n_ths, na.rm = TRUE),
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks) +
  labs(
    x = "Number of Establishments in commuting zone",
    y = "Log fee"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_wage <-
  ggplot(
    dplyr::filter(plot_df, .data$var == "Log wage"),
    aes(x = .data$n_ths, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = unname(stats::coef(reg_w)["n_ths"]),
    intercept = mean(panel_df_top5$ln_w, na.rm = TRUE) -
      unname(stats::coef(reg_w)["n_ths"]) * mean(panel_df_top5$n_ths, na.rm = TRUE),
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks) +
  labs(
    x = "Number of Establishments in commuting zone",
    y = "Log wage"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_margin <-
  ggplot(
    dplyr::filter(plot_df, .data$var == "Log margin"),
    aes(x = .data$n_ths, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = unname(stats::coef(reg_m)["n_ths"]),
    intercept = mean(panel_df_top5$ln_m, na.rm = TRUE) -
      unname(stats::coef(reg_m)["n_ths"]) * mean(panel_df_top5$n_ths, na.rm = TRUE),
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks) +
  labs(
    x = "Number of Establishments in commuting zone",
    y = "Log margin"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

# save to cross_section directory (Figure 2 style)
out_dir <- here::here("draft/figuretable/descriptives/aggregate/cross_section")
if (!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)
combined_plot <- (p_fee + p_wage) / (p_margin + patchwork::plot_spacer())
ggsave(file.path(out_dir, "reduced_form_three_panel_top5_ths.pdf"), combined_plot, width = 12, height = 8)

combined_plot
```

```{r}
# regression table (similar to Table 2 in main.tex)
tab_tex <- 
  etable(
    reg_table,
    se.below = TRUE,
    keep = "n_ths",
    digits = 3,
    tex = TRUE,
    fitstat = c("r2", "n")
  )

# save table to cross_section directory (Table 2 style)
writeLines(
  tab_tex,
  con = file.path(
    here::here("draft/figuretable/descriptives/aggregate/cross_section"),
    "regress_top5ths.tex"
  )
)

# show in the knitted report as text output too
tab_view <- etable(
  reg_table,
  se.below = TRUE,
  keep = "n_ths",
  digits = 3,
  tex = FALSE,
  fitstat = c("r2", "n")
)

knitr::kable(tab_view)
```

## top5 data with number of distinctive firm_id

```{r}
# reuse panel_df; n_firms is already computed at cz-year level
panel_df_top5_firm <-
  panel_df_top5 %>%
  dplyr::select(
    year,
    cz,
    n_firms,
    w,
    f,
    margin,
    ln_f,
    ln_w,
    ln_m
  )

summary(panel_df_top5_firm)
```

```{r}
# two-way FE regressions: log fee, log wage, log margin on number of firms (top5 sample)
reg_fee_top5_firm <- feols(ln_f ~ n_firms | cz + year, data = panel_df_top5_firm)
reg_w_top5_firm   <- feols(ln_w ~ n_firms | cz + year, data = panel_df_top5_firm)
reg_m_top5_firm   <- feols(ln_m ~ n_firms | cz + year, data = panel_df_top5_firm)

reg_table_top5_firm <-
  list(
    "Log fee"    = reg_fee_top5_firm,
    "Log wage"   = reg_w_top5_firm,
    "Log margin" = reg_m_top5_firm
  )
```

```{r fig.width=12, fig.height=8}
# bin-scatter style plot with firm count (top5 sample)
plot_df_top5_firm <-
  make_binscatter_long(
    df = panel_df_top5_firm,
    x_var = "n_firms"
  )

p_breaks_top5_firm <- pretty(plot_df_top5_firm$n_firms, n = 5)

slope_fee_top5_firm <- unname(stats::coef(reg_fee_top5_firm)["n_firms"])
slope_wage_top5_firm <- unname(stats::coef(reg_w_top5_firm)["n_firms"])
slope_margin_top5_firm <- unname(stats::coef(reg_m_top5_firm)["n_firms"])

intercept_fee_top5_firm <- mean(panel_df_top5_firm$ln_f, na.rm = TRUE) - slope_fee_top5_firm * mean(panel_df_top5_firm$n_firms, na.rm = TRUE)
intercept_wage_top5_firm <- mean(panel_df_top5_firm$ln_w, na.rm = TRUE) - slope_wage_top5_firm * mean(panel_df_top5_firm$n_firms, na.rm = TRUE)
intercept_margin_top5_firm <- mean(panel_df_top5_firm$ln_m, na.rm = TRUE) - slope_margin_top5_firm * mean(panel_df_top5_firm$n_firms, na.rm = TRUE)

p_fee_top5_firm <-
  ggplot(
    dplyr::filter(plot_df_top5_firm, .data$var == "Log fee"),
    aes(x = .data$n_firms, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_fee_top5_firm,
    intercept = intercept_fee_top5_firm,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_top5_firm) +
  labs(
    x = "Number of firms in commuting zone",
    y = "Log fee"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_wage_top5_firm <-
  ggplot(
    dplyr::filter(plot_df_top5_firm, .data$var == "Log wage"),
    aes(x = .data$n_firms, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_wage_top5_firm,
    intercept = intercept_wage_top5_firm,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_top5_firm) +
  labs(
    x = "Number of firms in commuting zone",
    y = "Log wage"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_margin_top5_firm <-
  ggplot(
    dplyr::filter(plot_df_top5_firm, .data$var == "Log margin"),
    aes(x = .data$n_firms, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_margin_top5_firm,
    intercept = intercept_margin_top5_firm,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_top5_firm) +
  labs(
    x = "Number of firms in commuting zone",
    y = "Log margin"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

combined_plot_top5_firm <- (p_fee_top5_firm + p_wage_top5_firm) / (p_margin_top5_firm + patchwork::plot_spacer())
ggsave(file.path(out_dir, "reduced_form_three_panel_top5_firms_distinct.pdf"), combined_plot_top5_firm, width = 12, height = 8)

combined_plot_top5_firm
```

```{r}
# regression table (Top5 sample with firm count)
tab_tex_top5_firm <- 
  etable(
    reg_table_top5_firm,
    se.below = TRUE,
    keep = "n_firms",
    digits = 3,
    tex = TRUE,
    fitstat = c("r2", "n")
  )

writeLines(
  tab_tex_top5_firm,
  con = file.path(
    here::here("draft/figuretable/descriptives/aggregate/cross_section"),
    "regress_top5ths_top5_firms.tex"
  )
)

tab_view_top5_firm <- etable(
  reg_table_top5_firm,
  se.below = TRUE,
  keep = "n_firms",
  digits = 3,
  tex = FALSE,
  fitstat = c("r2", "n")
)

knitr::kable(tab_view_top5_firm)
```


## top5+fringe with number of ths 

```{r}
# build establishment-count regression sample directly from data_base_all
panel_df_top5fringe <-
  data_base_all %>%
  dplyr::group_by(
    year,
    cz
  ) %>%
  dplyr::mutate(
    n_ths = dplyr::n()
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f   = log(f),
    ln_w   = log(w),
    ln_m   = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_ths),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  ) %>%
  dplyr::select(
    year,
    cz,
    n_ths,
    w,
    f,
    margin,
    ln_f,
    ln_w,
    ln_m
  )
summary(panel_df_top5fringe)
```

```{r}
# two-way FE regressions: log fee, log wage, log margin on number of establishments
reg_fee_est <- feols(ln_f ~ n_ths | cz + year, data = panel_df_top5fringe)
reg_w_est   <- feols(ln_w ~ n_ths | cz + year, data = panel_df_top5fringe)
reg_m_est   <- feols(ln_m ~ n_ths | cz + year, data = panel_df_top5fringe)

reg_table_est <-
  list(
    "Log fee"    = reg_fee_est,
    "Log wage"   = reg_w_est,
    "Log margin" = reg_m_est
  )
```

```{r fig.width=12, fig.height=8}
# scatter on raw scale + fitted line slope from FE model
plot_df_est <-
  make_binscatter_long(
    df = panel_df_top5fringe,
    x_var = "n_ths"
  )

p_breaks_est <- pretty(plot_df_est$n_ths, n = 5)

slope_fee_est <- unname(stats::coef(reg_fee_est)["n_ths"])
slope_wage_est <- unname(stats::coef(reg_w_est)["n_ths"])
slope_margin_est <- unname(stats::coef(reg_m_est)["n_ths"])

intercept_fee_est <- mean(panel_df_top5fringe$ln_f, na.rm = TRUE) - slope_fee_est * mean(panel_df_top5fringe$n_ths, na.rm = TRUE)
intercept_wage_est <- mean(panel_df_top5fringe$ln_w, na.rm = TRUE) - slope_wage_est * mean(panel_df_top5fringe$n_ths, na.rm = TRUE)
intercept_margin_est <- mean(panel_df_top5fringe$ln_m, na.rm = TRUE) - slope_margin_est * mean(panel_df_top5fringe$n_ths, na.rm = TRUE)

p_fee_est <-
  ggplot(
    dplyr::filter(plot_df_est, .data$var == "Log fee"),
    aes(x = .data$n_ths, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_fee_est,
    intercept = intercept_fee_est,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_est) +
  labs(
    x = "Number of establishments in commuting zone",
    y = "Log fee"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_wage_est <-
  ggplot(
    dplyr::filter(plot_df_est, .data$var == "Log wage"),
    aes(x = .data$n_ths, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_wage_est,
    intercept = intercept_wage_est,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_est) +
  labs(
    x = "Number of establishments in commuting zone",
    y = "Log wage"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_margin_est <-
  ggplot(
    dplyr::filter(plot_df_est, .data$var == "Log margin"),
    aes(x = .data$n_ths, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_margin_est,
    intercept = intercept_margin_est,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_est) +
  labs(
    x = "Number of establishments in commuting zone",
    y = "Log margin"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

combined_plot_est <- (p_fee_est + p_wage_est) / (p_margin_est + patchwork::plot_spacer())
ggsave(file.path(out_dir, "reduced_form_three_panel_top5_fringe_ths.pdf"), combined_plot_est, width = 12, height = 8)

combined_plot_est
```

```{r}
# regression table (establishment count)
tab_tex_est <- 
  etable(
    reg_table_est,
    se.below = TRUE,
    keep = "n_ths",
    digits = 3,
    tex = TRUE,
    fitstat = c("r2", "n")
  )

writeLines(
  tab_tex_est,
  con = file.path(
    here::here("draft/figuretable/descriptives/aggregate/cross_section"),
    "regress_top5fringe_establishments.tex"
  )
)

tab_view_est <- 
  etable(
    reg_table_est,
    se.below = TRUE,
    keep = "n_ths",
    digits = 3,
    tex = FALSE,
    fitstat = c("r2", "n")
  )

knitr::kable(tab_view_est)
```

## top5+fringe with number of distinct firm_id
```{r}
# build sample with distinct firm_id count in each cz-year
panel_df_top5fringe_firm <-
  data_base_all %>%
  dplyr::group_by(
    year,
    cz
  ) %>%
  dplyr::mutate(
    n_firms = dplyr::n_distinct(firm_id)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f   = log(f),
    ln_w   = log(w),
    ln_m   = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_firms),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  ) %>%
  dplyr::select(
    year,
    cz,
    n_firms,
    w,
    f,
    margin,
    ln_f,
    ln_w,
    ln_m
  )

summary(panel_df_top5fringe_firm)
```

```{r}
# two-way FE regressions: log fee, log wage, log margin on number of distinct firm_id
reg_fee_firm_distinct <- feols(ln_f ~ n_firms | cz + year, data = panel_df_top5fringe_firm)
reg_w_firm_distinct   <- feols(ln_w ~ n_firms | cz + year, data = panel_df_top5fringe_firm)
reg_m_firm_distinct   <- feols(ln_m ~ n_firms | cz + year, data = panel_df_top5fringe_firm)

reg_table_firm_distinct <-
  list(
    "Log fee"    = reg_fee_firm_distinct,
    "Log wage"   = reg_w_firm_distinct,
    "Log margin" = reg_m_firm_distinct
  )
```

```{r fig.width=12, fig.height=8}
# bin-scatter style plot with distinct firm_id count
plot_df_firm_distinct <-
  make_binscatter_long(
    df = panel_df_top5fringe_firm,
    x_var = "n_firms"
  )

p_breaks_firm_distinct <- pretty(plot_df_firm_distinct$n_firms, n = 5)

slope_fee_firm_distinct <- unname(stats::coef(reg_fee_firm_distinct)["n_firms"])
slope_wage_firm_distinct <- unname(stats::coef(reg_w_firm_distinct)["n_firms"])
slope_margin_firm_distinct <- unname(stats::coef(reg_m_firm_distinct)["n_firms"])

intercept_fee_firm_distinct <- mean(panel_df_top5fringe_firm$ln_f, na.rm = TRUE) - slope_fee_firm_distinct * mean(panel_df_top5fringe_firm$n_firms, na.rm = TRUE)
intercept_wage_firm_distinct <- mean(panel_df_top5fringe_firm$ln_w, na.rm = TRUE) - slope_wage_firm_distinct * mean(panel_df_top5fringe_firm$n_firms, na.rm = TRUE)
intercept_margin_firm_distinct <- mean(panel_df_top5fringe_firm$ln_m, na.rm = TRUE) - slope_margin_firm_distinct * mean(panel_df_top5fringe_firm$n_firms, na.rm = TRUE)

p_fee_firm_distinct <-
  ggplot(
    dplyr::filter(plot_df_firm_distinct, .data$var == "Log fee"),
    aes(x = .data$n_firms, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_fee_firm_distinct,
    intercept = intercept_fee_firm_distinct,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_firm_distinct) +
  labs(
    x = "Number of firms in commuting zone",
    y = "Log fee"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_wage_firm_distinct <-
  ggplot(
    dplyr::filter(plot_df_firm_distinct, .data$var == "Log wage"),
    aes(x = .data$n_firms, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_wage_firm_distinct,
    intercept = intercept_wage_firm_distinct,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_firm_distinct) +
  labs(
    x = "Number of firms in commuting zone",
    y = "Log wage"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_margin_firm_distinct <-
  ggplot(
    dplyr::filter(plot_df_firm_distinct, .data$var == "Log margin"),
    aes(x = .data$n_firms, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_margin_firm_distinct,
    intercept = intercept_margin_firm_distinct,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_firm_distinct) +
  labs(
    x = "Number of firms in commuting zone",
    y = "Log margin"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

combined_plot_firm_distinct <- (p_fee_firm_distinct + p_wage_firm_distinct) / (p_margin_firm_distinct + patchwork::plot_spacer())
ggsave(file.path(out_dir, "reduced_form_three_panel_top5_fringe_firms_distinct.pdf"), combined_plot_firm_distinct, width = 12, height = 8)

combined_plot_firm_distinct
```

```{r}
# regression table (distinct firm_id count)
tab_tex_firm_distinct <- 
  etable(
    reg_table_firm_distinct,
    se.below = TRUE,
    keep = "n_firms",
    digits = 3,
    tex = TRUE,
    fitstat = c("r2", "n")
  )

writeLines(
  tab_tex_firm_distinct,
  con = file.path(
    here::here("draft/figuretable/descriptives/aggregate/cross_section"),
    "regress_top5fringe_firms_distinct.tex"
  )
)

tab_view_firm_distinct <- etable(
  reg_table_firm_distinct,
  se.below = TRUE,
  keep = "n_firms",
  digits = 3,
  tex = FALSE,
  fitstat = c("r2", "n")
)

knitr::kable(tab_view_firm_distinct)
```

```{r}
# rebuild analysis samples used across sections
panel_df_top5_ths_all <-
  data_base_top5 %>%
  dplyr::group_by(year, cz) %>%
  dplyr::mutate(
    n_ths = dplyr::n(),
    n_firms = dplyr::n_distinct(firm_id)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f = log(f),
    ln_w = log(w),
    ln_m = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_ths),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  )

panel_df_top5_firms_all <-
  panel_df_top5_ths_all %>%
  dplyr::filter(is.finite(n_firms))

panel_df_top5_fringe_ths_all <-
  data_base_all %>%
  dplyr::group_by(year, cz) %>%
  dplyr::mutate(
    n_ths = dplyr::n()
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f = log(f),
    ln_w = log(w),
    ln_m = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_ths),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  )

panel_df_top5_fringe_firms_all <-
  data_base_all %>%
  dplyr::group_by(year, cz) %>%
  dplyr::mutate(
    n_firms = dplyr::n_distinct(firm_id)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f = log(f),
    ln_w = log(w),
    ln_m = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_firms),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  )

panel_df_establishment_ths_all <-
  data_base %>%
  dplyr::group_by(year, cz) %>%
  dplyr::mutate(
    n_ths = dplyr::n() / 10000
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f = log(f),
    ln_w = log(w),
    ln_m = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_ths),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  )

panel_df_establishment_firms_all <-
  data_base %>%
  dplyr::group_by(year, cz) %>%
  dplyr::mutate(
    n_firms = dplyr::n_distinct(firm_id) / 10000
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f = log(f),
    ln_w = log(w),
    ln_m = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_firms),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  )
```

## cz-year-establishment data with number of ths 

```{r}
# build establishment-count regression sample directly from data_base_all
panel_df_est <-
  data_base %>%
  dplyr::group_by(
    year,
    cz
  ) %>%
  dplyr::mutate(
    n_ths = dplyr::n()/10000
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f   = log(f),
    ln_w   = log(w),
    ln_m   = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_ths),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  ) %>%
  dplyr::select(
    year,
    cz,
    n_ths,
    w,
    f,
    margin,
    ln_f,
    ln_w,
    ln_m
  )
summary(panel_df_est)
```

```{r}
# two-way FE regressions: log fee, log wage, log margin on number of establishments
reg_fee_est <- feols(ln_f ~ n_ths | cz + year, data = panel_df_est)
reg_w_est   <- feols(ln_w ~ n_ths | cz + year, data = panel_df_est)
reg_m_est   <- feols(ln_m ~ n_ths | cz + year, data = panel_df_est)

reg_table_est <-
  list(
    "Log fee"    = reg_fee_est,
    "Log wage"   = reg_w_est,
    "Log margin" = reg_m_est
  )
```

```{r fig.width=12, fig.height=8}
# scatter on raw scale + fitted line slope from FE model
plot_df_est <-
  make_binscatter_long(
    df = panel_df_est,
    x_var = "n_ths"
  )

p_breaks_est <- pretty(plot_df_est$n_ths, n = 5)

slope_fee_est <- unname(stats::coef(reg_fee_est)["n_ths"])
slope_wage_est <- unname(stats::coef(reg_w_est)["n_ths"])
slope_margin_est <- unname(stats::coef(reg_m_est)["n_ths"])

intercept_fee_est <- mean(panel_df_est$ln_f, na.rm = TRUE) - slope_fee_est * mean(panel_df_est$n_ths, na.rm = TRUE)
intercept_wage_est <- mean(panel_df_est$ln_w, na.rm = TRUE) - slope_wage_est * mean(panel_df_est$n_ths, na.rm = TRUE)
intercept_margin_est <- mean(panel_df_est$ln_m, na.rm = TRUE) - slope_margin_est * mean(panel_df_est$n_ths, na.rm = TRUE)

p_fee_est <-
  ggplot(
    dplyr::filter(plot_df_est, .data$var == "Log fee"),
    aes(x = .data$n_ths, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_fee_est,
    intercept = intercept_fee_est,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_est) +
  labs(
    x = "Number of establishments in commuting zone",
    y = "Log fee"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_wage_est <-
  ggplot(
    dplyr::filter(plot_df_est, .data$var == "Log wage"),
    aes(x = .data$n_ths, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_wage_est,
    intercept = intercept_wage_est,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_est) +
  labs(
    x = "Number of establishments in commuting zone",
    y = "Log wage"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_margin_est <-
  ggplot(
    dplyr::filter(plot_df_est, .data$var == "Log margin"),
    aes(x = .data$n_ths, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_margin_est,
    intercept = intercept_margin_est,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_est) +
  labs(
    x = "Number of establishments in commuting zone",
    y = "Log margin"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

combined_plot_est <- (p_fee_est + p_wage_est) / (p_margin_est + patchwork::plot_spacer())
ggsave(file.path(out_dir, "reduced_form_three_panel_establishments_ths.pdf"), combined_plot_est, width = 12, height = 8)

combined_plot_est
```

```{r}
# regression table (establishment count)
tab_tex_est <- etable(
  reg_table_est,
  se.below = TRUE,
  keep = "n_ths",
  digits = 3,
  tex = TRUE,
  fitstat = c("r2", "n")
)

writeLines(
  tab_tex_est,
  con = file.path(
    here::here("draft/figuretable/descriptives/aggregate/cross_section"),
    "regress_allths_establishments.tex"
  )
)

tab_view_est <- etable(
  reg_table_est,
  se.below = TRUE,
  keep = "n_ths",
  digits = 3,
  tex = FALSE,
  fitstat = c("r2", "n")
)

knitr::kable(tab_view_est)
```

## cz_year_establishment with number of distinct firm_id
```{r}
# build sample with distinct firm_id count in each cz-year
panel_df_est_firm_distinct <-
  data_base %>%
  dplyr::group_by(
    year,
    cz
  ) %>%
  dplyr::mutate(
    n_firms = dplyr::n_distinct(firm_id)/10000
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f   = log(f),
    ln_w   = log(w),
    ln_m   = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(n_firms),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  ) %>%
  dplyr::select(
    year,
    cz,
    n_firms,
    w,
    f,
    margin,
    ln_f,
    ln_w,
    ln_m
  )

summary(panel_df_est_firm_distinct)
```

```{r}
# two-way FE regressions: log fee, log wage, log margin on number of distinct firm_id
reg_fee_firm_distinct <- feols(ln_f ~ n_firms | cz + year, data = panel_df_est_firm_distinct)
reg_w_firm_distinct   <- feols(ln_w ~ n_firms | cz + year, data = panel_df_est_firm_distinct)
reg_m_firm_distinct   <- feols(ln_m ~ n_firms | cz + year, data = panel_df_est_firm_distinct)

reg_table_firm_distinct <-
  list(
    "Log fee"    = reg_fee_firm_distinct,
    "Log wage"   = reg_w_firm_distinct,
    "Log margin" = reg_m_firm_distinct
  )
```

```{r fig.width=12, fig.height=8}
# bin-scatter style plot with distinct firm_id count
plot_df_firm_distinct <-
  make_binscatter_long(
    df = panel_df_est_firm_distinct,
    x_var = "n_firms"
  )

p_breaks_firm_distinct <- pretty(plot_df_firm_distinct$n_firms, n = 5)

slope_fee_firm_distinct <- unname(stats::coef(reg_fee_firm_distinct)["n_firms"])
slope_wage_firm_distinct <- unname(stats::coef(reg_w_firm_distinct)["n_firms"])
slope_margin_firm_distinct <- unname(stats::coef(reg_m_firm_distinct)["n_firms"])

intercept_fee_firm_distinct <- mean(panel_df_est_firm_distinct$ln_f, na.rm = TRUE) - slope_fee_firm_distinct * mean(panel_df_est_firm_distinct$n_firms, na.rm = TRUE)
intercept_wage_firm_distinct <- mean(panel_df_est_firm_distinct$ln_w, na.rm = TRUE) - slope_wage_firm_distinct * mean(panel_df_est_firm_distinct$n_firms, na.rm = TRUE)
intercept_margin_firm_distinct <- mean(panel_df_est_firm_distinct$ln_m, na.rm = TRUE) - slope_margin_firm_distinct * mean(panel_df_est_firm_distinct$n_firms, na.rm = TRUE)

p_fee_firm_distinct <-
  ggplot(
    dplyr::filter(plot_df_firm_distinct, .data$var == "Log fee"),
    aes(x = .data$n_firms, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_fee_firm_distinct,
    intercept = intercept_fee_firm_distinct,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_firm_distinct) +
  labs(
    x = "Number of firms in commuting zone",
    y = "Log fee"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_wage_firm_distinct <-
  ggplot(
    dplyr::filter(plot_df_firm_distinct, .data$var == "Log wage"),
    aes(x = .data$n_firms, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_wage_firm_distinct,
    intercept = intercept_wage_firm_distinct,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_firm_distinct) +
  labs(
    x = "Number of firms in commuting zone",
    y = "Log wage"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

p_margin_firm_distinct <-
  ggplot(
    dplyr::filter(plot_df_firm_distinct, .data$var == "Log margin"),
    aes(x = .data$n_firms, y = .data$value)
  ) +
  geom_point(alpha = 0.95, size = 2, color = "#1f4e79") +
  geom_abline(
    slope = slope_margin_firm_distinct,
    intercept = intercept_margin_firm_distinct,
    color = "#7f4f5f"
  ) +
  scale_x_continuous(breaks = p_breaks_firm_distinct) +
  labs(
    x = "Number of firms in commuting zone",
    y = "Log margin"
  ) +
  theme_classic(base_size = 11) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

combined_plot_firm_distinct <- (p_fee_firm_distinct + p_wage_firm_distinct) / (p_margin_firm_distinct + patchwork::plot_spacer())
ggsave(file.path(out_dir, "reduced_form_three_panel_establishments_firms_distinct.pdf"), combined_plot_firm_distinct, width = 12, height = 8)

combined_plot_firm_distinct
```

```{r}
# regression table (distinct firm_id count)
tab_tex_firm_distinct <- 
  etable(
    reg_table_firm_distinct,
    se.below = TRUE,
    keep = "n_firms",
    digits = 3,
    tex = TRUE,
    fitstat = c("r2", "n")
  )

writeLines(
  tab_tex_firm_distinct,
  con = file.path(
    here::here("draft/figuretable/descriptives/aggregate/cross_section"),
    "regress_allths_firms_distinct.tex"
  )
)

tab_view_firm_distinct <- etable(
  reg_table_firm_distinct,
  se.below = TRUE,
  keep = "n_firms",
  digits = 3,
  tex = FALSE,
  fitstat = c("r2", "n")
)

knitr::kable(tab_view_firm_distinct)
```

# summary of results
## combined table: FE (number of THS and number of firms)
```{r}
reg_all_fe <-
  list(
    "Top5 fee (n_ths)" = feols(ln_f ~ n_ths | cz + year, data = panel_df_top5),
    "Top5 wage (n_ths)" = feols(ln_w ~ n_ths | cz + year, data = panel_df_top5),
    "Top5 margin (n_ths)" = feols(ln_m ~ n_ths | cz + year, data = panel_df_top5),
    "Top5+fringe fee (n_ths)" = feols(ln_f ~ n_ths | cz + year, data = panel_df_top5fringe),
    "Top5+fringe wage (n_ths)" = feols(ln_w ~ n_ths | cz + year, data = panel_df_top5fringe),
    "Top5+fringe margin (n_ths)" = feols(ln_m ~ n_ths | cz + year, data = panel_df_top5fringe),
    "Establishment fee (n_ths)" = feols(ln_f ~ n_ths | cz + year, data = panel_df_est),
    "Establishment wage (n_ths)" = feols(ln_w ~ n_ths | cz + year, data = panel_df_est),
    "Establishment margin (n_ths)" = feols(ln_m ~ n_ths | cz + year, data = panel_df_est),
    "Top5 fee (n_firms)" = feols(ln_f ~ n_firms | cz + year, data = panel_df_top5_firm),
    "Top5 wage (n_firms)" = feols(ln_w ~ n_firms | cz + year, data = panel_df_top5_firm),
    "Top5 margin (n_firms)" = feols(ln_m ~ n_firms | cz + year, data = panel_df_top5_firm),
    "Top5+fringe fee (n_firms)" = feols(ln_f ~ n_firms | cz + year, data = panel_df_top5fringe_firm),
    "Top5+fringe wage (n_firms)" = feols(ln_w ~ n_firms | cz + year, data = panel_df_top5fringe_firm),
    "Top5+fringe margin (n_firms)" = feols(ln_m ~ n_firms | cz + year, data = panel_df_top5fringe_firm),
    "Establishment fee (n_firms)" = feols(ln_f ~ n_firms | cz + year, data = panel_df_est_firm_distinct),
    "Establishment wage (n_firms)" = feols(ln_w ~ n_firms | cz + year, data = panel_df_est_firm_distinct),
    "Establishment margin (n_firms)" = feols(ln_m ~ n_firms | cz + year, data = panel_df_est_firm_distinct)
  )

tab_all_fe <-
  etable(
    reg_all_fe,
    se.below = TRUE,
    digits = 3,
    tex = FALSE,
    fitstat = c("r2", "n")
  )

knitr::kable(tab_all_fe, caption = "Combined FE regressions: number of THS and number of firms")
```

## combined table: OLS (number of THS and number of firms)
```{r}
reg_all_ols_ths <-
  list(
    "Top5 fee (n_ths)" = feols(ln_f ~ n_ths, data = panel_df_top5),
    "Top5 wage (n_ths)" = feols(ln_w ~ n_ths, data = panel_df_top5),
    "Top5 margin (n_ths)" = feols(ln_m ~ n_ths, data = panel_df_top5),
    "Top5+fringe fee (n_ths)" = feols(ln_f ~ n_ths, data = panel_df_top5fringe),
    "Top5+fringe wage (n_ths)" = feols(ln_w ~ n_ths, data = panel_df_top5fringe),
    "Top5+fringe margin (n_ths)" = feols(ln_m ~ n_ths, data = panel_df_top5fringe),
    "Establishment fee (n_ths)" = feols(ln_f ~ n_ths, data = panel_df_est),
    "Establishment wage (n_ths)" = feols(ln_w ~ n_ths, data = panel_df_est),
    "Establishment margin (n_ths)" = feols(ln_m ~ n_ths, data = panel_df_est)
  )

tab_tex_all_ols_ths <-
  etable(
    reg_all_ols_ths,
    keep = c("n_ths", "(Intercept)"),
    order = c("n_ths", "(Intercept)"),
    dict = c("(Intercept)" = "Constant"),
    se.below = TRUE,
    digits = 3,
    tex = TRUE,
    fitstat = c("r2", "n")
  )

writeLines(
  tab_tex_all_ols_ths,
  con = file.path(
    here::here("draft/figuretable/descriptives/aggregate/cross_section"),
    "regress_all_ols_ths.tex"
  )
)

tab_view_all_ols_ths <-
  etable(
    reg_all_ols_ths,
    keep = c("n_ths", "(Intercept)"),
    order = c("n_ths", "(Intercept)"),
    dict = c("(Intercept)" = "Constant"),
    se.below = TRUE,
    digits = 3,
    tex = FALSE,
    fitstat = c("r2", "n")
  )

knitr::kable(tab_view_all_ols_ths, caption = "Combined OLS regressions: number of THS")

reg_all_ols_firms <-
  list(
    "Top5 fee (n_firms)" = feols(ln_f ~ n_firms, data = panel_df_top5_firm),
    "Top5 wage (n_firms)" = feols(ln_w ~ n_firms, data = panel_df_top5_firm),
    "Top5 margin (n_firms)" = feols(ln_m ~ n_firms, data = panel_df_top5_firm),
    "Top5+fringe fee (n_firms)" = feols(ln_f ~ n_firms, data = panel_df_top5fringe_firm),
    "Top5+fringe wage (n_firms)" = feols(ln_w ~ n_firms, data = panel_df_top5fringe_firm),
    "Top5+fringe margin (n_firms)" = feols(ln_m ~ n_firms, data = panel_df_top5fringe_firm),
    "Establishment fee (n_firms)" = feols(ln_f ~ n_firms, data = panel_df_est_firm_distinct),
    "Establishment wage (n_firms)" = feols(ln_w ~ n_firms, data = panel_df_est_firm_distinct),
    "Establishment margin (n_firms)" = feols(ln_m ~ n_firms, data = panel_df_est_firm_distinct)
  )

tab_tex_all_ols_firms <-
  etable(
    reg_all_ols_firms,
    keep = c("n_firms", "(Intercept)"),
    order = c("n_firms", "(Intercept)"),
    dict = c("(Intercept)" = "Constant"),
    se.below = TRUE,
    digits = 3,
    tex = TRUE,
    fitstat = c("r2", "n")
  )

writeLines(
  tab_tex_all_ols_firms,
  con = file.path(
    here::here("draft/figuretable/descriptives/aggregate/cross_section"),
    "regress_all_ols_firms.tex"
  )
)

tab_view_all_ols_firms <-
  etable(
    reg_all_ols_firms,
    keep = c("n_firms", "(Intercept)"),
    order = c("n_firms", "(Intercept)"),
    dict = c("(Intercept)" = "Constant"),
    se.below = TRUE,
    digits = 3,
    tex = FALSE,
    fitstat = c("r2", "n")
  )

knitr::kable(tab_view_all_ols_firms, caption = "Combined OLS regressions: number of firms")
```


## top5 dependent only with top5+fringe explanatory variables (same FE setting)
```{r}
panel_df_top5_dep_top5fringe_x <-
  data_base_top5 %>%
  dplyr::mutate(
    margin = (f - w) / f,
    ln_f = log(f),
    ln_w = log(w),
    ln_m = log(margin)
  ) %>%
  dplyr::filter(
    is.finite(cz),
    is.finite(year),
    is.finite(ln_f),
    is.finite(ln_w),
    is.finite(ln_m)
  ) %>%
  dplyr::select(
    year,
    cz,
    firm_id,
    ln_f,
    ln_w,
    ln_m
  )

market_size_top5fringe_setting <-
  data_base_all %>%
  dplyr::group_by(
    year,
    cz
  ) %>%
  dplyr::summarise(
    n_ths = dplyr::n(),
    n_firms = dplyr::n_distinct(firm_id),
    .groups = "drop"
  )

panel_df_top5_dep_top5fringe_x <-
  panel_df_top5_dep_top5fringe_x %>%
  dplyr::left_join(
    market_size_top5fringe_setting,
    by = c("year", "cz")
  ) %>%
  dplyr::filter(
    is.finite(n_ths),
    is.finite(n_firms)
  )

reg_top5_dep_top5fringe_x <-
  list(
    "Top5 dep: fee (n_ths)" = feols(ln_f ~ n_ths | cz + year, data = panel_df_top5_dep_top5fringe_x),
    "Top5 dep: wage (n_ths)" = feols(ln_w ~ n_ths | cz + year, data = panel_df_top5_dep_top5fringe_x),
    "Top5 dep: margin (n_ths)" = feols(ln_m ~ n_ths | cz + year, data = panel_df_top5_dep_top5fringe_x),
    "Top5 dep: fee (n_firms)" = feols(ln_f ~ n_firms | cz + year, data = panel_df_top5_dep_top5fringe_x),
    "Top5 dep: wage (n_firms)" = feols(ln_w ~ n_firms | cz + year, data = panel_df_top5_dep_top5fringe_x),
    "Top5 dep: margin (n_firms)" = feols(ln_m ~ n_firms | cz + year, data = panel_df_top5_dep_top5fringe_x)
  )

tab_tex_top5_dep_top5fringe_x <-
  etable(
    reg_top5_dep_top5fringe_x,
    keep = c("n_ths", "n_firms"),
    order = c("n_ths", "n_firms"),
    se.below = TRUE,
    digits = 3,
    tex = TRUE,
    fitstat = c("r2", "n"),
    vcov = ~cz
  )

writeLines(
  tab_tex_top5_dep_top5fringe_x,
  con = file.path(
    here::here("draft/figuretable/descriptives/aggregate/cross_section"),
    "regress_top5_dep_top5fringe_x_fe.tex"
  )
)

tab_view_top5_dep_top5fringe_x <-
  etable(
    reg_top5_dep_top5fringe_x,
    keep = c("n_ths", "n_firms"),
    order = c("n_ths", "n_firms"),
    se.below = TRUE,
    digits = 3,
    tex = FALSE,
    fitstat = c("r2", "n"),
    vcov = ~cz
  )

knitr::kable(
  tab_view_top5_dep_top5fringe_x,
  caption = "Top5 dependent only with Top5+fringe explanatory variables (FE, clustered by cz)"
)
```

## replication and modified specification (drop tokutei in dependent variables only)
```{r}
build_reduced_form_sample <- function(drop_tokutei_dep = FALSE) {
  data_est <- haven::read_dta(here::here("cleaned/data_establishments.dta"))
  data_zip <- haven::read_dta(here::here("cleaned/data_zipcode.dta"))
  data_area <- haven::read_dta(here::here("cleaned/data_area.dta"))
  data_mw <- haven::read_dta(here::here("cleaned/data_pref_year_minimum_wage.dta"))
  data_pw <- haven::read_dta(here::here("cleaned/data_pref_year_partwage.dta"))
  data_year_dta <- haven::read_dta(here::here("cleaned/data_year.dta"))

  df_full <- data_est %>%
    dplyr::inner_join(data_zip, by = "zipcode") %>%
    dplyr::inner_join(data_area, by = "area_code") %>%
    dplyr::inner_join(data_mw, by = c("pref", "year")) %>%
    dplyr::inner_join(data_pw, by = c("pref", "year")) %>%
    dplyr::inner_join(data_year_dta, by = "year") %>%
    dplyr::mutate(
      temptot = tempperm + tempfixed,
      n_cz = sum(!is.na(temptot)),
      .by = c(year, cz)
    ) %>%
    dplyr::mutate(
      n_cz_10000 = n_cz / 10000,
      staffperm = perm - tempperm,
      stafffixed = fixed - tempfixed,
      margin = (fee - wage) / fee,
      margindaily = (feedaily - wagedaily) / feedaily,
      lfee = log(fee),
      lwage = log(wage),
      lfee_wage = lfee - lwage
    ) %>%
    dplyr::mutate(
      staffperm = dplyr::if_else(staffperm < 0, NA_real_, staffperm),
      stafffixed = dplyr::if_else(stafffixed < 0, NA_real_, stafffixed),
      margin = dplyr::if_else(margin < 0, NA_real_, margin),
      margindaily = dplyr::if_else(margindaily < 0, NA_real_, margindaily)
    )

  df <- df_full %>%
    dplyr::filter(
      year != 2015,
      temptot > 5,
      !is.na(staffperm),
      !is.na(stafffixed),
      !is.na(wage),
      !is.na(fee),
      wage <= fee,
      !((!is.na(wagedaily) & is.na(feedaily)) | (is.na(wagedaily) & !is.na(feedaily))),
      is.na(wagedaily) | is.na(feedaily) | wagedaily <= feedaily
    )

  if (drop_tokutei_dep) {
    df <- dplyr::filter(df, tokutei == 0)
  }

  df
}

estimate_three_outcomes <- function(df) {
  m_fee <- fixest::feols(lfee ~ n_cz_10000 | cz + year, data = df, vcov = ~cz)
  m_wage <- fixest::feols(lwage ~ n_cz_10000 | cz + year, data = df, vcov = ~cz)
  m_margin <- fixest::feols(lfee_wage ~ n_cz_10000 | cz + year, data = df, vcov = ~cz)

  extract <- function(model, outcome_name) {
    tibble::tibble(
      outcome = outcome_name,
      beta = unname(stats::coef(model)["n_cz_10000"]),
      se = unname(fixest::se(model)["n_cz_10000"]),
      n = as.numeric(stats::nobs(model))
    )
  }

  dplyr::bind_rows(
    extract(m_fee, "lfee"),
    extract(m_wage, "lwage"),
    extract(m_margin, "lfee_wage")
  )
}

result_baseline <- estimate_three_outcomes(build_reduced_form_sample(drop_tokutei_dep = FALSE)) %>%
  dplyr::rename(
    beta_baseline = beta,
    se_baseline = se,
    n_baseline = n
  )

result_drop_tokutei_dep <- estimate_three_outcomes(build_reduced_form_sample(drop_tokutei_dep = TRUE)) %>%
  dplyr::rename(
    beta_drop_tokutei_dep = beta,
    se_drop_tokutei_dep = se,
    n_drop_tokutei_dep = n
  )

comparison_tbl <- result_baseline %>%
  dplyr::left_join(result_drop_tokutei_dep, by = "outcome") %>%
  dplyr::mutate(
    delta_beta = beta_drop_tokutei_dep - beta_baseline
  )

comparison_display <- comparison_tbl %>%
  dplyr::mutate(
    dplyr::across(
      c(beta_baseline, se_baseline, beta_drop_tokutei_dep, se_drop_tokutei_dep, delta_beta),
      ~ round(., 6)
    )
  )

knitr::kable(
  comparison_display,
  caption = "Replication baseline vs drop tokutei in dependent variables only (n_cz_10000 counts all establishments)"
)

comparison_tex <- comparison_display %>%
  knitr::kable(
    format = "latex",
    booktabs = TRUE,
    caption = "Replication baseline vs drop tokutei in dependent variables only"
  )

writeLines(
  comparison_tex,
  con = here::here("draft/figuretable/descriptives/aggregate/cross_section/regress_replication_vs_drop_tokutei_dep.tex")
)
```

