---
title: "report data analysis (first order difference)"
author: "Chiho Taniguchi"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 3, fig.width = 4)

library("magrittr")
library("kableExtra")
library("ggplot2")

height <- 6
width <- 8

```

```{r }

 data_establishments <- 
  here::here(file = "cleaned/data_establishments.rds") %>% 
  readRDS()

 data_zipcode <- 
   here::here(file = "cleaned/data_zipcode.rds") %>% 
   readRDS()
 
 data_area <- 
   here::here(file = "cleaned/data_area.rds") %>% 
   readRDS()
 
 data_zip_establishments <- 
   here::here(file = "output/data_zip_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments <- 
   here::here(file = "output/data_cz_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann <- 
   here::here(file = "output/data_cz_establishments_all_ippann.rds") %>% 
   readRDS()
 
 data_zip_establishments_all_ippann <- 
   here::here(file = "output/data_zip_establishments_all_ippann.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann_unique <- 
   here::here(file = "output/data_cz_establishments_all_ippann_unique.rds") %>% 
   readRDS()
 
 data_zip_establishments_all_ippann_unique <- 
   here::here(file = "output/data_zip_establishments_all_ippann_unique.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann_unique_wage <- 
   here::here(file = "output/data_cz_establishments_all_ippann_unique_wage.rds") %>% 
   readRDS()
 
 data_zip_establishments_all_ippann_unique_wage <- 
   here::here(file = "output/data_zip_establishments_all_ippann_unique_wage.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann_unique_fee <- 
   here::here(file = "output/data_cz_establishments_all_ippann_unique_fee.rds") %>%
   readRDS()
 
 data_zip_establishments_all_ippann_unique_fee <- 
   here::here(file = "output/data_zip_establishments_all_ippann_unique_fee.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann_unique_weights <- 
   here::here(file = "output/data_cz_establishments_all_ippann_unique_weights.rds") %>%
   readRDS()
 
 data_zip_establishments_all_ippann_unique_weights <- 
   here::here(file = "output/data_zip_establishments_all_ippann_unique_weights.rds") %>% 
   readRDS()
 

```

# cz data

## First stage (cz) {.tabset}
Regress the growth rate of the number of general establishments between 2014 and 2010 (N_growth) on the percentage of tokutei establishments at the initial period(share_cz_2010). "N_growth" is defined as (N_j2014 - N_j2010) / N_j2010.

### N_growth

N_growth = (N_j2014 - N_j2010) / N_j2010

```{r}

results_diff_cz_a <- list()

 results_diff_cz_a[[1]] <- 
   estimatr::lm_robust(
     formula = N_growth ~ share_cz_2010,
     data = data_cz_establishments_all_ippann_unique,
     se_type = "stata"
   )
   
 result_diffcza <- 
   list(
     "N_growth" = results_diff_cz_a[[1]]
   )
 
 modelsummary::modelsummary(
   result_diffcza,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

### N_growth (weighted)

(weighted by the number of general establishments in 2010)

```{r}

results_diff_cz_w <- list()

results_diff_cz_w[[1]] <- 
  estimatr::lm_robust(
    formula = N_growth ~  share_cz_2010,
    data = data_cz_establishments_all_ippann_unique,
    weights = weights,
    se_type = "stata"
  )

result_diffczw <- 
  list(
    "N_growth(weighted)" = results_diff_cz_w[[1]]
  )

modelsummary::modelsummary(
  result_diffczw,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```


### Plot for first stage

"estab." represents establishments. y represents the growth rate "(#general establishments in 2014 - #general establishments in 2010) / (#general establishments in 2010)".

```{r}

id_1 <- c(1:198)

data_cz_establishments_all_ippann_share <-
   data_cz_establishments_all_ippann_unique %>% 
   dplyr::select(
     cz,
     share_cz_2010,
     N_growth
   ) %>% 
   unique() %>% 
  dplyr::arrange(
    cz
  ) 

data_cz_establishments_all_ippann_share <-
  cbind(
    id_1,
    data_cz_establishments_all_ippann_share
  )
 
data_cz_establishments_all_ippann_share <-
  data_cz_establishments_all_ippann_share %>% 
  dplyr::mutate(
    cz_bin = cut(id_1, 
                 breaks = 50)
  ) %>% 
  dplyr::group_by(
    cz_bin
  ) %>% 
  dplyr::mutate(
    N_growth_avr = mean(N_growth),
    share_cz_2010_avr = mean(share_cz_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_cz_establishments_all_ippann_share_avr <- 
   data_cz_establishments_all_ippann_share %>% 
   dplyr::select(
     share_cz_2010_avr,
     N_growth_avr
   ) %>% 
   dplyr::distinct()
   

 g13 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_share,
     mapping = aes(x = share_cz_2010, y = N_growth),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("y") 
 
 print(g13)
 
 
```

### binscatter plot for first stage 

```{r}

 g23 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_share_avr,
     mapping = aes(x = share_cz_2010_avr, y = N_growth_avr),
     size = 0.3
   ) +
   stat_smooth(
   method = "lm",
   data = data_cz_establishments_all_ippann_share_avr,
   mapping = aes(x = share_cz_2010_avr, y = N_growth_avr),
    se = FALSE,
    size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("y") 
 
 print(g23)
 
 
```

## Reduced form (cz){.tabset}

Regress wage growth rate between 2014 and 2010 (wage_growth_14_10 = (wage_2014-wage_2010)/wage_2010) on the percentage of tokutei establishments at the initial period(share_cz_2010).

### wage (wage_growth_14_10)

wage_growth_14_10 = (wage_2014-wage_2010)/wage_2010

```{r}

### wage

results_growth_cza <- list()

results_growth_cza[[1]] <- 
  estimatr::lm_robust(
    formula = wage_growth_14_10 ~  share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_wage,
    se_type = "stata"
    )

result_growthcza <- 
  list(
    "wage_growth_14_10" = results_growth_cza[[1]]
  )

modelsummary::modelsummary(
  result_growthcza,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```


### wage(weighted / wage_growth_14_10)

```{r}

### wage

results_growth_cz_wa <- list()

results_growth_cz_wa[[1]] <- 
  estimatr::lm_robust(
    formula = wage_growth_14_10 ~  share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_wage,
    weights = weights,
    se_type = "stata"
     )

result_growthczwa <- 
  list(
    "wage_growth_14_10(weighted)" = results_growth_cz_wa[[1]]
  )

modelsummary::modelsummary(
  result_growthczwa,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### Plot for reduced form (wage)

```{r}

id_2 <- c(1:198)

data_cz_establishments_all_ippann_wage <-
   data_cz_establishments_all_ippann_unique_wage %>% 
   dplyr::select(
     cz,
     share_cz_2010,
     wage_growth_14_10
   ) %>% 
   unique() %>% 
  dplyr::arrange(
    cz
  ) 
 
data_cz_establishments_all_ippann_wage <-
  data_cz_establishments_all_ippann_wage %>% 
  dplyr::mutate(
    cz_bin = cut(id_2, 
                 breaks = 30)
  ) %>% 
  dplyr::group_by(
    cz_bin
  ) %>% 
  dplyr::mutate(
    wage_growth_14_10_avr = mean(wage_growth_14_10),
    share_cz_2010_med = median(share_cz_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_cz_establishments_all_ippann_wage_avr <- 
   data_cz_establishments_all_ippann_wage %>% 
   dplyr::select(
     share_cz_2010_med,
     wage_growth_14_10_avr
   ) %>% 
   dplyr::distinct()
   
 

 g14 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_wage,
     mapping = aes(x = share_cz_2010, y = wage_growth_14_10),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("growth rate (wage)") 
 
 print(g14)

```

### binscatter plot for reduced form (wage)

```{r}

 g24 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_wage_avr,
     mapping = aes(x = share_cz_2010_med, y = wage_growth_14_10_avr),
     size = 0.5
   ) +
   stat_smooth(
     data = data_cz_establishments_all_ippann_wage_avr,
     method = "lm",
     mapping = aes(x = share_cz_2010_med, y = wage_growth_14_10_avr),
     se = FALSE,
     size = 0.5
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("growth rate (wage)")
 
 print(g24)

```

### fee (fee_growth_14_10)

```{r}

### fee

results_feegrowth_cza <- list()

results_feegrowth_cza[[1]] <- 
  estimatr::lm_robust(
    formula = fee_growth_14_10 ~  share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_fee,
    se_type = "stata"
     )


result_feegrowthcza <- 
  list(
    "fee_growth_14_10" = results_feegrowth_cza[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthcza,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```



### fee(fee_growth_14_10 / weighted)

```{r}

### fee

results_feegrowth_cz_wa <- list()

results_feegrowth_cz_wa[[1]] <- 
  estimatr::lm_robust(
    formula = fee_growth_14_10 ~  share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_fee,
    weights = weights,
    se_type = "stata"
    )


result_feegrowthczwa <- 
  list(
    "fee_growth_14_10(weighted)" = results_feegrowth_cz_wa[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthczwa,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```


### Plot for reduced form (fee)

```{r}

id_3 <- c(1:220)

data_cz_establishments_all_ippann_fee <-
   data_cz_establishments_all_ippann %>% 
   dplyr::select(
     cz,
     share_cz_2010,
     fee_growth_14_10
   ) %>% 
   unique() %>% 
  dplyr::arrange(
    cz
  ) 
 
data_cz_establishments_all_ippann_fee <-
  data_cz_establishments_all_ippann_fee %>% 
  dplyr::mutate(
    cz_bin = cut(id_3, 
                 breaks = 50)
  ) %>% 
  dplyr::group_by(
    cz_bin
  ) %>% 
  dplyr::mutate(
    fee_growth_14_10_avr = mean(fee_growth_14_10),
    share_cz_2010_med = median(share_cz_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_cz_establishments_all_ippann_fee_avr <- 
   data_cz_establishments_all_ippann_fee %>% 
   dplyr::select(
     share_cz_2010_med,
     fee_growth_14_10_avr
   ) %>% 
   dplyr::distinct()
   
 

 g15 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_fee,
     mapping = aes(x = share_cz_2010, y = fee_growth_14_10),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("growth rate (fee)")
 
 print(g15)


```

### binscatter plot for reduced form (fee)

```{r}

 g25 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_fee_avr,
     mapping = aes(x = share_cz_2010_med, y = fee_growth_14_10_avr),
     size = 0.5
   ) +
   stat_smooth(
     method = "lm",
     data = data_cz_establishments_all_ippann_fee_avr,
     mapping = aes(x = share_cz_2010_med, y = fee_growth_14_10_avr),
     se = FALSE,
     size = 0.5
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("growth rate (fee)")
 
 print(g25)


```

## Structural form (cz){.tabset}

Regress the wage growth rate between 2014 and 2010 on the growth rate of the number of general establishments between 2014 and 2010 (N_growth). We use the ratio of tokutei establishments at the initial periods as the instrument variable for the growth rate of the number of general establishments between 2014 and 2010 (N_growth).


### 2nd stage (wage / wage_growth_14_10)

```{r}

results_s_wage_cz_a <- list()

results_s_wage_cz_a[[1]] <- 
  fixest::feols(
    fml = wage_growth_14_10 ~ 1 | N_growth ~ share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_wage,
    se = "hetero"
  )

result_swagegrowthcza <- 
  list(
    "wage_growth_14_10" = results_s_wage_cz_a[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthcza,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```


### 2nd stage (wage / wage_growth_14_10 / weighted)

```{r}

results_s_wage_cz_2nd_a <- list()

results_s_wage_cz_2nd_a[[1]] <- 
  fixest::feols(
    fml = wage_growth_14_10 ~ 1 | N_growth ~ share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_wage,
    se = "hetero",
    weights = ~ weights
  )


result_swagegrowthcz2nda <- 
  list(
    "wage_growth_14_10(weighted)" = results_s_wage_cz_2nd_a[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthcz2nda,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 1st stage (wage / wage_growth_14_10)

```{r}


modelsummary::modelsummary(
  results_s_wage_cz_a[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

### 1st stage (wage / wage_growth_14_10 / weighted)

```{r}

modelsummary::modelsummary(
  results_s_wage_cz_2nd_a[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)


```


### 2nd stage (fee / fee_growth_14_10)

```{r}

results_s_fee_cz_a <- list()

results_s_fee_cz_a[[1]] <- 
  fixest::feols(
    fml = fee_growth_14_10 ~ 1 | N_growth ~ share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_fee,
    se = "hetero"
  )


result_sfeegrowthcza <- 
  list(
    "fee_growth_14_10" = results_s_fee_cz_a[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthcza,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (fee / fee_growth_14_10 / weighted)

```{r}

results_s_fee_cz_2nd_a <- list()

results_s_fee_cz_2nd_a[[1]] <- 
  fixest::feols(
    fml = fee_growth_14_10 ~ 1 | N_growth ~ share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_fee,
    se = "hetero",
    weights = ~ weights
  )


result_sfeegrowthcz2nda <- 
  list(
    "fee_growth_14_10(weighted)" = results_s_fee_cz_2nd_a[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthcz2nda,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 1st stage (fee / fee_growth_14_10)

```{r}

modelsummary::modelsummary(
  results_s_fee_cz_a[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```



### 1st stage (fee / fee_growth_14_10 / weighted )

```{r}

modelsummary::modelsummary(
  results_s_fee_cz_2nd_a[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# zip data

## First stage (zip) {.tabset}

Regress the growth rate of the number of general establishments between 2014 and 2010 (N_growth) on the percentage of tokutei establishments at the initial period(share_zip_2010). "N_growth" is defined as (N_zip2014 - N_zip2010) / N_zip2010.


### N_growth

```{r}

results_diff_zip_a <- list()


 results_diff_zip_a[[1]] <- 
   estimatr::lm_robust(
     formula = N_growth ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique,
     se_type = "stata"
     )
 
 result_diffzipa <- 
   list(
     "N_growth" = results_diff_zip_a[[1]]
   )
 
 modelsummary::modelsummary(
   result_diffzipa,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

### N_growth (weighted)

(weighted by the number of general establishments in 2010)

```{r}

results_diff_zip_w_a <- list()
 
 
 results_diff_zip_w_a[[1]] <- 
   estimatr::lm_robust(
     formula = N_growth ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique,
     se_type = "stata",
     weights = weights
     )
 
 result_diffzipwa <- 
   list(
     "N_growth" = results_diff_zip_w_a[[1]]
   )
 
 modelsummary::modelsummary(
   result_diffzipwa,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

### Plot for first stage

"estab." represents establishments. y represents the growth rate "(#general establishments in 2014 - #general establishments in 2010) / (#general establishments in 2010)".

```{r}

id_4 <- c(1:778)

data_zip_establishments_all_ippann_share <-
   data_zip_establishments_all_ippann_unique %>% 
   dplyr::select(
     zip_three,
     share_zip_2010,
     N_growth
   ) %>% 
  dplyr::distinct() %>% 
  dplyr::arrange(
    zip_three
  ) 

data_zip_establishments_all_ippann_share <-
  cbind(
    id_4,
    data_zip_establishments_all_ippann_share
  )
 
data_zip_establishments_all_ippann_share <-
  data_zip_establishments_all_ippann_share %>% 
  dplyr::mutate(
    zip_bin = cut(id_4, 
                 breaks = 200)
  ) %>% 
  dplyr::group_by(
    zip_bin
  ) %>% 
  dplyr::mutate(
    N_growth_avr = mean(N_growth),
    share_zip_2010_med = median(share_zip_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_zip_establishments_all_ippann_share_avr <- 
   data_zip_establishments_all_ippann_share %>% 
   dplyr::select(
     share_zip_2010_med,
     N_growth_avr
   ) %>% 
   dplyr::distinct()
   

 g16 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_share,
     mapping = aes(x = share_zip_2010, y = N_growth),
     size = 0.3
     ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("y") 
 
 print(g16)
 
 
```

### binscatter plot for first stage

```{r}

 g26 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_share_avr,
     mapping = aes(x = share_zip_2010_med, y = N_growth_avr),
     size = 0.3
   ) +
   stat_smooth(
     method = "lm",
     data = data_zip_establishments_all_ippann_share_avr,
     mapping = aes(x = share_zip_2010_med, y = N_growth_avr),
     se = FALSE,
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("y") 
 
 print(g26)
 
 
```

## Reduced form (zip) {.tabset}

Regress wage growth rate between 2014 and 2010 (wage_growth_14_10 = (wage_2014-wage_2010)/wage_2010) on the percentage of tokutei establishments at the initial period(share_zip_2010).

### wage(wage_growth_14_10)

```{r}

### wage

results_growth_zip_a <- list()

results_growth_zip_a[[1]] <- 
  estimatr::lm_robust(
    formula = wage_growth_14_10 ~  share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_wage,
    se_type = "stata"
     )

result_growthzipa <- 
  list(
    "wage_growth_14_10" = results_growth_zip_a[[1]]
  )

modelsummary::modelsummary(
  result_growthzipa,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```



### wage(weighted / wage_growth_14_10)

```{r}

### wage

results_growth_zip_w_a <- list()

results_growth_zip_w_a[[1]] <- 
  estimatr::lm_robust(
    formula = wage_growth_14_10 ~  share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_wage,
    se_type = "stata",
    weights = weights
     )

result_growthzipwa <- 
  list(
    "wage_growth_14_10(weighted)" = results_growth_zip_w_a[[1]]
  )

modelsummary::modelsummary(
  result_growthzipwa,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### Plot for reduced form (wage)

```{r}

id_5 <- c(1:778)

data_zip_establishments_all_ippann_wage <-
   data_zip_establishments_all_ippann_unique_wage %>% 
   dplyr::select(
     zip_three,
     share_zip_2010,
     wage_growth_14_10
   ) %>% 
   dplyr::distinct() %>% 
  dplyr::arrange(
    zip_three
  ) 
 
data_zip_establishments_all_ippann_wage <-
  data_zip_establishments_all_ippann_wage %>% 
  dplyr::mutate(
    zip_bin = cut(id_5, 
                 breaks = 200)
  ) %>% 
  dplyr::group_by(
    zip_bin
  ) %>% 
  dplyr::mutate(
    wage_growth_14_10_avr = mean(wage_growth_14_10),
    share_zip_2010_med = median(share_zip_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_zip_establishments_all_ippann_wage_avr <- 
   data_zip_establishments_all_ippann_wage %>% 
   dplyr::select(
     share_zip_2010_med,
     wage_growth_14_10_avr
   ) %>% 
   dplyr::distinct()
   
 

 g17 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_wage,
     mapping = aes(x = share_zip_2010, y = wage_growth_14_10),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average wage)")
 
 print(g17)
 
```

### binscatter plot for reduced form (wage)

```{r}

 g27 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_wage_avr,
     mapping = aes(x = share_zip_2010_med, y = wage_growth_14_10_avr),
     size = 0.5
   ) +
   stat_smooth(
     data = data_zip_establishments_all_ippann_wage_avr,
     method = "lm",
     mapping = aes(x = share_zip_2010_med, y = wage_growth_14_10_avr),
     se = FALSE,
     size = 0.5
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average wage)")
 
 print(g27)
 
```


### fee(fee_growth_14_10)

```{r}

### fee

results_feegrowth_zip_a <- list()

results_feegrowth_zip_a[[1]] <- 
  estimatr::lm_robust(
    formula = fee_growth_14_10 ~  share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_fee,
    se_type = "stata"
    )

result_feegrowthzipa <- 
  list(
    "fee_growth_14_10" = results_feegrowth_zip_a[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthzipa,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```


### fee(fee_growth_14_10/ weighted )

```{r}

### fee

results_feegrowth_zip_w_a <- list()

results_feegrowth_zip_w_a[[1]] <- 
  estimatr::lm_robust(
    formula = fee_growth_14_10 ~  share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_fee,
    se_type = "stata",
    weights = weights
     )

result_feegrowthzipawa <- 
  list(
    "fee_growth_14_10(weighted)" = results_feegrowth_zip_w_a[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthzipawa,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### Plot for reduced form (fee)

```{r}

id_6 <- c(1:778)

data_zip_establishments_all_ippann_fee <-
   data_zip_establishments_all_ippann_unique_fee %>% 
   dplyr::select(
     zip_three,
     share_zip_2010,
     fee_growth_14_10
   ) %>% 
   dplyr::distinct() %>% 
  dplyr::arrange(
    zip_three
  ) 
 
data_zip_establishments_all_ippann_fee <-
  data_zip_establishments_all_ippann_fee %>% 
  dplyr::mutate(
    zip_bin = cut(id_6, 
                 breaks = 200)
  ) %>% 
  dplyr::group_by(
    zip_bin
  ) %>% 
  dplyr::mutate(
    fee_growth_14_10_avr = mean(fee_growth_14_10),
    share_zip_2010_med = median(share_zip_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_zip_establishments_all_ippann_fee_avr <- 
   data_zip_establishments_all_ippann_fee %>% 
   dplyr::select(
     share_zip_2010_med,
     fee_growth_14_10_avr
   ) %>% 
   dplyr::distinct()
   

 g18 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_fee,
     mapping = aes(x = share_zip_2010, y = fee_growth_14_10),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average fee)")
 
 print(g18)
 
```

### binscatter plot for reduced form (fee)

```{r}

 g28 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_fee_avr,
     mapping = aes(x = share_zip_2010_med, y = fee_growth_14_10_avr),
     size = 0.3
   ) +
   stat_smooth(
     data = data_zip_establishments_all_ippann_fee_avr,
     method = "lm",
     mapping = aes(x = share_zip_2010_med, y = fee_growth_14_10_avr),
     se = FALSE,
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("growthe rate(fee)")
 
 print(g28)
 
```

## Structural form (zip) {.tabset}

Regress the wage growth rate between 2014 and 2010 on the growth rate of the number of general establishments between 2014 and 2010 (N_growth). We use the ratio of tokutei establishments at the initial periods as the instrument variable for the growth rate of the number of general establishments between 2014 and 2010 (N_growth).

### 2nd stage (wage / wage_growth_14_10)

```{r}
results_s_wage_zip_a <- list()

results_s_wage_zip_a[[1]] <- 
  fixest::feols(
    fml = wage_growth_14_10 ~ 1 | N_growth ~ share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_wage,
    se = "hetero"
  )


result_swagegrowthzipa <- 
  list(
    "wage_growth_14_10" = results_s_wage_zip_a[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthzipa,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```



### 2nd stage (wage / wage_growth_14_10 / weighted)

```{r}

results_s_wage_zip_2nd_a <- list()

results_s_wage_zip_2nd_a[[1]] <- 
  fixest::feols(
    fml = wage_growth_14_10 ~ 1 | N_growth ~ share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_wage,
    se = "hetero",
    weights = ~ weights
  )

result_swagegrowthzip2nda <- 
  list(
    "wage_growth_14_10(weighted)" = results_s_wage_zip_2nd_a[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthzip2nda,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 1st stage (wage / wage_growth_14_10 )

```{r}

modelsummary::modelsummary(
  results_s_wage_zip_a[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)



```

### 1st stage (wage / results_s_wage_zip_2nd_a[[1]] / weighted )

```{r}

modelsummary::modelsummary(
  results_s_wage_zip_2nd_a[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)


```


### 2nd stage (fee / fee_growth_14_10)

```{r}

results_s_fee_zip_a <- list()

results_s_fee_zip_a[[1]] <- 
  fixest::feols(
    fml = fee_growth_14_10 ~ 1 | N_growth ~ share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_fee,
    se = "hetero"
  )


result_sfeegrowthzipa <- 
  list(
    "fee_growth_14_10" = results_s_fee_zip_a[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthzipa,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```



### 2nd stage (fee / fee_growth_14_10 / weighted)

```{r}

results_s_fee_zip_2nd_a <- list()

results_s_fee_zip_2nd_a[[1]] <- 
  fixest::feols(
    fml = fee_growth_14_10 ~ 1 | N_growth ~ share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_fee,
    se = "hetero",
    weights = ~ weights
  )

result_sfeegrowthzip2nda <- 
  list(
    "fee_growth_14_10" = results_s_fee_zip_2nd_a[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthzip2nda,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```


### 1st stage (fee / fee_growth_14_10)

```{r}

modelsummary::modelsummary(
  results_s_fee_zip_a[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```



### 1st stage (fee / fee_growth_14_10 / weighted)

```{r}

modelsummary::modelsummary(
  results_s_fee_zip_2nd_a[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)


```

