---
title: "report data analysis for zip data"
author: "Chiho Taniguchi"
date: "2023-02-26"
output: 
  html_document:
    toc: true
---
```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 3, fig.width = 4)

library("magrittr")
library("kableExtra")
library("ggplot2")

height <- 6
width <- 8

```


```{r }

 data_establishments <- 
  here::here(file = "cleaned/data_establishments.rds") %>% 
  readRDS()

 data_zipcode <- 
   here::here(file = "cleaned/data_zipcode.rds") %>% 
   readRDS()
 
 data_area <- 
   here::here(file = "cleaned/data_area.rds") %>% 
   readRDS()
 
 data_zip_establishments <- 
   here::here(file = "output/data_zip_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments <- 
   here::here(file = "output/data_cz_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments_all <- 
   here::here(file = "output/data_cz_establishments_all.rds") %>% 
   readRDS()
 
 data_zip_establishments_all <- 
   here::here(file = "output/data_zip_establishments_all.rds") %>% 
   readRDS()
   
 data_cz_establishments_all_ippann <- 
   here::here(file = "output/data_cz_establishments_all_ippann.rds") %>% 
   readRDS()
 
 data_zip_establishments_all_ippann <- 
   here::here(file = "output/data_zip_establishments_all_ippann.rds") %>% 
   readRDS()
 
```

# Data construction
We use data defining the market as first three digits of the zipcode (zip_three) and restrict data to the general establishments only for analysis.
After dropping establishments which have missing either of wage / fee / zip_three data and creating log transformed wage / fee, we create N_zip_t and dummy variables indicating the N_zip_t. N_zip_t and dummy variables are explained in detail later.

# Descriptive statistics {.tabset}

## wage (wage_{it})

```{r}
 data_zip_establishments_wage_fee <- 
   data_zip_establishments %>% 
   dplyr::group_by(
     year, 
     zip_three
   ) %>% 
   dplyr::mutate(
     wage_jt = mean(wage),
     fee_jt = mean(fee)
   ) 
 
 wage_jt_unique <- 
   data_zip_establishments_wage_fee %>% 
   dplyr::select(wage_jt) %>% 
   unique()
 
 summary(wage_jt_unique$wage_jt) 
 
```

## fee (fee_{it})

```{r}

 fee_jt_unique <- 
   data_zip_establishments_wage_fee %>% 
   dplyr::select(fee_jt) %>% 
   unique() 
 
 summary(fee_jt_unique$fee_jt)

```

## N_zip_t

N_zip_t is a variable that indicates the number of general establishments present in the market defined first three digits of zip code (zip) in year t.

```{r }
 N_zip_t_unique <- 
   data_zip_establishments %>% 
   dplyr::select(N_zip_t) %>% 
   unique()
 
 quantile(
   N_zip_t_unique$N_zip_t, 
   c(0.05, 0.1, 0.25, 0.5, 0.75, 1)
 ) %>% 
   kbl(col.names = "N_zip_t") %>% 
   kable_styling(full_width = FALSE)
```


### Show historgam

On the left is the distribution of N_zip_t, without duplicates, and on the right is the distribution of N_zip_t, using all data (allowing duplicates).

```{r}
# Unique data for N_zip_t

histogram_N_zip_t_unique <- 
   ggplot() + 
   geom_histogram(
     data = N_zip_t_unique, 
     mapping = aes(x = N_zip_t),
     bins = 100
   )
 
 print(histogram_N_zip_t_unique)
 
 # All data for N_zip_t
 
 data_zip_establishments_N_zip_t <- 
   data_zip_establishments %>% 
   dplyr::select(N_zip_t)
 
 histogram_N_zip_t <- 
   ggplot() + 
   geom_histogram(
     data = data_zip_establishments_N_zip_t, 
     mapping = aes(x = N_zip_t),
     bins = 100
   )
 
 print(histogram_N_zip_t)
```

# Analyze different N_zip_t {.tabset}

Analyze the impact of the number of general establishments in each market (zip) on the log transformed wage / fee:

$$

Y_{ijt} = \beta N_{jt} + c_{j}  + c_{t} + u_{ijt},\\
Y_{ijt} = \beta N_{jt} + c_{i} + c_{t} + u_{ijt},\\
Y_{ijt} = \beta N_{jt} + c_{j} + c_{i} + c_{t} + u_{ijt}.

$$

$i$: Establishment, $j$: zip three area, $t$: Year<br>
$Y_{ijt}$: $\log{(wage_{ijt})}$, $\log{(fee_{ijt})}$

We also analyze N_zip_t is divided by the number after N_zip_t.

## Analyze for N_zip_t

```{r}

results11 <- list()

results11[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t | zip_three + year ,
    data = data_zip_establishments
  )

results11[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t | year + firm_id ,
    data = data_zip_establishments
  )

results11[[3]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t | year + firm_id + zip_three,
    data = data_zip_establishments
  )

results11[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t | zip_three + year ,
    data = data_zip_establishments
  )

results11[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t | year + firm_id ,
    data = data_zip_establishments
  )

results11[[6]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t | year + firm_id + zip_three,
    data = data_zip_establishments
  )

rows <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`, ~`(6)`,
    'j_FE', 'Y', 'N', 'Y', 'Y', 'N', 'Y',
    't_FE', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y',
    'i_FE', 'N', 'Y', 'Y', 'N', 'Y', 'Y',
  )

attr(rows, 'position') <- c(3, 4, 5, 6)

result_11 <- 
  list(
    "log(fee)" = results11[[1]],
    "log(fee)" = results11[[2]],
    "log(fee)" = results11[[3]],
    "log(wage)" = results11[[4]],
    "log(wage)" = results11[[5]],
    "log(wage)" = results11[[6]]
  )

modelsummary::modelsummary(
  result_11,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 

```

## Analyze for N_zip_t_10

```{r}

results33 <- list()

results33[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_10 | zip_three + year ,
    data = data_zip_establishments
  )

results33[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_10 | year + firm_id ,
    data = data_zip_establishments
  )

results33[[3]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_10 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

results33[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_10 | zip_three + year ,
    data = data_zip_establishments
  )

results33[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_10 | year + firm_id ,
    data = data_zip_establishments
  )

results33[[6]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_10 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

attr(rows, 'position') <- c(3, 4, 5, 6)

result_33 <- 
  list(
    "log(fee)" = results33[[1]],
    "log(fee)" = results33[[2]],
    "log(fee)" = results33[[3]],
    "log(wage)" = results33[[4]],
    "log(wage)" = results33[[5]],
    "log(wage)" = results33[[6]]
  )

modelsummary::modelsummary(
  result_33,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 

```

## Analyze for N_zip_t_100

```{r}

results55 <- list()

results55[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_100 | zip_three + year ,
    data = data_zip_establishments
  )

results55[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_100 | year + firm_id ,
    data = data_zip_establishments
  )

results55[[3]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_100 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

results55[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_100 | zip_three + year ,
    data = data_zip_establishments
  )

results55[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_100 | year + firm_id ,
    data = data_zip_establishments
  )

results55[[6]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_100 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

attr(rows, 'position') <- c(3, 4, 5, 6)

result_55 <- 
  list(
    "log(fee)" = results55[[1]],
    "log(fee)" = results55[[2]],
    "log(fee)" = results55[[3]],
    "log(wage)" = results55[[4]],
    "log(wage)" = results55[[5]],
    "log(wage)" = results55[[6]]
  )

modelsummary::modelsummary(
  result_55,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 

```

## Analyze for N_zip_t_1000

```{r}

results44 <- list()

results44[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_1000 | zip_three + year ,
    data = data_zip_establishments
  )

results44[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_1000 | year + firm_id ,
    data = data_zip_establishments
  )

results44[[3]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_1000 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

results44[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_1000 | zip_three + year ,
    data = data_zip_establishments
  )

results44[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_1000 | year + firm_id ,
    data = data_zip_establishments
  )

results44[[6]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_1000 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

attr(rows, 'position') <- c(3, 4, 5, 6)

result_44 <- 
  list(
    "log(fee)" = results44[[1]],
    "log(fee)" = results44[[2]],
    "log(fee)" = results44[[3]],
    "log(wage)" = results44[[4]],
    "log(wage)" = results44[[5]],
    "log(wage)" = results44[[6]]
  )

modelsummary::modelsummary(
  result_44,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 


```

## Analyze for N_zip_t_10000

```{r}

results66 <- list()

results66[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_10000 | zip_three + year ,
    data = data_zip_establishments
  )

results66[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_10000 | year + firm_id ,
    data = data_zip_establishments
  )

results66[[3]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_10000 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

results66[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_10000 | zip_three + year ,
    data = data_zip_establishments
  )

results66[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_10000 | year + firm_id ,
    data = data_zip_establishments
  )

results66[[6]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_10000 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

attr(rows, 'position') <- c(3, 4, 5, 6)

result_66 <- 
  list(
    "log(fee)" = results66[[1]],
    "log(fee)" = results66[[2]],
    "log(fee)" = results66[[3]],
    "log(wage)" = results66[[4]],
    "log(wage)" = results66[[5]],
    "log(wage)" = results66[[6]]
  )

modelsummary::modelsummary(
  result_66,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 

```

## Analyze for N_zip_t_100000

```{r}

results77 <- list()

results77[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_100000 | zip_three + year ,
    data = data_zip_establishments
  )

results77[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_100000 | year + firm_id ,
    data = data_zip_establishments
  )

results77[[3]] <- 
  lfe::felm(
    formula = log_fee ~  N_zip_t_100000 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

results77[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_100000 | zip_three + year ,
    data = data_zip_establishments
  )

results77[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_100000 | year + firm_id ,
    data = data_zip_establishments
  )

results77[[6]] <- 
  lfe::felm(
    formula = log_wage ~  N_zip_t_100000 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

attr(rows, 'position') <- c(3, 4, 5, 6)

result_77 <- 
  list(
    "log(fee)" = results77[[1]],
    "log(fee)" = results77[[2]],
    "log(fee)" = results77[[3]],
    "log(wage)" = results77[[4]],
    "log(wage)" = results77[[5]],
    "log(wage)" = results77[[6]]
  )

modelsummary::modelsummary(
  result_77,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 

```

# Analyze for N_zip_t with categorical dummy variables {.tabset}

Analyze the impact of the marginally increase in the number of general establishments in each market (zip) on the log transformed wage / fee:

$$



$$


$i$: Establishment, $j$: zip three area, $t$: Year<br>
$Y_{ijt}$: $\log{(wage_{ijt})}$, $\log{(fee_{ijt})}$


## Categorical variables per quantile (20)

We create categorical dummy variables as follows.

D_20 : Dummy variable that takes 1 when N_zip_t is less than the 20th percentile value<br>
D_40 : Dummy variable that takes 1 when N_zip_t is greater than or equal to the 20th percentile value and less than or equal to the 40th percentile value<br>
D_60 : Dummy variable that takes 1 when N_zip_t is greater than the 40th percentile value and less than the 60th percentile value<br>
D_80 : Dummy variable that takes 1 when N_zip_t is above the 60th percentile value and below the 80th percentile value<br>
D_100 : Dummy variable that takes 1 when N_zip_t is greater than or equal to the 80th percentile value


```{r}

results222 <- list()

results222[[1]] <- 
  lfe::felm(
    formula = log_fee ~ D_40 + D_60 + D_80 + D_100 | zip_three + year ,
    data = data_zip_establishments
  )

results222[[2]] <- 
  lfe::felm(
    formula = log_fee ~ D_40 + D_60 + D_80 + D_100 | year + firm_id ,
    data = data_zip_establishments
  )

results222[[3]] <- 
  lfe::felm(
    formula = log_fee ~ D_40 + D_60 + D_80 + D_100 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

results222[[4]] <- 
  lfe::felm(
    formula = log_wage ~ D_40 + D_60 + D_80 + D_100 | zip_three + year ,
    data = data_zip_establishments
  )

results222[[5]] <- 
  lfe::felm(
    formula = log_wage ~ D_40 + D_60 + D_80 + D_100 | year + firm_id ,
    data = data_zip_establishments
  )

results222[[6]] <- 
  lfe::felm(
    formula = log_wage ~ D_40 + D_60 + D_80 + D_100 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

rows_D <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`, ~`(6)`,
    'j_FE', 'Y', 'N', 'Y', 'Y', 'N', 'Y',
    't_FE', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y',
    'i_FE', 'N', 'Y', 'Y', 'N', 'Y', 'Y',
  )

attr(rows_D, 'position') <- c(9, 10, 11, 12)

result_222 <- 
  list(
    "log(fee)" = results222[[1]],
    "log(fee)" = results222[[2]],
    "log(fee)" = results222[[3]],
    "log(wage)" = results222[[4]],
    "log(wage)" = results222[[5]],
    "log(wage)" = results222[[6]]
  )

modelsummary::modelsummary(
  result_222,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows_D
) 

```


## Categorical variables per quantile (10)

We create categorical dummy variables as follows.

D10 : Dummy variable that takes 1 when N_zip_t is less than the 10th percentile value<br>
D20 : Dummy variable that takes 1 when N_zip_t is greater than or equal to the 10th percentile value and less than the 20th percentile value<br>
D30 : Dummy variable that takes 1 when N_zip_t is greater than the 20th percentile value and less than the 30th percentile value<br>
D40 : Dummy variable that takes 1 when N_zip_t is above the 30th percentile value and below the 40th percentile value<br>
D50 : Dummy variable that takes 1 when N_zip_t is above the 40th percentile value and below the 50th percentile value<br>
D60 : Dummy variable that takes 1 when N_zip_t is above the 50th percentile value and below the 60th percentile value<br>
D70 : Dummy variable that takes 1 when N_zip_t is above the 60th percentile value and below the 70th percentile value<br>
D80 : Dummy variable that takes 1 when N_zip_t is above the 70th percentile value and below the 80th percentile value<br>
D90 : Dummy variable that takes 1 when N_zip_t is above the 80th percentile value and below the 90th percentile value<br>
D100 : Dummy variable that takes 1 when N_zip_t is greater than or equal to the 90th percentile value

```{r}

results88 <- list()

results88[[1]] <- 
  lfe::felm(
    formula = log_fee ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | zip_three + year ,
    data = data_zip_establishments
  )

results88[[2]] <- 
  lfe::felm(
    formula = log_fee ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | year + firm_id ,
    data = data_zip_establishments
  )

results88[[3]] <- 
  lfe::felm(
    formula = log_fee ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

results88[[4]] <- 
  lfe::felm(
    formula = log_wage ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | zip_three + year ,
    data = data_zip_establishments
  )

results88[[5]] <- 
  lfe::felm(
    formula = log_wage ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | year + firm_id ,
    data = data_zip_establishments
  )

results88[[6]] <- 
  lfe::felm(
    formula = log_wage ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | year + firm_id + zip_three,
    data = data_zip_establishments
  )

rows_D <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`, ~`(6)`,
    'j_FE', 'Y', 'N', 'Y', 'Y', 'N', 'Y',
    't_FE', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y',
    'i_FE', 'N', 'Y', 'Y', 'N', 'Y', 'Y',
  )

attr(rows_D, 'position') <- c(19, 20, 21, 22)

result_88 <- 
  list(
    "log(fee)" = results88[[1]],
    "log(fee)" = results88[[2]],
    "log(fee)" = results88[[3]],
    "log(wage)" = results88[[4]],
    "log(wage)" = results88[[5]],
    "log(wage)" = results88[[6]]
  )

modelsummary::modelsummary(
  result_88,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows_D
) 

```


# Analyze using Bartik IV (bartik_zip_t) {.tabset}

$$

$$

$i$: Establishment, $j$: zip three area, $t$: Year<br>
$Y_{ijt}$: $\log{(wage_{ijt})}$, $\log{(fee_{ijt})}$

## 2nd stage

$$

$$

```{r}

results_b11 <- list()
 
 results_b11[[1]] <- 
   lfe::felm(
     formula = log_fee ~ 1 | zip_three + year | (N_zip_t_1000 ~ bartik_zip_t) | zip_three,
     data = data_zip_establishments_all_ippann
   )
 
 results_b11[[2]] <- 
   lfe::felm(
     formula = log_wage ~ 1 | zip_three + year | (N_zip_t_1000 ~ bartik_zip_t) | zip_three,
     data = data_zip_establishments_all_ippann
   )
 
 rows <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`,
     'j_FE', 'Y', 'Y',
     't_FE', 'Y', 'Y',
     'i_FE', 'N', 'N', 
   )
 
 attr(rows, 'position') <- c(3, 4, 5, 6)
 
 resultsb11 <- 
   list(
     "log(fee)" = results_b11[[1]],
     "log(wage)" = results_b11[[2]]
   )
 
 modelsummary::modelsummary(
   resultsb11,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```


## 1st stage

$$

$$


```{r}

rows <- 
   tibble::tribble(
     ~term, ~`(1)`
   )
 
 attr(rows, 'position') <- c(3, 4, 5, 6)
 
 resultsb33 <- 
   list(
     "N_zip_t_1000(1st stage zip)" = results_b11[[1]]$stage1
   )
 
 modelsummary::modelsummary(
   resultsb33,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95
 )

```


## reduced form

$$

$$

```{r}

results_b22 <- list()
 
 results_b22[[1]] <- 
   lfe::felm(
     formula = log_fee ~ bartik_zip_t | zip_three + year ,
     data = data_zip_establishments_all_ippann
   )
 
 results_b22[[2]] <- 
   lfe::felm(
     formula = log_wage ~ bartik_zip_t | zip_three + year,
     data = data_zip_establishments_all_ippann
   )
 
 rows <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`,
     'j_FE', 'Y', 'Y',
     't_FE', 'Y', 'Y',
     'i_FE', 'N', 'N', 
   )
 
 attr(rows, 'position') <- c(3, 4, 5, 6)
 
 resultsb22 <- 
   list(
     "log(fee)" = results_b22[[1]],
     "log(wage)" = results_b22[[2]]
   )
 
 modelsummary::modelsummary(
   resultsb22,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

# Analyze residuals for zip data {.tabset}

## Regress N_zip_t on zip three area (zip) / year fixed effect

$$


$$

```{r}

 result_u_zip <- 
   lfe::felm(
     formula = N_zip_t ~ 1 + zip_three + year ,
     data = data_zip_establishments_all_ippann
   )
 
 id_zip <- c(1:72954)
 
 residual_zip <-
   as.data.frame(result_u_zip$residuals) %>% 
   dplyr::rename(u_hat_zip = N_zip_t) %>% 
   cbind(id_zip)
 
 residual_zip_unique <- 
   residual_zip %>% 
   dplyr::select(
     u_hat_zip
   ) %>% 
   unique() %>% 
   as.data.frame() 

```

### Show histogram (unique)

On the left is the distribution of the residuals, without duplicates, and on the right is the distribution of the residuals, using all data (allowing duplicates).

```{r}
 
histogram_residuals_zip_unique <- 
   ggplot() + 
   geom_histogram(
     data = residual_zip_unique, 
     mapping = aes(x = u_hat_zip),
     bins = 100
   )
 
 print(histogram_residuals_zip_unique)

 
 residual_zip_all <- 
   residual_zip 
 
 histogram_residuals_zip_all <- 
   ggplot() + 
   geom_histogram(
     data = residual_zip_all, 
     mapping = aes(x = u_hat_zip),
     bins = 100
   )
 
 print(histogram_residuals_zip_all)

```

### Summary of the residuals

```{r}

summary(residual_zip_all$u_hat_zip)

```

