---
title: "report_data_counterfactual_minimum_wage_across_markets"
author: "Daisy Dan Song"
date: "2025-11-11"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )
rm(list = ls())
library(Dispatching)
library(foreach)
library(magrittr)
library(codetools)
library(ggplot2)
library(kableExtra)
```

# import solved equilibrium
```{r}
equilibrium <-
  readRDS(
    file = "output/multihome/estimate_data/equilibrium_updated_constrained.rds" %>%
    here::here()
  )
updated_ownership <- 
  readRDS(
    file = "output/multihome/make_equilibrium_nationwide_top5_from_data/updated_ownership_matrix.rds" %>%
    here::here()
  )

equilibrium$constant$use_exp <- FALSE
```

# update ownership 
```{r}
for (
  t in seq_along(equilibrium$exogenous)
) {
  for (
    j in seq_along(equilibrium$exogenous[[t]])
  ){
    equilibrium$exogenous[[t]][[j]]$owner <- updated_ownership[[t]][[j]]$owner 
  }
}
```

# counterfactual with minimum wage 
## minimum wage {.tabset}
```{r}
counterfactual <- 
    readRDS(
    file = "output/multihome/counterfactual/counterfactual_minimum_wage_combined.rds" %>%
    here::here()
  ) 
summary(counterfactual)
```

### s_w < 0
```{r}
counterfactual_1 <-
  counterfactual %>%
  dplyr::filter(s_w < 0)
nrow(counterfactual_1)
```


### add real_index from ownership matrix
```{r}
# For each market-zone combination, recover the real establishment index
# from the owner matrix for firms i >= 3
# 
# The counterfactual i index corresponds to:
# - i=0: outside option
# - i=1,2: fringe firms (always present)
# - i>=3: THS firms (may or may not exist in each market)
#
# For i>=3, we need to find which establishment (row) in the owner matrix
# corresponds to this firm. The owner matrix columns represent firms (top-5),
# and rows represent establishments. We need to map i to the actual row index.

counterfactual_with_real_index <-
  counterfactual %>%
  dplyr::mutate(
    real_index = NA_integer_
  ) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(
    real_index = {
      # In rowwise context, i should be a single value
      # Check if i exists and has valid length
      if (length(i) == 0) {
        NA_integer_
      } else {
        # Convert factor to integer value (not factor level)
        # If i is a factor, as.integer(i) returns the level number (1,2,3...)
        # We need to convert to character first to get the actual value
        if (is.factor(i)) {
          i_char <- as.character(i)
          # Check if character conversion succeeded
          if (length(i_char) == 0 || nchar(i_char[1]) == 0) {
            NA_integer_
          } else {
            i_int <- suppressWarnings(as.integer(i_char[1]))
            # Check if conversion succeeded
            if (length(i_int) == 0 || is.na(i_int)) {
              NA_integer_
            } else {
              # For i = 0, real_index is 0 (outside option)
              if (i_int == 0) {
                0L
              } else if (i_int <= 2) {
                # For i = 1, 2, real_index is the same as i (fringe firms)
                i_int
              } else {
                # For i >= 3, find which establishment (row) in owner matrix
                # corresponds to this firm
                # The owner matrix columns directly correspond to i:
                # Column 1 = i=1, Column 2 = i=2, Column 3 = i=3, etc.
                # The rows represent real_index (establishment indices)
                owner_tj <- equilibrium$exogenous[[t]][[j]]$owner
                firm_col <- i_int  # Column directly corresponds to i
                
                if (firm_col <= ncol(owner_tj)) {
                  # Find which establishment (row) has a 1 in this firm column
                  # This gives us the establishment(s) that belong to this firm
                  # The row number is the real_index
                  establishment_rows <- which(owner_tj[, firm_col] == 1)
                  
                  if (length(establishment_rows) > 0) {
                    # Use the first establishment that belongs to this firm
                    # This is the "real_index" - the actual row number in the owner matrix
                    establishment_rows[1]
                  } else {
                    # Firm doesn't exist in this market
                    NA_integer_
                  }
                } else {
                  # Firm column doesn't exist
                  NA_integer_
                }
              }
            }
          }
        } else {
          i_int <- as.integer(i[1])
          # Check if conversion succeeded
          if (length(i_int) == 0 || is.na(i_int)) {
            NA_integer_
          } else {
            # For i = 0, real_index is 0 (outside option)
            if (i_int == 0) {
              0L
            } else if (i_int <= 2) {
              # For i = 1, 2, real_index is the same as i (fringe firms)
              i_int
            } else {
              # For i >= 3, find which establishment (row) in owner matrix
              # corresponds to this firm
              owner_tj <- equilibrium$exogenous[[t]][[j]]$owner
              firm_col <- i_int
              
              if (firm_col <= ncol(owner_tj)) {
                establishment_rows <- which(owner_tj[, firm_col] == 1)
                
                if (length(establishment_rows) > 0) {
                  establishment_rows[1]
                } else {
                  NA_integer_
                }
              } else {
                NA_integer_
              }
            }
          }
        }
      }
    }
  ) %>%
  dplyr::ungroup()
counterfactual_with_real_index %>% summary()
```

### aggregate across markets
```{r}
# Define which columns to average vs sum
avg_cols <- 
  c(
    "w", 
    "f", 
    "m"
    )  # wages, fees, markups - take average
share_cols <- 
  c(
    "s_w",
    "s_f"
    )  # shares - sum then divide by number of markets
sum_cols <- 
  c(
    "profit_ths",
    "surplus_w", 
    "surplus_f"
    )  # profits, surpluses - take sum

counterfactual_aggregated <-
  counterfactual_with_real_index %>%
  # Filter out rows where real_index is NA (firms that don't exist in that market)
  dplyr::filter(
    !is.na(real_index)
    ) %>%
  dplyr::group_by(
    real_index, 
    minimum_wage
    ) %>%
  dplyr::summarise(
    # Average wages/fees/markups across markets
    dplyr::across(
      dplyr::any_of(avg_cols),
      ~ mean(.x, na.rm = TRUE),
      .names = "{.col}"
    ),
    # Sum shares then divide by number of markets (average share)
    dplyr::across(
      dplyr::any_of(share_cols),
      ~ sum(.x, na.rm = TRUE) / dplyr::n(),
      .names = "{.col}"
    ),
    # Sum profits/surpluses across markets
    dplyr::across(
      dplyr::any_of(sum_cols),
      ~ sum(.x, na.rm = TRUE),
      .names = "{.col}"
    ),
    # Keep other columns as mean
    dplyr::across(
      dplyr::any_of(
        c("augmented_foc_w", 
          "augmented_foc_f", 
          "foc_w", 
          "foc_f", 
          "complementarity", 
          "foc_s_f", 
          "eta_w", 
          "meeting_probability_w", 
          "meeting_probability_f", 
          "c_w",
          "c_f")
        ),
      ~ mean(.x, na.rm = TRUE),
      .names = "{.col}"
    ),
    # Count how many markets this real_index appears in
    n_markets = dplyr::n(),
    # Keep i for reference (should be consistent within real_index, but take first)
    i = dplyr::first(i),
    .groups = "drop"
  ) %>%
  dplyr::arrange(real_index, minimum_wage)
summary(counterfactual_aggregated)
```


### table 
```{r, results = "asis"}
counterfactual_aggregated %>%
  kbl() %>%
  kable_styling()
```


### outside market {.tabset}
```{r, results = "asis"}

p <- 
  plot_counterfactual_minimum_wage_outside(
    counterfactual = counterfactual_aggregated
  )
p
```


### inside market {.tabset}
```{r, results = "asis"}
p <- 
  plot_counterfactual_minimum_wage_inside(
    counterfactual = counterfactual_aggregated
  )
p
```



