---
title: "report data analysis (use distance data)"
author: "Chiho Taniguchi"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 3, fig.width = 4)

library("magrittr")
library("kableExtra")
library("ggplot2")

height <- 6
width <- 8

```

```{r }
 
 data_cz_establishments <- 
   here::here(file = "output/data_cz_establishments.rds") %>% 
   readRDS()
 
 data_area_area_distance <- 
   here::here(file = "cleaned/data_area_area_distance.rds") %>% 
   readRDS()
 
 ## there are two establishments whose firm_id are NA in data_cz_establishments
 
 data_cz_establishments_distance <- 
   here::here(file = "output/data_cz_establishments_distance.rds") %>% 
   readRDS()
 
```

# distance mean 

## first stage

```{r}

data_cz_establishments_distance_na <- 
  data_cz_establishments_distance %>% 
  tidyr::drop_na(
    distance_min_r
  ) %>% 
  dplyr::group_by(
    year,
    cz
  ) %>% 
  dplyr::mutate(
    distance_min_avr_dropna = mean(distance_min_r),
    distance_min_med_dropna = stats::median(distance_min_r),
    distance_min_10_dropna = stats::quantile(distance_min_r, 0.1),
    distance_min_25_dropna = stats::quantile(distance_min_r, 0.25),
    distance_min_75_dropna = stats::quantile(distance_min_r, 0.75),
    distance_min_90_dropna = stats::quantile(distance_min_r, 0.9),
    log_wage_avr = mean(log_wage),
    log_fee_avr = mean(log_fee)
  ) 
  
 
data_cz_establishments_distance_na_distinct <- 
  data_cz_establishments_distance_na %>% 
  dplyr::arrange(
    year,
    cz
  ) %>% 
  dplyr::select(
    year,
    cz,
    distance_min_avr_dropna,
    distance_min_med_dropna,
    distance_min_10_dropna,
    distance_min_25_dropna,
    distance_min_75_dropna,
    distance_min_90_dropna,
    N_jt,
    N_jt_1000,
    N_jt_10000,
    log_wage_avr,
    log_fee_avr
  ) %>% 
  dplyr::distinct() 

data_cz_establishments_distance_na_distinct <- 
  data_cz_establishments_distance_na_distinct %>% 
  dplyr::mutate(
    distance_min_avr_dropna_10000 = distance_min_avr_dropna / 10000,
    distance_min_avr_dropna_100000 = distance_min_avr_dropna / 100000,
    distance_min_avr_dropna_1000000 = distance_min_avr_dropna / 1000000,
    distance_min_med_dropna_1000000 = distance_min_med_dropna / 1000000,
    distance_min_10_dropna_1000000 = distance_min_10_dropna / 1000000,
    distance_min_25_dropna_1000000 = distance_min_25_dropna / 1000000,
    distance_min_75_dropna_1000000 = distance_min_75_dropna / 1000000,
    distance_min_90_dropna_1000000 = distance_min_90_dropna / 1000000
  )

 results <- list()
 
 results[[1]] <- 
   estimatr::lm_robust(
     formula = N_jt ~ distance_min_avr_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`,
     'year_FE', 'Y',
     'cz_FE', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(3,4)
 
 result <- 
   list(
     "N_jt" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 


```

## reduced form

```{r}

resultsr <- list()
 
 resultsr[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_avr ~ distance_min_avr_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 resultsr[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_avr ~ distance_min_avr_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 rows <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`,
    'year_FE', 'Y', 'Y',
    'cz_FE', 'Y', 'Y'
  )
 
 attr(rows, 'position') <- c(3,4)
 
 result_r <- 
   list(
     "log_wage_avr" = resultsr[[1]],
     "log_fee_avr" = resultsr[[2]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## structural form {.tabset}

### 2nd stage

```{r}

resultss <- list()

resultss[[1]] <- 
  fixest::feols(
    fml = log_wage_avr ~ 1 | year + cz | N_jt ~ distance_min_avr_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

resultss[[2]] <- 
  fixest::feols(
    fml = log_fee_avr ~ 1 | year + cz | N_jt ~ distance_min_avr_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

results_s <- 
  list(
    "log_wage_avr" = resultss[[1]],
    "log_fee_avr" = resultss[[2]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultss[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```
 
# distance median 

## first stage

```{r}

 resultsm <- list()
 
 resultsm[[1]] <- 
   estimatr::lm_robust(
     formula = N_jt ~ distance_min_med_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`,
     'year_FE', 'Y',
     'cz_FE', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(3,4)
 
 resultm <- 
   list(
     "N_jt" = resultsm[[1]]
   )
 
 modelsummary::modelsummary(
   resultm,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 


```

## reduced form

```{r}

resultsrm <- list()
 
 resultsrm[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_avr ~ distance_min_med_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 resultsrm[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_avr ~ distance_min_med_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 rows <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`,
    'year_FE', 'Y', 'Y',
    'cz_FE', 'Y', 'Y'
  )
 
 attr(rows, 'position') <- c(3,4)
 
 result_rm <- 
   list(
     "log_wage_avr" = resultsrm[[1]],
     "log_fee_avr" = resultsrm[[2]]
   )
 
 modelsummary::modelsummary(
   result_rm,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## structural form {.tabset}

### 2nd stage

```{r}

resultssm <- list()

resultssm[[1]] <- 
  fixest::feols(
    fml = log_wage_avr ~ 1 | year + cz | N_jt ~ distance_min_med_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

resultssm[[2]] <- 
  fixest::feols(
    fml = log_fee_avr ~ 1 | year + cz | N_jt ~ distance_min_med_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

results_sm <- 
  list(
    "log_wage_avr" = resultssm[[1]],
    "log_fee_avr" = resultssm[[2]]
  )

modelsummary::modelsummary(
  results_sm,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultssm[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# distance 10 percentile 

## first stage

```{r}

 results10 <- list()
 
 results10[[1]] <- 
   estimatr::lm_robust(
     formula = N_jt ~ distance_min_10_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`,
     'year_FE', 'Y',
     'cz_FE', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(3,4)
 
 result10 <- 
   list(
     "N_jt" = results10[[1]]
   )
 
 modelsummary::modelsummary(
   result10,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 


```

## reduced form

```{r}

resultsr10 <- list()
 
 resultsr10[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_avr ~ distance_min_10_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 resultsr10[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_avr ~ distance_min_10_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 rows <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`,
    'year_FE', 'Y', 'Y',
    'cz_FE', 'Y', 'Y'
  )
 
 attr(rows, 'position') <- c(3,4)
 
 result_r10 <- 
   list(
     "log_wage_avr" = resultsr10[[1]],
     "log_fee_avr" = resultsr10[[2]]
   )
 
 modelsummary::modelsummary(
   result_r10,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## structural form {.tabset}

### 2nd stage

```{r}

resultss10 <- list()

resultss10[[1]] <- 
  fixest::feols(
    fml = log_wage_avr ~ 1 | year + cz | N_jt ~ distance_min_10_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

resultss10[[2]] <- 
  fixest::feols(
    fml = log_fee_avr ~ 1 | year + cz | N_jt ~ distance_min_10_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

results_s10 <- 
  list(
    "log_wage_avr" = resultss10[[1]],
    "log_fee_avr" = resultss10[[2]]
  )

modelsummary::modelsummary(
  results_s10,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultss10[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# distance 25 percentile 

## first stage

```{r}

 results25 <- list()
 
 results25[[1]] <- 
   estimatr::lm_robust(
     formula = N_jt ~ distance_min_25_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`,
     'year_FE', 'Y',
     'cz_FE', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(3,4)
 
 result25 <- 
   list(
     "N_jt" = results25[[1]]
   )
 
 modelsummary::modelsummary(
   result25,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 


```

## reduced form

```{r}

resultsr25 <- list()
 
 resultsr25[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_avr ~ distance_min_25_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 resultsr25[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_avr ~ distance_min_25_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 rows <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`,
    'year_FE', 'Y', 'Y',
    'cz_FE', 'Y', 'Y'
  )
 
 attr(rows, 'position') <- c(3,4)
 
 result_r25 <- 
   list(
     "log_wage_avr" = resultsr25[[1]],
     "log_fee_avr" = resultsr25[[2]]
   )
 
 modelsummary::modelsummary(
   result_r25,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## structural form {.tabset}

### 2nd stage

```{r}

resultss25 <- list()

resultss25[[1]] <- 
  fixest::feols(
    fml = log_wage_avr ~ 1 | year + cz | N_jt ~ distance_min_25_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

resultss25[[2]] <- 
  fixest::feols(
    fml = log_fee_avr ~ 1 | year + cz | N_jt ~ distance_min_25_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

results_s25 <- 
  list(
    "log_wage_avr" = resultss25[[1]],
    "log_fee_avr" = resultss25[[2]]
  )

modelsummary::modelsummary(
  results_s25,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultss25[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# distance 75 percentile 

## first stage

```{r}

 results75 <- list()
 
 results75[[1]] <- 
   estimatr::lm_robust(
     formula = N_jt ~ distance_min_75_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`,
     'year_FE', 'Y',
     'cz_FE', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(3,4)
 
 result75 <- 
   list(
     "N_jt" = results75[[1]]
   )
 
 modelsummary::modelsummary(
   result75,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 


```

## reduced form

```{r}

resultsr75 <- list()
 
 resultsr75[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_avr ~ distance_min_75_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 resultsr75[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_avr ~ distance_min_75_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 rows <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`,
    'year_FE', 'Y', 'Y',
    'cz_FE', 'Y', 'Y'
  )
 
 attr(rows, 'position') <- c(3,4)
 
 result_r75 <- 
   list(
     "log_wage_avr" = resultsr75[[1]],
     "log_fee_avr" = resultsr75[[2]]
   )
 
 modelsummary::modelsummary(
   result_r75,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## structural form {.tabset}

### 2nd stage

```{r}

resultss75 <- list()

resultss75[[1]] <- 
  fixest::feols(
    fml = log_wage_avr ~ 1 | year + cz | N_jt ~ distance_min_75_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

resultss75[[2]] <- 
  fixest::feols(
    fml = log_fee_avr ~ 1 | year + cz | N_jt ~ distance_min_75_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

results_s75 <- 
  list(
    "log_wage_avr" = resultss75[[1]],
    "log_fee_avr" = resultss75[[2]]
  )

modelsummary::modelsummary(
  results_s75,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultss75[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# distance 90 percentile 

## first stage

```{r}

 results90 <- list()
 
 results90[[1]] <- 
   estimatr::lm_robust(
     formula = N_jt ~ distance_min_90_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`,
     'year_FE', 'Y',
     'cz_FE', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(3,4)
 
 result90 <- 
   list(
     "N_jt" = results90[[1]]
   )
 
 modelsummary::modelsummary(
   result90,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 


```

## reduced form

```{r}

resultsr90 <- list()
 
 resultsr90[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_avr ~ distance_min_90_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 resultsr90[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_avr ~ distance_min_90_dropna_1000000,
     fixed_effects = year + cz,
     se_type = "stata",
     data = data_cz_establishments_distance_na_distinct
   )
 
 rows <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`,
    'year_FE', 'Y', 'Y',
    'cz_FE', 'Y', 'Y'
  )
 
 attr(rows, 'position') <- c(3,4)
 
 result_r90 <- 
   list(
     "log_wage_avr" = resultsr10[[1]],
     "log_fee_avr" = resultsr10[[2]]
   )
 
 modelsummary::modelsummary(
   result_r90,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## structural form {.tabset}

### 2nd stage

```{r}

resultss90 <- list()

resultss90[[1]] <- 
  fixest::feols(
    fml = log_wage_avr ~ 1 | year + cz | N_jt ~ distance_min_90_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

resultss90[[2]] <- 
  fixest::feols(
    fml = log_fee_avr ~ 1 | year + cz | N_jt ~ distance_min_90_dropna_1000000,
    data = data_cz_establishments_distance_na_distinct,
    se = "hetero"
  )

results_s90 <- 
  list(
    "log_wage_avr" = resultss90[[1]],
    "log_fee_avr" = resultss90[[2]]
  )

modelsummary::modelsummary(
  results_s90,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultss90[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```


