---
title: "report_estimation_costs_patterns"
author: "Daisy Dan Song"
date: "2025-05-14"
output: html_document
---

# initialize
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )
rm(list = ls())
library(Dispatching)
library(foreach)
library(magrittr)
library(codetools)
library(ggplot2)
library(kableExtra)
library(purrr)
library(doParallel)
registerDoParallel()
```

# import estimation equilibrium
```{r}
equilibrium <-
  readRDS(
    file = "output/multihome/estimate_data_initial/equilibrium_updated_initial.rds" %>%
    here::here()
  )

equilibrium_simulate <-
  readRDS(
    file = "output/multihome/simulate/equilibrium.rds" %>%
    here::here()
  )
equilibrium_simulate$constant$use_exp <- FALSE
```

# actual data {.tabset}
## problematic ths {.tabset}
### not eliciting demand shocks

```{r}
equilibrium$constant$method_s_w <- "exact"
t <- 1
j <- 42
i <- 2
```

#### c_w
##### check s_w_d_w

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- s_w_d_w_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "s_w_d_w ths 1"
  ) +
  ylim(
    0, 
    max(objective_values$objective)
    )  
g_1

```

##### -s_w/s_w_d_w

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- 
        -s_w[i]/s_w_d_w_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "-s_w/s_w_d_w"
  ) +
  ylim(
    min(objective_values$objective),
    0
    )
g_1

```

##### all together

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      f <- equilibrium$endogenous[[t]][[j]]$f
      w <- equilibrium$endogenous[[t]][[j]]$w
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- 
        -s_w[i]/s_w_d_w_tj[i] + f[i] - w[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    size = 0.1
  ) +
  geom_line() +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w"
  )
g_1
```

#### c_f
##### check s_f_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        obj <- s_f_d_f_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "s_f_d_f"
  )+
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### check q_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
        s_f_d_f <- 
          solve_s_f_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_f = equilibrium$parameter$beta_f,
            lambda_f = param_value,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        meeting_number_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f
          )
        meeting_number_d_f <-  
            diag(meeting_number_d_f) %>% as.matrix()

        obj <- meeting_number_d_f[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q_d_f"
  )+
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### check s_w_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          ) 
        s_w_d_f_tj <-  
            diag(s_w_d_f_tj)

        obj <- s_w_d_f_tj[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "s_w_d_f"
  )
g_1

```

##### q * s_w / (size_f * s_f_d_f)

```{r}

target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        obj <- 
          q[i] * s_w[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q * s_w / (size_f * s_f_d_f)"
  ) +
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### q_d_f * s_w / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )

        q_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f_tj
          )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        q_d_f <-  
            diag(q_d_f) %>% as.matrix()
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        obj <- 
          q_d_f[i] * s_w[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_f_d_f_tj = s_f_d_f_tj[i],
          q_d_f = q_d_f[i]
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q_d_f * s_w / (size_f * s_f_d_f)"
  ) +
  ylim(
    0, 
    max(objective_values$objective)
    ) 
g_1
```

##### q * s_w_d_f / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )  
        s_w_d_f_tj <-  
          diag(s_w_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        obj <- 
          q[i] * s_w_d_f_tj[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q * s_w_d_f / (size_f * s_f_d_f)"
  )
g_1
```

##### all together

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )

        q_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f_tj
          )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        q_d_f <-  
            diag(q_d_f) %>% as.matrix()
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )  
        s_w_d_f_tj <-  
          diag(s_w_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        f <- equilibrium$endogenous[[t]][[j]]$f
        w <- equilibrium$endogenous[[t]][[j]]$w
        c_w <- 
            compute_supply_shock_c_w_tj(
              m_w = equilibrium$parameter$m_w,
              m_f = equilibrium$parameter$m_f,
              beta_w = equilibrium$parameter$beta_w,
              lambda_w = equilibrium$parameter$lambda_w,
              x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
              size_w = equilibrium$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium$exogenous[[t]][[j]]$size_f,
              mu = equilibrium$shock[[t]][[j]]$mu,
              ea_w = equilibrium$shock[[t]][[j]]$ea_w,
              f = equilibrium$endogenous[[t]][[j]]$f,
              w = equilibrium$endogenous[[t]][[j]]$w,
              s_f = equilibrium$endogenous[[t]][[j]]$s_f,
              s_w = equilibrium$endogenous[[t]][[j]]$s_w,
              owner = equilibrium$exogenous[[t]][[j]]$owner,
              method_s_w = equilibrium$constant$method_s_w,
              margin = equilibrium$constant$margin,
              quadrature_size = equilibrium$constant$quadrature_size,
              tol = equilibrium$constant$tol
            )
        obj <- 
          q[i] * s_w[i] /( s_f_d_f_tj[i] * size_f) +
          (
            q_d_f[i] * s_w[i] /( s_f_d_f_tj[i] * size_f) +
            q[i] * s_w_d_f_tj[i] /( s_f_d_f_tj[i] * size_f)
          ) * (f[i] - w[i] - c_w[i])
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f"
  )
g_1
```

### eliciting demand shocks
#### c_w
##### check s_w_d_w

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = param_value,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      beta_w <- equilibrium$parameter$beta_w
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
        
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- s_w_d_w_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "s_w_d_w ths 1"
  ) +
  ylim(
    0, 
    max(objective_values$objective)
    ) 
g_1

```

##### -s_w/s_w_d_w

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = param_value,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      beta_w <- equilibrium$parameter$beta_w
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
        
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- 
        -s_w[i]/s_w_d_w_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "-s_w/s_w_d_w"
  )  +
  ylim(
    -4e6,
    0
    )
g_1

```

##### all together

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = param_value,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      beta_w <- equilibrium$parameter$beta_w
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
        
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      f <- equilibrium$endogenous[[t]][[j]]$f
      w <- equilibrium$endogenous[[t]][[j]]$w
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- 
        -s_w[i]/s_w_d_w_tj[i] + f[i] - w[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    size = 0.1
  ) +
  geom_line() +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w"
  )
g_1
```

#### c_f
##### check s_f_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        obj <- s_f_d_f_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "s_f_d_f"
  ) +
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### check q_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      meeting_number_d_f <- 
        compute_meeting_number_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_f_d_f = s_f_d_f_tj
        )
        meeting_number_d_f <-  
            diag(meeting_number_d_f) %>% as.matrix()

        obj <- meeting_number_d_f[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q_d_f"
  ) +
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### check s_w_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()

        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = ea_w,
            ea_f = ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          ) 
        s_w_d_f_tj <-  
            diag(s_w_d_f_tj)

        obj <- s_w_d_f_tj[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "s_w_d_f"
  )
g_1

```

##### q * s_w / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      s_f_d_f_tj <-  
          diag(s_f_d_f_tj)
      q <- 
        compute_meeting_number_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      size_f <- equilibrium$exogenous[[t]][[j]]$size_f
      obj <- 
        q[i] * s_w[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q * s_w / (size_f * s_f_d_f)"
  )  +
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### q_d_f * s_w / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )

      q_d_f <- 
        compute_meeting_number_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_f_d_f = s_f_d_f_tj
        )
      s_f_d_f_tj <-  
          diag(s_f_d_f_tj)
      q_d_f <-  
          diag(q_d_f) %>% as.matrix()
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      size_f <- equilibrium$exogenous[[t]][[j]]$size_f
      obj <- 
        q_d_f[i] * s_w[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_f_d_f_tj = s_f_d_f_tj[i],
          q_d_f = q_d_f[i]
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q_d_f * s_w / (size_f * s_f_d_f)"
  ) +
  ylim(
    0, 
    max(objective_values$objective)
    )  
g_1
```

##### q * s_w_d_f / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = ea_w,
            ea_f = ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )  
        s_w_d_f_tj <-  
          diag(s_w_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        obj <- 
          q[i] * s_w_d_f_tj[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q * s_w_d_f / (size_f * s_f_d_f)"
  )
g_1
```

##### all together

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = ea_w,
            ea_f = ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )  

        q_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f_tj
          )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        q_d_f <-  
            diag(q_d_f) %>% as.matrix()
        s_w_d_f_tj <-  
          diag(s_w_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        f <- equilibrium$endogenous[[t]][[j]]$f
        w <- equilibrium$endogenous[[t]][[j]]$w
        c_w <- 
          compute_supply_shock_c_w_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            lambda_w = equilibrium$parameter$lambda_w,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = ea_w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_w = equilibrium$endogenous[[t]][[j]]$s_w,
            owner = equilibrium$exogenous[[t]][[j]]$owner,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )
        obj <- 
          q[i] * s_w[i] /( s_f_d_f_tj[i] * size_f) +
          (
            q_d_f[i] * s_w[i] /( s_f_d_f_tj[i] * size_f) +
            q[i] * s_w_d_f_tj[i] /( s_f_d_f_tj[i] * size_f)
          ) * (f[i] - w[i] - c_w[i])
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f"
  )
g_1
```

## normal ths {.tabset}
### not eliciting demand shocks

```{r}
t <- 1
j <- 1
i <- 2
```

#### c_w
##### check s_w_d_w

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- s_w_d_w_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "s_w_d_w ths 1"
  ) +
  ylim(
    0, 
    max(objective_values$objective)
    )  
g_1

```

##### -s_w/s_w_d_w

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- 
        -s_w[i]/s_w_d_w_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "-s_w/s_w_d_w"
  ) +
  ylim(
    min(objective_values$objective),
    0
    )
g_1

```

##### all together

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      f <- equilibrium$endogenous[[t]][[j]]$f
      w <- equilibrium$endogenous[[t]][[j]]$w
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- 
        -s_w[i]/s_w_d_w_tj[i] + f[i] - w[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    size = 0.1
  ) +
  geom_line() +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w"
  )
g_1
```

#### c_f
##### check s_f_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        obj <- s_f_d_f_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "s_f_d_f"
  )+
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### check q_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
        s_f_d_f <- 
          solve_s_f_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_f = equilibrium$parameter$beta_f,
            lambda_f = param_value,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        meeting_number_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f
          )
        meeting_number_d_f <-  
            diag(meeting_number_d_f) %>% as.matrix()

        obj <- meeting_number_d_f[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q_d_f"
  )+
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### check s_w_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          ) 
        s_w_d_f_tj <-  
            diag(s_w_d_f_tj)

        obj <- s_w_d_f_tj[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "s_w_d_f"
  )
g_1

```

##### q * s_w / (size_f * s_f_d_f)

```{r}

target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        obj <- 
          q[i] * s_w[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q * s_w / (size_f * s_f_d_f)"
  ) +
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### q_d_f * s_w / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )

        q_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f_tj
          )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        q_d_f <-  
            diag(q_d_f) %>% as.matrix()
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        obj <- 
          q_d_f[i] * s_w[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_f_d_f_tj = s_f_d_f_tj[i],
          q_d_f = q_d_f[i]
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q_d_f * s_w / (size_f * s_f_d_f)"
  ) +
  ylim(
    0, 
    max(objective_values$objective)
    ) 
g_1
```

##### q * s_w_d_f / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )  
        s_w_d_f_tj <-  
          diag(s_w_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        obj <- 
          q[i] * s_w_d_f_tj[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q * s_w_d_f / (size_f * s_f_d_f)"
  )
g_1
```

##### all together

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )

        q_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f_tj
          )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        q_d_f <-  
            diag(q_d_f) %>% as.matrix()
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )  
        s_w_d_f_tj <-  
          diag(s_w_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        f <- equilibrium$endogenous[[t]][[j]]$f
        w <- equilibrium$endogenous[[t]][[j]]$w
        c_w <- 
            compute_supply_shock_c_w_tj(
              m_w = equilibrium$parameter$m_w,
              m_f = equilibrium$parameter$m_f,
              beta_w = equilibrium$parameter$beta_w,
              lambda_w = equilibrium$parameter$lambda_w,
              x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
              size_w = equilibrium$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium$exogenous[[t]][[j]]$size_f,
              mu = equilibrium$shock[[t]][[j]]$mu,
              ea_w = equilibrium$shock[[t]][[j]]$ea_w,
              f = equilibrium$endogenous[[t]][[j]]$f,
              w = equilibrium$endogenous[[t]][[j]]$w,
              s_f = equilibrium$endogenous[[t]][[j]]$s_f,
              s_w = equilibrium$endogenous[[t]][[j]]$s_w,
              owner = equilibrium$exogenous[[t]][[j]]$owner,
              method_s_w = equilibrium$constant$method_s_w,
              margin = equilibrium$constant$margin,
              quadrature_size = equilibrium$constant$quadrature_size,
              tol = equilibrium$constant$tol
            )
        obj <- 
          q[i] * s_w[i] /( s_f_d_f_tj[i] * size_f) +
          (
            q_d_f[i] * s_w[i] /( s_f_d_f_tj[i] * size_f) +
            q[i] * s_w_d_f_tj[i] /( s_f_d_f_tj[i] * size_f)
          ) * (f[i] - w[i] - c_w[i])
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f"
  )
g_1
```

### eliciting demand shocks
#### c_w
##### check s_w_d_w

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = param_value,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      beta_w <- equilibrium$parameter$beta_w
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
        
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- s_w_d_w_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "s_w_d_w ths 1"
  ) +
  ylim(
    0, 
    max(objective_values$objective)
    ) 
g_1

```

##### -s_w/s_w_d_w

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = param_value,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      beta_w <- equilibrium$parameter$beta_w
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
        
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- 
        -s_w[i]/s_w_d_w_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "-s_w/s_w_d_w"
  )  +
  ylim(
    -4e6,
    0
    )
g_1

```

##### all together

```{r}
target_list <- 
  list(
    lambda_w = 
      seq(
        0.05, 
        30,
        by = 0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = param_value,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      beta_w <- equilibrium$parameter$beta_w
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
        
      s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      f <- equilibrium$endogenous[[t]][[j]]$f
      w <- equilibrium$endogenous[[t]][[j]]$w
      s_w_d_w_tj <-  
          diag(s_w_d_w_tj)
      obj <- 
        -s_w[i]/s_w_d_w_tj[i] + f[i] - w[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    size = 0.1
  ) +
  geom_line() +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w"
  )
g_1
```

#### c_f
##### check s_f_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        obj <- s_f_d_f_tj[i]
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "s_f_d_f"
  ) +
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### check q_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      meeting_number_d_f <- 
        compute_meeting_number_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_f_d_f = s_f_d_f_tj
        )
        meeting_number_d_f <-  
            diag(meeting_number_d_f) %>% as.matrix()

        obj <- meeting_number_d_f[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q_d_f"
  ) +
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### check s_w_d_f

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()

        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = ea_w,
            ea_f = ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          ) 
        s_w_d_f_tj <-  
            diag(s_w_d_f_tj)

        obj <- s_w_d_f_tj[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "s_w_d_f"
  )
g_1

```

##### q * s_w / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      s_f_d_f_tj <-  
          diag(s_f_d_f_tj)
      q <- 
        compute_meeting_number_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        ) 
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      size_f <- equilibrium$exogenous[[t]][[j]]$size_f
      obj <- 
        q[i] * s_w[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q * s_w / (size_f * s_f_d_f)"
  )  +
  ylim(
    min(objective_values$objective),
    0
    )
g_1
```

##### q_d_f * s_w / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )

      q_d_f <- 
        compute_meeting_number_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_f_d_f = s_f_d_f_tj
        )
      s_f_d_f_tj <-  
          diag(s_f_d_f_tj)
      q_d_f <-  
          diag(q_d_f) %>% as.matrix()
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      size_f <- equilibrium$exogenous[[t]][[j]]$size_f
      obj <- 
        q_d_f[i] * s_w[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_f_d_f_tj = s_f_d_f_tj[i],
          q_d_f = q_d_f[i]
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q_d_f * s_w / (size_f * s_f_d_f)"
  ) +
  ylim(
    0, 
    max(objective_values$objective)
    )  
g_1
```

##### q * s_w_d_f / (size_f * s_f_d_f)

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = ea_w,
            ea_f = ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )  
        s_w_d_f_tj <-  
          diag(s_w_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        obj <- 
          q[i] * s_w_d_f_tj[i] /( s_f_d_f_tj[i] * size_f)
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "q * s_w_d_f / (size_f * s_f_d_f)"
  )
g_1
```

##### all together

```{r}
target_list <- 
  list(
    lambda_f = 
      seq(
        -0.5, 
        -30,
        by = -0.1
      )
  )

objective_values <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
      a_f <- 
        compute_demand_shock_a_f_tj_rcpp(
          m_f = equilibrium$parameter$m_f,
          m_w = equilibrium$parameter$m_w,
          lambda_f = param_value,
          mu = equilibrium$shock[[t]][[j]]$mu,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
      a_w <- 
        compute_demand_shock_nleqslv_a_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          lambda_w = equilibrium$parameter$lambda_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
      x_a_w <-  equilibrium$exogenous[[t]][[j]]$x_a_w
      x_a_f <-  equilibrium$exogenous[[t]][[j]]$x_a_f
      beta_w <- equilibrium$parameter$beta_w
      beta_f <- equilibrium$parameter$beta_f
      ea_w <-
        a_w - x_a_w %*% beta_w
      ea_w <-
        ea_w %>% as.matrix()
      
      ea_f <-
        a_f - x_a_f %*% beta_f
      ea_f <-
        ea_f %>% as.matrix()
      s_f_d_f_tj <- 
        solve_s_f_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_f = equilibrium$parameter$beta_f,
          lambda_f = param_value,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_f = ea_f,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        )
        s_w_d_f_tj <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = ea_w,
            ea_f = ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )  

        q_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f_tj
          )
        s_f_d_f_tj <-  
            diag(s_f_d_f_tj)
        q_d_f <-  
            diag(q_d_f) %>% as.matrix()
        s_w_d_f_tj <-  
          diag(s_w_d_f_tj)
        q <- 
          compute_meeting_number_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
        size_f <- equilibrium$exogenous[[t]][[j]]$size_f
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        f <- equilibrium$endogenous[[t]][[j]]$f
        w <- equilibrium$endogenous[[t]][[j]]$w
        c_w <- 
          compute_supply_shock_c_w_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            lambda_w = equilibrium$parameter$lambda_w,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = ea_w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_w = equilibrium$endogenous[[t]][[j]]$s_w,
            owner = equilibrium$exogenous[[t]][[j]]$owner,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )
        obj <- 
          q[i] * s_w[i] /( s_f_d_f_tj[i] * size_f) +
          (
            q_d_f[i] * s_w[i] /( s_f_d_f_tj[i] * size_f) +
            q[i] * s_w_d_f_tj[i] /( s_f_d_f_tj[i] * size_f)
          ) * (f[i] - w[i] - c_w[i])
      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_1 <-
  ggplot(
    objective_values, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point()  +
  geom_hline(
    yintercept = 0,
    color = "red"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f"
  )
g_1
```
