---
title: "report data analysis (use difference data)"
author: "Chiho Taniguchi"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 3, fig.width = 4)

library("magrittr")
library("kableExtra")
library("ggplot2")

height <- 6
width <- 8

```

```{r }
 
 data_cz_establishments <- 
   here::here(file = "output/data_cz_establishments.rds") %>% 
   readRDS()
 
 data_area_area_distance <- 
   here::here(file = "cleaned/data_area_area_distance.rds") %>% 
   readRDS()
 
 ## there are two establishments whose firm_id are NA in data_cz_establishments
 
 data_cz_establishments_distance <- 
   here::here(file = "output/data_cz_establishments_distance.rds") %>% 
   readRDS()
 
```

```{r}

data_cz_establishments_distance_na_10 <- 
  data_cz_establishments_distance %>% 
  tidyr::drop_na(
    distance_min_r
  ) %>% 
  dplyr::filter(
    year == 2010 
  ) %>% 
  dplyr::group_by(
    cz
  ) %>% 
  dplyr::mutate(
    N_j2010 = N_jt,
    n_j2010 = dplyr::n(),
    distance_min_avr_dropna_2010 = mean(distance_min_r),
    distance_min_med_dropna_2010 = stats::median(distance_min_r),
    distance_min_10_dropna_2010 = stats::quantile(distance_min_r, 0.1),
    distance_min_25_dropna_2010 = stats::quantile(distance_min_r, 0.25),
    distance_min_75_dropna_2010 = stats::quantile(distance_min_r, 0.75),
    distance_min_90_dropna_2010 = stats::quantile(distance_min_r, 0.9),
    wage_avr_2010 = mean(wage),
    fee_avr_2010 = mean(fee)
  ) %>% 
  dplyr::mutate(
    log_wage_avr_2010 = log(wage_avr_2010),
    log_fee_avr_2010 = log(fee_avr_2010)
  ) %>% 
  dplyr::select(
    cz,
    n_j2010,
    N_j2010,
    distance_min_avr_dropna_2010,
    distance_min_med_dropna_2010,
    distance_min_10_dropna_2010,
    distance_min_25_dropna_2010,
    distance_min_75_dropna_2010,
    distance_min_90_dropna_2010,
    log_wage_avr_2010,
    log_fee_avr_2010
  ) %>% 
  dplyr::distinct()

data_cz_establishments_distance_na_11 <- 
  data_cz_establishments_distance %>% 
  tidyr::drop_na(
    distance_min_r
  ) %>% 
  dplyr::filter(
    year == 2011 
  ) %>% 
  dplyr::group_by(
    cz
  ) %>% 
  dplyr::mutate(
    N_j2011 = N_jt,
    n_j2011 = dplyr::n(),
    distance_min_avr_dropna_2011 = mean(distance_min_r),
    wage_avr_2011 = mean(wage),
    fee_avr_2011 = mean(fee)
  ) %>% 
  dplyr::mutate(
    log_wage_avr_2011 = log(wage_avr_2011),
    log_fee_avr_2011 = log(fee_avr_2011)
  ) %>% 
  dplyr::select(
    cz,
    year,
    n_j2011,
    N_j2011,
    distance_min_avr_dropna_2011,
    log_wage_avr_2011,
    log_fee_avr_2011
  ) %>% 
  dplyr::distinct()

data_cz_establishments_distance_na_12 <- 
  data_cz_establishments_distance %>% 
  tidyr::drop_na(
    distance_min_r
  ) %>% 
  dplyr::filter(
    year == 2012 
  ) %>% 
  dplyr::group_by(
    cz
  ) %>% 
  dplyr::mutate(
    N_j2012 = N_jt,
    n_j2012 = dplyr::n(),
    distance_min_avr_dropna_2012 = mean(distance_min_r),
    wage_avr_2012 = mean(wage),
    fee_avr_2012 = mean(fee)
  ) %>% 
  dplyr::mutate(
    log_wage_avr_2012 = log(wage_avr_2012),
    log_fee_avr_2012 = log(fee_avr_2012)
  ) %>% 
  dplyr::select(
    cz,
    year,
    n_j2012,
    N_j2012,
    distance_min_avr_dropna_2012,
    log_wage_avr_2012,
    log_fee_avr_2012
  ) %>% 
  dplyr::distinct()

data_cz_establishments_distance_na_13 <- 
  data_cz_establishments_distance %>% 
  tidyr::drop_na(
    distance_min_r
  ) %>% 
  dplyr::filter(
    year == 2013 
  ) %>% 
  dplyr::group_by(
    cz
  ) %>% 
  dplyr::mutate(
    N_j2013 = N_jt,
    n_j2013 = dplyr::n(),
    distance_min_avr_dropna_2013 = mean(distance_min_r),
    wage_avr_2013 = mean(wage),
    fee_avr_2013 = mean(fee)
  ) %>% 
  dplyr::mutate(
    log_wage_avr_2013 = log(wage_avr_2013),
    log_fee_avr_2013 = log(fee_avr_2013)
  ) %>% 
  dplyr::select(
    cz,
    year,
    n_j2013,
    N_j2013,
    distance_min_avr_dropna_2013,
    log_wage_avr_2013,
    log_fee_avr_2013
  ) %>% 
  dplyr::distinct()
  
 data_cz_establishments_distance_na_14 <- 
  data_cz_establishments_distance %>% 
  tidyr::drop_na(
    distance_min_r
  ) %>% 
   dplyr::filter(
    year == 2014 
  ) %>% 
  dplyr::group_by(
    cz
  ) %>% 
  dplyr::mutate(
    N_j2014 = N_jt,
    n_j2014 = dplyr::n(),
    distance_min_avr_dropna_2014 = mean(distance_min_r),
    wage_avr_2014 = mean(wage),
    fee_avr_2014 = mean(fee)
  ) %>% 
   dplyr::mutate(
     log_wage_avr_2014 = log(wage_avr_2014),
     log_fee_avr_2014 = log(fee_avr_2014)
   ) %>% 
   dplyr::select(
    cz,
    year,
    N_j2014,
    n_j2014,
    distance_min_avr_dropna_2014,
    log_wage_avr_2014,
    log_fee_avr_2014
  ) %>% 
  dplyr::distinct()
 
 data_cz_establishments_distance_na_11_10 <- 
   dplyr::full_join(
     data_cz_establishments_distance_na_10,
     data_cz_establishments_distance_na_11,
     by = "cz"
   )
 
 data_cz_establishments_distance_na_11_10 <- 
   data_cz_establishments_distance_na_11_10 %>% 
   tidyr::drop_na(
     N_j2010,
     N_j2011,
     n_j2010,
     n_j2011,
     log_wage_avr_2010,
     log_wage_avr_2011,
     log_fee_avr_2010,
     log_fee_avr_2011,
     distance_min_avr_dropna_2010
   ) %>% 
   dplyr::mutate(
     N_j1110 = N_j2011 - N_j2010,
     n_j1110 = n_j2011 - n_j2010,
     log_wage_1110 = log_wage_avr_2011 - log_wage_avr_2010,
     log_fee_1110 = log_fee_avr_2011 - log_fee_avr_2010
   ) %>% 
   dplyr::mutate(
     distance_min_avr_dropna_2010_100000 = distance_min_avr_dropna_2010 / 100000,
     log_wage_diff = log_wage_1110,
     log_fee_diff = log_fee_1110,
     Nj_diff = N_j1110
   ) 
 
  data_cz_establishments_distance_na11 <- 
    data_cz_establishments_distance_na_11_10 %>% 
    dplyr::select(
      cz,
      year,
      log_wage_diff,
      log_fee_diff,
      Nj_diff,
      distance_min_avr_dropna_2010,
      distance_min_avr_dropna_2010_100000,
      distance_min_med_dropna_2010,
      distance_min_10_dropna_2010,
      distance_min_25_dropna_2010,
      distance_min_75_dropna_2010,
      distance_min_90_dropna_2010
    )
 
 
 data_cz_establishments_distance_na_12_10 <- 
   dplyr::full_join(
     data_cz_establishments_distance_na_10,
     data_cz_establishments_distance_na_12,
     by = "cz"
   )
 
 data_cz_establishments_distance_na_12_10 <- 
   data_cz_establishments_distance_na_12_10 %>% 
   tidyr::drop_na(
     N_j2010,
     N_j2012,
     n_j2010,
     n_j2012,
     log_wage_avr_2010,
     log_wage_avr_2012,
     log_fee_avr_2010,
     log_fee_avr_2012,
     distance_min_avr_dropna_2010
   ) %>% 
   dplyr::mutate(
     N_j1210 = N_j2012 - N_j2010,
     n_j1210 = n_j2012 - n_j2010,
     log_wage_1210 = log_wage_avr_2012 - log_wage_avr_2010,
     log_fee_1210 = log_fee_avr_2012 - log_fee_avr_2010
   ) %>% 
   dplyr::mutate(
     distance_min_avr_dropna_2010_100000 = distance_min_avr_dropna_2010 / 100000,
     log_wage_diff = log_wage_1210 / 2,
     log_fee_diff = log_fee_1210 / 2,
     Nj_diff = N_j1210 / 2
   )
 
 data_cz_establishments_distance_na12 <- 
    data_cz_establishments_distance_na_12_10 %>% 
    dplyr::select(
      cz,
      year,
      log_wage_diff,
      log_fee_diff,
      Nj_diff,
      distance_min_avr_dropna_2010,
      distance_min_avr_dropna_2010_100000,
      distance_min_med_dropna_2010,
      distance_min_10_dropna_2010,
      distance_min_25_dropna_2010,
      distance_min_75_dropna_2010,
      distance_min_90_dropna_2010
    )
 
 data_cz_establishments_distance_na_13_10 <- 
   dplyr::full_join(
     data_cz_establishments_distance_na_10,
     data_cz_establishments_distance_na_13,
     by = "cz"
   )
 
 data_cz_establishments_distance_na_13_10 <- 
   data_cz_establishments_distance_na_13_10 %>% 
   tidyr::drop_na(
     N_j2010,
     N_j2013,
     n_j2010,
     n_j2013,
     log_wage_avr_2010,
     log_wage_avr_2013,
     log_fee_avr_2010,
     log_fee_avr_2013,
     distance_min_avr_dropna_2010
   ) %>% 
   dplyr::mutate(
     N_j1310 = N_j2013 - N_j2010,
     n_j1310 = n_j2013 - n_j2010,
     log_wage_1310 = log_wage_avr_2013 - log_wage_avr_2010,
     log_fee_1310 = log_fee_avr_2013 - log_fee_avr_2010
   ) %>% 
   dplyr::mutate(
     distance_min_avr_dropna_2010_100000 = distance_min_avr_dropna_2010 / 100000,
     log_wage_diff = log_wage_1310 / 3,
     log_fee_diff = log_fee_1310 / 3,
     Nj_diff = N_j1310 / 3
   )
 
 data_cz_establishments_distance_na13 <- 
    data_cz_establishments_distance_na_13_10 %>% 
    dplyr::select(
      cz,
      year,
      log_wage_diff,
      log_fee_diff,
      Nj_diff,
      distance_min_avr_dropna_2010,
      distance_min_avr_dropna_2010_100000,
      distance_min_med_dropna_2010,
      distance_min_10_dropna_2010,
      distance_min_25_dropna_2010,
      distance_min_75_dropna_2010,
      distance_min_90_dropna_2010
    )
 
 data_cz_establishments_distance_na_14_10 <- 
   dplyr::full_join(
     data_cz_establishments_distance_na_10,
     data_cz_establishments_distance_na_14,
     by = "cz"
   )
 
 data_cz_establishments_distance_na_14_10 <- 
   data_cz_establishments_distance_na_14_10 %>% 
   tidyr::drop_na(
     N_j2010,
     N_j2014,
     n_j2010,
     n_j2014,
     log_wage_avr_2010,
     log_wage_avr_2014,
     log_fee_avr_2010,
     log_fee_avr_2014,
     distance_min_avr_dropna_2010
   ) %>% 
   dplyr::mutate(
     N_j1410 = N_j2014 - N_j2010,
     n_j1410 = n_j2014 - n_j2010,
     log_wage_1410 = log_wage_avr_2014 - log_wage_avr_2010,
     log_fee_1410 = log_fee_avr_2014 - log_fee_avr_2010
   ) %>% 
   dplyr::mutate(
     distance_min_avr_dropna_2010_100000 = distance_min_avr_dropna_2010 / 100000,
     log_wage_diff = log_wage_1410 / 4,
     log_fee_diff = log_fee_1410 / 4,
     Nj_diff = N_j1410 / 4
   )
 
 data_cz_establishments_distance_na14 <- 
    data_cz_establishments_distance_na_14_10 %>% 
    dplyr::select(
      cz,
      year,
      log_wage_diff,
      log_fee_diff,
      Nj_diff,
      distance_min_avr_dropna_2010,
      distance_min_avr_dropna_2010_100000,
      distance_min_med_dropna_2010,
      distance_min_10_dropna_2010,
      distance_min_25_dropna_2010,
      distance_min_75_dropna_2010,
      distance_min_90_dropna_2010
    )
 
 data_cz_establishments_distance_na_all <- 
   rbind(data_cz_establishments_distance_na11,
         data_cz_establishments_distance_na12) %>% 
   rbind(data_cz_establishments_distance_na13) %>% 
   rbind(data_cz_establishments_distance_na14)
 
 data_cz_establishments_distance_na_all <- 
   data_cz_establishments_distance_na_all %>% 
   dplyr::mutate(
     log_wage_diff_100 = log_wage_diff*100,
     log_fee_diff_100 = log_fee_diff*100,
     distance_min_avr_dropna_2010_1000 = distance_min_avr_dropna_2010 / 1000,
     margin = log_fee_diff - log_wage_diff,
     distance_min_med_dropna_2010_100000 = distance_min_med_dropna_2010 / 100000,
     distance_min_10_dropna_2010_100000 = distance_min_10_dropna_2010 / 100000,
     distance_min_25_dropna_2010_100000 = distance_min_25_dropna_2010 / 100000,
     distance_min_75_dropna_2010_100000 = distance_min_75_dropna_2010 / 100000,
     distance_min_90_dropna_2010_100000 = distance_min_90_dropna_2010 / 100000
   )
 
 
```



```{r}

binscatter_mean <- function(res, v, title){

  df = data_cz_establishments_distance_na_all
  
  
  fitted <- as.data.frame(res$fitted.values) 
  fitted <- set_colnames(x = fitted, value = c("fitted"))
  
  
  df <- 
    cbind(df,
          fitted) 
  
  residuals = df[,v] - df[, "fitted"] 
  
  residuals <- set_colnames(x = residuals, value = c("residuals"))
  
  df <- 
    cbind(df,
          residuals)
  
  df_mean <- 
    df %>% 
    dplyr::select(
      cz,
      distance_min_avr_dropna_2010_100000,
      residuals
      ) %>% 
    dplyr::distinct() %>%
    dplyr::arrange(
      cz
      ) 
  
  id_1 <- c(1:nrow(df_mean)) 
  
  df_mean <-
    cbind(
      id_1,
      df_mean
      ) %>% 
    dplyr::rename(
      num = "...1"
    )
  
num_groups <- 30
group_names <- paste0("Group ", 1:num_groups)

df_mean$group <- 
  cut(
    df_mean$num, 
    breaks = num_groups, 
    labels = group_names, 
    include.lowest = TRUE
    )

  df_mean <-
    df_mean %>% 
    dplyr::group_by(
      group
      ) %>% 
    dplyr::mutate(
      distance_min_avr_dropna_2010_100000_med = stats::median(distance_min_avr_dropna_2010_100000),
      residuals_avr = mean(residuals)
      ) %>% 
    dplyr::ungroup()
 
 df_mean_avr <- 
   df_mean %>% 
   dplyr::select(
     distance_min_avr_dropna_2010_100000_med,
     residuals_avr
   ) %>% 
   dplyr::distinct()
 
 g <- ggplot() +
   geom_point(
     data = df_mean_avr,
     mapping = aes(x = distance_min_avr_dropna_2010_100000_med, y = residuals_avr),
     size = 0.1
   ) +
   stat_smooth(
   method = "lm",
   data = df_mean_avr,
   mapping = aes(x = distance_min_avr_dropna_2010_100000_med, y = residuals_avr),
    se = FALSE,
    size = 0.1
   ) +
   xlab("distance_min_avr_dropna_2010_100000") +
   ylab("residuals") +　
   ggtitle(title) +
   theme_classic()
 
 print(g)
}



```

# use all years' data
全ての年度のデータを使用するため、Nj_diff =（N_jt ー N_j(2010)）/(t-2010)及び、log_wage_diff = （ln(wage)_jt ー ln(fee)_j(2010)）/(t-2010)、log_fee_diff（ln(fee)_jt ー ln(wage)_j(2010)）/(t-2010)を作成して回帰する。<b>
distance_min_avr_dropna_2010_100000は、kmを100で割った値。元データの距離の単位がメートルで、まず1000で除して、キロメートルに修正。その後、一括で100で割っている。

# mean

## summary of distance_min_avr_dropna_2010_100000
```{r}

summary(data_cz_establishments_distance_na_all$distance_min_avr_dropna_2010_100000)
```

```{r}

plot_average <- 
  data_cz_establishments_distance_na_all %>% 
  dplyr::filter(
    year == 2011
  ) %>% 
  dplyr::select(
    distance_min_avr_dropna_2010_100000,
    cz
  ) %>% 
  ggplot() +
  geom_histogram(
    aes(x = distance_min_avr_dropna_2010_100000),
    size = 0.5
  ) +
  labs(
    x = "mean"
    ) +
  theme_classic()

print(plot_average)


```

## first stage (mean)

```{r}

results <- list()
 
 results[[1]] <- 
   estimatr::lm_robust(
     formula = Nj_diff ~ distance_min_avr_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

```{r}

binscatter_mean(results[[1]], "Nj_diff", "mean first stage")

```

## reduced form (mean)

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_diff ~ distance_min_avr_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultr[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_diff ~ distance_min_avr_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
resultr[[3]] <- 
   estimatr::lm_robust(
     formula = margin ~ distance_min_avr_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

```{r}
binscatter_mean(resultr[[1]], "log_wage_diff", "mean wage reduced form")

```

```{r}
binscatter_mean(resultr[[2]], "log_fee_diff", "mean fee reduced form")
```

```{r}
binscatter_mean(resultr[[3]], "margin", "mean (fee - wage) reduced form")
```

## structural form (mean){.tabset}

### 2nd stage

```{r}

resultss <- list()

resultss[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | Nj_diff ~ distance_min_avr_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | Nj_diff ~ distance_min_avr_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | Nj_diff ~ distance_min_avr_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

results_s <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```
```{r}
binscatter_mean(resultss[[1]], "log_wage_diff", "mean wage structural form")
```

```{r}
binscatter_mean(resultss[[2]], "log_fee_diff", "mean wage structural form")
```

```{r}
binscatter_mean(resultss[[3]], "margin", "mean (fee - wage) structural form")
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultss[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# median
```{r}

binscatter_med <- function(res, v, title){

  df = data_cz_establishments_distance_na_all
  
  
  fitted <- as.data.frame(res$fitted.values) 
  fitted <- set_colnames(x = fitted, value = c("fitted"))
  
  
  df <- 
    cbind(df,
          fitted) 
  
  residuals = df[,v] - df[, "fitted"] 
  
  residuals <- set_colnames(x = residuals, value = c("residuals"))
  
  df <- 
    cbind(df,
          residuals)
  
  df_mean <- 
    df %>% 
    dplyr::select(
      cz,
      distance_min_med_dropna_2010_100000,
      residuals
      ) %>% 
    dplyr::distinct() %>%
    dplyr::arrange(
      cz
      ) 
  
  id_1 <- c(1:nrow(df_mean)) 
  
  df_mean <-
    cbind(
      id_1,
      df_mean
      ) %>% 
    dplyr::rename(
      num = "...1"
    )
  
num_groups <- 30
group_names <- paste0("Group ", 1:num_groups)

df_mean$group <- cut(df_mean$num, breaks = num_groups, labels = group_names, include.lowest = TRUE)

  df_mean <-
    df_mean %>% 
    dplyr::group_by(
      group
      ) %>% 
    dplyr::mutate(
      distance_min_med_dropna_2010_100000_med = stats::median(distance_min_med_dropna_2010_100000),
      residuals_avr = mean(residuals)
      ) %>% 
    dplyr::ungroup()
 
 df_mean_avr <- 
   df_mean %>% 
   dplyr::select(
     distance_min_med_dropna_2010_100000_med,
     residuals_avr
   ) %>% 
   dplyr::distinct()
 
 g <- ggplot() +
   geom_point(
     data = df_mean_avr,
     mapping = aes(x = distance_min_med_dropna_2010_100000_med, y = residuals_avr),
     size = 0.1
   ) +
   stat_smooth(
   method = "lm",
   data = df_mean_avr,
   mapping = aes(x = distance_min_med_dropna_2010_100000_med, y = residuals_avr),
    se = FALSE,
    size = 0.1
   ) +
   xlab("distance_min_med_dropna_2010_100000") +
   ylab("residuals") +　
   ggtitle(title) +
   theme_classic()
 
 print(g)
}


```

## summary of distance_min_med_dropna_2010_100000
```{r}

summary(data_cz_establishments_distance_na_all$distance_min_med_dropna_2010_100000)
```

```{r}

plot_med <- 
  data_cz_establishments_distance_na_all %>% 
  dplyr::filter(
    year == 2011
  ) %>% 
  dplyr::select(
    distance_min_med_dropna_2010_100000,
    cz
  ) %>% 
  ggplot() +
  geom_histogram(
    aes(x = distance_min_med_dropna_2010_100000),
    size = 0.5
  ) +
  labs(
    x = "median"
    ) +
  theme_classic()

print(plot_med)


```

## first stage (median)

```{r}

resultsmed <- list()
 
 resultsmed[[1]] <- 
   estimatr::lm_robust(
     formula = Nj_diff ~ distance_min_med_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 
 result <- 
   list(
     "Nj_diff" = resultsmed[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```
```{r}
binscatter_med(resultsmed[[1]], "Nj_diff", "median first stage")
```
## reduced form (median)

```{r}

resultrmed <- list()
 
 resultrmed[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_diff ~ distance_min_med_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultrmed[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_diff ~ distance_min_med_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultrmed[[3]] <- 
   estimatr::lm_robust(
     formula = margin ~ distance_min_med_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 result_r <- 
   list(
     "log_wage_diff" = resultrmed[[1]],
     "log_fee_diff" = resultrmed[[2]],
     "log_diff_fee - log_diff_wage" = resultrmed[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```
```{r}
binscatter_med(resultrmed[[1]], "log_wage_diff", "median wage reduced form")
```
```{r}
binscatter_med(resultrmed[[2]], "log_fee_diff", "median fee reduced form")
```

```{r}
binscatter_med(resultrmed[[3]], "margin", "median (fee - wage) reduced form")
```
## structural form (median){.tabset}

### 2nd stage

```{r}

resultssmed <- list()

resultssmed[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | Nj_diff ~ distance_min_med_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultssmed[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | Nj_diff ~ distance_min_med_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultssmed[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | Nj_diff ~ distance_min_med_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

results_s <- 
  list(
    "log_diff_wage" = resultssmed[[1]],
    "log_diff_fee" = resultssmed[[2]],
    "log_diff_fee - log_diff_wage" = resultssmed[[3]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```
```{r}
binscatter_med(resultssmed[[1]], "log_wage_diff", "median wage structural form")
```

```{r}
binscatter_med(resultssmed[[2]], "log_fee_diff", "median wage structural form")
```

```{r}
binscatter_med(resultssmed[[3]], "margin", "median (fee - wage) structural form")
```
### 1st stage

```{r}

modelsummary::modelsummary(
  resultssmed[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# 10 percentile

```{r}

binscatter_10 <- function(res, v, title){

  df = data_cz_establishments_distance_na_all
  
  
  fitted <- as.data.frame(res$fitted.values) 
  fitted <- set_colnames(x = fitted, value = c("fitted"))
  
  
  df <- 
    cbind(df,
          fitted) 
  
  residuals = df[,v] - df[, "fitted"] 
  
  residuals <- set_colnames(x = residuals, value = c("residuals"))
  
  df <- 
    cbind(df,
          residuals)
  
  df_mean <- 
    df %>% 
    dplyr::select(
      cz,
      distance_min_10_dropna_2010_100000,
      residuals
      ) %>% 
    dplyr::distinct() %>%
    dplyr::arrange(
      cz
      ) 
  
  id_1 <- c(1:nrow(df_mean)) 
  
  df_mean <-
    cbind(
      id_1,
      df_mean
      ) %>% 
    dplyr::rename(
      num = "...1"
    )
  
num_groups <- 30
group_names <- paste0("Group ", 1:num_groups)

df_mean$group <- cut(df_mean$num, breaks = num_groups, labels = group_names, include.lowest = TRUE)

  df_mean <-
    df_mean %>% 
    dplyr::group_by(
      group
      ) %>% 
    dplyr::mutate(
      distance_min_10_dropna_2010_100000_med = stats::median(distance_min_10_dropna_2010_100000),
      residuals_avr = mean(residuals)
      ) %>% 
    dplyr::ungroup()
 
 df_mean_avr <- 
   df_mean %>% 
   dplyr::select(
     distance_min_10_dropna_2010_100000_med,
     residuals_avr
   ) %>% 
   dplyr::distinct()
 
 g <- ggplot() +
   geom_point(
     data = df_mean_avr,
     mapping = aes(x = distance_min_10_dropna_2010_100000_med, y = residuals_avr),
     size = 0.1
   ) +
   stat_smooth(
   method = "lm",
   data = df_mean_avr,
   mapping = aes(x = distance_min_10_dropna_2010_100000_med, y = residuals_avr),
    se = FALSE,
    size = 0.1
   ) +
   xlab("distance_min_10_dropna_2010_100000") +
   ylab("residuals") +　
   ggtitle(title) +
   theme_classic()
 
 print(g)
}


```

## summary of distance_min_10_dropna_2010_100000

```{r}

summary(data_cz_establishments_distance_na_all$distance_min_10_dropna_2010_100000)
```

```{r}

plot_10 <- 
  data_cz_establishments_distance_na_all %>% 
  dplyr::filter(
    year == 2011
  ) %>% 
  dplyr::select(
    distance_min_10_dropna_2010_100000,
    cz
  ) %>% 
  ggplot() +
  geom_histogram(
    aes(x = distance_min_10_dropna_2010_100000),
    size = 0.5
  ) +
  labs(
    x = "10 pernentile"
    ) +
  theme_classic()

print(plot_10)


```


## first stage (10 percentile)

```{r}

results10 <- list()
 
 results10[[1]] <- 
   estimatr::lm_robust(
     formula = Nj_diff ~ distance_min_10_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 
 result <- 
   list(
     "Nj_diff" = results10[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```
```{r}
binscatter_10(results10[[1]], "Nj_diff", "10 percentile first stage")


```
## reduced form (10 percentile)

```{r}

resultr10 <- list()
 
 resultr10[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_diff ~ distance_min_10_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultr10[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_diff ~ distance_min_10_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultr10[[3]] <- 
   estimatr::lm_robust(
     formula = margin ~ distance_min_10_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 result_r <- 
   list(
     "log_wage_diff" = resultr10[[1]],
     "log_fee_diff" = resultr10[[2]],
     "log_diff_fee - log_diff_wage" = resultr10[[3]]
   )
 
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

```{r}
binscatter_10(resultr10[[1]], "log_wage_diff", "10 percentile wage reduced form")
```
```{r}
binscatter_10(resultr10[[2]], "log_fee_diff", "percentile fee reduced form")
```

```{r}
binscatter_10(resultr10[[3]], "margin", "percentile (fee - wage) reduced form")
```
## structural form (10 percentile){.tabset}

### 2nd stage

```{r}

resultss10 <- list()

resultss10[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | Nj_diff ~ distance_min_10_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss10[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | Nj_diff ~ distance_min_10_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss10[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | Nj_diff ~ distance_min_10_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

results_s <- 
  list(
    "log_diff_wage" = resultss10[[1]],
    "log_diff_fee" = resultss10[[2]],
    "log_diff_fee - log_diff_wage" = resultss10[[3]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

```{r}
binscatter_10(resultss10[[1]], "log_wage_diff", "10 percentile wage structural form")
```

```{r}
binscatter_10(resultss10[[2]], "log_fee_diff", "10 percentile wage structural form")
```

```{r}
binscatter_10(resultss10[[3]], "margin", "10 percentile (fee - wage) structural form")
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultss10[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```


# 25 percentile
```{r}

binscatter_25 <- function(res, v, title){

  df = data_cz_establishments_distance_na_all
  
  
  fitted <- as.data.frame(res$fitted.values) 
  fitted <- set_colnames(x = fitted, value = c("fitted"))
  
  
  df <- 
    cbind(df,
          fitted) 
  
  residuals = df[,v] - df[, "fitted"] 
  
  residuals <- set_colnames(x = residuals, value = c("residuals"))
  
  df <- 
    cbind(df,
          residuals)
  
  df_mean <- 
    df %>% 
    dplyr::select(
      cz,
      distance_min_25_dropna_2010_100000,
      residuals
      ) %>% 
    dplyr::distinct() %>%
    dplyr::arrange(
      cz
      ) 
  
  id_1 <- c(1:nrow(df_mean)) 
  
  df_mean <-
    cbind(
      id_1,
      df_mean
      ) %>% 
    dplyr::rename(
      num = "...1"
    )
  
num_groups <- 30
group_names <- paste0("Group ", 1:num_groups)

df_mean$group <- cut(df_mean$num, breaks = num_groups, labels = group_names, include.lowest = TRUE)

  df_mean <-
    df_mean %>% 
    dplyr::group_by(
      group
      ) %>% 
    dplyr::mutate(
      distance_min_25_dropna_2010_100000_med = stats::median(distance_min_25_dropna_2010_100000),
      residuals_avr = mean(residuals)
      ) %>% 
    dplyr::ungroup()
 
 df_mean_avr <- 
   df_mean %>% 
   dplyr::select(
     distance_min_25_dropna_2010_100000_med,
     residuals_avr
   ) %>% 
   dplyr::distinct()
 
 g <- ggplot() +
   geom_point(
     data = df_mean_avr,
     mapping = aes(x = distance_min_25_dropna_2010_100000_med, y = residuals_avr),
     size = 0.1
   ) +
   stat_smooth(
   method = "lm",
   data = df_mean_avr,
   mapping = aes(x = distance_min_25_dropna_2010_100000_med, y = residuals_avr),
    se = FALSE,
    size = 0.1
   ) +
   xlab("distance_min_25_dropna_2010_100000") +
   ylab("residuals") +　
   ggtitle(title) +
   theme_classic()
 
 print(g)
}


```

## summary of distance_min_25_dropna_2010_100000
```{r}

summary(data_cz_establishments_distance_na_all$distance_min_25_dropna_2010_100000)
```

```{r}

plot_25 <- 
  data_cz_establishments_distance_na_all %>% 
  dplyr::filter(
    year == 2011
  ) %>% 
  dplyr::select(
    distance_min_25_dropna_2010_100000,
    cz
  ) %>% 
  ggplot() +
  geom_histogram(
    aes(x = distance_min_25_dropna_2010_100000),
    size = 0.5
  ) +
  labs(
    x = "25 pernentile"
    ) +
  theme_classic()

print(plot_25)


```


## first stage (25 percentile)

```{r}

results25 <- list()
 
 results25[[1]] <- 
   estimatr::lm_robust(
     formula = Nj_diff ~ distance_min_25_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 
 result <- 
   list(
     "Nj_diff" = results25[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```
```{r}

binscatter_25(results25[[1]], "Nj_diff", "25 percentile first stage")
```
## reduced form (25 percentile)

```{r}

resultr25 <- list()
 
 resultr25[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_diff ~ distance_min_25_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultr25[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_diff ~ distance_min_25_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultr25[[3]] <- 
   estimatr::lm_robust(
     formula = margin ~ distance_min_25_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 result_r <- 
   list(
     "log_wage_diff" = resultr25[[1]],
     "log_fee_diff" = resultr25[[2]],
     "llog_diff_fee - log_diff_wage" = resultr25[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```
```{r}
binscatter_25(resultr25[[1]], "log_wage_diff", "25 percentile wage reduced form")
```

```{r}
binscatter_25(resultr25[[2]], "log_fee_diff", "25 percentile wage reduced form")
```

```{r}
binscatter_25(resultr25[[3]], "margin", "25 percentile (fee - wage) reduced form")
```
## structural form (25 percentile){.tabset}

### 2nd stage

```{r}

resultss25 <- list()

resultss25[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | Nj_diff ~ distance_min_25_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss25[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | Nj_diff ~ distance_min_25_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss25[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | Nj_diff ~ distance_min_25_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

results_s <- 
  list(
    "log_diff_wage" = resultss25[[1]],
    "log_diff_fee" = resultss25[[2]],
    "log_diff_fee - log_diff_wage" = resultss25[[3]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

```{r}
binscatter_25(resultss25[[1]], "log_wage_diff", "25 percentile wage structural form")
```

```{r}
binscatter_25(resultss25[[2]], "log_fee_diff", "25 percentile wage structural form")
```

```{r}
binscatter_25(resultss25[[3]], "margin", "25 percentile (fee - wage) structural form")
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultss25[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# 75 percentile

```{r}

binscatter_75 <- function(res, v, title){

  df = data_cz_establishments_distance_na_all
  
  
  fitted <- as.data.frame(res$fitted.values) 
  fitted <- set_colnames(x = fitted, value = c("fitted"))
  
  
  df <- 
    cbind(df,
          fitted) 
  
  residuals = df[,v] - df[, "fitted"] 
  
  residuals <- set_colnames(x = residuals, value = c("residuals"))
  
  df <- 
    cbind(df,
          residuals)
  
  df_mean <- 
    df %>% 
    dplyr::select(
      cz,
      distance_min_75_dropna_2010_100000,
      residuals
      ) %>% 
    dplyr::distinct() %>%
    dplyr::arrange(
      cz
      ) 
  
  id_1 <- c(1:nrow(df_mean)) 
  
  df_mean <-
    cbind(
      id_1,
      df_mean
      ) %>% 
    dplyr::rename(
      num = "...1"
    )
  
num_groups <- 30
group_names <- paste0("Group ", 1:num_groups)

df_mean$group <- cut(df_mean$num, breaks = num_groups, labels = group_names, include.lowest = TRUE)

  df_mean <-
    df_mean %>% 
    dplyr::group_by(
      group
      ) %>% 
    dplyr::mutate(
      distance_min_75_dropna_2010_100000_med = stats::median(distance_min_75_dropna_2010_100000),
      residuals_avr = mean(residuals)
      ) %>% 
    dplyr::ungroup()
 
 df_mean_avr <- 
   df_mean %>% 
   dplyr::select(
     distance_min_75_dropna_2010_100000_med,
     residuals_avr
   ) %>% 
   dplyr::distinct()
 
 g <- ggplot() +
   geom_point(
     data = df_mean_avr,
     mapping = aes(x = distance_min_75_dropna_2010_100000_med, y = residuals_avr),
     size = 0.1
   ) +
   stat_smooth(
   method = "lm",
   data = df_mean_avr,
   mapping = aes(x = distance_min_75_dropna_2010_100000_med, y = residuals_avr),
    se = FALSE,
    size = 0.1
   ) +
   xlab("distance_min_75_dropna_2010_100000") +
   ylab("residuals") +　
   ggtitle(title) +
   theme_classic()
 
 print(g)
}


```

## summary of distance_min_75_dropna_2010_100000

```{r}

summary(data_cz_establishments_distance_na_all$distance_min_75_dropna_2010_100000)
```

```{r}

plot_75 <- 
  data_cz_establishments_distance_na_all %>% 
  dplyr::filter(
    year == 2011
  ) %>% 
  dplyr::select(
    distance_min_75_dropna_2010_100000,
    cz
  ) %>% 
  ggplot() +
  geom_histogram(
    aes(x = distance_min_75_dropna_2010_100000),
    size = 0.5
  ) +
  labs(
    x = "75 pernentile"
    ) +
  theme_classic()

print(plot_75)


```

## first stage (75 percentile)

```{r}

results75 <- list()
 
 results75[[1]] <- 
   estimatr::lm_robust(
     formula = Nj_diff ~ distance_min_75_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 
 result <- 
   list(
     "Nj_diff" = results75[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```
```{r}

binscatter_75(results75[[1]], "Nj_diff", "75 percentile first stage")
```
## reduced form (75 percentile)

```{r}

resultr75 <- list()
 
 resultr75[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_diff ~ distance_min_75_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultr75[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_diff ~ distance_min_75_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultr75[[3]] <- 
   estimatr::lm_robust(
     formula = margin ~ distance_min_75_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 result_r <- 
   list(
     "log_wage_diff" = resultr75[[1]],
     "log_fee_diff" = resultr75[[2]],
     "log_diff_fee - log_diff_wage" = resultr75[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```
```{r}
binscatter_75(resultr75[[1]], "log_wage_diff", "75 percentile wage reduced form")
```

```{r}
binscatter_75(resultr75[[2]], "log_fee_diff", "75 percentile wage reduced form")
```

```{r}
binscatter_75(resultr75[[3]], "margin", "75 percentile (fee - wage) reduced form")
```
## structural form (75 percentile){.tabset}

### 2nd stage

```{r}

resultss75 <- list()

resultss75[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | Nj_diff ~ distance_min_75_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss75[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | Nj_diff ~ distance_min_75_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss75[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | Nj_diff ~ distance_min_75_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

results_s <- 
  list(
    "log_diff_wage" = resultss75[[1]],
    "log_diff_fee" = resultss75[[2]],
    "log_diff_fee - log_diff_wage" = resultss75[[3]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

```{r}
binscatter_75(resultss75[[1]], "log_wage_diff", "75 percentile wage structural form")
```

```{r}
binscatter_75(resultss75[[2]], "log_fee_diff", "75 percentile wage structural form")
```

```{r}
binscatter_75(resultss75[[3]], "margin", "75 percentile (fee - wage) structural form")
```
### 1st stage

```{r}

modelsummary::modelsummary(
  resultss75[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# 90 percentile

```{r}

binscatter_90 <- function(res, v, title){

  df = data_cz_establishments_distance_na_all
  
  
  fitted <- as.data.frame(res$fitted.values) 
  fitted <- set_colnames(x = fitted, value = c("fitted"))
  
  
  df <- 
    cbind(df,
          fitted) 
  
  residuals = df[,v] - df[, "fitted"] 
  
  residuals <- set_colnames(x = residuals, value = c("residuals"))
  
  df <- 
    cbind(df,
          residuals)
  
  df_mean <- 
    df %>% 
    dplyr::select(
      cz,
      distance_min_90_dropna_2010_100000,
      residuals
      ) %>% 
    dplyr::distinct() %>%
    dplyr::arrange(
      cz
      ) 
  
  id_1 <- c(1:nrow(df_mean)) 
  
  df_mean <-
    cbind(
      id_1,
      df_mean
      ) %>% 
    dplyr::rename(
      num = "...1"
    )
  
num_groups <- 30
group_names <- paste0("Group ", 1:num_groups)

df_mean$group <- cut(df_mean$num, breaks = num_groups, labels = group_names, include.lowest = TRUE)

  df_mean <-
    df_mean %>% 
    dplyr::group_by(
      group
      ) %>% 
    dplyr::mutate(
      distance_min_90_dropna_2010_100000_med = stats::median(distance_min_90_dropna_2010_100000),
      residuals_avr = mean(residuals)
      ) %>% 
    dplyr::ungroup()
 
 df_mean_avr <- 
   df_mean %>% 
   dplyr::select(
     distance_min_90_dropna_2010_100000_med,
     residuals_avr
   ) %>% 
   dplyr::distinct()
 
 g <- ggplot() +
   geom_point(
     data = df_mean_avr,
     mapping = aes(x = distance_min_90_dropna_2010_100000_med, y = residuals_avr),
     size = 0.1
   ) +
   stat_smooth(
   method = "lm",
   data = df_mean_avr,
   mapping = aes(x = distance_min_90_dropna_2010_100000_med, y = residuals_avr),
    se = FALSE,
    size = 0.1
   ) +
   xlab("distance_min_90_dropna_2010_100000") +
   ylab("residuals") +　
   ggtitle(title) +
   theme_classic()
 
 print(g)
}


```
## summary of distance_min_90_dropna_2010_100000

```{r}

summary(data_cz_establishments_distance_na_all$distance_min_90_dropna_2010_100000)
```

```{r}

plot_90 <- 
  data_cz_establishments_distance_na_all %>% 
  dplyr::filter(
    year == 2011
  ) %>% 
  dplyr::select(
    distance_min_90_dropna_2010_100000,
    cz
  ) %>% 
  ggplot() +
  geom_histogram(
    aes(x = distance_min_90_dropna_2010_100000),
    size = 0.5
  ) +
  labs(
    x = "90 pernentile"
    ) +
  theme_classic()

print(plot_90)


```

## first stage (90 percentile)

```{r}

results90 <- list()
 
 results90[[1]] <- 
   estimatr::lm_robust(
     formula = Nj_diff ~ distance_min_90_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 
 result <- 
   list(
     "Nj_diff" = results90[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

```{r}

binscatter_90(results90[[1]], "Nj_diff", "90 percentile first stage")

```

## reduced form (90 percentile)

```{r}

resultr90 <- list()
 
 resultr90[[1]] <- 
   estimatr::lm_robust(
     formula = log_wage_diff ~ distance_min_90_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )
 
 resultr90[[2]] <- 
   estimatr::lm_robust(
     formula = log_fee_diff ~ distance_min_90_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 resultr90[[3]] <- 
   estimatr::lm_robust(
     formula = margin ~ distance_min_90_dropna_2010_100000,
     se_type = "stata",
     data = data_cz_establishments_distance_na_all
   )

 result_r <- 
   list(
     "log_wage_diff" = resultr90[[1]],
     "log_fee_diff" = resultr90[[2]],
     "log_diff_wage - log_diff_fee" = resultr90[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```
```{r}
binscatter_90(resultr90[[1]], "log_wage_diff", "90 percentile wage reduced form")
```

```{r}
binscatter_90(resultr90[[2]], "log_fee_diff", "90 percentile wage reduced form")
```

```{r}
binscatter_90(resultr90[[3]], "margin", "90 percentile (fee - wage) reduced form")
```
## structural form (90 percentile){.tabset}

### 2nd stage

```{r}

resultss90 <- list()

resultss90[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | Nj_diff ~ distance_min_90_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss90[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | Nj_diff ~ distance_min_90_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

resultss90[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | Nj_diff ~ distance_min_90_dropna_2010_100000,
    data = data_cz_establishments_distance_na_all,
    se = "hetero"
  )

results_s <- 
  list(
    "log_diff_wage" = resultss90[[1]],
    "log_diff_fee" = resultss90[[2]],
    "log_diff_fee - log_diff_wage" = resultss90[[3]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

```{r}
binscatter_90(resultss90[[1]], "log_wage_diff", "90 percentile wage structural form")
```

```{r}
binscatter_90(resultss90[[2]], "log_fee_diff", "90 percentile wage structural form")
```

```{r}
binscatter_90(resultss90[[3]], "margin", "90 percentile (fee - wage) structural form")
```

### 1st stage

```{r}

modelsummary::modelsummary(
  resultss90[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```








