---
title: "report_data_counterfactual_monopoly_across_markets"
author: "Daisy Dan Song"
date: "2026-05-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
rm(list = ls())
library(Dispatching)
library(foreach)
library(magrittr)
library(codetools)
library(ggplot2)
library(kableExtra)
```

# import solved equilibrium
```{r}
equilibrium <-
  readRDS(
    file = "output/multihome/estimate_data/equilibrium_updated_constrained.rds" %>%
      here::here()
  )
updated_ownership <-
  readRDS(
    file = "output/multihome/make_equilibrium_nationwide_top5_from_data/updated_ownership_matrix.rds" %>%
      here::here()
  )

equilibrium$constant$use_exp <- FALSE
```

# update ownership
```{r}
for (
  t in seq_along(equilibrium$exogenous)
) {
  for (
    j in seq_along(equilibrium$exogenous[[t]])
  ) {
    equilibrium$exogenous[[t]][[j]]$owner <- updated_ownership[[t]][[j]]$owner
  }
}
```

# monopoly counterfactual setup
#
# Structural monopoly (instead of zeroing rival mu): rows 1–2 are part-time
# private and fringe; THS platforms start at row `ths_first_row` (3). The
# survivor is the THS row with the largest baseline `s_f`; rows 1–2 are never
# candidates (only `s_f[ths_first_row:nr, ]` is compared). Then drop other THSs
# and align exogenous, shock, and endogenous objects. Owner columns with no
# remaining platform are dropped.
```{r}
ths_first_row <- 3L

for (
  t in seq_along(equilibrium$exogenous)
) {
  for (
    j in seq_along(equilibrium$exogenous[[t]])
  ) {
    ex <-
      equilibrium$exogenous[[t]][[j]]
    nr <-
      nrow(ex$x_a_w)
    if (
      nr <= ths_first_row
    ) {
      next
    }
    ths <-
      ths_first_row:nr
    if (
      length(ths) <= 1L
    ) {
      next
    }
    own <-
      ex$owner
    end <-
      equilibrium$endogenous[[t]][[j]]
    # ths == ths_first_row:nr only; exclude part-time (row 1) and fringe (row 2).
    # `1L` is the column index of the single-column matrix s_f.
    s_sub <-
      end$s_f[ths, 1L, drop = TRUE]
    survivor <-
      ths[which.max(s_sub)]
    keep_rows <-
      c(
        1L,
        2L,
        survivor
      )
    ex$x_a_w <-
      ex$x_a_w[keep_rows, , drop = FALSE]
    ex$x_a_f <-
      ex$x_a_f[keep_rows, , drop = FALSE]
    ex$x_c_w <-
      ex$x_c_w[keep_rows, , drop = FALSE]
    ex$x_c_f <-
      ex$x_c_f[keep_rows, , drop = FALSE]
    own_k <-
      own[keep_rows, , drop = FALSE]
    keep_cols <-
      which(
        colSums(abs(own_k)) > 1e-10
      )
    if (
      length(keep_cols) == 0L
    ) {
      stop(
        "owner has no active columns after restricting to dominant THS"
      )
    }
    ex$owner <-
      own_k[, keep_cols, drop = FALSE]
    if (
      length(ex$size_w) == nr
    ) {
      ex$size_w <-
        ex$size_w[keep_rows]
    }
    if (
      length(ex$size_f) == nr
    ) {
      ex$size_f <-
        ex$size_f[keep_rows]
    }
    sh <-
      equilibrium$shock[[t]][[j]]
    for (
      nm in c("mu", "ea_w", "ea_f", "ec_w", "ec_f")
    ) {
      sh[[nm]] <-
        sh[[nm]][keep_rows, , drop = FALSE]
    }
    en <-
      equilibrium$endogenous[[t]][[j]]
    for (
      nm in c("w", "f", "s_w", "s_f")
    ) {
      en[[nm]] <-
        en[[nm]][keep_rows, , drop = FALSE]
    }
    equilibrium$exogenous[[t]][[j]] <-
      ex
    equilibrium$shock[[t]][[j]] <-
      sh
    equilibrium$endogenous[[t]][[j]] <-
      en
  }
}
```

# time
```{r}
# `solve_equilibrium_tj` returns the modified equilibrium; R does not update the
# caller's `equilibrium` object in place. Assign the return value back, or you
# will still see the pre-solve endogenous values on `equilibrium`.
system.time(
  equilibrium <-
    solve_equilibrium_tj(
      t = 1,
      j = 2,
      equilibrium = equilibrium,
      solver = "nleqslv",
      multistart = 20
    )
)
```

# run counterfactual for all markets
```{r}
# Same rule as `solve_equilibrium_tj`: use the returned object (`equilibrium_monopoly`);
# the argument `equilibrium` in the calling environment is not updated in place.
equilibrium_monopoly <-
  solve_equilibrium(
    equilibrium = equilibrium,
    solver = "nleqslv",
    multistart = 20
  )
```

```{r}
counterfactual <- 
  check_equilibrium(
    equilibrium = equilibrium_monopoly
  )
```

# counterfactual with monopoly market

### diagnostics
```{r}
counterfactual %>%
  dplyr::count(role)
```

### aggregate across markets
```{r}
role_levels <-
  c(
    "outside",
    "private",
    "fringe",
    "survivor_ths",
    "shutdown_ths"
  )

counterfactual_market_role <-
  counterfactual %>%
  dplyr::filter(role %in% role_levels) %>%
  dplyr::group_by(
    t,
    j,
    rival_mu,
    role
  ) %>%
  dplyr::summarise(
    w = mean(w, na.rm = TRUE),
    f = mean(f, na.rm = TRUE),
    m = mean(m, na.rm = TRUE),
    s_w = sum(s_w, na.rm = TRUE),
    s_f = sum(s_f, na.rm = TRUE),
    profit_ths = sum(profit_ths, na.rm = TRUE),
    surplus_w = sum(surplus_w, na.rm = TRUE),
    surplus_f = sum(surplus_f, na.rm = TRUE),
    foc_w = mean(foc_w, na.rm = TRUE),
    foc_f = mean(foc_f, na.rm = TRUE),
    foc_s_f = mean(foc_s_f, na.rm = TRUE),
    meeting_probability_w = mean(meeting_probability_w, na.rm = TRUE),
    meeting_probability_f = mean(meeting_probability_f, na.rm = TRUE),
    c_w = mean(c_w, na.rm = TRUE),
    c_f = mean(c_f, na.rm = TRUE),
    n_firms_in_role = dplyr::n(),
    .groups = "drop"
  )

counterfactual_aggregated <-
  counterfactual_market_role %>%
  dplyr::group_by(
    role,
    rival_mu
  ) %>%
  dplyr::summarise(
    w = mean(w, na.rm = TRUE),
    f = mean(f, na.rm = TRUE),
    m = mean(m, na.rm = TRUE),
    s_w = mean(s_w, na.rm = TRUE),
    s_f = mean(s_f, na.rm = TRUE),
    profit_ths = sum(profit_ths, na.rm = TRUE),
    surplus_w = sum(surplus_w, na.rm = TRUE),
    surplus_f = sum(surplus_f, na.rm = TRUE),
    foc_w = mean(foc_w, na.rm = TRUE),
    foc_f = mean(foc_f, na.rm = TRUE),
    foc_s_f = mean(foc_s_f, na.rm = TRUE),
    meeting_probability_w = mean(meeting_probability_w, na.rm = TRUE),
    meeting_probability_f = mean(meeting_probability_f, na.rm = TRUE),
    c_w = mean(c_w, na.rm = TRUE),
    c_f = mean(c_f, na.rm = TRUE),
    n_markets = dplyr::n(),
    avg_firms_in_role = mean(n_firms_in_role, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    role =
      factor(
        role,
        levels = role_levels
      )
  ) %>%
  dplyr::arrange(
    role,
    dplyr::desc(rival_mu)
  )

summary(counterfactual_aggregated)
```

### table
```{r, results = "asis"}
counterfactual_aggregated %>%
  dplyr::select(
    role,
    rival_mu,
    w,
    f,
    m,
    s_w,
    s_f,
    profit_ths,
    surplus_w,
    surplus_f,
    n_markets,
    avg_firms_in_role
  ) %>%
  kbl() %>%
  kable_styling()
```

### outside/private/fringe {.tabset}
```{r, results = "asis"}
outside_plot_data <-
  counterfactual_aggregated %>%
  dplyr::filter(
    role %in% c("outside", "private", "fringe")
  ) %>%
  dplyr::select(
    role,
    rival_mu,
    s_w,
    s_f,
    surplus_w,
    surplus_f
  ) %>%
  tidyr::pivot_longer(
    cols = c(
      s_w,
      s_f,
      surplus_w,
      surplus_f
    ),
    names_to = "variable",
    values_to = "value"
  )

outside_plot_data$variable <-
  factor(
    outside_plot_data$variable,
    levels = c(
      "s_w",
      "s_f",
      "surplus_w",
      "surplus_f"
    )
  )

p_outside <-
  ggplot(
    outside_plot_data,
    aes(
      x = rival_mu,
      y = value,
      color = role
    )
  ) +
  geom_line(linewidth = 0.7) +
  geom_point(size = 1.4) +
  scale_x_log10() +
  facet_wrap(
    ~ variable,
    scales = "free_y"
  ) +
  labs(
    title = "Outside, private, and fringe outcomes under monopoly counterfactual",
    subtitle = "Lower rival mu means non-surviving THS firms are more effectively shut down",
    x = "Rival THS matching efficiency (mu)",
    y = "Value",
    color = "Role"
  ) +
  theme_classic()

p_outside
```

### inside THS {.tabset}
```{r, results = "asis"}
inside_plot_data <-
  counterfactual_aggregated %>%
  dplyr::filter(
    role %in% c("survivor_ths", "shutdown_ths")
  ) %>%
  dplyr::select(
    role,
    rival_mu,
    w,
    f,
    m,
    s_w,
    s_f,
    profit_ths,
    surplus_w,
    surplus_f
  ) %>%
  tidyr::pivot_longer(
    cols = c(
      w,
      f,
      m,
      s_w,
      s_f,
      profit_ths,
      surplus_w,
      surplus_f
    ),
    names_to = "variable",
    values_to = "value"
  )

inside_plot_data$variable <-
  factor(
    inside_plot_data$variable,
    levels = c(
      "w",
      "f",
      "m",
      "s_w",
      "s_f",
      "profit_ths",
      "surplus_w",
      "surplus_f"
    )
  )

p_inside <-
  ggplot(
    inside_plot_data,
    aes(
      x = rival_mu,
      y = value,
      color = role
    )
  ) +
  geom_line(linewidth = 0.7) +
  geom_point(size = 1.4) +
  scale_x_log10() +
  facet_wrap(
    ~ variable,
    scales = "free_y"
  ) +
  labs(
    title = "THS outcomes under monopoly counterfactual",
    subtitle = "Survivor THS stays active while rival THS platforms have mu pushed toward zero",
    x = "Rival THS matching efficiency (mu)",
    y = "Value",
    color = "Role"
  ) +
  theme_classic()

p_inside
```
