---
title: "report_estimation_costs_parameter"
author: "Daisy Dan Song"
date: "2025-05-14"
output: html_document
---

# initialize
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )
rm(list = ls())
library(Dispatching)
library(foreach)
library(magrittr)
library(codetools)
library(ggplot2)
library(kableExtra)
library(purrr)
library(gridExtra)
library(doParallel)
registerDoParallel()
```

# import estimation equilibrium
```{r}
equilibrium <-
  readRDS(
    file = "output/multihome/estimate_data_initial/equilibrium_updated_initial.rds" %>%
    here::here()
  )

# prepare equilibrium for varying analysis of parameters
equilibrium_updated <- equilibrium

# prepare equilibrium for exact method
equilibrium_small <- equilibrium
```

# Clarify the issues

```{r}
start <- 0.1
end <- 5
step <- 0.3

target_list <- 
  list(
    lambda_w = 
      seq(
        start, 
        end, 
        by = step
      ),
    lambda_f = 
      seq(
        -start, 
        -end, 
        by = -step
      )
  )
```

## Use approximate method

### without updating demand shocks

```{r, cache=TRUE}
# c_w with varying lambda_w

obj_lambda_w_1 <- 
  foreach(
    param_value = target_list[[1]],
    iter = seq_along(target_list[[1]]),
    .combine = "cbind"
  ) %do% {
        
    c_w <-
      foreach(
        t = seq_along(equilibrium$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_w_t <- 
          foreach(
            j = seq_along(equilibrium$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            s_w_d_w <-
              solve_s_w_d_w_tj(
                m_w = equilibrium$parameter$m_w,
                m_f = equilibrium$parameter$m_f,
                beta_w = equilibrium$parameter$beta_w,
                lambda_w = param_value,
                x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium$exogenous[[t]][[j]]$size_f,
                mu = equilibrium$shock[[t]][[j]]$mu,
                ea_w = equilibrium$shock[[t]][[j]]$ea_w,
                w = equilibrium$endogenous[[t]][[j]]$w,
                s_f = equilibrium$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium$constant$method_s_w,
                margin = equilibrium$constant$margin,
                quadrature_size = equilibrium$constant$quadrature_size,
                tol = equilibrium$constant$tol
              ) 
            owner <- equilibrium$exogenous[[t]][[j]]$owner
            o <- t(owner) %*% owner
            f <- equilibrium$endogenous[[t]][[j]]$f
            w <- equilibrium$endogenous[[t]][[j]]$w
            s_w <- equilibrium$endogenous[[t]][[j]]$s_w
            b <- 
              (s_w_d_w * o) %*% (f - w) - s_w
            
            A <- s_w_d_w * o
            
            #ridge regularization
            cond_A <- kappa(A)
            
            # Threshold for acceptable conditioning (commonly 1e12)
            if (cond_A < 1e12) {
              condition_c_w <- "well-conditioned"
              # Well-conditioned: solve directly
              c_w_tj <- Matrix::solve(A, b)
            } else {
              # Ill-conditioned: use adaptive ridge regularization
              epsilon <- 1e-10
              condition_c_w <- "ill-conditioned"
              A_reg <- A + epsilon * diag(ncol(A))
              c_w_tj <- Matrix::solve(A_reg, b)
            }
            df_tj <- 
              data.frame(
                c_w = c_w_tj,
                i = 
                  seq(
                    1,
                    length(c_w_tj)
                  ),
                t = t,
                j = j,
                lambda_f = equilibrium$parameter$lambda_f,
                lambda_w = param_value,
                condition_c_w = condition_c_w
              ) %>% 
                setNames(
                    c(
                    paste0("c_w_", iter),
                    paste0("i_", iter),
                    paste0("t_", iter),
                    paste0("j_", iter),
                    paste0("lambda_f_", iter),
                    paste0("lambda_w_", iter),
                    paste0("condition_c_w_", iter)
                  )
                )
              return(df_tj)         
              }
        return(c_w_t)
      }
    return(c_w)
  }

max_cost_w_1 <- 
  obj_lambda_w_1 %>% 
  dplyr::select(
    starts_with("c_w")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_w = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_w
  )

df_w_1 <- 
  cbind(
    obj_lambda_w_1,
    max_cost_w_1
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_w
  )
```


```{r, cache=TRUE}
obj_lambda_f_1 <- 
  foreach(
    param_value = target_list[[2]],
    iter = seq_along(target_list[[2]]),
    .combine = "cbind"
  ) %do% {

    c_f <-
      foreach(
        t = seq_along(equilibrium$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_f_t <- 
          foreach(
            j = seq_along(equilibrium$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            c_w <- 
              compute_supply_shock_c_w_tj(
                m_w = equilibrium$parameter$m_w,
                m_f = equilibrium$parameter$m_f,
                beta_w = equilibrium$parameter$beta_w,
                lambda_w = equilibrium$parameter$lambda_w,
                x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium$exogenous[[t]][[j]]$size_f,
                mu = equilibrium$shock[[t]][[j]]$mu,
                ea_w = equilibrium$shock[[t]][[j]]$ea_w,
                f = equilibrium$endogenous[[t]][[j]]$f,
                w = equilibrium$endogenous[[t]][[j]]$w,
                s_f = equilibrium$endogenous[[t]][[j]]$s_f,
                s_w = equilibrium$endogenous[[t]][[j]]$s_w,
                owner = equilibrium$exogenous[[t]][[j]]$owner,
                method_s_w = equilibrium$constant$method_s_w,
                margin = equilibrium$constant$margin,
                quadrature_size = equilibrium$constant$quadrature_size,
                tol = equilibrium$constant$tol
              )
            s_f_d_f <- 
              solve_s_f_d_f_tj(
                m_w = equilibrium$parameter$m_w,
                m_f = equilibrium$parameter$m_f,
                beta_f = equilibrium$parameter$beta_f,
                lambda_f = param_value,
                x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
                size_w = equilibrium$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium$exogenous[[t]][[j]]$size_f,
                mu = equilibrium$shock[[t]][[j]]$mu,
                ea_f = equilibrium$shock[[t]][[j]]$ea_f,
                f = equilibrium$endogenous[[t]][[j]]$f,
                s_f = equilibrium$endogenous[[t]][[j]]$s_f
              )
            
            s_w_d_f <- 
              solve_s_w_d_f_tj(
                m_w = equilibrium$parameter$m_w,
                m_f = equilibrium$parameter$m_f,
                beta_w = equilibrium$parameter$beta_w,
                beta_f = equilibrium$parameter$beta_f,
                lambda_w = equilibrium$parameter$lambda_w,
                lambda_f = param_value,
                x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
                x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
                size_w = equilibrium$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium$exogenous[[t]][[j]]$size_f,
                mu = equilibrium$shock[[t]][[j]]$mu,
                ea_w = equilibrium$shock[[t]][[j]]$ea_w,
                ea_f = equilibrium$shock[[t]][[j]]$ea_f,
                w = equilibrium$endogenous[[t]][[j]]$w,
                f = equilibrium$endogenous[[t]][[j]]$f,
                s_f = equilibrium$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium$constant$method_s_w,
                margin = equilibrium$constant$margin,
                quadrature_size = equilibrium$constant$quadrature_size,
                tol = equilibrium$constant$tol
              ) 
            
          meeting_number <- 
            compute_meeting_number_tj(
              m_w = equilibrium$parameter$m_w,
              m_f = equilibrium$parameter$m_f,
              size_w = equilibrium$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium$exogenous[[t]][[j]]$size_f,
              mu = equilibrium$shock[[t]][[j]]$mu,
              s_f = equilibrium$endogenous[[t]][[j]]$s_f
            ) 
            
          meeting_number_d_f <- 
            compute_meeting_number_d_f_tj(
              m_w = equilibrium$parameter$m_w,
              m_f = equilibrium$parameter$m_f,
              size_w = equilibrium$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium$exogenous[[t]][[j]]$size_f,
              mu = equilibrium$shock[[t]][[j]]$mu,
              s_f = equilibrium$endogenous[[t]][[j]]$s_f,
              s_f_d_f = s_f_d_f
            ) 
          owner <- equilibrium$exogenous[[t]][[j]]$owner
          o <- t(owner) %*% owner
          f <- equilibrium$endogenous[[t]][[j]]$f
          w <- equilibrium$endogenous[[t]][[j]]$w
          s_w <- equilibrium$endogenous[[t]][[j]]$s_w
          size_f <- equilibrium$exogenous[[t]][[j]]$size_f
          
          b <-  meeting_number * s_w +
            (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
            (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
          
          A <-  (o * s_f_d_f) * size_f
          
          #ridge regularization
          cond_A <- kappa(A)
          
          # Threshold for acceptable conditioning (commonly 1e12)
          if (cond_A < 1e12) {
            condition_c_f <- "well-conditioned"
            c_f_tj <- Matrix::solve(A, b)
          } else {
            condition_c_f <- "ill-conditioned"
            epsilon <- 1e-10
            A_reg <- A + epsilon * diag(ncol(A))
            c_f_tj <- Matrix::solve(A_reg, b)
          }
          df_tj <- 
            data.frame(
              c_f = c_f_tj,
              i = 
                seq(
                  1,
                  length(c_f_tj)
                ),
              t = t,
              j = j,
              lambda_f = param_value,
              lambda_w = equilibrium$parameter$lambda_w,
              condition_c_f = condition_c_f
            ) %>% 
              setNames(
                  c(
                  paste0("c_f_", iter),
                  paste0("i_", iter),
                  paste0("t_", iter),
                  paste0("j_", iter),
                  paste0("lambda_f_", iter),
                  paste0("lambda_w_", iter),
                  paste0("condition_c_f_", iter)
                )
              )
          return(df_tj)          
              }
        return(c_f_t)
          }
    return(c_f)
  }

max_cost_f_1 <- 
  obj_lambda_f_1 %>% 
  dplyr::select(
    starts_with("c_f")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_f = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_f
  )

df_f_1 <- 
  cbind(
    obj_lambda_f_1,
    max_cost_f_1
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_f
  )
```

#### ths with negative costs

```{r, cache=TRUE}
df_1 <- 
  data.frame(
   max_cost_f = df_f_1$max_cost_f,
   max_cost_w = df_w_1$max_cost_w,
   t = df_w_1$t_1,
   j = df_w_1$j_1,
   i = df_w_1$i_1
  ) %>%
  dplyr::filter(
    max_cost_f < 0 | max_cost_w < 0
  )
head(df_1)
```

```{r}
total_market_num <- 
  df_f_1 %>%
  dplyr::distinct(
    t_1,
    j_1
  ) %>%
  nrow()

total_ths_num <- 
  df_f_1 %>%
  nrow()

count_market_c_f_1 <- 
  df_1 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_market_c_w_1 <- 
  df_1 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_ths_c_f_1 <- 
  df_1 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  nrow()

count_ths_c_w_1 <- 
  df_1 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  nrow()
```

### with updating demand shocks

```{r, cache=TRUE}
# c_w with varying lambda_w

obj_lambda_w_2 <- 
  foreach(
    param_value = target_list[[1]],
    iter = seq_along(target_list[[1]]),
    .combine = "cbind"
  ) %do% {
    equilibrium_updated$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_updated
      )
    equilibrium_updated <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_updated
      ) 
        
    c_w <-
      foreach(
        t = seq_along(equilibrium_updated$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_w_t <- 
          foreach(
            j = seq_along(equilibrium_updated$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            s_w_d_w <-
              solve_s_w_d_w_tj(
                m_w = equilibrium_updated$parameter$m_w,
                m_f = equilibrium_updated$parameter$m_f,
                beta_w = equilibrium_updated$parameter$beta_w,
                lambda_w = param_value,
                x_a_w = equilibrium_updated$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_updated$shock[[t]][[j]]$mu,
                ea_w = equilibrium_updated$shock[[t]][[j]]$ea_w,
                w = equilibrium_updated$endogenous[[t]][[j]]$w,
                s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium_updated$constant$method_s_w,
                margin = equilibrium_updated$constant$margin,
                quadrature_size = equilibrium_updated$constant$quadrature_size,
                tol = equilibrium_updated$constant$tol
              ) 
            owner <- equilibrium_updated$exogenous[[t]][[j]]$owner
            o <- t(owner) %*% owner
            f <- equilibrium_updated$endogenous[[t]][[j]]$f
            w <- equilibrium_updated$endogenous[[t]][[j]]$w
            s_w <- equilibrium_updated$endogenous[[t]][[j]]$s_w
            b <- 
              (s_w_d_w * o) %*% (f - w) - s_w
            
            A <- s_w_d_w * o
            
            #ridge regularization
            cond_A <- kappa(A)
            
            # Threshold for acceptable conditioning (commonly 1e12)
            if (cond_A < 1e12) {
              condition_c_w <- "well-conditioned"
              # Well-conditioned: solve directly
              c_w_tj <- Matrix::solve(A, b)
            } else {
              # Ill-conditioned: use adaptive ridge regularization
              epsilon <- 1e-10
              condition_c_w <- "ill-conditioned"
              A_reg <- A + epsilon * diag(ncol(A))
              c_w_tj <- Matrix::solve(A_reg, b)
            }
            df_tj <- 
              data.frame(
                c_w = c_w_tj,
                i = 
                  seq(
                    1,
                    length(c_w_tj)
                  ),
                t = t,
                j = j,
                lambda_f = equilibrium_updated$parameter$lambda_f,
                lambda_w = param_value,
                condition_c_w = condition_c_w
              ) %>% 
                setNames(
                    c(
                    paste0("c_w_", iter),
                    paste0("i_", iter),
                    paste0("t_", iter),
                    paste0("j_", iter),
                    paste0("lambda_f_", iter),
                    paste0("lambda_w_", iter),
                    paste0("condition_c_w_", iter)
                  )
                )
              return(df_tj)         
              }
        return(c_w_t)
      }
    return(c_w)
  }

max_cost_w_2 <- 
  obj_lambda_w_2 %>% 
  dplyr::select(
    starts_with("c_w")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_w = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_w
  )

df_w_2 <- 
  cbind(
    obj_lambda_w_2,
    max_cost_w_2
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_w
  )
```


```{r, cache=TRUE}

obj_lambda_f_2 <- 
  foreach(
    param_value = target_list[[2]],
    iter = seq_along(target_list[[2]]),
    .combine = "cbind"
  ) %do% {
    equilibrium_updated$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_updated
      )
    equilibrium_updated <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_updated
      ) 
    c_f <-
      foreach(
        t = seq_along(equilibrium_updated$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_f_t <- 
          foreach(
            j = seq_along(equilibrium_updated$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            c_w <- 
              compute_supply_shock_c_w_tj(
                m_w = equilibrium_updated$parameter$m_w,
                m_f = equilibrium_updated$parameter$m_f,
                beta_w = equilibrium_updated$parameter$beta_w,
                lambda_w = equilibrium_updated$parameter$lambda_w,
                x_a_w = equilibrium_updated$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_updated$shock[[t]][[j]]$mu,
                ea_w = equilibrium_updated$shock[[t]][[j]]$ea_w,
                f = equilibrium_updated$endogenous[[t]][[j]]$f,
                w = equilibrium_updated$endogenous[[t]][[j]]$w,
                s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f,
                s_w = equilibrium_updated$endogenous[[t]][[j]]$s_w,
                owner = equilibrium_updated$exogenous[[t]][[j]]$owner,
                method_s_w = equilibrium_updated$constant$method_s_w,
                margin = equilibrium_updated$constant$margin,
                quadrature_size = equilibrium_updated$constant$quadrature_size,
                tol = equilibrium_updated$constant$tol
              )
          s_f_d_f <- 
            solve_s_f_d_f_tj(
              m_w = equilibrium_updated$parameter$m_w,
              m_f = equilibrium_updated$parameter$m_f,
              beta_f = equilibrium_updated$parameter$beta_f,
              lambda_f = param_value,
              x_a_f = equilibrium_updated$exogenous[[t]][[j]]$x_a_f,
              size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
              mu = equilibrium_updated$shock[[t]][[j]]$mu,
              ea_f = equilibrium_updated$shock[[t]][[j]]$ea_f,
              f = equilibrium_updated$endogenous[[t]][[j]]$f,
              s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f
            )
          
          s_w_d_f <- 
            solve_s_w_d_f_tj(
              m_w = equilibrium_updated$parameter$m_w,
              m_f = equilibrium_updated$parameter$m_f,
              beta_w = equilibrium_updated$parameter$beta_w,
              beta_f = equilibrium_updated$parameter$beta_f,
              lambda_w = equilibrium_updated$parameter$lambda_w,
              lambda_f = param_value,
              x_a_w = equilibrium_updated$exogenous[[t]][[j]]$x_a_w,
              x_a_f = equilibrium_updated$exogenous[[t]][[j]]$x_a_f,
              size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
              mu = equilibrium_updated$shock[[t]][[j]]$mu,
              ea_w = equilibrium_updated$shock[[t]][[j]]$ea_w,
              ea_f = equilibrium_updated$shock[[t]][[j]]$ea_f,
              w = equilibrium_updated$endogenous[[t]][[j]]$w,
              f = equilibrium_updated$endogenous[[t]][[j]]$f,
              s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f,
              method_s_w = equilibrium_updated$constant$method_s_w,
              margin = equilibrium_updated$constant$margin,
              quadrature_size = equilibrium_updated$constant$quadrature_size,
              tol = equilibrium_updated$constant$tol
            ) 
          
        meeting_number <- 
          compute_meeting_number_tj(
            m_w = equilibrium_updated$parameter$m_w,
            m_f = equilibrium_updated$parameter$m_f,
            size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
            mu = equilibrium_updated$shock[[t]][[j]]$mu,
            s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f
          ) 
          
        meeting_number_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium_updated$parameter$m_w,
            m_f = equilibrium_updated$parameter$m_f,
            size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
            mu = equilibrium_updated$shock[[t]][[j]]$mu,
            s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f
          ) 
          owner <- equilibrium_updated$exogenous[[t]][[j]]$owner
          o <- t(owner) %*% owner
          f <- equilibrium_updated$endogenous[[t]][[j]]$f
          w <- equilibrium_updated$endogenous[[t]][[j]]$w
          s_w <- equilibrium_updated$endogenous[[t]][[j]]$s_w
          size_f <- equilibrium_updated$exogenous[[t]][[j]]$size_f
          
          b <-  meeting_number * s_w +
            (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
            (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
          
          A <-  (o * s_f_d_f) * size_f
          
          #ridge regularization
          cond_A <- kappa(A)
          
          # Threshold for acceptable conditioning (commonly 1e12)
          if (cond_A < 1e12) {
            condition_c_f <- "well-conditioned"
            c_f_tj <- Matrix::solve(A, b)
          } else {
            condition_c_f <- "ill-conditioned"
            epsilon <- 1e-10
            A_reg <- A + epsilon * diag(ncol(A))
            c_f_tj <- Matrix::solve(A_reg, b)
          }
          df_tj <- 
            data.frame(
              c_f = c_f_tj,
              i = 
                seq(
                  1,
                  length(c_f_tj)
                ),
              t = t,
              j = j,
              lambda_f = param_value,
              lambda_w = equilibrium_updated$parameter$lambda_w,
              condition_c_f = condition_c_f
            ) %>% 
              setNames(
                  c(
                  paste0("c_f_", iter),
                  paste0("i_", iter),
                  paste0("t_", iter),
                  paste0("j_", iter),
                  paste0("lambda_f_", iter),
                  paste0("lambda_w_", iter),
                  paste0("condition_c_f_", iter)
                )
              )
          return(df_tj)          
              }
        return(c_f_t)
          }
    return(c_f)
  }

max_cost_f_2 <- 
  obj_lambda_f_2 %>% 
  dplyr::select(
    starts_with("c_f")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_f = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_f
  )

df_f_2 <- 
  cbind(
    obj_lambda_f_2,
    max_cost_f_2
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_f
  )
```

#### ths with negative costs
```{r, cache=TRUE}
df_2 <- 
  data.frame(
   max_cost_f = df_f_2$max_cost_f,
   max_cost_w = df_w_2$max_cost_w,
   t = df_w_2$t_1,
   j = df_w_2$j_1,
   i = df_w_2$i_1
  ) %>%
  dplyr::filter(
    max_cost_f < 0 | max_cost_w < 0
  )
head(df_2)
```

```{r}
count_market_c_f_2 <- 
  df_2 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_market_c_w_2 <- 
  df_2 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_ths_c_f_2 <- 
  df_2 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  nrow()

count_ths_c_w_2 <- 
  df_2 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  nrow()
```

- In the estimation, we cannot find the parameters that make some costs positive for any lambda_w and lambda_f.
  - How many markets show this problem? 
    - Without updating demand shocks, only `r count_market_c_w_1` market out of `r total_market_num` for c_w, `r count_market_c_f_1` market out of `r total_market_num` for c_f
    - With updating demand shocks, `r count_market_c_w_2` market out of `r total_market_num`  for c_w, `r count_market_c_f_2` market out of `r total_market_num` for c_f 
    
  - How many ths show this problem?  
    - Without updating demand shocks, only `r count_ths_c_w_1` ths out of `r total_ths_num` for c_w, `r count_ths_c_f_1` ths out of `r total_ths_num` for c_f
    - With updating demand shocks, `r count_ths_c_w_2` ths out of `r total_ths_num`  for c_w, `r count_ths_c_f_2` ths out of `r total_ths_num` for c_f 


## Use exact method

```{r}
method_s_w <- "exact"
```

- delete large markets
```{r}
num_ths <- 
  foreach(
    t = seq_along(equilibrium$endogenous),
    .combine = "rbind"
  ) %do% {
    foreach(
      j = seq_along(equilibrium$endogenous[[t]]),
    .combine = "rbind"
    ) %do% {
      num <- length(equilibrium$endogenous[[t]][[j]]$w)
      return(
        data.frame(
          t = t,
          j = j,
          num = num
        )
      )
    }
  }

small_market <- 
  num_ths %>%
  dplyr::filter(
    num < 5
  )
```

### without updating demand shocks

```{r, cache=TRUE}
# c_w with varying lambda_w

obj_lambda_w_3 <- 
  foreach(
    param_value = target_list[[1]],
    iter = seq_along(target_list[[1]]),
    .combine = "cbind"
  ) %do% {
        
    c_w <-
      foreach(
        m = 
          seq(
            1,
            nrow(small_market)
          ),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        t <- small_market$t[m]
        j <- small_market$j[m]
        s_w_d_w <-
          solve_s_w_d_w_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            lambda_w = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            w = equilibrium$endogenous[[t]][[j]]$w,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          ) 
        owner <- equilibrium$exogenous[[t]][[j]]$owner
        o <- t(owner) %*% owner
        f <- equilibrium$endogenous[[t]][[j]]$f
        w <- equilibrium$endogenous[[t]][[j]]$w
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        b <- 
          (s_w_d_w * o) %*% (f - w) - s_w
        
        A <- s_w_d_w * o
        
        #ridge regularization
        cond_A <- kappa(A)
        
        # Threshold for acceptable conditioning (commonly 1e12)
        if (cond_A < 1e12) {
          condition_c_w <- "well-conditioned"
          # Well-conditioned: solve directly
          c_w_tj <- Matrix::solve(A, b)
        } else {
          # Ill-conditioned: use adaptive ridge regularization
          epsilon <- 1e-10
          condition_c_w <- "ill-conditioned"
          A_reg <- A + epsilon * diag(ncol(A))
          c_w_tj <- Matrix::solve(A_reg, b)
        }
        df_tj <- 
          data.frame(
            c_w = c_w_tj,
            i = 
              seq(
                1,
                length(c_w_tj)
              ),
            t = t,
            j = j,
            lambda_f = equilibrium$parameter$lambda_f,
            lambda_w = param_value,
            condition_c_w = condition_c_w
          ) %>% 
            setNames(
                c(
                paste0("c_w_", iter),
                paste0("i_", iter),
                paste0("t_", iter),
                paste0("j_", iter),
                paste0("lambda_f_", iter),
                paste0("lambda_w_", iter),
                paste0("condition_c_w_", iter)
              )
            )
          return(df_tj)         
      }
    return(c_w)
  }

max_cost_w_3 <- 
  obj_lambda_w_3 %>% 
  dplyr::select(
    starts_with("c_w")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_w = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_w
  )

df_w_3 <- 
  cbind(
    obj_lambda_w_3,
    max_cost_w_3
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_w
  )
```


```{r, cache=TRUE}

obj_lambda_f_3 <- 
  foreach(
    param_value = target_list[[2]],
    iter = seq_along(target_list[[2]]),
    .combine = "cbind"
  ) %do% {

    c_f <-
      foreach(
        m = 
          seq(
            1,
            nrow(small_market)
          ),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        t <- small_market$t[m]
        j <- small_market$j[m]
        c_w <- 
          compute_supply_shock_c_w_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            lambda_w = equilibrium$parameter$lambda_w,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_w = equilibrium$endogenous[[t]][[j]]$s_w,
            owner = equilibrium$exogenous[[t]][[j]]$owner,
            method_s_w = method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )
        s_f_d_f <- 
          solve_s_f_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_f = equilibrium$parameter$beta_f,
            lambda_f = param_value,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          )
        
        s_w_d_f <- 
          solve_s_w_d_f_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          ) 
        
      meeting_number <- 
        compute_meeting_number_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        ) 
        
      meeting_number_d_f <- 
        compute_meeting_number_d_f_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_f_d_f = s_f_d_f
        ) 
      owner <- equilibrium$exogenous[[t]][[j]]$owner
      o <- t(owner) %*% owner
      f <- equilibrium$endogenous[[t]][[j]]$f
      w <- equilibrium$endogenous[[t]][[j]]$w
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      size_f <- equilibrium$exogenous[[t]][[j]]$size_f
      
      b <-  meeting_number * s_w +
        (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
        (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
      
      A <-  (o * s_f_d_f) * size_f
      
      #ridge regularization
      cond_A <- kappa(A)
      
      # Threshold for acceptable conditioning (commonly 1e12)
      if (cond_A < 1e12) {
        condition_c_f <- "well-conditioned"
        c_f_tj <- Matrix::solve(A, b)
      } else {
        condition_c_f <- "ill-conditioned"
        epsilon <- 1e-10
        A_reg <- A + epsilon * diag(ncol(A))
        c_f_tj <- Matrix::solve(A_reg, b)
      }
      df_tj <- 
        data.frame(
          c_f = c_f_tj,
          i = 
            seq(
              1,
              length(c_f_tj)
            ),
          t = t,
          j = j,
          lambda_f = param_value,
          lambda_w = equilibrium$parameter$lambda_w,
          condition_c_f = condition_c_f
        ) %>% 
          setNames(
              c(
              paste0("c_f_", iter),
              paste0("i_", iter),
              paste0("t_", iter),
              paste0("j_", iter),
              paste0("lambda_f_", iter),
              paste0("lambda_w_", iter),
              paste0("condition_c_f_", iter)
            )
          )
      return(df_tj)          
          }
    return(c_f)
  }

max_cost_f_3 <- 
  obj_lambda_f_3 %>% 
  dplyr::select(
    starts_with("c_f")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_f = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_f
  )

df_f_3 <- 
  cbind(
    obj_lambda_f_3,
    max_cost_f_3
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_f
  )
```

#### ths with negative costs

```{r}
df_3 <- 
  data.frame(
   max_cost_f = df_f_3$max_cost_f,
   max_cost_w = df_w_3$max_cost_w,
   t = df_w_3$t_1,
   j = df_w_3$j_1,
   i = df_w_3$i_1
  ) %>%
  dplyr::filter(
    max_cost_f < 0 | max_cost_w < 0
  )
head(df_3)
```

```{r}
total_market_num_exact <- 
  df_f_3 %>%
  dplyr::distinct(
    t_1,
    j_1
  ) %>%
  nrow()

total_ths_num_exact <- 
  df_f_3 %>%
  nrow()

count_market_c_f_3 <- 
  df_3 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_market_c_w_3 <- 
  df_3 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_ths_c_f_3 <- 
  df_3 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  nrow()

count_ths_c_w_3 <- 
  df_3 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  nrow()
```

### with updating demand shocks

```{r}
# discard large markets
large_market <- 
  num_ths %>%
  dplyr::filter(
    num >= 5
  )

large_market <- 
  large_market[
    order(
      large_market$t,
      large_market$j,
      decreasing = TRUE
    ), 
  ]
for (
  i in 1:nrow(large_market)
) {
  equilibrium_small$shock[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$endogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$exogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
}

equilibrium_small$constant$method_s_w <- "exact"
```

```{r, cache=TRUE}

obj_lambda_w_4 <- 
  foreach(
    param_value = target_list[[1]],
    iter = seq_along(target_list[[1]]),
    .combine = "cbind"
  ) %do% {
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
        
    c_w <-
      foreach(
        t = seq_along(equilibrium_small$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_w_t <- 
          foreach(
            j = seq_along(equilibrium_small$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            s_w_d_w <-
              solve_s_w_d_w_tj(
                m_w = equilibrium_small$parameter$m_w,
                m_f = equilibrium_small$parameter$m_f,
                beta_w = equilibrium_small$parameter$beta_w,
                lambda_w = equilibrium_small$parameter$lambda_w,
                x_a_w = equilibrium_small$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_small$shock[[t]][[j]]$mu,
                ea_w = equilibrium_small$shock[[t]][[j]]$ea_w,
                w = equilibrium_small$endogenous[[t]][[j]]$w,
                s_f = equilibrium_small$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium_small$constant$method_s_w,
                margin = equilibrium_small$constant$margin,
                quadrature_size = equilibrium_small$constant$quadrature_size,
                tol = equilibrium_small$constant$tol
              ) 
            owner <- equilibrium_small$exogenous[[t]][[j]]$owner
            o <- t(owner) %*% owner
            f <- equilibrium_small$endogenous[[t]][[j]]$f
            w <- equilibrium_small$endogenous[[t]][[j]]$w
            s_w <- equilibrium_small$endogenous[[t]][[j]]$s_w
            b <- 
              (s_w_d_w * o) %*% (f - w) - s_w
            
            A <- s_w_d_w * o
            
            #ridge regularization
            cond_A <- kappa(A)
            
            # Threshold for acceptable conditioning (commonly 1e12)
            if (cond_A < 1e12) {
              condition_c_w <- "well-conditioned"
              # Well-conditioned: solve directly
              c_w_tj <- Matrix::solve(A, b)
            } else {
              # Ill-conditioned: use adaptive ridge regularization
              epsilon <- 1e-10
              condition_c_w <- "ill-conditioned"
              A_reg <- A + epsilon * diag(ncol(A))
              c_w_tj <- Matrix::solve(A_reg, b)
            }
            df_tj <- 
              data.frame(
                c_w = c_w_tj,
                i = 
                  seq(
                    1,
                    length(c_w_tj)
                  ),
                t = t,
                j = j,
                lambda_f = equilibrium_small$parameter$lambda_f,
                lambda_w = param_value,
                condition_c_w = condition_c_w
              ) %>% 
                setNames(
                    c(
                    paste0("c_w_", iter),
                    paste0("i_", iter),
                    paste0("t_", iter),
                    paste0("j_", iter),
                    paste0("lambda_f_", iter),
                    paste0("lambda_w_", iter),
                    paste0("condition_c_w_", iter)
                  )
                )
            return(df_tj)         
          }
        return(c_w_t)
      }
    return(c_w)
  }

max_cost_w_4 <- 
  obj_lambda_w_4 %>% 
  dplyr::select(
    starts_with("c_w")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_w = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_w
  )

df_w_4 <- 
  cbind(
    obj_lambda_w_4,
    max_cost_w_4
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_w
  )
```


```{r, cache=TRUE}
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
obj_lambda_f_4 <- 
  foreach(
    param_value = target_list[[2]],
    iter = seq_along(target_list[[2]]),
    .combine = "cbind"
  ) %do% {
    equilibrium_small$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    
    c_f <-
      foreach(
        t = seq_along(equilibrium_small$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_f_t <- 
          foreach(
            j = seq_along(equilibrium_small$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            c_w <- 
              compute_supply_shock_c_w_tj(
                m_w = equilibrium_small$parameter$m_w,
                m_f = equilibrium_small$parameter$m_f,
                beta_w = equilibrium_small$parameter$beta_w,
                lambda_w = equilibrium_small$parameter$lambda_w,
                x_a_w = equilibrium_small$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_small$shock[[t]][[j]]$mu,
                ea_w = equilibrium_small$shock[[t]][[j]]$ea_w,
                f = equilibrium_small$endogenous[[t]][[j]]$f,
                w = equilibrium_small$endogenous[[t]][[j]]$w,
                s_f = equilibrium_small$endogenous[[t]][[j]]$s_f,
                s_w = equilibrium_small$endogenous[[t]][[j]]$s_w,
                owner = equilibrium_small$exogenous[[t]][[j]]$owner,
                method_s_w = equilibrium_small$constant$method_s_w,
                margin = equilibrium_small$constant$margin,
                quadrature_size = equilibrium_small$constant$quadrature_size,
                tol = equilibrium_small$constant$tol
              )
            s_f_d_f <- 
              solve_s_f_d_f_tj(
                m_w = equilibrium_small$parameter$m_w,
                m_f = equilibrium_small$parameter$m_f,
                beta_f = equilibrium_small$parameter$beta_f,
                lambda_f = param_value,
                x_a_f = equilibrium_small$exogenous[[t]][[j]]$x_a_f,
                size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_small$shock[[t]][[j]]$mu,
                ea_f = equilibrium_small$shock[[t]][[j]]$ea_f,
                f = equilibrium_small$endogenous[[t]][[j]]$f,
                s_f = equilibrium_small$endogenous[[t]][[j]]$s_f
              )
            
            s_w_d_f <- 
              solve_s_w_d_f_tj(
                m_w = equilibrium_small$parameter$m_w,
                m_f = equilibrium_small$parameter$m_f,
                beta_w = equilibrium_small$parameter$beta_w,
                beta_f = equilibrium_small$parameter$beta_f,
                lambda_w = equilibrium_small$parameter$lambda_w,
                lambda_f = param_value,
                x_a_w = equilibrium_small$exogenous[[t]][[j]]$x_a_w,
                x_a_f = equilibrium_small$exogenous[[t]][[j]]$x_a_f,
                size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_small$shock[[t]][[j]]$mu,
                ea_w = equilibrium_small$shock[[t]][[j]]$ea_w,
                ea_f = equilibrium_small$shock[[t]][[j]]$ea_f,
                w = equilibrium_small$endogenous[[t]][[j]]$w,
                f = equilibrium_small$endogenous[[t]][[j]]$f,
                s_f = equilibrium_small$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium_small$constant$method_s_w,
                margin = equilibrium_small$constant$margin,
                quadrature_size = equilibrium_small$constant$quadrature_size,
                tol = equilibrium_small$constant$tol
              ) 
            
          meeting_number <- 
            compute_meeting_number_tj(
              m_w = equilibrium_small$parameter$m_w,
              m_f = equilibrium_small$parameter$m_f,
              size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
              mu = equilibrium_small$shock[[t]][[j]]$mu,
              s_f = equilibrium_small$endogenous[[t]][[j]]$s_f
            ) 
            
          meeting_number_d_f <- 
            compute_meeting_number_d_f_tj(
              m_w = equilibrium_small$parameter$m_w,
              m_f = equilibrium_small$parameter$m_f,
              size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
              mu = equilibrium_small$shock[[t]][[j]]$mu,
              s_f = equilibrium_small$endogenous[[t]][[j]]$s_f,
              s_f_d_f = s_f_d_f
            ) 
          owner <- equilibrium_small$exogenous[[t]][[j]]$owner
          o <- t(owner) %*% owner
          f <- equilibrium_small$endogenous[[t]][[j]]$f
          w <- equilibrium_small$endogenous[[t]][[j]]$w
          s_w <- equilibrium_small$endogenous[[t]][[j]]$s_w
          size_f <- equilibrium_small$exogenous[[t]][[j]]$size_f
          
          b <-  meeting_number * s_w +
            (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
            (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
          
          A <-  (o * s_f_d_f) * size_f
          
          #ridge regularization
          cond_A <- kappa(A)
          
          # Threshold for acceptable conditioning (commonly 1e12)
          if (cond_A < 1e12) {
            condition_c_f <- "well-conditioned"
            c_f_tj <- Matrix::solve(A, b)
          } else {
            condition_c_f <- "ill-conditioned"
            epsilon <- 1e-10
            A_reg <- A + epsilon * diag(ncol(A))
            c_f_tj <- Matrix::solve(A_reg, b)
          }
          df_tj <- 
            data.frame(
              c_f = c_f_tj,
              i = 
                seq(
                  1,
                  length(c_f_tj)
                ),
              t = t,
              j = j,
              lambda_f = param_value,
              lambda_w = equilibrium_small$parameter$lambda_w,
              condition_c_f = condition_c_f
            ) %>% 
              setNames(
                  c(
                  paste0("c_f_", iter),
                  paste0("i_", iter),
                  paste0("t_", iter),
                  paste0("j_", iter),
                  paste0("lambda_f_", iter),
                  paste0("lambda_w_", iter),
                  paste0("condition_c_f_", iter)
                )
              )
          return(df_tj)          
          }
        return(c_f_t)
      }
    return(c_f)
  }

max_cost_f_4 <- 
  obj_lambda_f_4 %>% 
  dplyr::select(
    starts_with("c_f")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_f = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_f
  )

df_f_4 <- 
  cbind(
    obj_lambda_f_4,
    max_cost_f_4
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_f
  )
```

#### ths with negative costs

```{r}
df_4 <- 
  data.frame(
   max_cost_f = df_f_4$max_cost_f,
   max_cost_w = df_w_4$max_cost_w,
   t = df_w_4$t_1,
   j = df_w_4$j_1,
   i = df_w_4$i_1
  ) %>%
  dplyr::filter(
    max_cost_f < 0 | max_cost_w < 0
  )
head(df_4)
```

```{r}
count_market_c_f_4 <- 
  df_4 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_market_c_w_4 <- 
  df_4 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_ths_c_f_4 <- 
  df_4 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  nrow()

count_ths_c_w_4 <- 
  df_4 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  nrow()
```

- In the estimation, we cannot find the parameters that make some costs positive for any lambda_w and lambda_f
  - How many markets show this problem? 
    - Without updating demand shocks, only `r count_market_c_w_3` market out of `r total_market_num_exact` for c_w, `r count_market_c_f_3` market out of `r total_market_num_exact` for c_f
    - With updating demand shocks, `r count_market_c_w_4` market out of `r total_market_num_exact`  for c_w, `r count_market_c_f_4` market out of `r total_market_num_exact` for c_f 
    
  - How many ths show this problem?  
    - Without updating demand shocks, only `r count_ths_c_w_3` ths out of `r total_ths_num_exact` for c_w, `r count_ths_c_f_3` ths out of `r total_ths_num_exact` for c_f
    - With updating demand shocks, `r count_ths_c_w_4` ths out of `r total_ths_num_exact`  for c_w, `r count_ths_c_f_4` ths out of `r total_ths_num_exact` for c_f 

# Make $m_w + m_f = 1.5 > 1$

```{r}
# reset equilibrium
equilibrium_updated <- equilibrium
equilibrium_small <- equilibrium
m_w <- 0.75
m_f <- 0.75
```

## Use approximate method

### without updating demand shocks

```{r, cache=TRUE}
# c_w with varying lambda_w

obj_lambda_w_5 <- 
  foreach(
    param_value = target_list[[1]],
    iter = seq_along(target_list[[1]]),
    .combine = "cbind"
  ) %do% {
        
    c_w <-
      foreach(
        t = seq_along(equilibrium$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_w_t <- 
          foreach(
            j = seq_along(equilibrium$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            s_w_d_w <-
              solve_s_w_d_w_tj(
                m_w = m_w,
                m_f = m_f,
                beta_w = equilibrium$parameter$beta_w,
                lambda_w = param_value,
                x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium$exogenous[[t]][[j]]$size_f,
                mu = equilibrium$shock[[t]][[j]]$mu,
                ea_w = equilibrium$shock[[t]][[j]]$ea_w,
                w = equilibrium$endogenous[[t]][[j]]$w,
                s_f = equilibrium$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium$constant$method_s_w,
                margin = equilibrium$constant$margin,
                quadrature_size = equilibrium$constant$quadrature_size,
                tol = equilibrium$constant$tol
              ) 
            owner <- equilibrium$exogenous[[t]][[j]]$owner
            o <- t(owner) %*% owner
            f <- equilibrium$endogenous[[t]][[j]]$f
            w <- equilibrium$endogenous[[t]][[j]]$w
            s_w <- equilibrium$endogenous[[t]][[j]]$s_w
            b <- 
              (s_w_d_w * o) %*% (f - w) - s_w
            
            A <- s_w_d_w * o
            
            #ridge regularization
            cond_A <- kappa(A)
            
            # Threshold for acceptable conditioning (commonly 1e12)
            if (cond_A < 1e12) {
              condition_c_w <- "well-conditioned"
              # Well-conditioned: solve directly
              c_w_tj <- Matrix::solve(A, b)
            } else {
              # Ill-conditioned: use adaptive ridge regularization
              epsilon <- 1e-10
              condition_c_w <- "ill-conditioned"
              A_reg <- A + epsilon * diag(ncol(A))
              c_w_tj <- Matrix::solve(A_reg, b)
            }
            df_tj <- 
              data.frame(
                c_w = c_w_tj,
                i = 
                  seq(
                    1,
                    length(c_w_tj)
                  ),
                t = t,
                j = j,
                lambda_f = equilibrium$parameter$lambda_f,
                lambda_w = param_value,
                condition_c_w = condition_c_w
              ) %>% 
                setNames(
                    c(
                    paste0("c_w_", iter),
                    paste0("i_", iter),
                    paste0("t_", iter),
                    paste0("j_", iter),
                    paste0("lambda_f_", iter),
                    paste0("lambda_w_", iter),
                    paste0("condition_c_w_", iter)
                  )
                )
              return(df_tj)         
              }
        return(c_w_t)
      }
    return(c_w)
  }

max_cost_w_5 <- 
  obj_lambda_w_5 %>% 
  dplyr::select(
    starts_with("c_w")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_w = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_w
  )

df_w_5 <- 
  cbind(
    obj_lambda_w_5,
    max_cost_w_5
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_w
  )
```


```{r, cache=TRUE}
obj_lambda_f_5 <- 
  foreach(
    param_value = target_list[[2]],
    iter = seq_along(target_list[[2]]),
    .combine = "cbind"
  ) %do% {

    c_f <-
      foreach(
        t = seq_along(equilibrium$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_f_t <- 
          foreach(
            j = seq_along(equilibrium$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            c_w <- 
              compute_supply_shock_c_w_tj(
                m_w = m_w,
                m_f = m_f,
                beta_w = equilibrium$parameter$beta_w,
                lambda_w = equilibrium$parameter$lambda_w,
                x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium$exogenous[[t]][[j]]$size_f,
                mu = equilibrium$shock[[t]][[j]]$mu,
                ea_w = equilibrium$shock[[t]][[j]]$ea_w,
                f = equilibrium$endogenous[[t]][[j]]$f,
                w = equilibrium$endogenous[[t]][[j]]$w,
                s_f = equilibrium$endogenous[[t]][[j]]$s_f,
                s_w = equilibrium$endogenous[[t]][[j]]$s_w,
                owner = equilibrium$exogenous[[t]][[j]]$owner,
                method_s_w = equilibrium$constant$method_s_w,
                margin = equilibrium$constant$margin,
                quadrature_size = equilibrium$constant$quadrature_size,
                tol = equilibrium$constant$tol
              )
            s_f_d_f <- 
              solve_s_f_d_f_tj(
                m_w = m_w,
                m_f = m_f,
                beta_f = equilibrium$parameter$beta_f,
                lambda_f = param_value,
                x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
                size_w = equilibrium$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium$exogenous[[t]][[j]]$size_f,
                mu = equilibrium$shock[[t]][[j]]$mu,
                ea_f = equilibrium$shock[[t]][[j]]$ea_f,
                f = equilibrium$endogenous[[t]][[j]]$f,
                s_f = equilibrium$endogenous[[t]][[j]]$s_f
              )
            
            s_w_d_f <- 
              solve_s_w_d_f_tj(
                m_w = m_w,
                m_f = m_f,
                beta_w = equilibrium$parameter$beta_w,
                beta_f = equilibrium$parameter$beta_f,
                lambda_w = equilibrium$parameter$lambda_w,
                lambda_f = param_value,
                x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
                x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
                size_w = equilibrium$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium$exogenous[[t]][[j]]$size_f,
                mu = equilibrium$shock[[t]][[j]]$mu,
                ea_w = equilibrium$shock[[t]][[j]]$ea_w,
                ea_f = equilibrium$shock[[t]][[j]]$ea_f,
                w = equilibrium$endogenous[[t]][[j]]$w,
                f = equilibrium$endogenous[[t]][[j]]$f,
                s_f = equilibrium$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium$constant$method_s_w,
                margin = equilibrium$constant$margin,
                quadrature_size = equilibrium$constant$quadrature_size,
                tol = equilibrium$constant$tol
              ) 
            
          meeting_number <- 
            compute_meeting_number_tj(
              m_w = m_w,
              m_f = m_f,
              size_w = equilibrium$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium$exogenous[[t]][[j]]$size_f,
              mu = equilibrium$shock[[t]][[j]]$mu,
              s_f = equilibrium$endogenous[[t]][[j]]$s_f
            ) 
            
          meeting_number_d_f <- 
            compute_meeting_number_d_f_tj(
              m_w = m_w,
              m_f = m_f,
              size_w = equilibrium$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium$exogenous[[t]][[j]]$size_f,
              mu = equilibrium$shock[[t]][[j]]$mu,
              s_f = equilibrium$endogenous[[t]][[j]]$s_f,
              s_f_d_f = s_f_d_f
            ) 
          owner <- equilibrium$exogenous[[t]][[j]]$owner
          o <- t(owner) %*% owner
          f <- equilibrium$endogenous[[t]][[j]]$f
          w <- equilibrium$endogenous[[t]][[j]]$w
          s_w <- equilibrium$endogenous[[t]][[j]]$s_w
          size_f <- equilibrium$exogenous[[t]][[j]]$size_f
          
          b <-  meeting_number * s_w +
            (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
            (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
          
          A <-  (o * s_f_d_f) * size_f
          
          #ridge regularization
          cond_A <- kappa(A)
          
          # Threshold for acceptable conditioning (commonly 1e12)
          if (cond_A < 1e12) {
            condition_c_f <- "well-conditioned"
            c_f_tj <- Matrix::solve(A, b)
          } else {
            condition_c_f <- "ill-conditioned"
            epsilon <- 1e-10
            A_reg <- A + epsilon * diag(ncol(A))
            c_f_tj <- Matrix::solve(A_reg, b)
          }
          df_tj <- 
            data.frame(
              c_f = c_f_tj,
              i = 
                seq(
                  1,
                  length(c_f_tj)
                ),
              t = t,
              j = j,
              lambda_f = param_value,
              lambda_w = equilibrium$parameter$lambda_w,
              condition_c_f = condition_c_f
            ) %>% 
              setNames(
                  c(
                  paste0("c_f_", iter),
                  paste0("i_", iter),
                  paste0("t_", iter),
                  paste0("j_", iter),
                  paste0("lambda_f_", iter),
                  paste0("lambda_w_", iter),
                  paste0("condition_c_f_", iter)
                )
              )
          return(df_tj)          
              }
        return(c_f_t)
          }
    return(c_f)
  }

max_cost_f_5 <- 
  obj_lambda_f_5 %>% 
  dplyr::select(
    starts_with("c_f")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_f = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_f
  )

df_f_5 <- 
  cbind(
    obj_lambda_f_5,
    max_cost_f_5
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_f
  )
```

#### ths with negative costs

```{r, cache=TRUE}
df_5 <- 
  data.frame(
   max_cost_f = df_f_5$max_cost_f,
   max_cost_w = df_w_5$max_cost_w,
   t = df_w_5$t_1,
   j = df_w_5$j_1,
   i = df_w_5$i_1
  ) %>%
  dplyr::filter(
    max_cost_f < 0 | max_cost_w < 0
  )
head(df_5)
```

```{r}
total_market_num <- 
  df_f_5 %>%
  dplyr::distinct(
    t_1,
    j_1
  ) %>%
  nrow()

total_ths_num <- 
  df_f_5 %>%
  nrow()

count_market_c_f_5 <- 
  df_5 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_market_c_w_5 <- 
  df_5 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_ths_c_f_5 <- 
  df_5 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  nrow()

count_ths_c_w_5 <- 
  df_5 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  nrow()
```

### with updating demand shocks

```{r, cache=TRUE}
# c_w with varying lambda_w
equilibrium_updated$parameter$m_w <- 0.75
equilibrium_updated$parameter$m_f <- 0.75

obj_lambda_w_6 <- 
  foreach(
    param_value = target_list[[1]],
    iter = seq_along(target_list[[1]]),
    .combine = "cbind"
  ) %do% {
    equilibrium_updated$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_updated
      )
    equilibrium_updated <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_updated
      ) 
        
    c_w <-
      foreach(
        t = seq_along(equilibrium_updated$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_w_t <- 
          foreach(
            j = seq_along(equilibrium_updated$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            s_w_d_w <-
              solve_s_w_d_w_tj(
                m_w = equilibrium_updated$parameter$m_w,
                m_f = equilibrium_updated$parameter$m_f,
                beta_w = equilibrium_updated$parameter$beta_w,
                lambda_w = param_value,
                x_a_w = equilibrium_updated$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_updated$shock[[t]][[j]]$mu,
                ea_w = equilibrium_updated$shock[[t]][[j]]$ea_w,
                w = equilibrium_updated$endogenous[[t]][[j]]$w,
                s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium_updated$constant$method_s_w,
                margin = equilibrium_updated$constant$margin,
                quadrature_size = equilibrium_updated$constant$quadrature_size,
                tol = equilibrium_updated$constant$tol
              ) 
            owner <- equilibrium_updated$exogenous[[t]][[j]]$owner
            o <- t(owner) %*% owner
            f <- equilibrium_updated$endogenous[[t]][[j]]$f
            w <- equilibrium_updated$endogenous[[t]][[j]]$w
            s_w <- equilibrium_updated$endogenous[[t]][[j]]$s_w
            b <- 
              (s_w_d_w * o) %*% (f - w) - s_w
            
            A <- s_w_d_w * o
            
            #ridge regularization
            cond_A <- kappa(A)
            
            # Threshold for acceptable conditioning (commonly 1e12)
            if (cond_A < 1e12) {
              condition_c_w <- "well-conditioned"
              # Well-conditioned: solve directly
              c_w_tj <- Matrix::solve(A, b)
            } else {
              # Ill-conditioned: use adaptive ridge regularization
              epsilon <- 1e-10
              condition_c_w <- "ill-conditioned"
              A_reg <- A + epsilon * diag(ncol(A))
              c_w_tj <- Matrix::solve(A_reg, b)
            }
            df_tj <- 
              data.frame(
                c_w = c_w_tj,
                i = 
                  seq(
                    1,
                    length(c_w_tj)
                  ),
                t = t,
                j = j,
                lambda_f = equilibrium_updated$parameter$lambda_f,
                lambda_w = param_value,
                condition_c_w = condition_c_w
              ) %>% 
                setNames(
                    c(
                    paste0("c_w_", iter),
                    paste0("i_", iter),
                    paste0("t_", iter),
                    paste0("j_", iter),
                    paste0("lambda_f_", iter),
                    paste0("lambda_w_", iter),
                    paste0("condition_c_w_", iter)
                  )
                )
              return(df_tj)         
              }
        return(c_w_t)
      }
    return(c_w)
  }

max_cost_w_6 <- 
  obj_lambda_w_6 %>% 
  dplyr::select(
    starts_with("c_w")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_w = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_w
  )

df_w_6 <- 
  cbind(
    obj_lambda_w_6,
    max_cost_w_6
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_w
  )
```


```{r, cache=TRUE}

obj_lambda_f_6 <- 
  foreach(
    param_value = target_list[[2]],
    iter = seq_along(target_list[[2]]),
    .combine = "cbind"
  ) %do% {
    equilibrium_updated$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_updated
      )
    equilibrium_updated <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_updated
      ) 
    c_f <-
      foreach(
        t = seq_along(equilibrium_updated$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_f_t <- 
          foreach(
            j = seq_along(equilibrium_updated$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            c_w <- 
              compute_supply_shock_c_w_tj(
                m_w = equilibrium_updated$parameter$m_w,
                m_f = equilibrium_updated$parameter$m_f,
                beta_w = equilibrium_updated$parameter$beta_w,
                lambda_w = equilibrium_updated$parameter$lambda_w,
                x_a_w = equilibrium_updated$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_updated$shock[[t]][[j]]$mu,
                ea_w = equilibrium_updated$shock[[t]][[j]]$ea_w,
                f = equilibrium_updated$endogenous[[t]][[j]]$f,
                w = equilibrium_updated$endogenous[[t]][[j]]$w,
                s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f,
                s_w = equilibrium_updated$endogenous[[t]][[j]]$s_w,
                owner = equilibrium_updated$exogenous[[t]][[j]]$owner,
                method_s_w = equilibrium_updated$constant$method_s_w,
                margin = equilibrium_updated$constant$margin,
                quadrature_size = equilibrium_updated$constant$quadrature_size,
                tol = equilibrium_updated$constant$tol
              )
          s_f_d_f <- 
            solve_s_f_d_f_tj(
              m_w = equilibrium_updated$parameter$m_w,
              m_f = equilibrium_updated$parameter$m_f,
              beta_f = equilibrium_updated$parameter$beta_f,
              lambda_f = param_value,
              x_a_f = equilibrium_updated$exogenous[[t]][[j]]$x_a_f,
              size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
              mu = equilibrium_updated$shock[[t]][[j]]$mu,
              ea_f = equilibrium_updated$shock[[t]][[j]]$ea_f,
              f = equilibrium_updated$endogenous[[t]][[j]]$f,
              s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f
            )
          
          s_w_d_f <- 
            solve_s_w_d_f_tj(
              m_w = equilibrium_updated$parameter$m_w,
              m_f = equilibrium_updated$parameter$m_f,
              beta_w = equilibrium_updated$parameter$beta_w,
              beta_f = equilibrium_updated$parameter$beta_f,
              lambda_w = equilibrium_updated$parameter$lambda_w,
              lambda_f = param_value,
              x_a_w = equilibrium_updated$exogenous[[t]][[j]]$x_a_w,
              x_a_f = equilibrium_updated$exogenous[[t]][[j]]$x_a_f,
              size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
              mu = equilibrium_updated$shock[[t]][[j]]$mu,
              ea_w = equilibrium_updated$shock[[t]][[j]]$ea_w,
              ea_f = equilibrium_updated$shock[[t]][[j]]$ea_f,
              w = equilibrium_updated$endogenous[[t]][[j]]$w,
              f = equilibrium_updated$endogenous[[t]][[j]]$f,
              s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f,
              method_s_w = equilibrium_updated$constant$method_s_w,
              margin = equilibrium_updated$constant$margin,
              quadrature_size = equilibrium_updated$constant$quadrature_size,
              tol = equilibrium_updated$constant$tol
            ) 
          
        meeting_number <- 
          compute_meeting_number_tj(
            m_w = equilibrium_updated$parameter$m_w,
            m_f = equilibrium_updated$parameter$m_f,
            size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
            mu = equilibrium_updated$shock[[t]][[j]]$mu,
            s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f
          ) 
          
        meeting_number_d_f <- 
          compute_meeting_number_d_f_tj(
            m_w = equilibrium_updated$parameter$m_w,
            m_f = equilibrium_updated$parameter$m_f,
            size_w = equilibrium_updated$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium_updated$exogenous[[t]][[j]]$size_f,
            mu = equilibrium_updated$shock[[t]][[j]]$mu,
            s_f = equilibrium_updated$endogenous[[t]][[j]]$s_f,
            s_f_d_f = s_f_d_f
          ) 
          owner <- equilibrium_updated$exogenous[[t]][[j]]$owner
          o <- t(owner) %*% owner
          f <- equilibrium_updated$endogenous[[t]][[j]]$f
          w <- equilibrium_updated$endogenous[[t]][[j]]$w
          s_w <- equilibrium_updated$endogenous[[t]][[j]]$s_w
          size_f <- equilibrium_updated$exogenous[[t]][[j]]$size_f
          
          b <-  meeting_number * s_w +
            (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
            (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
          
          A <-  (o * s_f_d_f) * size_f
          
          #ridge regularization
          cond_A <- kappa(A)
          
          # Threshold for acceptable conditioning (commonly 1e12)
          if (cond_A < 1e12) {
            condition_c_f <- "well-conditioned"
            c_f_tj <- Matrix::solve(A, b)
          } else {
            condition_c_f <- "ill-conditioned"
            epsilon <- 1e-10
            A_reg <- A + epsilon * diag(ncol(A))
            c_f_tj <- Matrix::solve(A_reg, b)
          }
          df_tj <- 
            data.frame(
              c_f = c_f_tj,
              i = 
                seq(
                  1,
                  length(c_f_tj)
                ),
              t = t,
              j = j,
              lambda_f = param_value,
              lambda_w = equilibrium_updated$parameter$lambda_w,
              condition_c_f = condition_c_f
            ) %>% 
              setNames(
                  c(
                  paste0("c_f_", iter),
                  paste0("i_", iter),
                  paste0("t_", iter),
                  paste0("j_", iter),
                  paste0("lambda_f_", iter),
                  paste0("lambda_w_", iter),
                  paste0("condition_c_f_", iter)
                )
              )
          return(df_tj)          
              }
        return(c_f_t)
          }
    return(c_f)
  }

max_cost_f_6 <- 
  obj_lambda_f_6 %>% 
  dplyr::select(
    starts_with("c_f")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_f = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_f
  )

df_f_6 <- 
  cbind(
    obj_lambda_f_6,
    max_cost_f_6
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_f
  )
```

#### ths with negative costs
```{r, cache=TRUE}
df_6 <- 
  data.frame(
   max_cost_f = df_f_6$max_cost_f,
   max_cost_w = df_w_6$max_cost_w,
   t = df_w_6$t_1,
   j = df_w_6$j_1,
   i = df_w_6$i_1
  ) %>%
  dplyr::filter(
    max_cost_f < 0 | max_cost_w < 0
  )
head(df_6)
```

```{r}
count_market_c_f_6 <- 
  df_6 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_market_c_w_6 <- 
  df_6 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_ths_c_f_6 <- 
  df_6 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  nrow()

count_ths_c_w_6 <- 
  df_6 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  nrow()
```

- In the estimation, we cannot find the parameters that make some costs positive for any lambda_w and lambda_f.
  - How many markets show this problem? 
    - Without updating demand shocks, only `r count_market_c_w_5` market out of `r total_market_num` for c_w, `r count_market_c_f_5` market out of `r total_market_num` for c_f
    - With updating demand shocks, `r count_market_c_w_6` market out of `r total_market_num`  for c_w, `r count_market_c_f_6` market out of `r total_market_num` for c_f 
    
  - How many ths show this problem?  
    - Without updating demand shocks, only `r count_ths_c_w_5` ths out of `r total_ths_num` for c_w, `r count_ths_c_f_5` ths out of `r total_ths_num` for c_f
    - With updating demand shocks, `r count_ths_c_w_6` ths out of `r total_ths_num`  for c_w, `r count_ths_c_f_6` ths out of `r total_ths_num` for c_f 


## Use exact method

```{r}
method_s_w <- "exact"
```

- delete large markets
```{r}
num_ths <- 
  foreach(
    t = seq_along(equilibrium$endogenous),
    .combine = "rbind"
  ) %do% {
    foreach(
      j = seq_along(equilibrium$endogenous[[t]]),
    .combine = "rbind"
    ) %do% {
      num <- length(equilibrium$endogenous[[t]][[j]]$w)
      return(
        data.frame(
          t = t,
          j = j,
          num = num
        )
      )
    }
  }

small_market <- 
  num_ths %>%
  dplyr::filter(
    num < 5
  )
```

### without updating demand shocks

```{r, cache=TRUE}
# c_w with varying lambda_w

obj_lambda_w_7 <- 
  foreach(
    param_value = target_list[[1]],
    iter = seq_along(target_list[[1]]),
    .combine = "cbind"
  ) %do% {
        
    c_w <-
      foreach(
        m = 
          seq(
            1,
            nrow(small_market)
          ),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        t <- small_market$t[m]
        j <- small_market$j[m]
        s_w_d_w <-
          solve_s_w_d_w_tj(
            m_w = m_w,
            m_f = m_f,
            beta_w = equilibrium$parameter$beta_w,
            lambda_w = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            w = equilibrium$endogenous[[t]][[j]]$w,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          ) 
        owner <- equilibrium$exogenous[[t]][[j]]$owner
        o <- t(owner) %*% owner
        f <- equilibrium$endogenous[[t]][[j]]$f
        w <- equilibrium$endogenous[[t]][[j]]$w
        s_w <- equilibrium$endogenous[[t]][[j]]$s_w
        b <- 
          (s_w_d_w * o) %*% (f - w) - s_w
        
        A <- s_w_d_w * o
        
        #ridge regularization
        cond_A <- kappa(A)
        
        # Threshold for acceptable conditioning (commonly 1e12)
        if (cond_A < 1e12) {
          condition_c_w <- "well-conditioned"
          # Well-conditioned: solve directly
          c_w_tj <- Matrix::solve(A, b)
        } else {
          # Ill-conditioned: use adaptive ridge regularization
          epsilon <- 1e-10
          condition_c_w <- "ill-conditioned"
          A_reg <- A + epsilon * diag(ncol(A))
          c_w_tj <- Matrix::solve(A_reg, b)
        }
        df_tj <- 
          data.frame(
            c_w = c_w_tj,
            i = 
              seq(
                1,
                length(c_w_tj)
              ),
            t = t,
            j = j,
            lambda_f = equilibrium$parameter$lambda_f,
            lambda_w = param_value,
            condition_c_w = condition_c_w
          ) %>% 
            setNames(
                c(
                paste0("c_w_", iter),
                paste0("i_", iter),
                paste0("t_", iter),
                paste0("j_", iter),
                paste0("lambda_f_", iter),
                paste0("lambda_w_", iter),
                paste0("condition_c_w_", iter)
              )
            )
          return(df_tj)         
      }
    return(c_w)
  }

max_cost_w_7 <- 
  obj_lambda_w_7 %>% 
  dplyr::select(
    starts_with("c_w")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_w = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_w
  )

df_w_7 <- 
  cbind(
    obj_lambda_w_7,
    max_cost_w_7
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_w
  )
```


```{r, cache=TRUE}

obj_lambda_f_7 <- 
  foreach(
    param_value = target_list[[2]],
    iter = seq_along(target_list[[2]]),
    .combine = "cbind"
  ) %do% {

    c_f <-
      foreach(
        m = 
          seq(
            1,
            nrow(small_market)
          ),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        t <- small_market$t[m]
        j <- small_market$j[m]
        c_w <- 
          compute_supply_shock_c_w_tj(
            m_w = m_w,
            m_f = m_f,
            beta_w = equilibrium$parameter$beta_w,
            lambda_w = equilibrium$parameter$lambda_w,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_w = equilibrium$endogenous[[t]][[j]]$s_w,
            owner = equilibrium$exogenous[[t]][[j]]$owner,
            method_s_w = method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )
        s_f_d_f <- 
          solve_s_f_d_f_tj(
            m_w = m_w,
            m_f = m_f,
            beta_f = equilibrium$parameter$beta_f,
            lambda_f = param_value,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          )
        
        s_w_d_f <- 
          solve_s_w_d_f_tj(
            m_w = m_w,
            m_f = m_f,
            beta_w = equilibrium$parameter$beta_w,
            beta_f = equilibrium$parameter$beta_f,
            lambda_w = equilibrium$parameter$lambda_w,
            lambda_f = param_value,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            ea_f = equilibrium$shock[[t]][[j]]$ea_f,
            w = equilibrium$endogenous[[t]][[j]]$w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            method_s_w = method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          ) 
        
      meeting_number <- 
        compute_meeting_number_tj(
          m_w = m_w,
          m_f = m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f
        ) 
        
      meeting_number_d_f <- 
        compute_meeting_number_d_f_tj(
          m_w = m_w,
          m_f = m_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_f_d_f = s_f_d_f
        ) 
      owner <- equilibrium$exogenous[[t]][[j]]$owner
      o <- t(owner) %*% owner
      f <- equilibrium$endogenous[[t]][[j]]$f
      w <- equilibrium$endogenous[[t]][[j]]$w
      s_w <- equilibrium$endogenous[[t]][[j]]$s_w
      size_f <- equilibrium$exogenous[[t]][[j]]$size_f
      
      b <-  meeting_number * s_w +
        (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
        (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
      
      A <-  (o * s_f_d_f) * size_f
      
      #ridge regularization
      cond_A <- kappa(A)
      
      # Threshold for acceptable conditioning (commonly 1e12)
      if (cond_A < 1e12) {
        condition_c_f <- "well-conditioned"
        c_f_tj <- Matrix::solve(A, b)
      } else {
        condition_c_f <- "ill-conditioned"
        epsilon <- 1e-10
        A_reg <- A + epsilon * diag(ncol(A))
        c_f_tj <- Matrix::solve(A_reg, b)
      }
      df_tj <- 
        data.frame(
          c_f = c_f_tj,
          i = 
            seq(
              1,
              length(c_f_tj)
            ),
          t = t,
          j = j,
          lambda_f = param_value,
          lambda_w = equilibrium$parameter$lambda_w,
          condition_c_f = condition_c_f
        ) %>% 
          setNames(
              c(
              paste0("c_f_", iter),
              paste0("i_", iter),
              paste0("t_", iter),
              paste0("j_", iter),
              paste0("lambda_f_", iter),
              paste0("lambda_w_", iter),
              paste0("condition_c_f_", iter)
            )
          )
      return(df_tj)          
          }
    return(c_f)
  }

max_cost_f_7 <- 
  obj_lambda_f_7 %>% 
  dplyr::select(
    starts_with("c_f")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_f = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_f
  )

df_f_7 <- 
  cbind(
    obj_lambda_f_7,
    max_cost_f_7
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_f
  )
```

#### ths with negative costs

```{r}
df_7 <- 
  data.frame(
   max_cost_f = df_f_7$max_cost_f,
   max_cost_w = df_w_7$max_cost_w,
   t = df_w_7$t_1,
   j = df_w_7$j_1,
   i = df_w_7$i_1
  ) %>%
  dplyr::filter(
    max_cost_f < 0 | max_cost_w < 0
  )
head(df_7)
```

```{r}
total_market_num_exact <- 
  df_f_7 %>%
  dplyr::distinct(
    t_1,
    j_1
  ) %>%
  nrow()

total_ths_num_exact <- 
  df_f_7 %>%
  nrow()

count_market_c_f_7 <- 
  df_7 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_market_c_w_7 <- 
  df_7 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_ths_c_f_7 <- 
  df_7 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  nrow()

count_ths_c_w_7 <- 
  df_7 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  nrow()
```

### with updating demand shocks

```{r}
# discard large markets
large_market <- 
  num_ths %>%
  dplyr::filter(
    num >= 5
  )

large_market <- 
  large_market[
    order(
      large_market$t,
      large_market$j,
      decreasing = TRUE
    ), 
  ]
for (
  i in 1:nrow(large_market)
) {
  equilibrium_small$shock[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$endogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$exogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
}

equilibrium_small$constant$method_s_w <- "exact"
equilibrium_small$parameter$m_w <- 0.75
equilibrium_small$parameter$m_f <- 0.75
```

```{r, cache=TRUE}

obj_lambda_w_8 <- 
  foreach(
    param_value = target_list[[1]],
    iter = seq_along(target_list[[1]]),
    .combine = "cbind"
  ) %do% {
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
        
    c_w <-
      foreach(
        t = seq_along(equilibrium_small$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_w_t <- 
          foreach(
            j = seq_along(equilibrium_small$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            s_w_d_w <-
              solve_s_w_d_w_tj(
                m_w = equilibrium_small$parameter$m_w,
                m_f = equilibrium_small$parameter$m_f,
                beta_w = equilibrium_small$parameter$beta_w,
                lambda_w = equilibrium_small$parameter$lambda_w,
                x_a_w = equilibrium_small$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_small$shock[[t]][[j]]$mu,
                ea_w = equilibrium_small$shock[[t]][[j]]$ea_w,
                w = equilibrium_small$endogenous[[t]][[j]]$w,
                s_f = equilibrium_small$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium_small$constant$method_s_w,
                margin = equilibrium_small$constant$margin,
                quadrature_size = equilibrium_small$constant$quadrature_size,
                tol = equilibrium_small$constant$tol
              ) 
            owner <- equilibrium_small$exogenous[[t]][[j]]$owner
            o <- t(owner) %*% owner
            f <- equilibrium_small$endogenous[[t]][[j]]$f
            w <- equilibrium_small$endogenous[[t]][[j]]$w
            s_w <- equilibrium_small$endogenous[[t]][[j]]$s_w
            b <- 
              (s_w_d_w * o) %*% (f - w) - s_w
            
            A <- s_w_d_w * o
            
            #ridge regularization
            cond_A <- kappa(A)
            
            # Threshold for acceptable conditioning (commonly 1e12)
            if (cond_A < 1e12) {
              condition_c_w <- "well-conditioned"
              # Well-conditioned: solve directly
              c_w_tj <- Matrix::solve(A, b)
            } else {
              # Ill-conditioned: use adaptive ridge regularization
              epsilon <- 1e-10
              condition_c_w <- "ill-conditioned"
              A_reg <- A + epsilon * diag(ncol(A))
              c_w_tj <- Matrix::solve(A_reg, b)
            }
            df_tj <- 
              data.frame(
                c_w = c_w_tj,
                i = 
                  seq(
                    1,
                    length(c_w_tj)
                  ),
                t = t,
                j = j,
                lambda_f = equilibrium_small$parameter$lambda_f,
                lambda_w = param_value,
                condition_c_w = condition_c_w
              ) %>% 
                setNames(
                    c(
                    paste0("c_w_", iter),
                    paste0("i_", iter),
                    paste0("t_", iter),
                    paste0("j_", iter),
                    paste0("lambda_f_", iter),
                    paste0("lambda_w_", iter),
                    paste0("condition_c_w_", iter)
                  )
                )
            return(df_tj)         
          }
        return(c_w_t)
      }
    return(c_w)
  }

max_cost_w_8 <- 
  obj_lambda_w_8 %>% 
  dplyr::select(
    starts_with("c_w")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_w = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_w
  )

df_w_8 <- 
  cbind(
    obj_lambda_w_8,
    max_cost_w_8
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_w
  )
```


```{r, cache=TRUE}
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
obj_lambda_f_8 <- 
  foreach(
    param_value = target_list[[2]],
    iter = seq_along(target_list[[2]]),
    .combine = "cbind"
  ) %do% {
    equilibrium_small$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    
    c_f <-
      foreach(
        t = seq_along(equilibrium_small$endogenous),
        .combine = "rbind",
        .packages = 
          c(
            "Dispatching",
            "foreach",
            "magrittr"
          )
      ) %dopar% {
        c_f_t <- 
          foreach(
            j = seq_along(equilibrium_small$endogenous[[t]]),
            .combine = "rbind"
          ) %do% {  
            c_w <- 
              compute_supply_shock_c_w_tj(
                m_w = equilibrium_small$parameter$m_w,
                m_f = equilibrium_small$parameter$m_f,
                beta_w = equilibrium_small$parameter$beta_w,
                lambda_w = equilibrium_small$parameter$lambda_w,
                x_a_w = equilibrium_small$exogenous[[t]][[j]]$x_a_w,
                size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_small$shock[[t]][[j]]$mu,
                ea_w = equilibrium_small$shock[[t]][[j]]$ea_w,
                f = equilibrium_small$endogenous[[t]][[j]]$f,
                w = equilibrium_small$endogenous[[t]][[j]]$w,
                s_f = equilibrium_small$endogenous[[t]][[j]]$s_f,
                s_w = equilibrium_small$endogenous[[t]][[j]]$s_w,
                owner = equilibrium_small$exogenous[[t]][[j]]$owner,
                method_s_w = equilibrium_small$constant$method_s_w,
                margin = equilibrium_small$constant$margin,
                quadrature_size = equilibrium_small$constant$quadrature_size,
                tol = equilibrium_small$constant$tol
              )
            s_f_d_f <- 
              solve_s_f_d_f_tj(
                m_w = equilibrium_small$parameter$m_w,
                m_f = equilibrium_small$parameter$m_f,
                beta_f = equilibrium_small$parameter$beta_f,
                lambda_f = param_value,
                x_a_f = equilibrium_small$exogenous[[t]][[j]]$x_a_f,
                size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_small$shock[[t]][[j]]$mu,
                ea_f = equilibrium_small$shock[[t]][[j]]$ea_f,
                f = equilibrium_small$endogenous[[t]][[j]]$f,
                s_f = equilibrium_small$endogenous[[t]][[j]]$s_f
              )
            
            s_w_d_f <- 
              solve_s_w_d_f_tj(
                m_w = equilibrium_small$parameter$m_w,
                m_f = equilibrium_small$parameter$m_f,
                beta_w = equilibrium_small$parameter$beta_w,
                beta_f = equilibrium_small$parameter$beta_f,
                lambda_w = equilibrium_small$parameter$lambda_w,
                lambda_f = param_value,
                x_a_w = equilibrium_small$exogenous[[t]][[j]]$x_a_w,
                x_a_f = equilibrium_small$exogenous[[t]][[j]]$x_a_f,
                size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
                size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
                mu = equilibrium_small$shock[[t]][[j]]$mu,
                ea_w = equilibrium_small$shock[[t]][[j]]$ea_w,
                ea_f = equilibrium_small$shock[[t]][[j]]$ea_f,
                w = equilibrium_small$endogenous[[t]][[j]]$w,
                f = equilibrium_small$endogenous[[t]][[j]]$f,
                s_f = equilibrium_small$endogenous[[t]][[j]]$s_f,
                method_s_w = equilibrium_small$constant$method_s_w,
                margin = equilibrium_small$constant$margin,
                quadrature_size = equilibrium_small$constant$quadrature_size,
                tol = equilibrium_small$constant$tol
              ) 
            
          meeting_number <- 
            compute_meeting_number_tj(
              m_w = equilibrium_small$parameter$m_w,
              m_f = equilibrium_small$parameter$m_f,
              size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
              mu = equilibrium_small$shock[[t]][[j]]$mu,
              s_f = equilibrium_small$endogenous[[t]][[j]]$s_f
            ) 
            
          meeting_number_d_f <- 
            compute_meeting_number_d_f_tj(
              m_w = equilibrium_small$parameter$m_w,
              m_f = equilibrium_small$parameter$m_f,
              size_w = equilibrium_small$exogenous[[t]][[j]]$size_w,
              size_f = equilibrium_small$exogenous[[t]][[j]]$size_f,
              mu = equilibrium_small$shock[[t]][[j]]$mu,
              s_f = equilibrium_small$endogenous[[t]][[j]]$s_f,
              s_f_d_f = s_f_d_f
            ) 
          owner <- equilibrium_small$exogenous[[t]][[j]]$owner
          o <- t(owner) %*% owner
          f <- equilibrium_small$endogenous[[t]][[j]]$f
          w <- equilibrium_small$endogenous[[t]][[j]]$w
          s_w <- equilibrium_small$endogenous[[t]][[j]]$s_w
          size_f <- equilibrium_small$exogenous[[t]][[j]]$size_f
          
          b <-  meeting_number * s_w +
            (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
            (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
          
          A <-  (o * s_f_d_f) * size_f
          
          #ridge regularization
          cond_A <- kappa(A)
          
          # Threshold for acceptable conditioning (commonly 1e12)
          if (cond_A < 1e12) {
            condition_c_f <- "well-conditioned"
            c_f_tj <- Matrix::solve(A, b)
          } else {
            condition_c_f <- "ill-conditioned"
            epsilon <- 1e-10
            A_reg <- A + epsilon * diag(ncol(A))
            c_f_tj <- Matrix::solve(A_reg, b)
          }
          df_tj <- 
            data.frame(
              c_f = c_f_tj,
              i = 
                seq(
                  1,
                  length(c_f_tj)
                ),
              t = t,
              j = j,
              lambda_f = param_value,
              lambda_w = equilibrium_small$parameter$lambda_w,
              condition_c_f = condition_c_f
            ) %>% 
              setNames(
                  c(
                  paste0("c_f_", iter),
                  paste0("i_", iter),
                  paste0("t_", iter),
                  paste0("j_", iter),
                  paste0("lambda_f_", iter),
                  paste0("lambda_w_", iter),
                  paste0("condition_c_f_", iter)
                )
              )
          return(df_tj)          
          }
        return(c_f_t)
      }
    return(c_f)
  }

max_cost_f_8 <- 
  obj_lambda_f_8 %>% 
  dplyr::select(
    starts_with("c_f")
    ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    max_cost_f = 
      max(
        dplyr::c_across(
          everything()
          )
        )
  ) %>%
  dplyr::select(
    max_cost_f
  )

df_f_8 <- 
  cbind(
    obj_lambda_f_8,
    max_cost_f_8
  ) %>%
  dplyr::filter(
    i_1 > 1
  ) %>%
  dplyr::select(
    t_1,
    j_1,
    i_1,
    max_cost_f
  )
```

#### ths with negative costs

```{r}
df_8 <- 
  data.frame(
   max_cost_f = df_f_8$max_cost_f,
   max_cost_w = df_w_8$max_cost_w,
   t = df_w_8$t_1,
   j = df_w_8$j_1,
   i = df_w_8$i_1
  ) %>%
  dplyr::filter(
    max_cost_f < 0 | max_cost_w < 0
  )
head(df_8)
```

```{r}
count_market_c_f_8 <- 
  df_8 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_market_c_w_8 <- 
  df_8 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  dplyr::distinct(t, j) %>%
  nrow()

count_ths_c_f_8 <- 
  df_8 %>%
  dplyr::filter(
    max_cost_f < 0
    ) %>%
  nrow()

count_ths_c_w_8 <- 
  df_8 %>%
  dplyr::filter(
    max_cost_w < 0
    ) %>%
  nrow()
```

- In the estimation, we cannot find the parameters that make some costs positive for any lambda_w and lambda_f
  - How many markets show this problem? 
    - Without updating demand shocks, only `r count_market_c_w_7` market out of `r total_market_num_exact` for c_w, `r count_market_c_f_7` market out of `r total_market_num_exact` for c_f
    - With updating demand shocks, `r count_market_c_w_8` market out of `r total_market_num_exact`  for c_w, `r count_market_c_f_8` market out of `r total_market_num_exact` for c_f 
    
  - How many ths show this problem?  
    - Without updating demand shocks, only `r count_ths_c_w_7` ths out of `r total_ths_num_exact` for c_w, `r count_ths_c_f_7` ths out of `r total_ths_num_exact` for c_f
    - With updating demand shocks, `r count_ths_c_w_8` ths out of `r total_ths_num_exact`  for c_w, `r count_ths_c_f_8` ths out of `r total_ths_num_exact` for c_f 
    
# Explore the causes

```{r}
start <- 0.1
end <- 5
step <- 0.01

target_list <- 
  list(
    lambda_w = 
      seq(
        start, 
        end, 
        by = step
      ),
    lambda_f = 
      seq(
        -start, 
        -end, 
        by = -step
      )
  )
```

# Check each component

- Use exact method and update demand shocks.
```{r}
equilibrium_small <- equilibrium
equilibrium_small$constant$method_s_w <- "exact"
```

```{r}
num_ths <- 
  foreach(
    t = seq_along(equilibrium$endogenous),
    .combine = "rbind"
  ) %do% {
    foreach(
      j = seq_along(equilibrium$endogenous[[t]]),
    .combine = "rbind"
    ) %do% {
      num <- length(equilibrium$endogenous[[t]][[j]]$w)
      return(
        data.frame(
          t = t,
          j = j,
          num = num
        )
      )
    }
  }

large_market <- 
  num_ths %>%
  dplyr::filter(
    num >= 5
  )

large_market <- 
  large_market[
    order(
      large_market$t,
      large_market$j,
      decreasing = TRUE
    ), 
  ]
for (
  i in 1:nrow(large_market)
) {
  equilibrium_small$shock[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$endogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$exogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
}

```

# m_f + m_w = 1
- Pick up normal ths in normal markets (i.e., $c_i^W > 0$ and $c_i^F > 0$ for all $i$ in the market)
  - t = 1, j = 1

- Make two graphs:
  - Change $\lambda_w$
    - In the y-axis of the same graph, overlay the lines of
    - $c_i^W$
    - $- \frac{s_i^W(\boldsymbol w, \boldsymbol f)}{\frac{\partial s_i^W}{\partial w_i}}$
    - $f_i - w_i$.
  - Change $\lambda_f$
    - $c_i^F$
    - term 1: $\frac{q_i(\boldsymbol f) s_i^W(\boldsymbol w, \boldsymbol f)}{S^F \frac{\partial s_i^F (\boldsymbol f )}{\partial f_i}}$
    - term 2: $\frac{q_i(\boldsymbol f) \frac{\partial s_i^W(\boldsymbol w, \boldsymbol f)}{\partial f_i}}{S^F \frac{\partial s_i^F (\boldsymbol f )}{\partial f_i}}(f_i - w_i - c_i^W)$
    - term 3:$\frac{\frac{\partial  q_i(\boldsymbol f)}{\partial f_i}}{S^F \frac{\partial s_i^F (\boldsymbol f )}{\partial f_i}} s_i^W(\boldsymbol w, \boldsymbol f) (f_i - w_i - c_i^W)$
    
## normal market
```{r}
t <- 1
j <- 1
```

### normal ths 1
```{r}
i <- 2
```

#### lambda_w
```{r, cache=TRUE}

objective_values_1 <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
        
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
    s_w_d_w_tj <- diag(s_w_d_w_tj)
    s_w_d_w <- -equilibrium$endogenous[[t]][[j]]$s_w/s_w_d_w_tj
    s_w_d_w <- s_w_d_w[i]
    obj <- c_w[i]

      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_w_d_w = s_w_d_w
        )
      )
    }


g_1 <-
  ggplot(
    objective_values_1, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(color = objective > 0)
    ) +
  geom_line() +
  geom_hline(
  yintercept = equilibrium$endogenous[[t]][[j]]$f[i] - equilibrium$endogenous[[t]][[j]]$w[i],
  color = "blue", 
  linetype = "solid"
  ) +
  geom_point(
    data = objective_values_1,  
    aes(
      x = value, 
      y = s_w_d_w
      ),
    color = "green",
    size = 0.1
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w ths 1"
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    name = "c_w > 0"
  ) +
  annotate(
    "text",
    x = 4,
    y = equilibrium$endogenous[[t]][[j]]$f[i] - equilibrium$endogenous[[t]][[j]]$w[i] + 1,
    label = "f - w",
    color = "blue",
    hjust = + 0.1
  )  +
annotate(
    "text",
    x = 4,
    y = -10,
    label = "-s_w/s_w_d_w",
    color = "green",
    hjust = + 0.1
  ) 
g_1

```

#### lambda_f
```{r, cache=TRUE}
# reset lambda_w 
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w

objective_values_2 <- 
  foreach(
    param_value = target_list[[2]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = equilibrium$parameter$lambda_w,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_f_d_f <- 
      solve_s_f_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_f = equilibrium$parameter$beta_f,
        lambda_f = param_value,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      )
          
    s_w_d_f <- 
      solve_s_w_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        beta_f = equilibrium$parameter$beta_f,
        lambda_w = equilibrium$parameter$lambda_w,
        lambda_f = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      ) 
          
    meeting_number <- 
      compute_meeting_number_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      ) 
      
    meeting_number_d_f <- 
      compute_meeting_number_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_f_d_f = s_f_d_f
      ) 
    owner <- equilibrium$exogenous[[t]][[j]]$owner
    o <- t(owner) %*% owner
    f <- equilibrium$endogenous[[t]][[j]]$f
    w <- equilibrium$endogenous[[t]][[j]]$w
    s_w <- equilibrium$endogenous[[t]][[j]]$s_w
    size_f <- equilibrium$exogenous[[t]][[j]]$size_f
    
    b <-  meeting_number * s_w +
      (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
      (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
    
    A <-  (o * s_f_d_f) * size_f
    
    #ridge regularization
    cond_A <- kappa(A)
    
    # Threshold for acceptable conditioning (commonly 1e12)
    if (cond_A < 1e12) {
      condition_c_f <- "well-conditioned"
      c_f <- Matrix::solve(A, b)
    } else {
      condition_c_f <- "ill-conditioned"
      epsilon <- 1e-10
      A_reg <- A + epsilon * diag(ncol(A))
      c_f <- Matrix::solve(A_reg, b)
    }
    obj <- c_f[i]
    term_1 <- (meeting_number * s_w) / diag( (o * s_f_d_f) * size_f)
    term_2 <- (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
    term_3 <- (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
      
      return(
        data.frame(
          value = param_value,
          objective = obj,
          term_1 = term_1[i],
          term_2 = term_2[i],
          term_3 = term_3[i]
        )
      )
    }


g_2 <-
  ggplot(
    objective_values_2, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
      )
    ) +  
  geom_point(
    data = objective_values_2,  
    aes(
      x = value, 
      y = term_1
      ),
    color = "#ff7f0e",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_2,  
    aes(
      x = value, 
      y = term_2
      ),
    color = "#2ca02c"
  ) +
  geom_line(
    data = objective_values_2,  
    aes(
      x = value, 
      y = term_3
      ),
    color = "#1f77b4"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = 
      c(
        "FALSE" = "black", 
        "TRUE" = "red"
        ),  
    name = "c_f > 0"  # Legend title
  ) 
```

```{r}
g2 <-
  ggplot(
    objective_values_2, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
    )
  ) +  
  geom_point(
    data = objective_values_2,  
    aes(
      x = value, 
      y = term_1
    ),
    color = "#ff7f0e",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_2,  
    aes(
      x = value, 
      y = term_2
    ),
    color = "#2ca02c",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_2,  
    aes(
      x = value, 
      y = term_3
    ),
    color = "#1f77b4",
    size = 0.5
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = c(
      "FALSE" = "black", 
      "TRUE" = "red"
    ),  
    name = "c_f > 0"
  ) +
  annotate(
    "text",
    x = 0,
    y = -100,
    label = "term 1",
    color =  "#ff7f0e"
  ) +
  annotate(
    "text",
    x = 0,
    y = -300,
    label = "term 2",
    color = "#2ca02c"
  )  +
  annotate(
    "text",
    x = 0,
    y = -200,
    label = "term 3",
    color = "#1f77b4"
  ) +
  coord_cartesian(ylim = c(-500, 500))  # This restricts the y-axis range

```


```{r, fig.width=12, fig.height=6, out.width='100%'}
gridExtra::grid.arrange(
  g_2,
  g2, 
  ncol=2
  )
```


### normal ths 2
```{r}
i <- 3
```

#### lambda_w
```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f

objective_values_9 <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
        
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
    s_w_d_w_tj <- diag(s_w_d_w_tj)
    s_w_d_w <- -equilibrium$endogenous[[t]][[j]]$s_w/s_w_d_w_tj
    s_w_d_w <- s_w_d_w[i]
    obj <- c_w[i]

      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_w_d_w = s_w_d_w
        )
      )
    }


g_9 <-
  ggplot(
    objective_values_9, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
      )
    ) +
  geom_line() +
  geom_hline(
  yintercept = equilibrium$endogenous[[t]][[j]]$f[i] - equilibrium$endogenous[[t]][[j]]$w[i],
  color = "blue", 
  linetype = "solid"
  ) +
  geom_point(
    data = objective_values_9,  
    aes(
      x = value, 
      y = s_w_d_w
      ),
    color = "green",
    size = 0.2
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w ths 2"
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    name = "c_w > 0"
  ) 

g_9

```

#### lambda_f
```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f

objective_values_10 <- 
  foreach(
    param_value = target_list[[2]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = equilibrium$parameter$lambda_w,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_f_d_f <- 
      solve_s_f_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_f = equilibrium$parameter$beta_f,
        lambda_f = param_value,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      )
          
    s_w_d_f <- 
      solve_s_w_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        beta_f = equilibrium$parameter$beta_f,
        lambda_w = equilibrium$parameter$lambda_w,
        lambda_f = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      ) 
          
    meeting_number <- 
      compute_meeting_number_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      ) 
      
    meeting_number_d_f <- 
      compute_meeting_number_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_f_d_f = s_f_d_f
      ) 
    owner <- equilibrium$exogenous[[t]][[j]]$owner
    o <- t(owner) %*% owner
    f <- equilibrium$endogenous[[t]][[j]]$f
    w <- equilibrium$endogenous[[t]][[j]]$w
    s_w <- equilibrium$endogenous[[t]][[j]]$s_w
    size_f <- equilibrium$exogenous[[t]][[j]]$size_f
    
    b <-  meeting_number * s_w +
      (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
      (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
    
    A <-  (o * s_f_d_f) * size_f
    
    #ridge regularization
    cond_A <- kappa(A)
    
    # Threshold for acceptable conditioning (commonly 1e12)
    if (cond_A < 1e12) {
      condition_c_f <- "well-conditioned"
      c_f <- Matrix::solve(A, b)
    } else {
      condition_c_f <- "ill-conditioned"
      epsilon <- 1e-10
      A_reg <- A + epsilon * diag(ncol(A))
      c_f <- Matrix::solve(A_reg, b)
    }
    obj <- c_f[i]
    term_1 <- (meeting_number * s_w) / diag( (o * s_f_d_f) * size_f)
    term_2 <- (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
    term_3 <- (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
      
      return(
        data.frame(
          value = param_value,
          objective = obj,
          term_1 = term_1[i],
          term_2 = term_2[i],
          term_3 = term_3[i]
        )
      )
    }


g_10 <-
  ggplot(
    objective_values_10, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
      )
    ) +  
  geom_point(
    data = objective_values_10,  
    aes(
      x = value, 
      y = term_1
      ),
    color = "#ff7f0e",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_10,  
    aes(
      x = value, 
      y = term_2
      ),
    color = "#2ca02c"
  ) +
  geom_line(
    data = objective_values_10,  
    aes(
      x = value, 
      y = term_3
      ),
    color = "#1f77b4"
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 2"
  ) +
  scale_color_manual(
    values = 
      c(
        "FALSE" = "black", 
        "TRUE" = "red"
        ),  
    name = "c_f > 0"  # Legend title
  ) 
```

```{r}
g10 <-
  ggplot(
    objective_values_10, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
    )
  ) +  
  geom_point(
    data = objective_values_10,  
    aes(
      x = value, 
      y = term_1
    ),
    color = "#ff7f0e",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_10,  
    aes(
      x = value, 
      y = term_2
    ),
    color = "#2ca02c",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_10,  
    aes(
      x = value, 
      y = term_3
    ),
    color = "#1f77b4",
    size = 0.5
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = c(
      "FALSE" = "black", 
      "TRUE" = "red"
    ),  
    name = "c_f > 0"
  )  +
  annotate(
    "text",
    x = 0,
    y = -100,
    label = "term 1",
    color =  "#ff7f0e"
  ) +
  annotate(
    "text",
    x = 0,
    y = -300,
    label = "term 2",
    color = "#2ca02c"
  )  +
  annotate(
    "text",
    x = 0,
    y = -200,
    label = "term 3",
    color = "#1f77b4"
  ) +
  coord_cartesian(
    ylim = 
      c(
        -500, 
        500
        )
    )  # This restricts the y-axis range
```

```{r, fig.width=12, fig.height=6, out.width='100%'}
gridExtra::grid.arrange(
  g_10,
  g10, 
  ncol=2
  )
```

- Pick up a problematic ths in a problematic market (i.e., $c_i^W < 0$ or $c_i^F < 0$ for $i$ in the market)
  - t = 1, j = 7, i = 2
```{r}
t <- 1
j <- 7
i <- 2
```

## problematic ths
### lambda_w
```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f


objective_values_3 <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
        
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
    s_w_d_w_tj <- diag(s_w_d_w_tj)
    s_w_d_w <- -equilibrium$endogenous[[t]][[j]]$s_w/s_w_d_w_tj
    s_w_d_w <- s_w_d_w[i]
    obj <- c_w[i]

      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_w_d_w = s_w_d_w
        )
      )
    }


g_3 <-
  ggplot(
    objective_values_3, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
      ),
    size = 1.5
    ) +
  geom_line() +
  geom_hline(
  yintercept = equilibrium$endogenous[[t]][[j]]$f[i] - equilibrium$endogenous[[t]][[j]]$w[i],
  color = "blue", 
  linetype = "solid"
  ) +
  geom_point(
    data = objective_values_3,  
    aes(
      x = value, 
      y = s_w_d_w
      ),
    color = "green",
    size = 0.2
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w ths 1"
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    name = "c_w > 0"
  ) +
  annotate(
    "text",
    x = 4,
    y = equilibrium$endogenous[[t]][[j]]$f[i] - equilibrium$endogenous[[t]][[j]]$w[i] + 1,
    label = "f - w",
    color = "blue",
    hjust = + 0.1
  )  +
annotate(
    "text",
    x = 4,
    y = -10,
    label = "-s_w/s_w_d_w",
    color = "green",
    hjust = + 0.1
  ) 

g_3

```

### lambda_f
```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f


objective_values_4 <- 
  foreach(
    param_value = target_list[[2]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = equilibrium$parameter$lambda_w,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_f_d_f <- 
      solve_s_f_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_f = equilibrium$parameter$beta_f,
        lambda_f = param_value,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      )
          
    s_w_d_f <- 
      solve_s_w_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        beta_f = equilibrium$parameter$beta_f,
        lambda_w = equilibrium$parameter$lambda_w,
        lambda_f = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      ) 
          
    meeting_number <- 
      compute_meeting_number_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      ) 
      
    meeting_number_d_f <- 
      compute_meeting_number_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_f_d_f = s_f_d_f
      ) 
    owner <- equilibrium$exogenous[[t]][[j]]$owner
    o <- t(owner) %*% owner
    f <- equilibrium$endogenous[[t]][[j]]$f
    w <- equilibrium$endogenous[[t]][[j]]$w
    s_w <- equilibrium$endogenous[[t]][[j]]$s_w
    size_f <- equilibrium$exogenous[[t]][[j]]$size_f
    
    b <-  meeting_number * s_w +
      (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
      (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
    
    A <-  (o * s_f_d_f) * size_f
    
    #ridge regularization
    cond_A <- kappa(A)
    
    # Threshold for acceptable conditioning (commonly 1e12)
    if (cond_A < 1e12) {
      condition_c_f <- "well-conditioned"
      c_f <- Matrix::solve(A, b)
    } else {
      condition_c_f <- "ill-conditioned"
      epsilon <- 1e-10
      A_reg <- A + epsilon * diag(ncol(A))
      c_f <- Matrix::solve(A_reg, b)
    }
    obj <- c_f[i]
    term_1 <- (meeting_number * s_w) / diag( (o * s_f_d_f) * size_f)
    term_2 <- (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
    term_3 <- (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
      
      return(
        data.frame(
          value = param_value,
          objective = obj,
          term_1 = term_1[i],
          term_2 = term_2[i],
          term_3 = term_3[i]
        )
      )
    }


g_4 <-
  ggplot(
    objective_values_4, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
      )
    ) +  
  geom_point(
    data = objective_values_4,  
    aes(
      x = value, 
      y = term_1
      ),
    color = "#ff7f0e",
    size = 1
  ) +
  geom_line(
    data = objective_values_4,  
    aes(
      x = value, 
      y = term_2
      ),
    color = "#2ca02c",
    size = 1
  ) +
  geom_line(
    data = objective_values_4,  
    aes(
      x = value, 
      y = term_3
      ),
    color = "#1f77b4",
    size = 1
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = 
      c(
        "FALSE" = "black", 
        "TRUE" = "red"
        ),  
    name = "c_f > 0"  # Legend title
  )
```

```{r}
g4 <-
  ggplot(
    objective_values_4, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
    )
  ) +  
  geom_point(
    data = objective_values_4,  
    aes(
      x = value, 
      y = term_1
    ),
    color = "#ff7f0e",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_4,  
    aes(
      x = value, 
      y = term_2
    ),
    color = "#2ca02c",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_4,  
    aes(
      x = value, 
      y = term_3
    ),
    color = "#1f77b4",
    size = 0.5
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = c(
      "FALSE" = "black", 
      "TRUE" = "red"
    ),  
    name = "c_f > 0"
  ) +
  annotate(
    "text",
    x = 0,
    y = -100,
    label = "term 1",
    color =  "#ff7f0e"
  ) +
  annotate(
    "text",
    x = 0,
    y = -300,
    label = "term 2",
    color = "#2ca02c"
  )  +
  annotate(
    "text",
    x = 0,
    y = -200,
    label = "term 3",
    color = "#1f77b4"
  ) +
  coord_cartesian(
    ylim = 
      c(
        -500, 
        500
        )
    )  # This restricts the y-axis range
```

```{r, fig.width=12, fig.height=6, out.width='100%'}
gridExtra::grid.arrange(
  g_4, 
  g4, 
  ncol=2
  )
```

# m_f + m_w = 1.5

- Use exact method and update demand shocks.
```{r}
equilibrium_small <- equilibrium
equilibrium_small$constant$method_s_w <- "exact"
equilibrium_small$parameter$m_w <- 0.75
equilibrium_small$parameter$m_f <- 0.75
```

```{r}
num_ths <- 
  foreach(
    t = seq_along(equilibrium$endogenous),
    .combine = "rbind"
  ) %do% {
    foreach(
      j = seq_along(equilibrium$endogenous[[t]]),
    .combine = "rbind"
    ) %do% {
      num <- length(equilibrium$endogenous[[t]][[j]]$w)
      return(
        data.frame(
          t = t,
          j = j,
          num = num
        )
      )
    }
  }

large_market <- 
  num_ths %>%
  dplyr::filter(
    num >= 5
  )

large_market <- 
  large_market[
    order(
      large_market$t,
      large_market$j,
      decreasing = TRUE
    ), 
  ]
for (
  i in 1:nrow(large_market)
) {
  equilibrium_small$shock[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$endogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$exogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
}

```

- pick normal market t = 1, j = 1

### normal ths 1

```{r}
t <- 1
j <- 1
i <- 2
```

#### lambda_w
```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f

objective_values_5 <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
        
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
    s_w_d_w_tj <- diag(s_w_d_w_tj)
    s_w_d_w <- -equilibrium$endogenous[[t]][[j]]$s_w/s_w_d_w_tj
    s_w_d_w <- s_w_d_w[i]
    obj <- c_w[i]

      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_w_d_w = s_w_d_w
        )
      )
    }


g_5 <-
  ggplot(
    objective_values_5, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(aes(color = objective > 0)) +
  geom_line() +
  geom_hline(
  yintercept = equilibrium$endogenous[[t]][[j]]$f[i] - equilibrium$endogenous[[t]][[j]]$w[i],
  color = "blue", 
  linetype = "solid"
  ) +
  geom_point(
    data = objective_values_5,  
    aes(
      x = value, 
      y = s_w_d_w
      ),
    color = "green",
    size = 0.2
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w ths 1"
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    name = "c_w > 0"
  ) +
  annotate(
    "text",
    x = 4,
    y = equilibrium$endogenous[[t]][[j]]$f[i] - equilibrium$endogenous[[t]][[j]]$w[i] + 1,
    label = "f - w",
    color = "blue",
    hjust = + 0.1
  )  +
annotate(
    "text",
    x = 4,
    y = -10,
    label = "-s_w/s_w_d_w",
    color = "green",
    hjust = + 0.1
  ) 

g_5

```

#### lambda_f
```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f

objective_values_6 <- 
  foreach(
    param_value = target_list[[2]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = equilibrium$parameter$lambda_w,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_f_d_f <- 
      solve_s_f_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_f = equilibrium$parameter$beta_f,
        lambda_f = param_value,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      )
          
    s_w_d_f <- 
      solve_s_w_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        beta_f = equilibrium$parameter$beta_f,
        lambda_w = equilibrium$parameter$lambda_w,
        lambda_f = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      ) 
          
    meeting_number <- 
      compute_meeting_number_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      ) 
      
    meeting_number_d_f <- 
      compute_meeting_number_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_f_d_f = s_f_d_f
      ) 
    owner <- equilibrium$exogenous[[t]][[j]]$owner
    o <- t(owner) %*% owner
    f <- equilibrium$endogenous[[t]][[j]]$f
    w <- equilibrium$endogenous[[t]][[j]]$w
    s_w <- equilibrium$endogenous[[t]][[j]]$s_w
    size_f <- equilibrium$exogenous[[t]][[j]]$size_f
    
    b <-  meeting_number * s_w +
      (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
      (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
    
    A <-  (o * s_f_d_f) * size_f
    
    #ridge regularization
    cond_A <- kappa(A)
    
    # Threshold for acceptable conditioning (commonly 1e12)
    if (cond_A < 1e12) {
      condition_c_f <- "well-conditioned"
      c_f <- Matrix::solve(A, b)
    } else {
      condition_c_f <- "ill-conditioned"
      epsilon <- 1e-10
      A_reg <- A + epsilon * diag(ncol(A))
      c_f <- Matrix::solve(A_reg, b)
    }
    obj <- c_f[i]
    term_1 <- (meeting_number * s_w) / diag( (o * s_f_d_f) * size_f)
    term_2 <- (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
    term_3 <- (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
      
      return(
        data.frame(
          value = param_value,
          objective = obj,
          term_1 = term_1[i],
          term_2 = term_2[i],
          term_3 = term_3[i]
        )
      )
    }


g_6 <-
  ggplot(
    objective_values_6, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
      )
    ) +  
  geom_point(
    data = objective_values_6,  
    aes(
      x = value, 
      y = term_1
      ),
    color = "#ff7f0e",
    size = 0.2
  ) +
  geom_line(
    data = objective_values_6,  
    aes(
      x = value, 
      y = term_2
      ),
    color = "#2ca02c",
    size = 0.2
  ) +
  geom_line(
    data = objective_values_6,  
    aes(
      x = value, 
      y = term_3
      ),
    color = "#1f77b4",
    size = 0.2
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = 
      c(
        "FALSE" = "black", 
        "TRUE" = "red"
        ),  
    name = "c_f > 0"  # Legend title
  )
```

```{r}
g6 <-
  ggplot(
    objective_values_6, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
    )
  ) +  
  geom_point(
    data = objective_values_6,  
    aes(
      x = value, 
      y = term_1
    ),
    color = "#ff7f0e",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_6,  
    aes(
      x = value, 
      y = term_2
    ),
    color = "#2ca02c",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_6,  
    aes(
      x = value, 
      y = term_3
    ),
    color = "#1f77b4",
    size = 0.5
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = c(
      "FALSE" = "black", 
      "TRUE" = "red"
    ),  
    name = "c_f > 0"
  )  +
  annotate(
    "text",
    x = 0,
    y = -100,
    label = "term 1",
    color =  "#ff7f0e"
  ) +
  annotate(
    "text",
    x = 0,
    y = -300,
    label = "term 2",
    color = "#2ca02c"
  )  +
  annotate(
    "text",
    x = 0,
    y = -200,
    label = "term 3",
    color = "#1f77b4"
  ) +
  coord_cartesian(
    ylim = 
      c(
        -500, 
        500
        )
    )  # This restricts the y-axis range
```

```{r, fig.width=12, fig.height=6, out.width='100%'}
gridExtra::grid.arrange(
  g_6, 
  g6, 
  ncol=2
  )
```

### normal ths 2
```{r}
i <- 3
```

#### lambda_w
```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f

objective_values_11 <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
        
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
    s_w_d_w_tj <- diag(s_w_d_w_tj)
    s_w_d_w <- -equilibrium$endogenous[[t]][[j]]$s_w/s_w_d_w_tj
    s_w_d_w <- s_w_d_w[i]
    obj <- c_w[i]

      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_w_d_w = s_w_d_w
        )
      )
    }


g_11 <-
  ggplot(
    objective_values_11, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(aes(color = objective > 0)) +
  geom_line() +
  geom_hline(
  yintercept = equilibrium$endogenous[[t]][[j]]$f[i] - equilibrium$endogenous[[t]][[j]]$w[i],
  color = "blue", 
  linetype = "solid"
  ) +
  geom_point(
    data = objective_values_11,  
    aes(
      x = value, 
      y = s_w_d_w
      ),
    color = "green",
    size = 0.2
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w ths 2"
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    name = "c_w > 0"
  ) 

g_11

```

#### lambda_f
```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f

objective_values_12 <- 
  foreach(
    param_value = target_list[[2]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = equilibrium$parameter$lambda_w,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_f_d_f <- 
      solve_s_f_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_f = equilibrium$parameter$beta_f,
        lambda_f = param_value,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      )
          
    s_w_d_f <- 
      solve_s_w_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        beta_f = equilibrium$parameter$beta_f,
        lambda_w = equilibrium$parameter$lambda_w,
        lambda_f = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      ) 
          
    meeting_number <- 
      compute_meeting_number_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      ) 
      
    meeting_number_d_f <- 
      compute_meeting_number_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_f_d_f = s_f_d_f
      ) 
    owner <- equilibrium$exogenous[[t]][[j]]$owner
    o <- t(owner) %*% owner
    f <- equilibrium$endogenous[[t]][[j]]$f
    w <- equilibrium$endogenous[[t]][[j]]$w
    s_w <- equilibrium$endogenous[[t]][[j]]$s_w
    size_f <- equilibrium$exogenous[[t]][[j]]$size_f
    
    b <-  meeting_number * s_w +
      (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
      (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
    
    A <-  (o * s_f_d_f) * size_f
    
    #ridge regularization
    cond_A <- kappa(A)
    
    # Threshold for acceptable conditioning (commonly 1e12)
    if (cond_A < 1e12) {
      condition_c_f <- "well-conditioned"
      c_f <- Matrix::solve(A, b)
    } else {
      condition_c_f <- "ill-conditioned"
      epsilon <- 1e-10
      A_reg <- A + epsilon * diag(ncol(A))
      c_f <- Matrix::solve(A_reg, b)
    }
    obj <- c_f[i]
    term_1 <- (meeting_number * s_w) / diag( (o * s_f_d_f) * size_f)
    term_2 <- (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
    term_3 <- (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
      
      return(
        data.frame(
          value = param_value,
          objective = obj,
          term_1 = term_1[i],
          term_2 = term_2[i],
          term_3 = term_3[i]
        )
      )
    }


g_12 <-
  ggplot(
    objective_values_12, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
      )
    ) +  
  geom_point(
    data = objective_values_12,  
    aes(
      x = value, 
      y = term_1
      ),
    color = "#ff7f0e",
    size = 1
  ) +
  geom_line(
    data = objective_values_12,  
    aes(
      x = value, 
      y = term_2
      ),
    color = "#2ca02c",
    size = 1
  ) +
  geom_line(
    data = objective_values_12,  
    aes(
      x = value, 
      y = term_3
      ),
    color = "#1f77b4",
    size = 1
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 2"
  ) +
  scale_color_manual(
    values = 
      c(
        "FALSE" = "black", 
        "TRUE" = "red"
        ),  
    name = "c_f > 0"  # Legend title
  ) 
```

```{r}
g12 <-
  ggplot(
    objective_values_12, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
    )
  ) +  
  geom_point(
    data = objective_values_12,  
    aes(
      x = value, 
      y = term_1
    ),
    color = "#ff7f0e",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_12,  
    aes(
      x = value, 
      y = term_2
    ),
    color = "#2ca02c",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_12,  
    aes(
      x = value, 
      y = term_3
    ),
    color = "#1f77b4",
    size = 0.5
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = c(
      "FALSE" = "black", 
      "TRUE" = "red"
    ),  
    name = "c_f > 0"
  )  +
  annotate(
    "text",
    x = 0,
    y = -100,
    label = "term 1",
    color =  "#ff7f0e"
  ) +
  annotate(
    "text",
    x = 0,
    y = -300,
    label = "term 2",
    color = "#2ca02c"
  )  +
  annotate(
    "text",
    x = 0,
    y = -200,
    label = "term 3",
    color = "#1f77b4"
  ) +
  coord_cartesian(
    ylim = 
      c(
        -500, 
        500
        )
    )  # This restricts the y-axis range
```

```{r, fig.width=12, fig.height=6, out.width='100%'}
gridExtra::grid.arrange(
  g_12, 
  g12, 
  ncol=2
  )
```
- Pick up a problematic ths in a problematic market (i.e., $c_i^W < 0$ or $c_i^F < 0$ for $i$ in the market)
  - t = 1, j = 3, i = 2
```{r}
t <- 1
j <- 3
i <- 2
```

## problematic ths

#### lambda_w

```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f

objective_values_7 <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
        
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
    s_w_d_w_tj <- diag(s_w_d_w_tj)
    s_w_d_w <- -equilibrium$endogenous[[t]][[j]]$s_w/s_w_d_w_tj
    s_w_d_w <- s_w_d_w[i]
    obj <- c_w[i]

      return(
        data.frame(
          value = param_value,
          objective = obj,
          s_w_d_w = s_w_d_w
        )
      )
    }


g_7 <-
  ggplot(
    objective_values_7, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
      )
    ) +
  geom_line() +
  geom_hline(
  yintercept = equilibrium$endogenous[[t]][[j]]$f[i] - equilibrium$endogenous[[t]][[j]]$w[i],
  color = "blue", 
  linetype = "solid"
  ) +
  geom_point(
    data = objective_values_7,  
    aes(
      x = value, 
      y = s_w_d_w
      ),
    color = "green",
    size = 0.2
  ) +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "c_w ths 1"
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    name = "c_w > 0"
  ) 
g_7

```

#### lambda_f
```{r, cache=TRUE}
# reset lambda_w and lambda_f
equilibrium_small$parameter$lambda_w <- equilibrium$parameter$lambda_w
equilibrium_small$parameter$lambda_f <- equilibrium$parameter$lambda_f

objective_values_8 <- 
  foreach(
    param_value = target_list[[2]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_f <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    c_w <- 
      compute_supply_shock_c_w_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        lambda_w = equilibrium$parameter$lambda_w,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_w = equilibrium$endogenous[[t]][[j]]$s_w,
        owner = equilibrium$exogenous[[t]][[j]]$owner,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      )
    s_f_d_f <- 
      solve_s_f_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_f = equilibrium$parameter$beta_f,
        lambda_f = param_value,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      )
          
    s_w_d_f <- 
      solve_s_w_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        beta_w = equilibrium$parameter$beta_w,
        beta_f = equilibrium$parameter$beta_f,
        lambda_w = equilibrium$parameter$lambda_w,
        lambda_f = param_value,
        x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
        x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        ea_w = equilibrium$shock[[t]][[j]]$ea_w,
        ea_f = equilibrium$shock[[t]][[j]]$ea_f,
        w = equilibrium$endogenous[[t]][[j]]$w,
        f = equilibrium$endogenous[[t]][[j]]$f,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        method_s_w = equilibrium$constant$method_s_w,
        margin = equilibrium$constant$margin,
        quadrature_size = equilibrium$constant$quadrature_size,
        tol = equilibrium$constant$tol
      ) 
          
    meeting_number <- 
      compute_meeting_number_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f
      ) 
      
    meeting_number_d_f <- 
      compute_meeting_number_d_f_tj(
        m_w = equilibrium$parameter$m_w,
        m_f = equilibrium$parameter$m_f,
        size_w = equilibrium$exogenous[[t]][[j]]$size_w,
        size_f = equilibrium$exogenous[[t]][[j]]$size_f,
        mu = equilibrium$shock[[t]][[j]]$mu,
        s_f = equilibrium$endogenous[[t]][[j]]$s_f,
        s_f_d_f = s_f_d_f
      ) 
    owner <- equilibrium$exogenous[[t]][[j]]$owner
    o <- t(owner) %*% owner
    f <- equilibrium$endogenous[[t]][[j]]$f
    w <- equilibrium$endogenous[[t]][[j]]$w
    s_w <- equilibrium$endogenous[[t]][[j]]$s_w
    size_f <- equilibrium$exogenous[[t]][[j]]$size_f
    
    b <-  meeting_number * s_w +
      (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) +
      (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) 
    
    A <-  (o * s_f_d_f) * size_f
    
    #ridge regularization
    cond_A <- kappa(A)
    
    # Threshold for acceptable conditioning (commonly 1e12)
    if (cond_A < 1e12) {
      condition_c_f <- "well-conditioned"
      c_f <- Matrix::solve(A, b)
    } else {
      condition_c_f <- "ill-conditioned"
      epsilon <- 1e-10
      A_reg <- A + epsilon * diag(ncol(A))
      c_f <- Matrix::solve(A_reg, b)
    }
    obj <- c_f[i]
    term_1 <- (meeting_number * s_w) / diag( (o * s_f_d_f) * size_f)
    term_2 <- (o * s_w_d_f) %*% (meeting_number * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
    term_3 <- (o * meeting_number_d_f) %*% (s_w * (f - w - c_w)) / diag( (o * s_f_d_f) * size_f)
      
      return(
        data.frame(
          value = param_value,
          objective = obj,
          term_1 = term_1[i],
          term_2 = term_2[i],
          term_3 = term_3[i]
        )
      )
    }


g_8 <-
  ggplot(
    objective_values_8, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
      )
    ) +  
  geom_point(
    data = objective_values_8,  
    aes(
      x = value, 
      y = term_1
      ),
    color = "#ff7f0e",
    size = 0.2
  ) +
  geom_line(
    data = objective_values_8,  
    aes(
      x = value, 
      y = term_2
      ),
    color = "#2ca02c",
    size = 0.2
  ) +
  geom_line(
    data = objective_values_8,  
    aes(
      x = value, 
      y = term_3
      ),
    color = "#1f77b4",
    size = 0.2
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = 
      c(
        "FALSE" = "black", 
        "TRUE" = "red"
        ),  
    name = "c_f > 0"  # Legend title
  ) 
```

```{r}
g8 <-
  ggplot(
    objective_values_8, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point(
    aes(
      color = objective > 0
    )
  ) +  
  geom_point(
    data = objective_values_8,  
    aes(
      x = value, 
      y = term_1
    ),
    color = "#ff7f0e",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_8,  
    aes(
      x = value, 
      y = term_2
    ),
    color = "#2ca02c",
    size = 0.5
  ) +
  geom_line(
    data = objective_values_8,  
    aes(
      x = value, 
      y = term_3
    ),
    color = "#1f77b4",
    size = 0.5
  ) +
  theme_classic() +
  labs(
    x = "Lambda_f",
    y = "c_f ths 1"
  ) +
  scale_color_manual(
    values = c(
      "FALSE" = "black", 
      "TRUE" = "red"
    ),  
    name = "c_f > 0"
  ) +
  annotate(
    "text",
    x = 0,
    y = -100,
    label = "term 1",
    color =  "#ff7f0e"
  ) +
  annotate(
    "text",
    x = 0,
    y = -300,
    label = "term 2",
    color = "#2ca02c"
  )  +
  annotate(
    "text",
    x = 0,
    y = -200,
    label = "term 3",
    color = "#1f77b4"
  ) +
  coord_cartesian(
    ylim = 
      c(
        -500, 
        500
        )
    )  # This restricts the y-axis range
```

```{r, fig.width=12, fig.height=6, out.width='100%'}
gridExtra::grid.arrange(
  g8, 
  g_8, 
  ncol=2
  )
```


# Why $\frac{\partial s_i^W}{\partial w_i}$ is not monotone in $\lambda_w$?

- From the above graph, pick up the point before and after the jump in $\frac{\partial s_i^W}{\partial w_i}$.
- Check why this is so different.


```{r}
# reset equilibrium
equilibrium_small <- equilibrium
equilibrium_small$constant$method_s_w <- "exact"

num_ths <- 
  foreach(
    t = seq_along(equilibrium$endogenous),
    .combine = "rbind"
  ) %do% {
    foreach(
      j = seq_along(equilibrium$endogenous[[t]]),
    .combine = "rbind"
    ) %do% {
      num <- length(equilibrium$endogenous[[t]][[j]]$w)
      return(
        data.frame(
          t = t,
          j = j,
          num = num
        )
      )
    }
  }

large_market <- 
  num_ths %>%
  dplyr::filter(
    num >= 5
  )

large_market <- 
  large_market[
    order(
      large_market$t,
      large_market$j,
      decreasing = TRUE
    ), 
  ]
for (
  i in 1:nrow(large_market)
) {
  equilibrium_small$shock[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$endogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
  equilibrium_small$exogenous[[large_market$t[i]]][[large_market$j[i]]] <- NULL
}

```

## normal market
```{r}
t <- 1
j <- 1
```

### normal ths 1
```{r}
i <- 2
```

```{r}

obj_s_w_d_w <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
    s_w_d_w_tj <- diag(s_w_d_w_tj)
    obj <- s_w_d_w_tj[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_s_w_d_w <-
  ggplot(
    obj_s_w_d_w, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "s_w_d_w ths 1"
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    name = "c_w > 0"
  ) 
g_s_w_d_w 

```


### normal ths 2
```{r}
i <- 3
```

```{r}

obj_s_w_d_w <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
    s_w_d_w_tj <- diag(s_w_d_w_tj)
    obj <- s_w_d_w_tj[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_s_w_d_w <-
  ggplot(
    obj_s_w_d_w, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "s_w_d_w ths 2"
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    name = "c_w > 0"
  ) 
g_s_w_d_w 

```

## problematic ths

```{r}
t <- 1
j <- 7
i <- 2
```

```{r}

obj_s_w_d_w <- 
  foreach(
    param_value = target_list[[1]],
    .combine = "rbind",
    .packages = 
      c(
        "Dispatching",
        "foreach",
        "magrittr"
      )
    ) %dopar% {
    
    equilibrium_small$parameter$lambda_w <- param_value
    result_demand <- 
      solve_demand_shock(
        equilibrium = equilibrium_small
      )
    equilibrium_small <-
      update_demand_ea_beta(
        result_demand = result_demand,
        equilibrium = equilibrium_small
      ) 
    s_w_d_w_tj <- 
        solve_s_w_d_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = param_value,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )
    s_w_d_w_tj <- diag(s_w_d_w_tj)
    obj <- s_w_d_w_tj[i]

      return(
        data.frame(
          value = param_value,
          objective = obj
        )
      )
    }


g_s_w_d_w <-
  ggplot(
    obj_s_w_d_w, 
    aes(
      x = value, 
      y = objective
    )
  ) +
  geom_point() +
  geom_line() +
  theme_classic() +
  labs(
    x = "Lambda_w",
    y = "s_w_d_w ths 1"
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    name = "c_w > 0"
  ) 
g_s_w_d_w 

```