---
title: "report data analysis for cz data"
author: "Chiho Taniguchi"
date: "2023-02-26"
output: 
  html_document:
    toc: true
---
```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 3, fig.width = 4)

library("magrittr")
library("kableExtra")
library("ggplot2")

height <- 6
width <- 8

```

```{css, echo = FALSE}

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

```


```{r }

 data_establishments <- 
  here::here(file = "cleaned/data_establishments.rds") %>% 
  readRDS()

 data_zipcode <- 
   here::here(file = "cleaned/data_zipcode.rds") %>% 
   readRDS()
 
 data_area <- 
   here::here(file = "cleaned/data_area.rds") %>% 
   readRDS()
 
 data_zip_establishments <- 
   here::here(file = "output/data_zip_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments <- 
   here::here(file = "output/data_cz_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments_all <- 
   here::here(file = "output/data_cz_establishments_all.rds") %>% 
   readRDS()
 
 data_zip_establishments_all <- 
   here::here(file = "output/data_zip_establishments_all.rds") %>% 
   readRDS()
   
 data_cz_establishments_all_ippann <- 
   here::here(file = "output/data_cz_establishments_all_ippann.rds") %>% 
   readRDS()
 
 data_zip_establishments_all_ippann <- 
   here::here(file = "output/data_zip_establishments_all_ippann.rds") %>% 
   readRDS()
 
```

# Data construction

We use data defining the market as commuting zone(cz) and restrict data to the general establishments only for analysis.
After dropping establishments which have missing either of wage / fee / cz data and creating log transformed wage / fee, we create N_jt and dummy variables indicating the N_jt. N_jt and dummy variables are explained in detail later.

# Descriptive statistics {.tabset}

## wage (wage_{it})

```{r}

data_cz_establishments_wage_fee <- 
   data_cz_establishments %>% 
   dplyr::group_by(
     year, 
     cz
     ) %>% 
   dplyr::mutate(
     wage_jt = mean(wage),
     fee_jt = mean(fee)
     ) 
 
 wage_jt_unique <- 
   data_cz_establishments_wage_fee %>% 
   dplyr::select(wage_jt) %>% 
   unique()
 
 summary(wage_jt_unique$wage_jt) 

```

## fee (fee_{it})

```{r}

fee_jt_unique <- 
   data_cz_establishments_wage_fee %>% 
   dplyr::select(fee_jt) %>% 
   unique() 
 
 summary(fee_jt_unique$fee_jt)

```

## N_jt

N_jt is a variable that indicates the number of general establishments present in commuting zone(j) in year t.

```{r }
 N_jt_unique <- 
   data_cz_establishments %>% 
   dplyr::select(N_jt) %>% 
   unique()
 
 quantile(
   N_jt_unique$N_jt, 
   c(0.1, 0.25, 0.5, 0.75, 1)
   ) %>% 
   kbl(col.names = "N_jt") %>% 
   kable_styling(full_width = FALSE)
```

### Show historgam

On the left is the distribution of N_jt, without duplicates, and on the right is the distribution of N_jt, using all data (allowing duplicates).

```{r}
 ## show histogram
 histogram_N_jt_unique <- 
   ggplot() + 
   geom_histogram(
     data = N_jt_unique, 
     mapping = aes(x = N_jt),
     bins = 100
   )
 
 print(histogram_N_jt_unique)
 
 data_cz_establishments_N_jt <- 
   data_cz_establishments %>% 
   dplyr::select(N_jt)
 
 histogram_N_jt <- 
   ggplot() + 
   geom_histogram(
     data = data_cz_establishments_N_jt, 
     mapping = aes(x = N_jt),
     bins = 100
   )
 
 print(histogram_N_jt)
```

# Analyze different N_jt {.tabset}

Analyze the impact of the number of general establishments in each market (cz) on the log transformed wage / fee:

$$

Y_{ijt} = \beta N_{jt} + c_{j}  + c_{t} + u_{ijt},\\
Y_{ijt} = \beta N_{jt} + c_{i} + c_{t} + u_{ijt},\\
Y_{ijt} = \beta N_{jt} + c_{j} + c_{i} + c_{t} + u_{ijt}.

$$

$i$: Establishment, $j$: Commuting zone, $t$: Year<br>
$Y_{ijt}$: $\log{(wage_{ijt})}$, $\log{(fee_{ijt})}$

We also analyze N_jt is divided by the number after N_jt.

## Analyze for N_jt

```{r}
results1 <- list()

results1[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt | cz + year ,
    data = data_cz_establishments
  )

results1[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt | year + firm_id ,
    data = data_cz_establishments
  )

results1[[3]] <- 
  lfe::felm(
    formula = log_fee ~ N_jt | year + firm_id + cz,
    data = data_cz_establishments
  )

results1[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt | cz + year ,
    data = data_cz_establishments
  )

results1[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt | year + firm_id ,
    data = data_cz_establishments
  )

results1[[6]] <- 
  lfe::felm(
    formula = log_wage ~ N_jt | year + firm_id + cz, 
    data = data_cz_establishments
  )

rows <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`, ~`(6)`,
    'j_FE', 'Y', 'N', 'Y', 'Y', 'N', 'Y',
    't_FE', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y',
    'i_FE', 'N', 'Y', 'Y', 'N', 'Y', 'Y',
  )

attr(rows, 'position') <- c(3, 4, 5, 6)

result_1 <- 
  list(
    "log(fee)" = results1[[1]],
    "log(fee)" = results1[[2]],
    "log(fee)" = results1[[3]],
    "log(wage)" = results1[[4]],
    "log(wage)" = results1[[5]],
    "log(wage)" = results1[[6]]
  )

modelsummary::modelsummary(
  result_1,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 

```

## Analyze for N_jt_10 

```{r}

results3 <- list()

results3[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_10 | cz + year ,
    data = data_cz_establishments
  )

results3[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_10 | year + firm_id ,
    data = data_cz_establishments
  )

results3[[3]] <- 
  lfe::felm(
    formula = log_fee ~ N_jt_10 | year + firm_id + cz,
    data = data_cz_establishments
  )

results3[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_10 | cz + year ,
    data = data_cz_establishments
  )

results3[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_10 | year + firm_id ,
    data = data_cz_establishments
  )

results3[[6]] <- 
  lfe::felm(
    formula = log_wage ~ N_jt_10 | year + firm_id + cz, 
    data = data_cz_establishments
  )


attr(rows, 'position') <- c(3, 4, 5, 6)

result_3 <- 
  list(
    "log(fee)" = results3[[1]],
    "log(fee)" = results3[[2]],
    "log(fee)" = results3[[3]],
    "log(wage)" = results3[[4]],
    "log(wage)" = results3[[5]],
    "log(wage)" = results3[[6]]
    )

modelsummary::modelsummary(
  result_3,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 


```
 
## Analyze for N_jt_100 
 
```{r}

results5 <- list()

results5[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_100 | cz + year ,
    data = data_cz_establishments
  )

results5[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_100 | year + firm_id ,
    data = data_cz_establishments
  )

results5[[3]] <- 
  lfe::felm(
    formula = log_fee ~ N_jt_100 | year + firm_id + cz,
    data = data_cz_establishments
  )

results5[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_100 | cz + year ,
    data = data_cz_establishments
  )

results5[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_100 | year + firm_id ,
    data = data_cz_establishments
  )

results5[[6]] <- 
  lfe::felm(
    formula = log_wage ~ N_jt_100 | year + firm_id + cz, 
    data = data_cz_establishments
  )


attr(rows, 'position') <- c(3, 4, 5, 6)

result_5 <- 
  list(
    "log(fee)" = results5[[1]],
    "log(fee)" = results5[[2]],
    "log(fee)" = results5[[3]],
    "log(wage)" = results5[[4]],
    "log(wage)" = results5[[5]],
    "log(wage)" = results5[[6]]
  )

modelsummary::modelsummary(
  result_5,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 


```

## Analyze for N_jt_1000

```{r}

results4 <- list()

results4[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_1000 | cz + year ,
    data = data_cz_establishments
  )

results4[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_1000 | year + firm_id ,
    data = data_cz_establishments
  )

results4[[3]] <- 
  lfe::felm(
    formula = log_fee ~ N_jt_1000 | year + firm_id + cz,
    data = data_cz_establishments
  )

results4[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_1000 | cz + year ,
    data = data_cz_establishments
  )

results4[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_1000 | year + firm_id ,
    data = data_cz_establishments
  )

results4[[6]] <- 
  lfe::felm(
    formula = log_wage ~ N_jt_1000 | year + firm_id + cz, 
    data = data_cz_establishments
  )


attr(rows, 'position') <- c(3, 4, 5, 6)

result_4 <- 
  list(
    "log(fee)" = results4[[1]],
    "log(fee)" = results4[[2]],
    "log(fee)" = results4[[3]],
    "log(wage)" = results4[[4]],
    "log(wage)" = results4[[5]],
    "log(wage)" = results4[[6]]
  )

modelsummary::modelsummary(
  result_4,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 

```

## Analyze for N_jt_10000 

```{r}

results6 <- list()

results6[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_10000 | cz + year ,
    data = data_cz_establishments
  )

results6[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_10000 | year + firm_id ,
    data = data_cz_establishments
  )

results6[[3]] <- 
  lfe::felm(
    formula = log_fee ~ N_jt_10000 | year + firm_id + cz,
    data = data_cz_establishments
  )

results6[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_10000 | cz + year ,
    data = data_cz_establishments
  )

results6[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_10000 | year + firm_id ,
    data = data_cz_establishments
  )

results6[[6]] <- 
  lfe::felm(
    formula = log_wage ~ N_jt_10000 | year + firm_id + cz, 
    data = data_cz_establishments
  )


attr(rows, 'position') <- c(3, 4, 5, 6)

result_6 <- 
  list(
    "log(fee)" = results6[[1]],
    "log(fee)" = results6[[2]],
    "log(fee)" = results6[[3]],
    "log(wage)" = results6[[4]],
    "log(wage)" = results6[[5]],
    "log(wage)" = results6[[6]]
  )

modelsummary::modelsummary(
  result_6,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 

```

## Analyze for N_jt_100000 

```{r}

results7 <- list()

results7[[1]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_100000 | cz + year ,
    data = data_cz_establishments
  )

results7[[2]] <- 
  lfe::felm(
    formula = log_fee ~  N_jt_100000 | year + firm_id ,
    data = data_cz_establishments
  )

results7[[3]] <- 
  lfe::felm(
    formula = log_fee ~ N_jt_100000 | year + firm_id + cz,
    data = data_cz_establishments
  )

results7[[4]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_100000 | cz + year ,
    data = data_cz_establishments
  )

results7[[5]] <- 
  lfe::felm(
    formula = log_wage ~  N_jt_100000 | year + firm_id ,
    data = data_cz_establishments
  )

results7[[6]] <- 
  lfe::felm(
    formula = log_wage ~ N_jt_100000 | year + firm_id + cz, 
    data = data_cz_establishments
  )


attr(rows, 'position') <- c(3, 4, 5, 6)

result_7 <- 
  list(
    "log(fee)" = results7[[1]],
    "log(fee)" = results7[[2]],
    "log(fee)" = results7[[3]],
    "log(wage)" = results7[[4]],
    "log(wage)" = results7[[5]],
    "log(wage)" = results7[[6]]
  )

modelsummary::modelsummary(
  result_7,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows
) 

```

# Analyze for N_jt with categorical dummy variables {.tabset}

Analyze the impact of the marginally increase in the number of general establishments in each market (cz) on the log transformed wage / fee:

$$



$$

$i$: Establishment, $j$: Commuting zone, $t$: Year<br>
$Y_{ijt}$: $\log{(wage_{ijt})}$, $\log{(fee_{ijt})}$

## Categorical variables per quantile (20)

We create categorical dummy variables as follows.

D_20 : Dummy variable that takes 1 when N_jt is less than the 20th percentile value<br>
D_40 : Dummy variable that takes 1 when N_jt is greater than or equal to the 20th percentile value and less than or equal to the 40th percentile value<br>
D_60 : Dummy variable that takes 1 when N_jt is greater than the 40th percentile value and less than the 60th percentile value<br>
D_80 : Dummy variable that takes 1 when N_jt is above the 60th percentile value and below the 80th percentile value<br>
D_100 : Dummy variable that takes 1 when N_jt is greater than or equal to the 80th percentile value

```{r}

results21 <- list()

results21[[1]] <- 
  lfe::felm(
    formula = log_fee ~ D_40 + D_60 + D_80 + D_100 | cz + year ,
    data = data_cz_establishments
  )

results21[[2]] <- 
  lfe::felm(
    formula = log_fee ~ D_40 + D_60 + D_80 + D_100 | year + firm_id ,
    data = data_cz_establishments
  )

results21[[3]] <- 
  lfe::felm(
    formula = log_fee ~ D_40 + D_60 + D_80 + D_100 | year + firm_id + cz,
    data = data_cz_establishments
  )

results21[[4]] <- 
  lfe::felm(
    formula = log_wage ~ D_40 + D_60 + D_80 + D_100 | cz + year ,
    data = data_cz_establishments
  )

results21[[5]] <- 
  lfe::felm(
    formula = log_wage ~ D_40 + D_60 + D_80 + D_100 | year + firm_id ,
    data = data_cz_establishments
  )

results21[[6]] <- 
  lfe::felm(
    formula = log_wage ~ D_40 + D_60 + D_80 + D_100 | year + firm_id + cz,
    data = data_cz_establishments
  )

rows_D <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`, ~`(6)`,
    'j_FE', 'Y', 'N', 'Y', 'Y', 'N', 'Y',
    't_FE', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y',
    'i_FE', 'N', 'Y', 'Y', 'N', 'Y', 'Y',
  )

attr(rows_D, 'position') <- c(9, 10, 11, 12)

result_21 <- 
  list(
    "log(fee)" = results21[[1]],
    "log(fee)" = results21[[2]],
    "log(fee)" = results21[[3]],
    "log(wage)" = results21[[4]],
    "log(wage)" = results21[[5]],
    "log(wage)" = results21[[6]]
  )

modelsummary::modelsummary(
  result_21,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows_D
) 

```

## Categorical variables per quantile (10)

We create categorical dummy variables as follows.

D10 : Dummy variable that takes 1 when N_jt is less than the 10th percentile value<br>
D20 : Dummy variable that takes 1 when N_jt is greater than or equal to the 10th percentile value and less than the 20th percentile value<br>
D30 : Dummy variable that takes 1 when N_jt is greater than the 20th percentile value and less than the 30th percentile value<br>
D40 : Dummy variable that takes 1 when N_jt is above the 30th percentile value and below the 40th percentile value<br>
D50 : Dummy variable that takes 1 when N_jt is above the 40th percentile value and below the 50th percentile value<br>
D60 : Dummy variable that takes 1 when N_jt is above the 50th percentile value and below the 60th percentile value<br>
D70 : Dummy variable that takes 1 when N_jt is above the 60th percentile value and below the 70th percentile value<br>
D80 : Dummy variable that takes 1 when N_jt is above the 70th percentile value and below the 80th percentile value<br>
D90 : Dummy variable that takes 1 when N_jt is above the 80th percentile value and below the 90th percentile value<br>
D100 : Dummy variable that takes 1 when N_jt is greater than or equal to the 90th percentile value

```{r}

results8 <- list()

results8[[1]] <- 
  lfe::felm(
    formula = log_fee ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | cz + year ,
    data = data_cz_establishments
  )

results8[[2]] <- 
  lfe::felm(
    formula = log_fee ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | year + firm_id ,
    data = data_cz_establishments
  )

results8[[3]] <- 
  lfe::felm(
    formula = log_fee ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | year + firm_id + cz,
    data = data_cz_establishments
  )

results8[[4]] <- 
  lfe::felm(
    formula = log_wage ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | cz + year ,
    data = data_cz_establishments
  )

results8[[5]] <- 
  lfe::felm(
    formula = log_wage ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | year + firm_id ,
    data = data_cz_establishments
  )

results8[[6]] <- 
  lfe::felm(
    formula = log_wage ~ D20 + D30 + D40 + D50 + D60 + D70 + D80 + D90 + D100 | year + firm_id + cz,
    data = data_cz_establishments
  )

rows_D <- 
  tibble::tribble(
    ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`, ~`(6)`,
    'j_FE', 'Y', 'N', 'Y', 'Y', 'N', 'Y',
    't_FE', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y',
    'i_FE', 'N', 'Y', 'Y', 'N', 'Y', 'Y',
  )

attr(rows_D, 'position') <- c(19, 20, 21, 22)

result_8 <- 
  list(
    "log(fee)" = results8[[1]],
    "log(fee)" = results8[[2]],
    "log(fee)" = results8[[3]],
    "log(wage)" = results8[[4]],
    "log(wage)" = results8[[5]],
    "log(wage)" = results8[[6]]
  )

modelsummary::modelsummary(
  result_8,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC",
  add_rows = rows_D
) 

```

# Analyze using Bartik IV (bartik_cz_t) {.tabset}

$$

$$

$i$: Establishment, $j$: Commuting zone, $t$: Year<br>
$Y_{ijt}$: $\log{(wage_{ijt})}$, $\log{(fee_{ijt})}$

## 2nd stage

$$

$$

```{r}

results_b1 <- list()
 
 results_b1[[1]] <- 
   lfe::felm(
     formula = log_fee ~ 1 | cz + year | (N_jt_1000 ~ bartik_cz_t) | cz,
     data = data_cz_establishments_all_ippann
   )
 
 results_b1[[2]] <- 
   lfe::felm(
     formula = log_wage ~ 1 | cz + year | (N_jt_1000 ~ bartik_cz_t) | cz,
     data = data_cz_establishments_all_ippann
   )
 
 rows <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`,
     'j_FE', 'Y', 'Y',
     't_FE', 'Y', 'Y',
     'i_FE', 'N', 'N', 
   )
 
 attr(rows, 'position') <- c(3, 4, 5, 6)
 
 resultsb1 <- 
   list(
     "log(fee)" = results_b1[[1]],
     "log(wage)" = results_b1[[2]]
   )
 
 modelsummary::modelsummary(
   resultsb1,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```


## 1st stage

$$

$$


```{r}

rows <- 
   tibble::tribble(
     ~term, ~`(1)`
     )
 
 attr(rows, 'position') <- c(3, 4, 5, 6)
 
 resultsb3 <- 
   list(
     "N_jt_1000(1st stage cz)" = results_b1[[1]]$stage1
   )
 
 modelsummary::modelsummary(
   resultsb3,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95
 )

```

## reduced form

$$

$$


```{r}

results_b2 <- list()
 
 results_b2[[1]] <- 
   lfe::felm(
     formula = log_fee ~ bartik_cz_t | cz + year ,
     data = data_cz_establishments_all_ippann
   )
 
 results_b2[[2]] <- 
   lfe::felm(
     formula = log_wage ~ bartik_cz_t | cz + year,
     data = data_cz_establishments_all_ippann
   )
 
 rows <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`,
     'j_FE', 'Y', 'Y',
     't_FE', 'Y', 'Y',
     'i_FE', 'N', 'N', 
   )
 
 attr(rows, 'position') <- c(3, 4, 5, 6)
 
 resultsb1 <- 
   list(
     "log(fee)" = results_b2[[1]],
     "log(wage)" = results_b2[[2]]
   )
 
 modelsummary::modelsummary(
   resultsb1,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

# Analyze residuals for cz data {.tabset}

## Regress N_jt on commuting zone (cz) / year fixed effect

$$


$$

```{r}

result_u_cz <- 
   lfe::felm(
     formula = N_jt_1000 ~ 1 + cz + year ,
     data = data_cz_establishments_all_ippann
   )
 
 id <- c(1:71486)
 
 residual_cz <-
   as.data.frame(result_u_cz$residuals) %>% 
   dplyr::rename(u_hat_cz = N_jt_1000) %>% 
   cbind(id)
 
 residual_cz_unique <- 
   residual_cz %>% 
   dplyr::select(
     u_hat_cz
   ) %>% 
   unique() %>% 
   as.data.frame() 

```

### Show histogram (unique)

On the left is the distribution of the residuals, without duplicates, and on the right is the distribution of the residuals, using all data (allowing duplicates).

```{r}

histogram_residuals_cz_unique <- 
   ggplot() + 
   geom_histogram(
     data = residual_cz_unique, 
     mapping = aes(x = u_hat_cz),
     bins = 100
   )
 
 print(histogram_residuals_cz_unique)
 
 residual_cz_all <- 
   residual_cz 
 
 histogram_residuals_cz_all <- 
   ggplot() + 
   geom_histogram(
     data = residual_cz_all, 
     mapping = aes(x = u_hat_cz),
     bins = 100
   )
 
 print(histogram_residuals_cz_all)
 

```

### Summary of the residuals

```{r}

summary(residual_cz_unique)

```


