---
title: "Standard Errors for Estimation Results"
author: "Daisy Dan Song"
date: "2026-01-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
library(Dispatching)
library(foreach)
library(magrittr)
library(dplyr)
library(tibble)
```

# Overview

This note documents how to compute standard errors for the method-of-moments
estimation reported in `draft/main.tex` (Estimation Results section).

Let $\hat{\theta}$ solve
$$
\min_{\theta}\; \widehat{g}(\theta)^{\prime} W \widehat{g}(\theta),
$$
where $\widehat{g}(\theta)$ stacks the sample moment conditions in
equations (sample demand and supply moments) of `draft/main.tex`.
Define
$$
G = \frac{\partial \widehat{g}(\theta)}{\partial \theta^{\prime}}
\Big|_{\theta = \hat{\theta}}, \quad
\widehat{\Omega} = \widehat{\mathbb{E}} \left[g_i(\hat{\theta}) g_i(\hat{\theta})^{\prime}\right].
$$
Then the asymptotic variance is
$$
\widehat{\mathrm{Var}}(\hat{\theta}) =
(G^{\prime} W G)^{-1} G^{\prime} W \widehat{\Omega} W G (G^{\prime} W G)^{-1}.
$$
If $W = \widehat{\Omega}^{-1}$ (efficient GMM), this reduces to
$$
(G^{\prime} \widehat{\Omega}^{-1} G)^{-1}.
$$

# Implementation template (R)

```{r}
# Estimated equilibrium from structural estimation
eq_hat <- 
    readRDS(
      file = "output/multihome/estimate_data/equilibrium_updated_constrained.rds" %>%
    here::here()
  )


instrument_demand <- 
  make_instrument_demand(equilibrium = eq_hat)

z_hat <- instrument_demand %>%
  purrr::map(purrr::reduce, rbind) %>%
  purrr::reduce(rbind)

combo_info <- caret::findLinearCombos(z_hat)

if (!is.null(combo_info$remove)) {
  z_hat <- z_hat[, -combo_info$remove, drop = FALSE]
}

theta_hat <- transform_parameter_to_theta_optim(
  mu_p = eq_hat$parameter$mu_p,
  mu_ths = eq_hat$parameter$mu_ths,
  m_f = eq_hat$parameter$m_f,
  lambda_w = eq_hat$parameter$lambda_w,
  lambda_f = eq_hat$parameter$lambda_f
) %>%
  as.numeric()

demand_hat <- solve_demand_shock(equilibrium = eq_hat)
g_w_hat <-
  (demand_hat$ea_w %*% t(rep(1, ncol(z_hat)))) *
  z_hat
g_f_hat <-
  (demand_hat$ea_f %*% t(rep(1, ncol(z_hat)))) *
  z_hat
gi_hat <- cbind(g_w_hat, g_f_hat)
n_obs <- nrow(gi_hat)
gbar_hat <- colMeans(gi_hat)

# Omega-hat = E[g_i g_i']
Omega_hat <- crossprod(gi_hat) / n_obs

# Jacobian G = d gbar(theta) / d theta'
# Numerical central differences (no function definitions)
eps <- 1e-6
k <- length(theta_hat)
G_hat <- matrix(NA_real_, nrow = length(gbar_hat), ncol = k)

for (p in seq_len(k)) {
  theta_plus <- theta_hat
  theta_minus <- theta_hat
  theta_plus[p] <- theta_plus[p] + eps
  theta_minus[p] <- theta_minus[p] - eps

  param_plus <- transform_theta_to_parameter_demand(
    theta = theta_plus,
    parameter = eq_hat$parameter
  )
  eq_plus <- eq_hat
  eq_plus$parameter <- param_plus
  eq_plus <- update_mu(equilibrium = eq_plus, parameter = param_plus)
  demand_plus <- solve_demand_shock(equilibrium = eq_plus)
  g_w_plus <-
    (demand_plus$ea_w %*% t(rep(1, ncol(z_hat)))) *
    z_hat
  g_f_plus <-
    (demand_plus$ea_f %*% t(rep(1, ncol(z_hat)))) *
    z_hat
  gbar_plus <- colMeans(cbind(g_w_plus, g_f_plus))

  param_minus <- transform_theta_to_parameter_demand(
    theta = theta_minus,
    parameter = eq_hat$parameter
  )
  eq_minus <- eq_hat
  eq_minus$parameter <- param_minus
  eq_minus <- update_mu(equilibrium = eq_minus, parameter = param_minus)
  demand_minus <- solve_demand_shock(equilibrium = eq_minus)
  g_w_minus <-
    (demand_minus$ea_w %*% t(rep(1, ncol(z_hat)))) *
    z_hat
  g_f_minus <-
    (demand_minus$ea_f %*% t(rep(1, ncol(z_hat)))) *
    z_hat
  gbar_minus <- colMeans(cbind(g_w_minus, g_f_minus))

  G_hat[, p] <- (gbar_plus - gbar_minus) / (2 * eps)
}

# Use the same W as your estimation step. Here we default to efficient W.
W_hat <- solve(Omega_hat)

# ---- Variance formulas --------------------------------------------------------
# Finite-sample scaling by 1/n_obs is included.

A <- solve(t(G_hat) %*% W_hat %*% G_hat)
V_theta_sandwich <-
  (A %*% (t(G_hat) %*% W_hat %*% Omega_hat %*% W_hat %*% G_hat) %*% A) /
  n_obs
V_theta_efficient <-
  solve(t(G_hat) %*% solve(Omega_hat) %*% G_hat) /
  n_obs

se_theta_sandwich <- sqrt(diag(V_theta_sandwich))
se_theta_efficient <- sqrt(diag(V_theta_efficient))

theta_table <- tibble::tibble(
  parameter_theta = c(
    "log_mu_p",
    "log_mu_ths",
    "logit_m_f",
    "log_lambda_w",
    "log_minus_lambda_f"
  ),
  estimate = theta_hat,
  se_sandwich = se_theta_sandwich,
  se_efficient = se_theta_efficient
)

theta_table
```

```{r}
# ---- Delta method: standard errors on structural parameters -------------------

m_f_hat <- exp(theta_hat[3]) / (1 + exp(theta_hat[3]))
dm_f_hat <- m_f_hat * (1 - m_f_hat)
J <- rbind(
  c(exp(theta_hat[1]), 0, 0, 0, 0),  # mu_p
  c(0, exp(theta_hat[2]), 0, 0, 0),  # mu_ths
  c(0, 0, dm_f_hat, 0, 0),           # m_f
  c(0, 0, -dm_f_hat, 0, 0),          # m_w = 1 - m_f
  c(0, 0, 0, exp(theta_hat[4]), 0),  # lambda_w
  c(0, 0, 0, 0, -exp(theta_hat[5]))  # lambda_f
)

V_param_sandwich <- J %*% V_theta_sandwich %*% t(J)
V_param_efficient <- J %*% V_theta_efficient %*% t(J)

param_est <- c(
  eq_hat$parameter$mu_p,
  eq_hat$parameter$mu_ths,
  eq_hat$parameter$m_f,
  eq_hat$parameter$m_w,
  eq_hat$parameter$lambda_w,
  eq_hat$parameter$lambda_f
)

param_table <- tibble::tibble(
  parameter = c(
    "mu_p",
    "mu_ths",
    "m_f",
    "m_w",
    "lambda_w",
    "lambda_f"
  ),
  estimate = param_est,
  se_sandwich = sqrt(diag(V_param_sandwich)),
  se_efficient = sqrt(diag(V_param_efficient))
)

param_table
```

```{r}
# Optional: write outputs to file for use in tables/appendix.
se_output <- list(
  theta = theta_table,
  structural = param_table,
  Omega_hat = Omega_hat,
  G_hat = G_hat,
  n_obs = n_obs
)

# saveRDS(
#   se_output,
#   here::here("output", "multihome", "estimate_data", "standard_errors.rds")
# )
```

This file is intended as a reproducible reference for the standard-error
calculations used in the paper.
