---
title: "report data analysis (use minimum wage data)"
author: "Chiho Taniguchi"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 3, fig.width = 4)

library("magrittr")
library("kableExtra")
library("ggplot2")

height <- 6
width <- 8

```

```{r }

 data_establishments <- 
  here::here(file = "cleaned/data_establishments.rds") %>% 
  readRDS()

 data_zipcode <- 
   here::here(file = "cleaned/data_zipcode.rds") %>% 
   readRDS()
 
 data_area <- 
   here::here(file = "cleaned/data_area.rds") %>% 
   readRDS()
 
 data_zip_establishments <- 
   here::here(file = "output/data_zip_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments <- 
   here::here(file = "output/data_cz_establishments.rds") %>% 
   readRDS()
 
 data_area_area_distance <- 
   here::here(file = "cleaned/data_area_area_distance.rds") %>% 
   readRDS()
 
 ## there are two establishments whose firm_id are NA in data_cz_establishments
 
 data_cz_establishments_distance <- 
   here::here(file = "output/data_cz_establishments_distance.rds") %>% 
   readRDS()
 
```

# cz data
Regress the number of general establishments on minimum wage, prefecture fixed effect(p_FE), and year fixed effect(t_FE) 

```{r}

results <- list()
 
 results[[1]] <- 
   estimatr::lm_robust(
     formula = N_jt_10000 ~ mw,
     fixed_effects = year + pref,
     se_type = "stata",
     data = data_cz_establishments
   )
 
 results[[2]] <- 
   estimatr::lm_robust(
     formula = N_jt_10000 ~ mw,
     fixed_effects = pref,
     se_type = "stata",
     data = data_cz_establishments
   )
 
 results[[3]] <- 
   estimatr::lm_robust(
     formula = N_jt_10000 ~ mw,
     fixed_effects = year,
     se_type = "stata",
     data = data_cz_establishments
   )
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`, ~`(3)`,
     'p_FE', 'Y', 'Y', 'N',
     't_FE', 'Y', 'N', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(4,5)
 
 result <- 
   list(
     "N_jt" = results[[1]],
     "N_jt" = results[[2]],
     "N_jt" = results[[3]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 

```

## Check the relation between mw and the number of general establishments

### All data

```{r}

data_cz_establishments_mw <- 
  data_cz_establishments %>% 
  dplyr::select(
    id_unique,
    firm_id,
    pref,
    year,
    mw,
    N_jt,
    N_jt_10000
  ) %>% 
  fastDummies::dummy_cols(
    select_columns = c("pref", "year"),
    remove_first_dummy = FALSE
  )

r_mw <- 
  estimatr::lm_robust(
    formula = mw ~ pref_2 + pref_3 + pref_4 + pref_5 + pref_6 + pref_7 + pref_8 + pref_9 + pref_10 +
      pref_11 + pref_12 + pref_13 + pref_14 + pref_15 + pref_16 + pref_17 + pref_18 + pref_19 + pref_20 +
      pref_21 + pref_22 + pref_23 + pref_24 + pref_25 + pref_26 + pref_27 + pref_28 + pref_29 + pref_30 +
      pref_31 + pref_32 + pref_33 + pref_34 + pref_35 + pref_36 + pref_37 + pref_38 + pref_39 + pref_40 +
      pref_41 + pref_42 + pref_43 + pref_44 + pref_45 + pref_46 + pref_47 +
      year_2011 + year_2012 + year_2013 + year_2014,
    se_type = "stata",
    data = data_cz_establishments_mw
  )

r_Njt <- 
  estimatr::lm_robust(
    formula = N_jt_10000 ~ pref_2 + pref_3 + pref_4 + pref_5 + pref_6 + pref_7 + pref_8 + pref_9 + pref_10 +
      pref_11 + pref_12 + pref_13 + pref_14 + pref_15 + pref_16 + pref_17 + pref_18 + pref_19 + pref_20 +
      pref_21 + pref_22 + pref_23 + pref_24 + pref_25 + pref_26 + pref_27 + pref_28 + pref_29 + pref_30 +
      pref_31 + pref_32 + pref_33 + pref_34 + pref_35 + pref_36 + pref_37 + pref_38 + pref_39 + pref_40 +
      pref_41 + pref_42 + pref_43 + pref_44 + pref_45 + pref_46 + pref_47 +
      year_2011 + year_2012 + year_2013 + year_2014,
    se_type = "stata",
    data = data_cz_establishments_mw
  )
  

residuals_mw <- 
  (r_mw$fitted.values - data_cz_establishments_mw$mw)

residuals_Njt <- 
  (r_mw$fitted.values - data_cz_establishments_mw$N_jt_10000)

binscatter_residuals <- 
  cbind(
    residuals_mw,
    residuals_Njt
  ) %>% 
  as.data.frame()

binscatter_residuals <- 
  binscatter_residuals %>% 
  cbind(data_cz_establishments_mw$id_unique) %>% 
  dplyr::rename(
    id_unique = "data_cz_establishments_mw$id_unique"
  ) 

binscatter_residuals <- 
  binscatter_residuals %>% 
  dplyr::select(
    id_unique,
    dplyr::everything()
  ) 

binscatter_residuals <- 
  binscatter_residuals %>% 
  dplyr::mutate(
    mw_bin = cut(
      id_unique,
      breaks = 500
    )
  ) %>% 
  dplyr::group_by(
    mw_bin
  ) %>% 
  dplyr::mutate(
    residuals_mw_avr = mean(residuals_mw),
    residuals_Njt_avr = mean(residuals_Njt)
  ) %>% 
  dplyr::ungroup()

 binscatter_residuals_unique <- 
   binscatter_residuals %>% 
   dplyr::select(
     residuals_mw_avr,
     residuals_Njt_avr
   ) %>% 
   dplyr::distinct()
 

 g_mw <- 
   ggplot() +
   geom_point(
     data = binscatter_residuals,
     mapping = aes(x = residuals_mw,
                   y = residuals_Njt),
     size = 0.3
   ) +
   theme_classic()
 
 g_mw

```

### binscatter plot

```{r}

 mw_binscatter <- ggplot() +
  geom_point(
    data = binscatter_residuals_unique,
    mapping = aes(x = residuals_mw_avr,
                  y = residuals_Njt_avr),
    size = 0.3
  ) +
  stat_smooth(
    method = "lm",
    data = binscatter_residuals_unique,
    mapping = aes(x = residuals_mw_avr,
                  y = residuals_Njt_avr),
    se = FALSE,
    size = 0.3
  ) +
  xlab("residuals of minimum wage") +
  ylab("residuals of N_jt") +
  theme_classic()

 mw_binscatter

```


## use data_cz_establishments_distance

```{r}

data_cz_establishments_distance <- 
  data_cz_establishments_distance %>% 
  dplyr::group_by(
    year,
    cz
  ) %>% 
  dplyr::mutate(
    distance_min_avr = mean(distance_min_r)
  )


```

### 1 st stage

```{r}



```

# zip data

Regress the number of general establishments on minimum wage, prefecture fixed effect(p_FE), and year fixed effect(t_FE) 

```{r}

results2 <- list()
 
 results2[[1]] <- 
   estimatr::lm_robust(
     formula = N_zip_t_100 ~ mw,
     fixed_effects = year + pref,
     se_type = "stata",
     data = data_zip_establishments
   )
 
 results2[[2]] <- 
   estimatr::lm_robust(
     formula = N_zip_t_100 ~ mw,
     fixed_effects = pref,
     se_type = "stata",
     data = data_zip_establishments
   )
 
 results2[[3]] <- 
   estimatr::lm_robust(
     formula = N_zip_t_100 ~ mw,
     fixed_effects = year,
     se_type = "stata",
     data = data_zip_establishments
   )
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`, ~`(3)`,
     'p_FE', 'Y', 'Y', 'N',
     't_FE', 'Y', 'N', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(4,5)
 
 result_2 <- 
   list(
     "N_jt" = results2[[1]],
     "N_jt" = results2[[2]],
     "N_jt" = results2[[3]]
   )
 
 modelsummary::modelsummary(
   result_2,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 

```

## Check the relation between mw and the number of general establishments 

### All data

```{r}

data_zip_establishments_mw <- 
  data_zip_establishments %>% 
  dplyr::select(
    id_unique,
    firm_id,
    pref,
    year,
    mw,
    N_zip_t,
    N_zip_t_100
  ) %>% 
  fastDummies::dummy_cols(
    select_columns = c("pref", "year"),
    remove_first_dummy = FALSE
  )

r_mw_zip <- 
  estimatr::lm_robust(
    formula = mw ~ pref_2 + pref_3 + pref_4 + pref_5 + pref_6 + pref_7 + pref_8 + pref_9 + pref_10 +
      pref_11 + pref_12 + pref_13 + pref_14 + pref_15 + pref_16 + pref_17 + pref_18 + pref_19 + pref_20 +
      pref_21 + pref_22 + pref_23 + pref_24 + pref_25 + pref_26 + pref_27 + pref_28 + pref_29 + pref_30 +
      pref_31 + pref_32 + pref_33 + pref_34 + pref_35 + pref_36 + pref_37 + pref_38 + pref_39 + pref_40 +
      pref_41 + pref_42 + pref_43 + pref_44 + pref_45 + pref_46 + pref_47 +
      year_2011 + year_2012 + year_2013 + year_2014,
    se_type = "stata",
    data = data_zip_establishments_mw
  )

r_N_zip_t <- 
  estimatr::lm_robust(
    formula = N_zip_t_100 ~ pref_2 + pref_3 + pref_4 + pref_5 + pref_6 + pref_7 + pref_8 + pref_9 + pref_10 +
      pref_11 + pref_12 + pref_13 + pref_14 + pref_15 + pref_16 + pref_17 + pref_18 + pref_19 + pref_20 +
      pref_21 + pref_22 + pref_23 + pref_24 + pref_25 + pref_26 + pref_27 + pref_28 + pref_29 + pref_30 +
      pref_31 + pref_32 + pref_33 + pref_34 + pref_35 + pref_36 + pref_37 + pref_38 + pref_39 + pref_40 +
      pref_41 + pref_42 + pref_43 + pref_44 + pref_45 + pref_46 + pref_47 +
      year_2011 + year_2012 + year_2013 + year_2014,
    se_type = "stata",
    data = data_zip_establishments_mw
  )
  

residuals_mw_zip <- 
  (r_mw_zip$fitted.values - data_zip_establishments_mw$mw)

residuals_N_zip_t <- 
  (r_N_zip_t$fitted.values - data_zip_establishments_mw$N_zip_t_100)

binscatter_residuals_zip <- 
  cbind(
    residuals_mw_zip,
    residuals_N_zip_t
  ) %>% 
  as.data.frame()

binscatter_residuals_zip <- 
  binscatter_residuals_zip %>% 
  cbind(data_zip_establishments_mw$id_unique) %>% 
  dplyr::rename(
    id_unique = "data_zip_establishments_mw$id_unique"
  ) 

binscatter_residuals_zip <- 
  binscatter_residuals_zip %>% 
  dplyr::select(
    id_unique,
    dplyr::everything()
  ) 

binscatter_residuals_zip <- 
  binscatter_residuals_zip %>% 
  dplyr::mutate(
    mw_bin_zip = cut(
      id_unique,
      breaks = 500
    )
  ) %>% 
  dplyr::group_by(
    mw_bin_zip
  ) %>% 
  dplyr::mutate(
    residuals_mw_zip_avr = mean(residuals_mw_zip),
    residuals_N_zip_t_avr = mean(residuals_N_zip_t)
  ) %>% 
  dplyr::ungroup()

 binscatter_residuals_zip_unique <- 
   binscatter_residuals_zip %>% 
   dplyr::select(
     residuals_mw_zip_avr,
     residuals_N_zip_t_avr
   ) %>% 
   dplyr::distinct()
 

 g_mw_zip <- 
   ggplot() +
   geom_point(
     data = binscatter_residuals_zip,
     mapping = aes(x = residuals_mw_zip,
                   y = residuals_N_zip_t),
     size = 0.3
   ) +
   theme_classic()
 
 g_mw

```

### binscatter plot

```{r}

 mw_binscatter_zip <- ggplot() +
  geom_point(
    data = binscatter_residuals_zip_unique,
    mapping = aes(x = residuals_mw_zip_avr,
                  y = residuals_N_zip_t_avr),
    size = 0.3
  ) +
  stat_smooth(
    method = "lm",
    data = binscatter_residuals_zip_unique,
    mapping = aes(x = residuals_mw_zip_avr,
                  y = residuals_N_zip_t_avr),
    se = FALSE,
    size = 0.3
  ) +
  xlab("residuals of minimum wage") +
  ylab("residuals of N_zip_t") +
  theme_classic()

 mw_binscatter_zip

```


