---
title: "Benchmark Equilibrium Case Comparison"
author: "Daisy Dan Song"
date: "2026-03-17"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
devtools::load_all(".")
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
library(dplyr)
library(tidyr)
library(purrr)
library(tibble)
library(foreach)
library(here)
foreach::registerDoSEQ()
```

## Purpose

This report compares endogenous equilibrium outcomes across four solver cases:

1. Baseline equilibrium (`solve_equilibrium`)  
2. Competitive benchmark (`solve_equilibrium_competitive`)  
3. Frictionless with free entry (`solve_equilibrium_frictionless_with_free_entry`)  
4. Frictionless without free entry (`solve_equilibrium_frictionless`)  

All differences are reported relative to the baseline case for endogenous variables:
`w`, `f`, `s_w`, and `s_f`.
Because time is limited and markets are a lot in actual data, we compare
only one market-zone pair: `t = 1`, `j = 1`.

```{r solve-cases, message=FALSE, warning=FALSE}
equilibrium <- 
  readRDS(
    file =  "output/multihome/estimate_data/equilibrium_updated_constrained.rds" %>%
    here::here()
  )

t <- 1
j <- 1

equilibrium_base <- equilibrium

equilibrium_competitive <-
  solve_equilibrium_competitive_tj(
    t = t,
    j = j,
    equilibrium = equilibrium_base,
    solver = "nleqslv",
    multistart = 10
  )

equilibrium_frictionless_free_entry <-
  solve_equilibrium_frictionless_with_free_entry_tj(
    t = t,
    j = j,
    equilibrium = equilibrium_base
  )

equilibrium_frictionless_no_free_entry <-
  solve_equilibrium_tj_frictionless(
    t = t,
    j = j,
    equilibrium = equilibrium_base,
    solver = "nleqslv",
    multistart = 10
  ) 

t_compare <- 1
j_compare <- 1
```

```{r helper-functions}
extract_endogenous_tj_long <- function(eq, case_name, t, j) {
  rows <- list()
  idx <- 1

  endo <- eq$endogenous[[t]][[j]]

  for (var_name in c("w", "f")) {
    values <- as.numeric(endo[[var_name]])
    rows[[idx]] <- tibble(
      case = case_name,
      t = t,
      j = j,
      variable = var_name,
      index = seq_along(values),
      value = values
    )
    idx <- idx + 1
  }

  bind_rows(rows)
}
```

```{r build-comparison}
baseline_long <-
  extract_endogenous_tj_long(
    eq = equilibrium_base,
    case_name = "baseline",
    t = t_compare,
    j = j_compare
  )

all_cases_long <-
  bind_rows(
    baseline_long,
    extract_endogenous_tj_long(
      eq = equilibrium_competitive,
      case_name = "free_entry",
      t = t_compare,
      j = j_compare
    ),
    extract_endogenous_tj_long(
      eq = equilibrium_frictionless_free_entry,
      case_name = "frictionless_free_entry",
      t = t_compare,
      j = j_compare
    ),
    extract_endogenous_tj_long(
      eq = equilibrium_frictionless_no_free_entry,
      case_name = "frictionless_no_free_entry",
      t = t_compare,
      j = j_compare
    )
  ) %>%
  filter(index >= 3)

comparison_table <-
  all_cases_long %>%
  select(variable, index, case, value) %>%
  tidyr::pivot_wider(
    names_from = case,
    values_from = value
  ) %>%
  mutate(
    diff_free_entry = free_entry- baseline,
    diff_frictionless_free_entry = frictionless_free_entry - baseline,
    diff_frictionless_no_free_entry = frictionless_no_free_entry - baseline
  )
```

## Case-specific Objectives (`t = 1`, `j = 1`, index >= 3)

```{r objective-table}
t <- 1
j <- 1
baseline_check <- check_equilibrium_tj(t = t_compare, j = j_compare, equilibrium = equilibrium_base)
competitive_check <- 
    compute_profit_ths_tj(
      m_w = equilibrium_competitive$parameter$m_w,
      m_f = equilibrium_competitive$parameter$m_f,
      gamma_w = equilibrium_competitive$parameter$gamma_w,
      gamma_f = equilibrium_competitive$parameter$gamma_f,
      x_c_w = equilibrium_competitive$exogenous[[t]][[j]]$x_c_w,
      x_c_f = equilibrium_competitive$exogenous[[t]][[j]]$x_c_f,
      size_w = equilibrium_competitive$exogenous[[t]][[j]]$size_w,
      size_f = equilibrium_competitive$exogenous[[t]][[j]]$size_f,
      owner = equilibrium_competitive$exogenous[[t]][[j]]$owner,
      mu = equilibrium_competitive$shock[[t]][[j]]$mu,
      ec_w = equilibrium_competitive$shock[[t]][[j]]$ec_w,
      ec_f = equilibrium_competitive$shock[[t]][[j]]$ec_f,
      w = equilibrium_competitive$endogenous[[t]][[j]]$w,
      f = equilibrium_competitive$endogenous[[t]][[j]]$f,
      s_w = equilibrium_competitive$endogenous[[t]][[j]]$s_w,
      s_f = equilibrium_competitive$endogenous[[t]][[j]]$s_f,
      use_exp = equilibrium_competitive$constant$use_exp
    ) 
competitive_check <- 
  max(
    abs(
      competitive_check[
        3:nrow(competitive_check),
        , 
        drop = FALSE
      ]
    )
  )

c_w <- 
  compute_c_w_tj(
    gamma_w = equilibrium_frictionless_free_entry$parameter$gamma_w,
    x_c_w = equilibrium_frictionless_free_entry$exogenous[[t]][[j]]$x_c_w,
    ec_w = equilibrium_frictionless_free_entry$shock[[t]][[j]]$ec_w,
    use_exp = equilibrium_frictionless_free_entry$constant$use_exp
  ) 

c_f <-
  compute_c_f_tj(
    gamma_f = equilibrium_frictionless_free_entry$parameter$gamma_f,
    x_c_f = equilibrium_frictionless_free_entry$exogenous[[t]][[j]]$x_c_f,
    ec_f = equilibrium_frictionless_free_entry$shock[[t]][[j]]$ec_f,
    use_exp = equilibrium_frictionless_free_entry$constant$use_exp
  ) 

frictionless_fe_check <- 
  equilibrium_frictionless_free_entry$endogenous[[t]][[j]]$f - equilibrium_frictionless_free_entry$endogenous[[t]][[j]]$w - c_w - c_f

frictionless_fe_check <- 
  max(
    abs(
      frictionless_fe_check[
        3:nrow(frictionless_fe_check),
        , 
        drop = FALSE
      ]
    )
  )
frictionless_no_fe_check <- 
  compute_foc_tj_frictionless(
    m_w = equilibrium_frictionless_no_free_entry$parameter$m_w,
    m_f = equilibrium_frictionless_no_free_entry$parameter$m_f,
    beta_w = equilibrium_frictionless_no_free_entry$parameter$beta_w,
    beta_f = equilibrium_frictionless_no_free_entry$parameter$beta_f,
    gamma_w = equilibrium_frictionless_no_free_entry$parameter$gamma_w,
    gamma_f = equilibrium_frictionless_no_free_entry$parameter$gamma_f,
    lambda_w = equilibrium_frictionless_no_free_entry$parameter$lambda_w,
    lambda_f = equilibrium_frictionless_no_free_entry$parameter$lambda_f,
    x_a_w = equilibrium_frictionless_no_free_entry$exogenous[[t]][[j]]$x_a_w,
    x_a_f = equilibrium_frictionless_no_free_entry$exogenous[[t]][[j]]$x_a_f,
    x_c_w = equilibrium_frictionless_no_free_entry$exogenous[[t]][[j]]$x_c_w,
    x_c_f = equilibrium_frictionless_no_free_entry$exogenous[[t]][[j]]$x_c_f,
    size_w = equilibrium_frictionless_no_free_entry$exogenous[[t]][[j]]$size_w,
    size_f = equilibrium_frictionless_no_free_entry$exogenous[[t]][[j]]$size_f,
    owner = equilibrium_frictionless_no_free_entry$exogenous[[t]][[j]]$owner,
    mu = equilibrium_frictionless_no_free_entry$shock[[t]][[j]]$mu,
    ea_w = equilibrium_frictionless_no_free_entry$shock[[t]][[j]]$ea_w,
    ea_f = equilibrium_frictionless_no_free_entry$shock[[t]][[j]]$ea_f,
    ec_w = equilibrium_frictionless_no_free_entry$shock[[t]][[j]]$ec_w,
    ec_f = equilibrium_frictionless_no_free_entry$shock[[t]][[j]]$ec_f,
    w = equilibrium_frictionless_no_free_entry$endogenous[[t]][[j]]$w,
    f = equilibrium_frictionless_no_free_entry$endogenous[[t]][[j]]$f,
    s_f = equilibrium_frictionless_no_free_entry$endogenous[[t]][[j]]$s_f,
    method_s_w = "exact",
    margin = equilibrium_frictionless_no_free_entry$constant$margin,
    quadrature_size = equilibrium_frictionless_no_free_entry$constant$quadrature_size,
    tol = equilibrium_frictionless_no_free_entry$constant$tol,
    use_exp = equilibrium_frictionless_no_free_entry$constant$use_exp
  ) 

frictionless_no_fe_check <- 
  max(
    abs(
      frictionless_no_fe_check
    )
  )

baseline_objective_foc <- max(abs(c(baseline_check$foc_w, baseline_check$foc_f)), na.rm = TRUE)
competitive_objective_profit <- competitive_check
frictionless_fe_objective_wedge <- frictionless_fe_check
frictionless_no_fe_objective_wedge <- frictionless_no_fe_check

objective_table <-
  tibble(
    baseline_foc = baseline_objective_foc,
    competitive_profit_zero = competitive_objective_profit,
    frictionless_free_entry_wedge_zero = frictionless_fe_objective_wedge,
    frictionless_no_free_entry_wedge_zero = frictionless_no_fe_objective_wedge
  )

knitr::kable(
  objective_table,
  digits = 8,
  caption = "Case-specific objective residuals (target is zero)"
)
```

## Endogenous Variables by Case (`t = 1`, `j = 1`, index >= 3)

```{r comparison-table}
knitr::kable(
  comparison_table %>% arrange(variable, index),
  digits = 6,
  caption = "Comparison across equilibrium cases with differences from baseline"
)
```


