---
title: "Benchmark Equilibrium Case Comparison (All Markets)"
author: "Daisy Dan Song"
date: "2026-03-17"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
devtools::load_all(".")

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

library(dplyr)
library(tidyr)
library(purrr)
library(tibble)
library(foreach)
library(here)
library(ggplot2)
library(scales)
library(doParallel)
foreach::registerDoSEQ()
```

## Purpose

This report applies the benchmark equilibrium comparison to **actual data** and compares
results across **all** market-zone pairs `(t, j)`.

Cases:

1. Baseline equilibrium (`solve_equilibrium`)
2. Free-entry benchmark (`solve_equilibrium_competitive`)
3. Frictionless with free entry (`solve_equilibrium_frictionless_with_free_entry`)
4. Frictionless without free entry (`solve_equilibrium_frictionless`)

The endogenous comparison focuses on `w` and `f` from index `>= 3`.

```{r, cache=TRUE}
equilibrium <-
  readRDS(
    file = "output/multihome/estimate_data/equilibrium_updated_constrained.rds" %>%
      here::here()
  )

equilibrium_base <- equilibrium

equilibrium_competitive <-
  solve_equilibrium_competitive(
    equilibrium = equilibrium_base,
    solver = "nleqslv"
  )
```

```{r, cache=TRUE}
equilibrium_frictionless_free_entry <-
  solve_equilibrium_frictionless_with_free_entry(
    equilibrium = equilibrium_base
  )

```

```{r, cache=TRUE}
equilibrium_frictionless_no_free_entry <-
  solve_equilibrium_frictionless(
    equilibrium = equilibrium_base,
    solver = "nleqslv",
    multistart = 1
  )
```


```{r}
t <- 1
j <- 1

m_w <- equilibrium$parameter$m_w
m_f <- equilibrium$parameter$m_f
beta_f <- equilibrium$parameter$beta_f
beta_w <- equilibrium$parameter$beta_w
lambda_w <- equilibrium$parameter$lambda_w
lambda_f <- equilibrium$parameter$lambda_f
gamma_f <- equilibrium$parameter$gamma_f
gamma_w <- equilibrium$parameter$gamma_w
x_a_f <- equilibrium$exogenous[[t]][[j]]$x_a_f
x_a_w <- equilibrium$exogenous[[t]][[j]]$x_a_w
x_c_w <- equilibrium$exogenous[[t]][[j]]$x_c_w
x_c_f <- equilibrium$exogenous[[t]][[j]]$x_c_f
size_w <- equilibrium$exogenous[[t]][[j]]$size_w
size_f <- equilibrium$exogenous[[t]][[j]]$size_f
owner <- equilibrium$exogenous[[t]][[j]]$owner
s_w <- equilibrium$endogenous[[t]][[j]]$s_w
mu <- equilibrium$shock[[t]][[j]]$mu
ea_f <- equilibrium$shock[[t]][[j]]$ea_f
ea_w <- equilibrium$shock[[t]][[j]]$ea_w
ec_f <- equilibrium$shock[[t]][[j]]$ec_f
ec_w <- equilibrium$shock[[t]][[j]]$ec_w
use_exp <- equilibrium$constant$use_exp
s_f<- equilibrium$endogenous[[t]][[j]]$s_f

w_parttime <- equilibrium$endogenous[[t]][[j]]$w
w_parttime[3:length(equilibrium$endogenous[[t]][[j]]$w)] <- equilibrium$endogenous[[t]][[j]]$w[2]
w <- w_parttime

active_idx <- 3:nrow(equilibrium$endogenous[[t]][[j]]$f)
f_grid <- seq(-100, 20, by = 0.1)

profit_curve_df <-
  purrr::map_dfr(
    active_idx,
    function(i) {
      s_f_start <- equilibrium$endogenous[[t]][[j]]$s_f
      purrr::map_dfr(
        f_grid,
        function(z) {
          f_z <- equilibrium$endogenous[[t]][[j]]$f
          f_z[i, 1] <- z

          s_f_x <-
            solve_s_f_tj(
              m_w = m_w,
              m_f = m_f,
              beta_f = beta_f,
              lambda_f = lambda_f,
              x_a_f = x_a_f,
              size_w = size_w,
              size_f = size_f,
              mu = mu,
              ea_f = ea_f,
              f = f_z,
              s_f = s_f_start
            ) %>%
            as.matrix()
          s_f_start <<- s_f_x

          q_x <-
            compute_meeting_number_tj(
              m_w = m_w,
              m_f = m_f,
              size_w = size_w,
              size_f = size_f,
              mu = mu,
              s_f = s_f_x
            ) %>%
            as.matrix()

          c_w_x <-
            compute_c_w_tj(
              gamma_w = gamma_w,
              x_c_w = x_c_w,
              ec_w = ec_w,
              use_exp = use_exp
            )
          c_f_x <-
            compute_c_f_tj(
              gamma_f = gamma_f,
              x_c_f = x_c_f,
              ec_f = ec_f,
              use_exp = use_exp
            )

          revenue_term_raw <- q_x * s_w * (f_z - w - c_w_x)
          cost_term_raw <- c_f_x * s_f_x * size_f
          revenue_term <- (t(owner) %*% owner) %*% revenue_term_raw
          cost_term <- (t(owner) %*% owner) %*% cost_term_raw

          tibble(
            i = i,
            f_value = z,
            c_f = c_f_x[i, 1],
            c_w_x = c_w_x[i, 1],
            revenue_term = as.numeric(revenue_term[i, 1]),
            cost_term = as.numeric(cost_term[i, 1]),
            profit = revenue_term - cost_term
          )
        }
      )
    }
  )

solution_df <-
  tibble(
    i = active_idx,
    f_solution = as.numeric(equilibrium_competitive$endogenous[[t]][[j]]$f[active_idx, 1])
  )

profit_components_df <-
  profit_curve_df %>%
  select(i, f_value, revenue_term, cost_term, profit) %>%
  pivot_longer(
    cols = c(revenue_term, cost_term),
    names_to = "component",
    values_to = "value"
  ) %>%
  mutate(
    component = recode(
      component,
      revenue_term = "Revenue term: q_x * s_w * (f_z - w - c_w_x)",
      cost_term = "Cost term: -c_f_x * s_f_x * size_f"
    )
  )

ggplot(profit_components_df, aes(x = f_value, y = value, color = factor(i), linetype = component)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black", linewidth = 0.3) +
  geom_line(linewidth = 0.7) +
  labs(
    title = "Profit decomposition terms vs fee for multiple THS indices",
    subtitle = "Dashed black: zero line; dotted colored: solved free-entry fee by index",
    x = "f_i",
    y = "Value",
    color = "THS index i",
    linetype = "Component"
  ) +
  theme_classic()

```

```{r}
f_grid <- seq(0, 50, by = 0.1)

profit_curve_df <-
  purrr::map_dfr(
    active_idx,
    function(i) {
      s_f_start <- equilibrium$endogenous[[t]][[j]]$s_f
      purrr::map_dfr(
        f_grid,
        function(z) {
          f_z <- equilibrium$endogenous[[t]][[j]]$f
          f_z[i, 1] <- z

          s_f_x <-
            solve_s_f_tj(
              m_w = m_w,
              m_f = m_f,
              beta_f = beta_f,
              lambda_f = lambda_f,
              x_a_f = x_a_f,
              size_w = size_w,
              size_f = size_f,
              mu = mu,
              ea_f = ea_f,
              f = f_z,
              s_f = s_f_start
            ) %>%
            as.matrix()
          s_f_start <<- s_f_x

          q_x <-
            compute_meeting_number_tj(
              m_w = m_w,
              m_f = m_f,
              size_w = size_w,
              size_f = size_f,
              mu = mu,
              s_f = s_f_x
            ) %>%
            as.matrix()

          c_w_x <-
            compute_c_w_tj(
              gamma_w = gamma_w,
              x_c_w = x_c_w,
              ec_w = ec_w,
              use_exp = use_exp
            )
          c_f_x <-
            compute_c_f_tj(
              gamma_f = gamma_f,
              x_c_f = x_c_f,
              ec_f = ec_f,
              use_exp = use_exp
            )

          revenue_term_raw <- q_x * s_w * (f_z - w - c_w_x)
          cost_term_raw <- c_f_x * s_f_x * size_f
          revenue_term <- (t(owner) %*% owner) %*% revenue_term_raw
          cost_term <- (t(owner) %*% owner) %*% cost_term_raw

          tibble(
            i = i,
            f_value = z,
            c_f = c_f_x[i, 1],
            c_w_x = c_w_x[i, 1],
            revenue_term = as.numeric(revenue_term[i, 1]),
            cost_term = as.numeric(cost_term[i, 1]),
            profit = revenue_term - cost_term
          )
        }
      )
    }
  )

solution_df <-
  tibble(
    i = active_idx,
    f_solution = as.numeric(equilibrium_competitive$endogenous[[t]][[j]]$f[active_idx, 1])
  )

profit_components_df <-
  profit_curve_df %>%
  select(i, f_value, revenue_term, cost_term, profit) %>%
  pivot_longer(
    cols = c(revenue_term, cost_term),
    names_to = "component",
    values_to = "value"
  ) %>%
  mutate(
    component = recode(
      component,
      revenue_term = "Revenue term: q_x * s_w * (f_z - w - c_w_x)",
      cost_term = "Cost term: -c_f_x * s_f_x * size_f"
    )
  )

ggplot(profit_components_df, aes(x = f_value, y = value, color = factor(i), linetype = component)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black", linewidth = 0.3) +
  geom_line(linewidth = 0.7) +
  labs(
    title = "Profit decomposition terms vs fee for multiple THS indices",
    subtitle = "Dashed black: zero line; dotted colored: solved free-entry fee by index",
    x = "f_i",
    y = "Value",
    color = "THS index i",
    linetype = "Component"
  ) +
  theme_classic()

```


```{r helper-functions}
extract_endogenous_all_markets <- function(eq, case_name, vars = c("w", "f"), min_index = 3) {
  rows <- list()
  idx <- 1

  for (t in seq_along(eq$endogenous)) {
    for (j in seq_along(eq$endogenous[[t]])) {
      endo <- eq$endogenous[[t]][[j]]

      for (var_name in vars) {
        values <- as.numeric(endo[[var_name]])
        rows[[idx]] <- tibble(
          case = case_name,
          t = t,
          j = j,
          variable = var_name,
          index = seq_along(values),
          value = values
        )
        idx <- idx + 1
      }
    }
  }

  bind_rows(rows) %>%
    filter(.data$index >= min_index)
}

compute_case_objective_tj <- function(eq, case_name, t, j) {
  if (case_name == "baseline") {
    chk <- check_equilibrium_tj(t = t, j = j, equilibrium = eq)
    return(max(abs(c(chk$foc_w, chk$foc_f)), na.rm = TRUE))
  }

  if (case_name == "free_entry") {
    profit_tj <-
      compute_profit_ths_tj(
        m_w = eq$parameter$m_w,
        m_f = eq$parameter$m_f,
        gamma_w = eq$parameter$gamma_w,
        gamma_f = eq$parameter$gamma_f,
        x_c_w = eq$exogenous[[t]][[j]]$x_c_w,
        x_c_f = eq$exogenous[[t]][[j]]$x_c_f,
        size_w = eq$exogenous[[t]][[j]]$size_w,
        size_f = eq$exogenous[[t]][[j]]$size_f,
        owner = eq$exogenous[[t]][[j]]$owner,
        mu = eq$shock[[t]][[j]]$mu,
        ec_w = eq$shock[[t]][[j]]$ec_w,
        ec_f = eq$shock[[t]][[j]]$ec_f,
        w = eq$endogenous[[t]][[j]]$w,
        f = eq$endogenous[[t]][[j]]$f,
        s_w = eq$endogenous[[t]][[j]]$s_w,
        s_f = eq$endogenous[[t]][[j]]$s_f,
        use_exp = eq$constant$use_exp
      )
    return(max(abs(profit_tj[3:nrow(profit_tj), , drop = FALSE]), na.rm = TRUE))
  }

  if (case_name == "frictionless_free_entry") {
    c_w <-
      compute_c_w_tj(
        gamma_w = eq$parameter$gamma_w,
        x_c_w = eq$exogenous[[t]][[j]]$x_c_w,
        ec_w = eq$shock[[t]][[j]]$ec_w,
        use_exp = eq$constant$use_exp
      )

    c_f <-
      compute_c_f_tj(
        gamma_f = eq$parameter$gamma_f,
        x_c_f = eq$exogenous[[t]][[j]]$x_c_f,
        ec_f = eq$shock[[t]][[j]]$ec_f,
        use_exp = eq$constant$use_exp
      )

    wedge <- eq$endogenous[[t]][[j]]$f - eq$endogenous[[t]][[j]]$w - c_w - c_f
    return(max(abs(wedge[3:nrow(wedge), , drop = FALSE]), na.rm = TRUE))
  }

  if (case_name == "frictionless_no_free_entry") {
    foc <-
      compute_foc_tj_frictionless(
        m_w = eq$parameter$m_w,
        m_f = eq$parameter$m_f,
        beta_w = eq$parameter$beta_w,
        beta_f = eq$parameter$beta_f,
        gamma_w = eq$parameter$gamma_w,
        gamma_f = eq$parameter$gamma_f,
        lambda_w = eq$parameter$lambda_w,
        lambda_f = eq$parameter$lambda_f,
        x_a_w = eq$exogenous[[t]][[j]]$x_a_w,
        x_a_f = eq$exogenous[[t]][[j]]$x_a_f,
        x_c_w = eq$exogenous[[t]][[j]]$x_c_w,
        x_c_f = eq$exogenous[[t]][[j]]$x_c_f,
        size_w = eq$exogenous[[t]][[j]]$size_w,
        size_f = eq$exogenous[[t]][[j]]$size_f,
        owner = eq$exogenous[[t]][[j]]$owner,
        mu = eq$shock[[t]][[j]]$mu,
        ea_w = eq$shock[[t]][[j]]$ea_w,
        ea_f = eq$shock[[t]][[j]]$ea_f,
        ec_w = eq$shock[[t]][[j]]$ec_w,
        ec_f = eq$shock[[t]][[j]]$ec_f,
        w = eq$endogenous[[t]][[j]]$w,
        f = eq$endogenous[[t]][[j]]$f,
        s_f = eq$endogenous[[t]][[j]]$s_f,
        method_s_w = "exact",
        margin = eq$constant$margin,
        quadrature_size = eq$constant$quadrature_size,
        tol = eq$constant$tol,
        use_exp = eq$constant$use_exp
      )
    return(max(abs(foc), na.rm = TRUE))
  }

  stop("Unknown case name.")
}
```

```{r build-endogenous-comparison}
baseline_long_all <-
  extract_endogenous_all_markets(
    eq = equilibrium_base,
    case_name = "baseline",
    vars = c("w", "f"),
    min_index = 3
  )

competitive_long_all <-
  extract_endogenous_all_markets(
    eq = equilibrium_competitive,
    case_name = "free_entry",
    vars = c("w", "f"),
    min_index = 3
  )

frictionless_free_entry_long_all <-
  extract_endogenous_all_markets(
    eq = equilibrium_frictionless_free_entry,
    case_name = "frictionless_free_entry",
    vars = c("w", "f"),
    min_index = 3
  )

frictionless_no_free_entry_long <-
  extract_endogenous_all_markets(
    eq = equilibrium_frictionless_no_free_entry,
    case_name = "frictionless_no_free_entry",
    vars = c("w", "f"),
    min_index = 3
  )

all_cases_long <-
  bind_rows(
    baseline_long_all,
    competitive_long_all,
    frictionless_free_entry_long_all,
    frictionless_no_free_entry_long
  )

comparison_long <-
  all_cases_long %>%
  left_join(
    baseline_long_all %>%
      select(t, j, variable, index, baseline_value = value),
    by = c("t", "j", "variable", "index")
  ) %>%
  mutate(
    diff = value - baseline_value,
    abs_diff = abs(diff)
  )
```

## Endogenous Comparison Summary (All Markets)

```{r endogenous-summary-table}
summary_table <-
  comparison_long %>%
  filter(case != "baseline") %>%
  group_by(case, variable) %>%
  summarise(
    n = n(),
    mean_diff = mean(diff, na.rm = TRUE),
    median_diff = median(diff, na.rm = TRUE),
    mean_abs_diff = mean(abs_diff, na.rm = TRUE),
    p90_abs_diff = quantile(abs_diff, probs = 0.9, na.rm = TRUE),
    max_abs_diff = max(abs_diff, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(case, variable)

knitr::kable(
  summary_table,
  digits = 6,
  caption = "Summary of deviations from baseline across all (t, j) markets"
)
```

```{r endogenous-top-markets-table}
market_diff_table <-
  comparison_long %>%
  filter(case != "baseline") %>%
  group_by(case, t, j, variable) %>%
  summarise(
    mean_abs_diff = mean(abs_diff, na.rm = TRUE),
    max_abs_diff = max(abs_diff, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(max_abs_diff)) %>%
  slice_head(n = 30)

knitr::kable(
  market_diff_table,
  digits = 6,
  caption = "Top market-zone pairs by max absolute deviation"
)
```

## Endogenous Comparison Graphs

```{r endogenous-diff-average-table}
avg_change_table <-
  comparison_long %>%
  filter(case != "baseline") %>%
  mutate(
    case = factor(
      case,
      levels = c("free_entry", "frictionless_free_entry", "frictionless_no_free_entry"),
      labels = c("Free entry", "Frictionless + free entry", "Frictionless no free entry")
    ),
    variable = factor(
      variable,
      levels = c("f", "w"),
      labels = c("Fee (f)", "Wage (w)")
    )
  ) %>%
  group_by(case, variable) %>%
  summarise(
    mean_change = mean(diff, na.rm = TRUE),
    median_change = median(diff, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(variable, case)

avg_change_wide <-
  avg_change_table %>%
  tidyr::pivot_longer(
    cols = c(mean_change, median_change),
    names_to = "stat",
    values_to = "value"
  ) %>%
  mutate(
    stat = dplyr::recode(
      stat,
      mean_change = "Mean",
      median_change = "Median"
    ),
    row_label = paste(variable, stat, sep = ": ")
  ) %>%
  select(row_label, case, value) %>%
  tidyr::pivot_wider(names_from = case, values_from = value)

out_dir <- here::here("draft/figuretable/estimation_result")
if (!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)
out_file <- file.path(out_dir, "benchmark_avg_signed_change.tex")

fmt_num <- function(x) formatC(x, format = "f", digits = 4)

latex_lines <- c(
  "\\begingroup",
  "\\centering",
  "\\scriptsize",
  "\\setlength{\\tabcolsep}{4pt}",
  "\\begin{tabular}{lccc}",
  "  \\toprule",
  "  & Free entry & Frictionless + free entry & Frictionless no free entry\\\\",
  "  \\midrule",
  apply(
    avg_change_wide,
    1,
    function(row) {
      paste0(
        "  ", row[["row_label"]], " & ",
        fmt_num(as.numeric(row[["Free entry"]])), " & ",
        fmt_num(as.numeric(row[["Frictionless + free entry"]])), " & ",
        fmt_num(as.numeric(row[["Frictionless no free entry"]])), "\\\\"
      )
    }
  ),
  "  \\bottomrule",
  "  \\multicolumn{4}{l}{\\emph{Entries are signed changes from baseline.}}\\\\",
  "\\end{tabular}",
  "\\par\\endgroup"
)

writeLines(latex_lines, out_file)

knitr::kable(
  avg_change_table,
  digits = 4,
  caption = "Average and median signed changes from baseline by case"
)
```

```{r endogenous-diff-boxplot, fig.width=10, fig.height=5}
plot_data <-
  comparison_long %>%
  filter(case != "baseline") %>%
  mutate(
    case = factor(
      case,
      levels = c("free_entry", "frictionless_free_entry", "frictionless_no_free_entry"),
      labels = c("Free entry", "Frictionless + free entry", "Frictionless no free entry")
    ),
    variable = factor(
      variable,
      levels = c("f", "w"),
      labels = c("Fee (f)", "Wage (w)")
    )
  )

p_endogenous_diff <- ggplot(plot_data, aes(x = case, y = diff, fill = case)) +
  geom_boxplot(
    width = 0.65,
    color = "black",
    outlier.shape = NA
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black", linewidth = 0.3) +
  facet_wrap(~ variable, scales = "free_y") +
  scale_fill_grey(start = 0.85, end = 0.45) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Signed deviations from baseline across all markets",
    subtitle = "Outlier points omitted for readability",
    x = NULL,
    y = "Deviation from baseline"
  ) +
  theme_bw(base_size = 12) +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(),
    strip.background = element_rect(fill = "white", color = "black"),
    axis.text.x = element_text(angle = 10, hjust = 1)
  )

out_dir <- here::here("draft/figuretable/estimation_result")
if (!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)
ggsave(
  filename = file.path(out_dir, "benchmark_endogenous_diff_all_markets.pdf"),
  plot = p_endogenous_diff,
  width = 10,
  height = 5
)
ggsave(
  filename = file.path(out_dir, "benchmark_endogenous_diff_sampled.pdf"),
  plot = p_endogenous_diff,
  width = 10,
  height = 5
)

p_endogenous_diff
```

```{r endogenous-heatmap, fig.width=12, fig.height=8}
heatmap_data <-
  comparison_long %>%
  filter(case != "baseline") %>%
  group_by(case, t, j, variable) %>%
  summarise(mean_abs_diff = mean(abs_diff, na.rm = TRUE), .groups = "drop")

ggplot(heatmap_data, aes(x = j, y = t, fill = mean_abs_diff)) +
  geom_tile() +
  facet_grid(variable ~ case) +
  scale_fill_viridis_c(labels = scales::comma) +
  labs(
    title = "Mean absolute deviation heatmap by market-zone pair",
    x = "Zone index (j)",
    y = "Market index (t)",
    fill = "Mean |diff|"
  ) +
  theme_minimal(base_size = 11)
```

## Case-specific Objective Comparison (All Markets)

```{r objective-computation}
tj_grid <-
  purrr::map_dfr(
    seq_along(equilibrium_base$endogenous),
    function(t) {
      tibble(
        t = t,
        j = seq_along(equilibrium_base$endogenous[[t]])
      )
    }
  )

case_map_full <-
  list(
    baseline = equilibrium_base,
    free_entry = equilibrium_competitive,
    frictionless_free_entry = equilibrium_frictionless_free_entry,
    frictionless_no_free_entry = equilibrium_frictionless_no_free_entry
  )

objective_long <-
  purrr::imap_dfr(
    case_map_full,
    function(eq_obj, case_name) {
      tj_grid %>%
        mutate(
          case = case_name,
          objective = purrr::map2_dbl(
            t,
            j,
            ~ compute_case_objective_tj(eq = eq_obj, case_name = case_name, t = .x, j = .y)
          )
        )
    }
  )
```

```{r objective-summary-table}
objective_summary <-
  objective_long %>%
  group_by(case) %>%
  summarise(
    n = n(),
    mean_objective = mean(objective, na.rm = TRUE),
    median_objective = median(objective, na.rm = TRUE),
    p90_objective = quantile(objective, probs = 0.9, na.rm = TRUE),
    max_objective = max(objective, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(case)

knitr::kable(
  objective_summary,
  digits = 8,
  caption = "Case-specific objective residuals across all markets (target is zero)"
)
```

```{r objective-boxplot, fig.width=9, fig.height=5}
objective_long %>%
  ggplot(aes(x = case, y = objective, fill = case)) +
  geom_boxplot(outlier.shape = NA) +
  scale_y_continuous(
    trans = scales::log1p_trans(),
    labels = scales::comma
  ) +
  labs(
    title = "Objective residual distribution across all markets",
    subtitle = "Outlier points omitted for readability",
    x = "Case",
    y = "Objective residual (log1p scale)"
  ) +
  theme_classic(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 15, hjust = 1)
  )
```

```{r objective-heatmap, fig.width=12, fig.height=4}
ggplot(objective_long, aes(x = j, y = t, fill = objective)) +
  geom_tile() +
  facet_wrap(~ case, nrow = 1) +
  scale_fill_viridis_c(labels = scales::comma) +
  labs(
    title = "Objective residual heatmap by market-zone pair",
    x = "Zone index (j)",
    y = "Market index (t)",
    fill = "Objective"
  ) +
  theme_minimal(base_size = 11)
```
