---
title: "Report data analysis"
author: "Chiho Taniguchi"
date: "2023-02-03"
output: 
  html_document:
    toc: true
---


```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 3, fig.width = 4)

library("magrittr")
library("kableExtra")
library("ggplot2")

height <- 6
width <- 8

```


```{r }

 data_establishments <- 
  here::here(file = "cleaned/data_establishments.rds") %>% 
  readRDS()

 data_zipcode <- 
   here::here(file = "cleaned/data_zipcode.rds") %>% 
   readRDS()
 
 data_area <- 
   here::here(file = "cleaned/data_area.rds") %>% 
   readRDS()
 
 data_zip_establishments <- 
   here::here(file = "output/data_zip_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments <- 
   here::here(file = "output/data_cz_establishments.rds") %>% 
   readRDS()
 
```
# Describe N_j_t

We use data defining the market using commuting zone(cz).
N_j_t is a variable that indicates the number of general establishments present in commuting zone(j) in year t.

```{r }
 N_jt_unique <- 
   data_cz_establishments %>% 
   dplyr::select(N_jt) %>% 
   unique()
 
 quantile(
   N_jt_unique$N_jt, 
   c(0.1, 0.25, 0.5, 0.75, 1)
   ) %>% 
   kbl(col.names = "N_jt") %>% 
   kable_styling(full_width = FALSE)
```

## Show historgam

On the left is the distribution of N_j_t, without duplicates, and on the right is the distribution of N_j_t, using all data (allowing duplicates).

```{r}
 ## show histogram
 histogram_N_jt_unique <- 
   ggplot() + 
   geom_histogram(
     data = N_jt_unique, 
     mapping = aes(x = N_jt),
     bins = 100
   )
 
 print(histogram_N_jt_unique)
 
 data_cz_establishments_N_jt <- 
   data_cz_establishments %>% 
   dplyr::select(N_jt)
 
 histogram_N_jt <- 
   ggplot() + 
   geom_histogram(
     data = data_cz_establishments_N_jt, 
     mapping = aes(x = N_jt),
     bins = 100
   )
 
 print(histogram_N_jt)
```

# Describe wage (wage_{it})

```{r}

data_cz_establishments_wage_fee <- 
   data_cz_establishments %>% 
   dplyr::group_by(
     year, 
     cz
     ) %>% 
   dplyr::mutate(
     wage_jt = mean(wage),
     fee_jt = mean(fee)
     ) 
 
 wage_jt_unique <- 
   data_cz_establishments_wage_fee %>% 
   dplyr::select(wage_jt) %>% 
   unique()
 
 summary(wage_jt_unique$wage_jt) 

```

# Describe fee (fee_{it})

```{r}

fee_jt_unique <- 
   data_cz_establishments_wage_fee %>% 
   dplyr::select(fee_jt) %>% 
   unique() 
 
 summary(fee_jt_unique$fee_jt)

```

# Describe N_zip_t

We use data that defines the market using the first three digits of the zipcode instead of commuting zone(cz).
N_zip_t is a variable that indicates the number of general establishments in the commuting zone(zip) defined using the firt three digits of the zipcode in year t.

```{r }
 N_zip_t_unique <- 
   data_zip_establishments %>% 
   dplyr::select(N_zip_t) %>% 
   unique()
 
 quantile(
   N_zip_t_unique$N_zip_t, 
   c(0.05, 0.1, 0.25, 0.5, 0.75, 1)
 ) %>% 
   kbl(col.names = "N_zip_t") %>% 
   kable_styling(full_width = FALSE)
```

## Show historgam

On the left is the distribution of N_zip_t, without duplicates, and on the right is the distribution of N_zip_t, using all data (allowing duplicates).

```{r}
# Unique data for N_zip_t

histogram_N_zip_t_unique <- 
   ggplot() + 
   geom_histogram(
     data = N_zip_t_unique, 
     mapping = aes(x = N_zip_t),
     bins = 100
   )
 
 print(histogram_N_zip_t_unique)
 
 # All data for N_zip_t
 
 data_zip_establishments_N_zip_t <- 
   data_zip_establishments %>% 
   dplyr::select(N_zip_t)
 
 histogram_N_zip_t <- 
   ggplot() + 
   geom_histogram(
     data = data_zip_establishments_N_zip_t, 
     mapping = aes(x = N_zip_t),
     bins = 100
   )
 
 print(histogram_N_zip_t)
```

# Describe wage (wage_{it})

```{r}
 data_zip_establishments_wage_fee <- 
   data_zip_establishments %>% 
   dplyr::group_by(
     year, 
     zip_three
   ) %>% 
   dplyr::mutate(
     wage_jt = mean(wage),
     fee_jt = mean(fee)
   ) 
 
 wage_jt_unique <- 
   data_zip_establishments_wage_fee %>% 
   dplyr::select(wage_jt) %>% 
   unique()
 
 summary(wage_jt_unique$wage_jt) 
 
```
 
# Describe fee (fee_{it})

```{r, warning=FALSE}

 fee_jt_unique <- 
   data_zip_establishments_wage_fee %>% 
   dplyr::select(fee_jt) %>% 
   unique() 
 
 summary(fee_jt_unique$fee_jt)

```


# Analyze D_ 

```{r}

results2 <- list()
 
 results2[[1]] <- 
   lfe::felm(
     formula = log_fee ~ D_2 + D_3 + D_4 + D_5 | cz + year ,
     data = data_cz_establishments
   )
 
 results2[[2]] <- 
   lfe::felm(
     formula = log_fee ~ D_2 + D_3 + D_4 + D_5 | year + firm_id ,
     data = data_cz_establishments
   )
 
 results2[[3]] <- 
   lfe::felm(
     formula = log_wage ~ D_2 + D_3 + D_4 + D_5 | cz + year ,
     data = data_cz_establishments
   )
 
 results2[[4]] <- 
   lfe::felm(
     formula = log_wage ~ D_2 + D_3 + D_4 + D_5 | year + firm_id ,
     data = data_cz_establishments
   )
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`,
     'j_FE', 'Y', 'N', 'Y', 'N',
     't_FE', 'Y', 'Y', 'Y', 'Y',
     'i_FE', 'N', 'Y', 'N', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(12, 13, 14, 15)
 
 result_2 <- 
   list(
     "log(fee)" = results2[[1]],
     "log(fee)" = results2[[2]],
     "log(wage)" = results2[[3]],
     "log(wage)" = results2[[4]]
   )
 
 modelsummary::modelsummary(
   result_2,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 

```

# Analyze different N_j_t {.tabset}

N_j_t is divided by the number after N_j_t.

## Analyze N_j_t

```{r}
results1 <- list()
 
 results1[[1]] <- 
   lfe::felm(
   formula = log_fee ~  N_jt | cz + year ,
   data = data_cz_establishments
   )
 
 results1[[2]] <- 
   lfe::felm(
   formula = log_fee ~  N_jt | year + firm_id ,
   data = data_cz_establishments
   )
 
 results1[[3]] <- 
   lfe::felm(
   formula = log_wage ~  N_jt | cz + year ,
   data = data_cz_establishments
   )
 
 results1[[4]] <- 
   lfe::felm(
   formula = log_wage ~  N_jt | year + firm_id ,
   data = data_cz_establishments
   )
 
 rows <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`,
                 'j_FE', 'Y', 'N', 'Y', 'N',
                 't_FE', 'Y', 'Y', 'Y', 'Y',
                 'i_FE', 'N', 'Y', 'N', 'Y' 
     )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_1 <- 
   list(
   "log(fee)" = results1[[1]],
   "log(fee)" = results1[[2]],
   "log(wage)" = results1[[3]],
   "log(wage)" = results1[[4]]
 )
 
 modelsummary::modelsummary(
   result_1,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
   ) 
 

```

## Analyze N_j_t_10
```{r}
results3 <- list()
 
 results3[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_10 | cz + year ,
     data = data_cz_establishments
   )
 
 results3[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_10 | year + firm_id ,
     data = data_cz_establishments
   )
 
 results3[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_10 | cz + year ,
     data = data_cz_establishments
   )
 
 results3[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_10 | year + firm_id ,
     data = data_cz_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_3 <- 
   list(
     "log(fee)" = results3[[1]],
     "log(fee)" = results3[[2]],
     "log(wage)" = results3[[3]],
     "log(wage)" = results3[[4]]
   )
 
 modelsummary::modelsummary(
   result_3,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 


```

## Analyze N_j_t_100

```{r}

results5 <- list()
 
 results5[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_100 | cz + year ,
     data = data_cz_establishments
   )
 
 results5[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_100 | year + firm_id ,
     data = data_cz_establishments
   )
 
 results5[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_100 | cz + year ,
     data = data_cz_establishments
   )
 
 results5[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_100 | year + firm_id ,
     data = data_cz_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_5 <- 
   list(
     "log(fee)" = results5[[1]],
     "log(fee)" = results5[[2]],
     "log(wage)" = results5[[3]],
     "log(wage)" = results5[[4]]
   )
 
 modelsummary::modelsummary(
   result_5,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```
 
## Analyze N_j_t_1000

```{r}

results4 <- list()
 
 results4[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_1000 | cz + year ,
     data = data_cz_establishments
   )
 
 results4[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_1000 | year + firm_id ,
     data = data_cz_establishments
   )
 
 results4[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_1000 | cz + year ,
     data = data_cz_establishments
   )
 
 results4[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_1000 | year + firm_id ,
     data = data_cz_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_4 <- 
   list(
     "log(fee)" = results4[[1]],
     "log(fee)" = results4[[2]],
     "log(wage)" = results4[[3]],
     "log(wage)" = results4[[4]]
   )
 
 modelsummary::modelsummary(
   result_4,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## Analyze N_j_t_10000

```{r}

results6 <- list()
 
 results6[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_10000 | cz + year ,
     data = data_cz_establishments
   )
 
 results6[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_10000 | year + firm_id ,
     data = data_cz_establishments
   )
 
 results6[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_10000 | cz + year ,
     data = data_cz_establishments
   )
 
 results6[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_10000 | year + firm_id ,
     data = data_cz_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_6 <- 
   list(
     "log(fee)" = results6[[1]],
     "log(fee)" = results6[[2]],
     "log(wage)" = results6[[3]],
     "log(wage)" = results6[[4]]
   )
 
 modelsummary::modelsummary(
   result_6,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## Analyze N_z_t_100000

```{r}

results7 <- list()
 
 results7[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_100000 | cz + year ,
     data = data_cz_establishments
   )
 
 results7[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_jt_100000 | year + firm_id ,
     data = data_cz_establishments
   )
 
 results7[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_100000 | cz + year ,
     data = data_cz_establishments
   )
 
 results7[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_jt_100000 | year + firm_id ,
     data = data_cz_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_7 <- 
   list(
     "log(fee)" = results7[[1]],
     "log(fee)" = results7[[2]],
     "log(wage)" = results7[[3]],
     "log(wage)" = results7[[4]]
   )
 
 modelsummary::modelsummary(
   result_7,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```


# Analyze D_ for zip_three {.tabset}

## Include D_1 to D_5

```{r}

results22 <- list()
 
 results22[[1]] <- 
   lfe::felm(
     formula = log_fee ~ D_2 + D_3 + D_4 + D_5  | zip_three + year ,
     data = data_zip_establishments
   )
 
 results22[[2]] <- 
   lfe::felm(
     formula = log_fee ~ D_2 + D_3 + D_4 + D_5 | year + firm_id ,
     data = data_zip_establishments
   )
 
 results22[[3]] <- 
   lfe::felm(
     formula = log_wage ~ D_2 + D_3 + D_4 + D_5 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results22[[4]] <- 
   lfe::felm(
     formula = log_wage ~ D_2 + D_3 + D_4 + D_5 | year + firm_id ,
     data = data_zip_establishments
   )
 
 rows_D <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`,
     'j_FE', 'Y', 'N', 'Y', 'N',
     't_FE', 'Y', 'Y', 'Y', 'Y',
     'i_FE', 'N', 'Y', 'N', 'Y' 
   )
 
 attr(rows_D, 'position') <- c(12, 13, 14, 15)
 
 result_22 <- 
   list(
     "log(fee)" = results22[[1]],
     "log(fee)" = results22[[2]],
     "log(wage)" = results22[[3]],
     "log(wage)" = results22[[4]]
   )
 
 modelsummary::modelsummary(
   result_22,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_D
 ) 
 
```

## Include D_1 to D_10

```{r}

results23 <- list()
 
 results23[[1]] <- 
   lfe::felm(
     formula = log_fee ~ D_2 + D_3 + D_4 + D_5 + D_6 + D_7 + D_8 + D_9 + D_10 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results23[[2]] <- 
   lfe::felm(
     formula = log_fee ~ D_2 + D_3 + D_4 + D_5 + D_6 + D_7 + D_8 + D_9 + D_10 | year + firm_id ,
     data = data_zip_establishments
   )
 
 results23[[3]] <- 
   lfe::felm(
     formula = log_wage ~ D_2 + D_3 + D_4 + D_5 + D_6 + D_7 + D_8 + D_9 + D_10 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results23[[4]] <- 
   lfe::felm(
     formula = log_wage ~ D_2 + D_3 + D_4 + D_5 + D_6 + D_7 + D_8 + D_9 + D_10 | year + firm_id ,
     data = data_zip_establishments
   )
 
 rows_DD <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`,
     'j_FE', 'Y', 'N', 'Y', 'N',
     't_FE', 'Y', 'Y', 'Y', 'Y',
     'i_FE', 'N', 'Y', 'N', 'Y' 
   )
 
 attr(rows_DD, 'position') <- c(20, 21, 22, 23)
 
 result_23 <- 
   list(
     "log(fee)" = results23[[1]],
     "log(fee)" = results23[[2]],
     "log(wage)" = results23[[3]],
     "log(wage)" = results23[[4]]
   )
 
 modelsummary::modelsummary(
   result_23,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows_DD
 )
```
 
# Analyze different N_zip_t {.tabset}

N_zip_t is divided by the number after N_zip_t.

## Analyze N_zip_t

```{r}
results11 <- list()
 
 results11[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t | zip_three + year ,
     data = data_zip_establishments
   )
 
 results11[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t | year + firm_id ,
     data = data_zip_establishments
   )
 
 results11[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t | zip_three + year ,
     data = data_zip_establishments
   )
 
 results11[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t | year + firm_id ,
     data = data_zip_establishments
   )
 
 rows <- 
   tibble::tribble(
     ~term, ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`,
     'j_FE', 'Y', 'N', 'Y', 'N',
     't_FE', 'Y', 'Y', 'Y', 'Y',
     'i_FE', 'N', 'Y', 'N', 'Y' 
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_11 <- 
   list(
     "log(fee)" = results11[[1]],
     "log(fee)" = results11[[2]],
     "log(wage)" = results11[[3]],
     "log(wage)" = results11[[4]]
   )
 
 modelsummary::modelsummary(
   result_11,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 
 
```

## Analyze N_zip_t_10

```{r}
 results33 <- list()
 
 results33[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_10 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results33[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_10 | year + firm_id ,
     data = data_zip_establishments
   )
 
 results33[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_10 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results33[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_10 | year + firm_id ,
     data = data_zip_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_33 <- 
   list(
     "log(fee)" = results33[[1]],
     "log(fee)" = results33[[2]],
     "log(wage)" = results33[[3]],
     "log(wage)" = results33[[4]]
   )
 
 modelsummary::modelsummary(
   result_33,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 
 
```

## Analyze N_zip_t_1000

```{r}
results44 <- list()
 
 results44[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_1000 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results44[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_1000 | year + firm_id ,
     data = data_zip_establishments
   )
 
 results44[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_1000 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results44[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_1000 | year + firm_id ,
     data = data_zip_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_44 <- 
   list(
     "log(fee)" = results44[[1]],
     "log(fee)" = results44[[2]],
     "log(wage)" = results44[[3]],
     "log(wage)" = results44[[4]]
   )
 
 modelsummary::modelsummary(
   result_44,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## Analyze N_zip_t_100

```{r}

results55 <- list()
 
 results55[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_100 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results55[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_100 | year + firm_id ,
     data = data_zip_establishments
   )
 
 results55[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_100 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results55[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_100 | year + firm_id ,
     data = data_zip_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_55 <- 
   list(
     "log(fee)" = results55[[1]],
     "log(fee)" = results55[[2]],
     "log(wage)" = results55[[3]],
     "log(wage)" = results55[[4]]
   )
 
 modelsummary::modelsummary(
   result_55,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```

## Analyze N_zip_t_10000

```{r}

results66 <- list()
 
 results66[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_10000 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results66[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_10000 | year + firm_id ,
     data = data_zip_establishments
   )
 
 results66[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_10000 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results66[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_10000 | year + firm_id ,
     data = data_zip_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_66 <- 
   list(
     "log(fee)" = results66[[1]],
     "log(fee)" = results66[[2]],
     "log(wage)" = results66[[3]],
     "log(wage)" = results66[[4]]
   )
 
 modelsummary::modelsummary(
   result_66,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 
 
```

## Analyze N_zip_t_100000

```{r }

results77 <- list()
 
 results77[[1]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_100000 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results77[[2]] <- 
   lfe::felm(
     formula = log_fee ~  N_zip_t_100000 | year + firm_id ,
     data = data_zip_establishments
   )
 
 results77[[3]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_100000 | zip_three + year ,
     data = data_zip_establishments
   )
 
 results77[[4]] <- 
   lfe::felm(
     formula = log_wage ~  N_zip_t_100000 | year + firm_id ,
     data = data_zip_establishments
   )
 
 attr(rows, 'position') <- c(6, 7, 8, 9)
 
 result_77 <- 
   list(
     "log(fee)" = results77[[1]],
     "log(fee)" = results77[[2]],
     "log(wage)" = results77[[3]],
     "log(wage)" = results77[[4]]
   )
 
 modelsummary::modelsummary(
   result_77,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC",
   add_rows = rows
 ) 

```
