---
title: "report_estimation_result_with_penalty_initial_hpc4"
author: "Daisy Dan Song"
date: "2025-07-06"
output: html_document
---

# initialize
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )
rm(list = ls())
library(Dispatching)
library(foreach)
library(magrittr)
library(codetools)
library(ggplot2)
library(kableExtra)
library(purrr)
```

# import estimation equilibrium
```{r}
equilibrium <-
  readRDS(
    file = "output/multihome/estimate_data/equilibrium_updated_constrained.rds" %>%
    here::here()
  )
```

# summary statistics for equilibrium
```{r}
T <- length(equilibrium$exogenous)
J_by_t <- vapply(equilibrium$exogenous, length, integer(1))
years <- if (T == 5) 2010:2014 else seq_len(T)

cat("Equilibrium object summary\n")
cat("- years (T):", T, "\n")
cat("- markets per year (J):", paste(J_by_t, collapse = ", "), "\n\n")

# Market-year level summary
rows_market <- list()
k <- 1L
for (t in seq_len(T)) {
  for (j in seq_along(equilibrium$exogenous[[t]])) {
    ex_tj <- equilibrium$exogenous[[t]][[j]]
    en_tj <- equilibrium$endogenous[[t]][[j]]
    rows_market[[k]] <- data.frame(
      year = years[t],
      market = j,
      n_options = length(en_tj$w),
      size_w = ex_tj$size_w,
      size_f = ex_tj$size_f
    )
    k <- k + 1L
  }
}
df_market <- do.call(rbind, rows_market)

cat("Market-year summary\n")
print(summary(df_market[, c("n_options", "size_w", "size_f")]))
cat("\nDistribution of number of options per market-year (n_options):\n")
print(table(df_market$n_options))

# Option-level summary (stack vectors into a long data frame)
rows_endog <- list()
k <- 1L
for (t in seq_len(T)) {
  for (j in seq_along(equilibrium$endogenous[[t]])) {
    en_tj <- equilibrium$endogenous[[t]][[j]]
    n <- length(en_tj$w)
    for (i in seq_len(n)) {
      rows_endog[[k]] <- data.frame(
        year = years[t],
        market = j,
        option = i,
        w = en_tj$w[i],
        f = en_tj$f[i],
        s_w = en_tj$s_w[i],
        s_f = en_tj$s_f[i]
      )
      k <- k + 1L
    }
  }
}
df_endog <- do.call(rbind, rows_endog)
df_endog$margin <- with(df_endog, ifelse(f == 0, NA, (f - w) / f))

cat("\nOption-level (endogenous) summary\n")
print(summary(df_endog[, c("w", "f", "s_w", "s_f", "margin")]))
cat("\nOption-level summary by option index (means)\n")
print(aggregate(cbind(w, f, s_w, s_f, margin) ~ option, data = df_endog, FUN = mean, na.rm = TRUE))
```

# demand linear parameters
```{r}
cbind(
  beta_w = equilibrium$parameter$beta_w,
  beta_f = equilibrium$parameter$beta_f
)
```

# Linear paramters corresponding names
```{r}
a_f <- 
  foreach(
    t = seq_along(equilibrium$endogenous),
    .combine = rbind,
    .packages = c(
      "foreach",
      "magrittr",
      "Dispatching"
    )
  ) %dopar% {
    a_f_t <- 
      foreach(
        j = seq_along(equilibrium$endogenous[[t]]),
        .combine = rbind
      ) %do% {
        a_f_tj <- 
          compute_demand_shock_a_f_tj_rcpp(
            m_f = equilibrium$parameter$m_f,
            m_w = equilibrium$parameter$m_w,
            lambda_f = equilibrium$parameter$lambda_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            f = equilibrium$endogenous[[t]][[j]]$f,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          )
        return(a_f_tj)
      }
    return(a_f_t)
  }

a_w <- 
  foreach(
    t = seq_along(equilibrium$endogenous),
    .combine = rbind,
    .packages = c(
      "foreach",
      "magrittr",
      "Dispatching"
    )
  ) %dopar% {
    a_w_t <- 
      foreach(
        j = seq_along(equilibrium$endogenous[[t]]),
        .combine = rbind
      ) %do% {
        a_w_tj <- 
          compute_demand_shock_nleqslv_a_w_tj(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            lambda_w = equilibrium$parameter$lambda_w,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            w = equilibrium$endogenous[[t]][[j]]$w,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f,
            s_w = equilibrium$endogenous[[t]][[j]]$s_w,
            method_s_w = equilibrium$constant$method_s_w,
            margin = equilibrium$constant$margin,
            quadrature_size = equilibrium$constant$quadrature_size,
            tol = equilibrium$constant$tol
          )
        return(a_w_tj)
      }
    return(a_w_t)
  }

x_a_w <- 
  foreach(
    t = seq_along(equilibrium$endogenous),
    .combine = rbind,
    .packages = c(
      "foreach",
      "magrittr",
      "Dispatching"
    )
  ) %dopar% {
    x_a_w_t <- 
      foreach(
        j = seq_along(equilibrium$endogenous[[t]]),
        .combine = rbind
      ) %do% {
        x_a_w_t_j <- equilibrium$exogenous[[t]][[j]]$x_a_w
        return(x_a_w_t_j)
      }
    return(x_a_w_t)
  }

x_a_f <- 
  foreach(
    t = seq_along(equilibrium$endogenous),
    .combine = rbind,
    .packages = c(
      "foreach",
      "magrittr",
      "Dispatching"
    )
  ) %dopar% {
    x_a_f_t <- 
      foreach(
        j = seq_along(equilibrium$endogenous[[t]]),
        .combine = rbind
      ) %do% {
        x_a_f_t_j <- equilibrium$exogenous[[t]][[j]]$x_a_f
        return(x_a_f_t_j)
      }
    return(x_a_f_t)
  }

result_w <- 
  lm(
    a_w ~ x_a_w + 0
  )

result_f <- 
  lm(
    a_f ~ x_a_f + 0 
  )
```

## beta_w
```{r}
result_w$coefficients
```

## beta_f
```{r}
result_f$coefficients
```

# supply linear parameters
```{r}
cbind(
  gamma_w = equilibrium$parameter$gamma_w,
  gamma_f = equilibrium$parameter$gamma_f
)
```

## gamma_w
```{r}
equilibrium$parameter$gamma_w
```

## gamma_f
```{r}
equilibrium$parameter$gamma_f
```

# non-linear parameters
```{r}
rbind(
  m_w = equilibrium$parameter$m_w,
  m_f = equilibrium$parameter$m_f,
  lambda_w = equilibrium$parameter$lambda_w,
  lambda_f = equilibrium$parameter$lambda_f,
  mu_p = equilibrium$parameter$mu_p,
  mu_ths = equilibrium$parameter$mu_ths
)
```

# demand shocks
```{r}
ea_w <- 
  foreach(
    t = seq_along(equilibrium$exogenous)
  ) %do%{
    ea_w_t <- 
      foreach(
        j = seq_along(equilibrium$exogenous[[t]])
      ) %do% { 
        ea_w_tj <- 
          equilibrium$shock[[t]][[j]]$ea_w
        return(ea_w_tj)
      }
    return(ea_w_t)
  }

ea_f <- 
  foreach(
    t = seq_along(equilibrium$exogenous)
  ) %do%{
    ea_f_t <- 
      foreach(
        j = seq_along(equilibrium$exogenous[[t]])
      ) %do% { 
        ea_f_tj <- 
          equilibrium$shock[[t]][[j]]$ea_f
        return(ea_f_tj)
      }
    return(ea_f_t)
  }

df <- 
  data.frame(
    ea_w = unlist(ea_w),
    ea_f = unlist(ea_f)
  )

g <- 
  ggplot(
    df, 
    aes(
      x = ea_w, 
      y = ea_f
    )
  ) +
  geom_point() +
  geom_vline(
    xintercept = 0, 
    color = "red", 
    lty = "solid"
  ) +
  geom_hline(
    yintercept = 0, 
    color = "red", 
    lty = "solid"
  ) +
  labs(
    x = "elicited ea_w", 
    y = "elicited ea_f", 
    title = "Scatter Plot of Demand Shocks"
  ) +
  theme_classic()
g
```

# supply shocks
```{r}
ec_w <- 
  foreach(
    t = seq_along(equilibrium$exogenous)
  ) %do%{
    ec_w_t <- 
      foreach(
        j = seq_along(equilibrium$exogenous[[t]])
      ) %do% { 
        ec_w_tj <- 
          equilibrium$shock[[t]][[j]]$ec_w
        return(ec_w_tj)
      }
    return(ec_w_t)
  }

ec_f <- 
  foreach(
    t = seq_along(equilibrium$exogenous)
  ) %do%{
    ec_f_t <- 
      foreach(
        j = seq_along(equilibrium$exogenous[[t]])
      ) %do% { 
        ec_f_tj <- 
          equilibrium$shock[[t]][[j]]$ec_f
        return(ec_f_tj)
      }
    return(ec_f_t)
  }

df$ec_w <-  unlist(ec_w)
df$ec_f <-  unlist(ec_f)

g <- 
  ggplot(
    df, 
    aes(
      x = ec_w, 
      y = ec_f
    )
  ) +
  geom_point() +
  geom_vline(
    xintercept = 0, 
    color = "red", 
    lty = "solid"
  ) +
  geom_hline(
    yintercept = 0, 
    color = "red", 
    lty = "solid"
  ) +
  labs(
    x = "elicited ec_w", 
    y = "elicited ec_f", 
    title = "Scatter Plot of Supply Shocks"
  ) +
  theme_classic()
g
```

## summary statistics
```{r}
summary(df)
```

# costs
```{r}
T <- length(equilibrium$exogenous)
J_by_t <- vapply(equilibrium$exogenous, length, integer(1))
years <- if (T == 5) 2010:2014 else seq_len(T)

safe_costs_tj <- function(t, j) {
  tryCatch(
    {
      c_w_tj <-
        compute_supply_shock_c_w_tj(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          lambda_w = equilibrium$parameter$lambda_w,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          w = equilibrium$endogenous[[t]][[j]]$w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          owner = equilibrium$exogenous[[t]][[j]]$owner,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )

      # Prepend outside-option value as a scalar (avoid rbind() -> matrix coercion)
      c_w_aug <- c(0.1, c_w_tj)

      c_f_tj <-
        compute_supply_shock_c_f_tj(
          c_w = c_w_aug,
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          beta_f = equilibrium$parameter$beta_f,
          lambda_w = equilibrium$parameter$lambda_w,
          lambda_f = equilibrium$parameter$lambda_f,
          x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
          x_a_f = equilibrium$exogenous[[t]][[j]]$x_a_f,
          size_w = equilibrium$exogenous[[t]][[j]]$size_w,
          size_f = equilibrium$exogenous[[t]][[j]]$size_f,
          mu = equilibrium$shock[[t]][[j]]$mu,
          ea_w = equilibrium$shock[[t]][[j]]$ea_w,
          ea_f = equilibrium$shock[[t]][[j]]$ea_f,
          owner = equilibrium$exogenous[[t]][[j]]$owner,
          w = equilibrium$endogenous[[t]][[j]]$w,
          f = equilibrium$endogenous[[t]][[j]]$f,
          s_w = equilibrium$endogenous[[t]][[j]]$s_w,
          s_f = equilibrium$endogenous[[t]][[j]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        )

      c_w_no0 <- c_w_aug[-1]
      if (length(c_f_tj) != length(c_w_no0)) {
        stop(paste0("length mismatch: length(c_f)=", length(c_f_tj),
                    ", length(c_w)=", length(c_w_no0)))
      }

      data.frame(
        year = years[t],
        market = j,
        c_w = c_w_no0,
        c_f = c_f_tj,
        error = NA_character_
      )
    },
    error = function(e) {
      data.frame(
        year = years[t],
        market = j,
        c_w = NA_real_,
        c_f = NA_real_,
        error = conditionMessage(e)
      )
    }
  )
}

rows_costs <- list()
k <- 1L
for (t in seq_len(T)) {
  for (j in seq_len(J_by_t[t])) {
    rows_costs[[k]] <- safe_costs_tj(t, j)
    k <- k + 1L
  }
}
c <- do.call(rbind, rows_costs)

cat("Costs computed for", nrow(c), "rows.\n")
cat("Number of failed market-years:", sum(!is.na(c$error)), "\n")
if (any(!is.na(c$error))) {
  cat("First few failures (year, market, error):\n")
  print(utils::head(c[!is.na(c$error), c("year", "market", "error")], 5))
}
```

```{r}
summary(c)
```

## negative number of c_w & c_f
```{r}
num_1 <- sum(c$c_w < 0, na.rm = TRUE)
num_2 <- sum(c$c_f < 0, na.rm = TRUE)
num_3 <- nrow(c)
```

- `r num_1` out of `r num_3` c_w are negetive
- `r num_2` out of `r num_3` c_f are negetive

# shares
```{r}
s_w_predicted <- 
  foreach(
    t = seq_along(equilibrium$exogenous),
    .combine = rbind
  ) %do% {
    foreach(
      j = seq_along(equilibrium$exogenous[[t]]),
      .combine = rbind
    ) %do% {
        solution_tj <- 
          solve_s_w_tj_exact_check(
            m_w = equilibrium$parameter$m_w,
            m_f = equilibrium$parameter$m_f,
            beta_w = equilibrium$parameter$beta_w,
            lambda_w = equilibrium$parameter$lambda_w,
            x_a_w = equilibrium$exogenous[[t]][[j]]$x_a_w,
            size_w = equilibrium$exogenous[[t]][[j]]$size_w,
            size_f = equilibrium$exogenous[[t]][[j]]$size_f,
            mu = equilibrium$shock[[t]][[j]]$mu,
            ea_w = equilibrium$shock[[t]][[j]]$ea_w,
            w = equilibrium$endogenous[[t]][[j]]$w,
            s_f = equilibrium$endogenous[[t]][[j]]$s_f
          ) 
      return(solution_tj)
    }
  }

```

```{r}
s_w_actual <- 
  foreach(
    t = seq_along(equilibrium$exogenous),
    .combine = rbind
  ) %do% {
    foreach(
      j = seq_along(equilibrium$exogenous[[t]]),
      .combine = rbind
    ) %do% {
      s_w_tj <- equilibrium$endogenous[[t]][[j]]$s_w
      return(s_w_tj)
    }
  }

```

```{r}
df_s_w <- 
  data.frame(
    s_w_actual = s_w_actual,
    s_w_predicted = s_w_predicted
  )
```

```{r}
g <- 
  ggplot(
    df_s_w, 
    aes(
      x = s_w_predicted, 
      y = s_w_actual
    )
  ) +
  geom_point() +
  geom_abline(
    slope = 1, 
    intercept = 0, 
    color = "red", 
    linetype = "solid"
  ) +
  labs(
    x = "s_w_predicted",
    y = "s_w_actual",
    title = "Scatter Plot of share of workers"
  ) +
  theme_classic()
g
```
