---
title: "report data analysis potential entrant (all sample)"
author: "Chiho Taniguchi"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 3, fig.width = 4)

library("magrittr")
library("kableExtra")
library("ggplot2")

height <- 6
width <- 8

```

```{r }
 
 data_cz_establishments <- 
   here::here(file = "output/data_cz_establishments.rds") %>% 
   readRDS()
 
 data_area_area_distance <- 
   here::here(file = "cleaned/data_area_area_distance.rds") %>% 
   readRDS()
 
 data_cz_potential_entrant_all <- 
   here::here(file = "output/data_cz_potential_entrant_all.rds") %>% 
   readRDS()

 data_cz_potential_entrant <- 
   here::here(file= "output/data_cz_potential_entrant.rds") %>% 
   readRDS()
 
 data_cz_potential_entrantunder3 <- 
   here::here(file= "output/data_cz_potential_entrantunder3.rds") %>% 
   readRDS()
 
 data_cz_potential_entrantunder5 <- 
   here::here(file= "output/data_cz_potential_entrantunder5.rds") %>% 
   readRDS()
 
```



```{r}

data_cz_potential_entrant =
  data_cz_potential_entrant %>% 
  dplyr::mutate(
    potential_entrant10km = potential_entrant10km / 1000,
    potential_entrant20km = potential_entrant20km / 1000,
    potential_entrant30km = potential_entrant30km / 1000,
    potential_entrant40km = potential_entrant40km / 1000,
    potential_entrant50km = potential_entrant50km / 1000
  )

data_cz_potential_entrantunder3 =
  data_cz_potential_entrantunder3 %>% 
  dplyr::mutate(
    potential_entrant10km = potential_entrant10km / 1000,
    potential_entrant20km = potential_entrant20km / 1000,
    potential_entrant30km = potential_entrant30km / 1000,
    potential_entrant40km = potential_entrant40km / 1000,
    potential_entrant50km = potential_entrant50km / 1000
  )

data_cz_potential_entrantunder5 =
  data_cz_potential_entrantunder5 %>% 
  dplyr::mutate(
    potential_entrant10km = potential_entrant10km / 1000,
    potential_entrant20km = potential_entrant20km / 1000,
    potential_entrant30km = potential_entrant30km / 1000,
    potential_entrant40km = potential_entrant40km / 1000,
    potential_entrant50km = potential_entrant50km / 1000
  )


```



# all sample

## first stage 

係数が小さくなるなるため、potential_entrantの数値は1000で除した値を使用。

### results {.tabset}

#### 5km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

#### 10km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

#### 20km

```{r}


results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```




#### 30km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

#### 40km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

#### 50 km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

### bonscatter plot {.tabset}

#### 5km

```{r}
  
plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant5km
  ) %>% 
  dplyr::mutate(
    id = c(1:802) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 200, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant5km_avr = mean(potential_entrant5km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant5km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant5km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 10km

```{r}
  
plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant10km
  ) %>% 
  dplyr::mutate(
    id = c(1:802) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 200, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant10km_avr = mean(potential_entrant10km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant10km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant10km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 20km

```{r}
  
 plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant20km
  ) %>% 
  dplyr::mutate(
    id = c(1:802) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 40, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant20km_avr = mean(potential_entrant20km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant20km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant20km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 30km

```{r}
  
 plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant30km
  ) %>% 
  dplyr::mutate(
    id = c(1:802) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 40, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant30km_avr = mean(potential_entrant30km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant30km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant30km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 40km

```{r}
  
  plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant40km
  ) %>% 
  dplyr::mutate(
    id = c(1:802) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 40, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant40km_avr = mean(potential_entrant40km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant40km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant40km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 50km

```{r}
  
  plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant50km
  ) %>% 
  dplyr::mutate(
    id = c(1:802) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 40, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant50km_avr = mean(potential_entrant50km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant50km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant50km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

## reduced form {.tabset}

### 5km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
   
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 10km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
   
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 20km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 30km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 40km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 50km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

## structural form {.tabset}

### 2nd stage {.tabset}

#### 5km

```{r}

resultss0 <- list()

resultss0[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant5km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss0[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant5km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss0[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant5km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s0 <- 
  list(
    "log_diff_wage" = resultss0[[1]],
    "log_diff_fee" = resultss0[[2]],
    "log_diff_fee - log_diff_wage" = resultss0[[3]]
  )

modelsummary::modelsummary(
  results_s0,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```




#### 10km

```{r}

resultss <- list()

resultss[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant10km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant10km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant10km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 20km

```{r}

resultss2 <- list()

resultss2[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant20km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss2[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant20km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss2[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant20km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s2 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s2,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 30km

```{r}

resultss3 <- list()

resultss3[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant30km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss3[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant30km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss3[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant30km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s3 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s3,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 40km

```{r}

resultss4 <- list()

resultss4[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant40km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss4[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant40km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss4[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant40km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s4 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s4,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 50km

```{r}

resultss5 <- list()

resultss5[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant50km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss5[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant50km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss5[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant50km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s5 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s5,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 1st stage {.tabset}

#### 5km

```{r}

modelsummary::modelsummary(
  resultss0[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 10km

```{r}

modelsummary::modelsummary(
  resultss[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 20km

```{r}

modelsummary::modelsummary(
  resultss2[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 30km

```{r}

modelsummary::modelsummary(
  resultss3[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 40km

```{r}

modelsummary::modelsummary(
  resultss4[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```


#### 50km

```{r}

modelsummary::modelsummary(
  resultss5[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

# sub sample 1

The number of establishments in cz in each year is equivalent to 3 or less than 3.

```{r}

data_cz_potential_entrant = data_cz_potential_entrantunder3

```

## first stage 

係数が小さくなるなるため、potential_entrantの数値は1000で除した値を使用。

### results {.tabset}

#### 5km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

#### 10km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

#### 20km

```{r}


results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```




#### 30km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

#### 40km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

#### 50 km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

### bonscatter plot {.tabset}

#### 5km

```{r}
  
plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant5km
  ) %>% 
  dplyr::mutate(
    id = c(1:151) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant5km_avr = mean(potential_entrant5km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant5km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant5km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 10km

```{r}
  
plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant10km
  ) %>% 
  dplyr::mutate(
    id = c(1:151) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant10km_avr = mean(potential_entrant10km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant10km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant10km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 20km

```{r}
  
 plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant20km
  ) %>% 
  dplyr::mutate(
    id = c(1:151) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant20km_avr = mean(potential_entrant20km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant20km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant20km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 30km

```{r}
  
 plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant30km
  ) %>% 
  dplyr::mutate(
    id = c(1:151) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant30km_avr = mean(potential_entrant30km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant30km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant30km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 40km

```{r}
  
  plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant40km
  ) %>% 
  dplyr::mutate(
    id = c(1:151) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant40km_avr = mean(potential_entrant40km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant40km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant40km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 50km

```{r}
  
  plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant50km
  ) %>% 
  dplyr::mutate(
    id = c(1:151) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant50km_avr = mean(potential_entrant50km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant50km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant50km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

## reduced form {.tabset}

### 5km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
   
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 10km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
   
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 20km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 30km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 40km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 50km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

## structural form {.tabset}

### 2nd stage {.tabset}

#### 5km

```{r}

resultss0 <- list()

resultss0[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant5km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss0[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant5km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss0[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant5km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s0 <- 
  list(
    "log_diff_wage" = resultss0[[1]],
    "log_diff_fee" = resultss0[[2]],
    "log_diff_fee - log_diff_wage" = resultss0[[3]]
  )

modelsummary::modelsummary(
  results_s0,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 10km

```{r}

resultss <- list()

resultss[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant10km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant10km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant10km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 20km

```{r}

resultss2 <- list()

resultss2[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant20km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss2[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant20km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss2[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant20km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s2 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s2,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 30km

```{r}

resultss3 <- list()

resultss3[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant30km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss3[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant30km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss3[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant30km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s3 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s3,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 40km

```{r}

resultss4 <- list()

resultss4[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant40km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss4[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant40km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss4[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant40km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s4 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s4,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 50km

```{r}

resultss5 <- list()

resultss5[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant50km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss5[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant50km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss5[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant50km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s5 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s5,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 1st stage {.tabset}

#### 5km

```{r}

modelsummary::modelsummary(
  resultss0[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 10km

```{r}

modelsummary::modelsummary(
  resultss[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 20km

```{r}

modelsummary::modelsummary(
  resultss2[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 30km

```{r}

modelsummary::modelsummary(
  resultss3[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 40km

```{r}

modelsummary::modelsummary(
  resultss4[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```


#### 50km

```{r}

modelsummary::modelsummary(
  resultss5[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```


# sub sample 2

The number of establishments in cz in each year is equivalent to 5 or less than 5.

```{r}

data_cz_potential_entrant = data_cz_potential_entrantunder5

```

## first stage 

係数が小さくなるなるため、potential_entrantの数値は1000で除した値を使用。

### results {.tabset}

#### 5km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

#### 10km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

#### 20km

```{r}


results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```




#### 30km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

#### 40km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 


```

#### 50 km

```{r}

results <- list()
 
 results[[1]] <- 
   fixest::feols(
    fml = Nj_diff ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 
 result <- 
   list(
     "Nj_diff" = results[[1]]
   )
 
 modelsummary::modelsummary(
   result,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

### bonscatter plot {.tabset}

#### 5km

```{r}
  
plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant5km
  ) %>% 
  dplyr::mutate(
    id = c(1:221) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant5km_avr = mean(potential_entrant5km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant5km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant5km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 10km

```{r}
  
plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant10km
  ) %>% 
  dplyr::mutate(
    id = c(1:221) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant10km_avr = mean(potential_entrant10km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant10km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant10km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 20km

```{r}
  
 plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant20km
  ) %>% 
  dplyr::mutate(
    id = c(1:221) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant20km_avr = mean(potential_entrant20km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant20km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant20km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 30km

```{r}
  
 plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant30km
  ) %>% 
  dplyr::mutate(
    id = c(1:221) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant30km_avr = mean(potential_entrant30km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant30km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant30km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 40km

```{r}
  
  plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant40km
  ) %>% 
  dplyr::mutate(
    id = c(1:221) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant40km_avr = mean(potential_entrant40km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant40km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant40km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

#### 50km

```{r}
  
  plot_firststage =
  data_cz_potential_entrant %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(
    potential_entrant50km
  ) %>% 
  dplyr::mutate(
    id = c(1:221) 
    )%>% 
  dplyr::mutate(
    cut_bin = cut(id, breaks = 100, labels = FALSE)
  ) %>% 
  dplyr::group_by(
    cut_bin
  ) %>% 
  dplyr::mutate(
    Nj_diff_avr = mean(Nj_diff),
    potential_entrant50km_avr = mean(potential_entrant50km)
  ) %>% 
  dplyr::select(
    Nj_diff_avr,
    potential_entrant50km_avr
  ) %>% 
  dplyr::distinct()

g <- ggplot() +
   geom_point(
     data = plot_firststage,
     mapping = aes(y = Nj_diff_avr, x = potential_entrant50km_avr),
     size = 0.5
   ) +
  theme_classic()
 
 print(g)

```

## reduced form {.tabset}

### 5km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
   
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant5km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 10km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
   
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant10km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 20km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant20km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 30km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant30km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 40km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant40km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

### 50km

```{r}

resultr <- list()
 
 resultr[[1]] <- 
   fixest::feols(
    fml = log_wage_diff ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
 resultr[[2]] <- 
   fixest::feols(
    fml = log_fee_diff ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )
 
resultr[[3]] <- 
   fixest::feols(
    fml = margin ~ potential_entrant50km | year + cz ,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

 result_r <- 
   list(
     "log_wage_diff" = resultr[[1]],
     "log_fee_diff" = resultr[[2]],
     "log_diff_fee - log_diff_wage" = resultr[[3]]
   )
 
 modelsummary::modelsummary(
   result_r,
   stars = c("*" = .1, "**" = .05, "***" = .01),
   statistic = 'std.error',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 



```

## structural form {.tabset}

### 2nd stage {.tabset}

#### 5km

```{r}

resultss00 <- list()

resultss00[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant5km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss00[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant5km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss00[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant5km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s00 <- 
  list(
    "log_diff_wage" = resultss00[[1]],
    "log_diff_fee" = resultss00[[2]],
    "log_diff_fee - log_diff_wage" = resultss00[[3]]
  )

modelsummary::modelsummary(
  results_s00,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 10km

```{r}

resultss <- list()

resultss[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant10km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant10km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant10km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 20km

```{r}

resultss2 <- list()

resultss2[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant20km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss2[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant20km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss2[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant20km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s2 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s2,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 30km

```{r}

resultss3 <- list()

resultss3[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant30km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss3[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant30km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss3[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant30km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s3 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s3,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 40km

```{r}

resultss4 <- list()

resultss4[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant40km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss4[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant40km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss4[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant40km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s4 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s4,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

#### 50km

```{r}

resultss5 <- list()

resultss5[[1]] <- 
  fixest::feols(
    fml = log_wage_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant50km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss5[[2]] <- 
  fixest::feols(
    fml = log_fee_diff ~ 1 | year + cz | Nj_diff ~ potential_entrant50km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

resultss5[[3]] <- 
  fixest::feols(
    fml = margin ~ 1 | year + cz | Nj_diff ~ potential_entrant50km,
    data = data_cz_potential_entrant,
    se = "hetero"
  )

results_s5 <- 
  list(
    "log_diff_wage" = resultss[[1]],
    "log_diff_fee" = resultss[[2]],
    "log_diff_fee - log_diff_wage" = resultss[[3]]
  )

modelsummary::modelsummary(
  results_s5,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 1st stage {.tabset}

#### 5km

```{r}

modelsummary::modelsummary(
  resultss00[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 10km

```{r}

modelsummary::modelsummary(
  resultss[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 20km

```{r}

modelsummary::modelsummary(
  resultss2[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 30km

```{r}

modelsummary::modelsummary(
  resultss3[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```

#### 40km

```{r}

modelsummary::modelsummary(
  resultss4[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```


#### 50km

```{r}

modelsummary::modelsummary(
  resultss5[[1]]$iv_first_stage,
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = 'std.error',
  conf_level = .95
)

```




