---
title: "report data analysis (first order difference)"
author: "Chiho Taniguchi"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 3, fig.width = 4)

library("magrittr")
library("kableExtra")
library("ggplot2")

height <- 6
width <- 8

```

```{r }

 data_establishments <- 
  here::here(file = "cleaned/data_establishments.rds") %>% 
  readRDS()

 data_zipcode <- 
   here::here(file = "cleaned/data_zipcode.rds") %>% 
   readRDS()
 
 data_area <- 
   here::here(file = "cleaned/data_area.rds") %>% 
   readRDS()
 
 data_zip_establishments <- 
   here::here(file = "output/data_zip_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments <- 
   here::here(file = "output/data_cz_establishments.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann <- 
   here::here(file = "output/data_cz_establishments_all_ippann.rds") %>% 
   readRDS()
 
 data_zip_establishments_all_ippann <- 
   here::here(file = "output/data_zip_establishments_all_ippann.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann_unique <- 
   here::here(file = "output/data_cz_establishments_all_ippann_unique.rds") %>% 
   readRDS()
 
 data_zip_establishments_all_ippann_unique <- 
   here::here(file = "output/data_zip_establishments_all_ippann_unique.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann_unique_wage <- 
   here::here(file = "output/data_cz_establishments_all_ippann_unique_wage.rds") %>% 
   readRDS()
 
 data_zip_establishments_all_ippann_unique_wage <- 
   here::here(file = "output/data_zip_establishments_all_ippann_unique_wage.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann_unique_fee <- 
   here::here(file = "output/data_cz_establishments_all_ippann_unique_fee.rds") %>%
   readRDS()
 
 data_zip_establishments_all_ippann_unique_fee <- 
   here::here(file = "output/data_zip_establishments_all_ippann_unique_fee.rds") %>% 
   readRDS()
 
 data_cz_establishments_all_ippann_unique_weights <- 
   here::here(file = "output/data_cz_establishments_all_ippann_unique_weights.rds") %>%
   readRDS()
 
 data_zip_establishments_all_ippann_unique_weights <- 
   here::here(file = "output/data_zip_establishments_all_ippann_unique_weights.rds") %>% 
   readRDS()
 

```

# cz data

## First stage (cz)
Regress the difference between 2014 and 2010 in the number of general establishments (log_diff_10_14) on the percentage of tokutei establishments at the initial period(share_cz_2010). "log_diff_10_14" is the natural logarithm of the number of general establishments in 2014 minus the natural logarithm of the number of general establishments in 2010.

### log_diff_10_14

log_diff_10_14 =  (ln(Nj_2014) - ln(Nj_2010))

```{r}

results_diff_cz <- list()

summary(data_cz_establishments_all_ippann_unique$log_diff_10_14)


 results_diff_cz[[1]] <- 
   lm(formula = log_diff_10_14 ~  share_cz_2010 ,
      data = data_cz_establishments_all_ippann_unique
   )
 
 result_diffcz <- 
   list(
     "log_diff_10_14" = results_diff_cz[[1]]
   )
 
 modelsummary::modelsummary(
   result_diffcz,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

### diff_14_10

diff_14_10 = Nj_2014 - Nj_2010

```{r}

results_diff_cz_a <- list()

summary(data_cz_establishments_all_ippann_unique$diff_14_10)


 results_diff_cz_a[[1]] <- 
   lm(formula = diff_14_10_1000 ~  share_cz_2010 ,
      data = data_cz_establishments_all_ippann_unique
   )
 
 result_diffcza <- 
   list(
     "diff_14_10" = results_diff_cz_a[[1]]
   )
 
 modelsummary::modelsummary(
   result_diffcza,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

## First stage (weighted by the number of general establishments in 2010)

### log_diff_10_14

```{r}

results_diff_cz_w <- list()

results_diff_cz_w[[1]] <- 
  lm(formula = log_diff_10_14 ~  share_cz_2010 ,
     data = data_cz_establishments_all_ippann_unique,
     weights = weights
  )

result_diffczw <- 
  list(
    "log_diff_10_14(weighted)" = results_diff_cz_w[[1]]
  )

modelsummary::modelsummary(
  result_diffczw,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### diff_14_10

```{r}

results_diff_cz_wa <- list()

results_diff_cz_wa[[1]] <- 
  lm(formula = diff_14_10_1000 ~  share_cz_2010 ,
     data = data_cz_establishments_all_ippann_unique,
     weights = weights
  )

result_diffczwa <- 
  list(
    "diff_14_10(weighted)" = results_diff_cz_wa[[1]]
  )

modelsummary::modelsummary(
  result_diffczwa,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

## Plot for first stage

"estab." represents establishments. y represents "log(#general establishments in 2014) - log(#general establishments in 2010)".

```{r}

id_1 <- c(1:198)

data_cz_establishments_all_ippann_share <-
   data_cz_establishments_all_ippann_unique %>% 
   dplyr::select(
     cz,
     share_cz_2010,
     log_diff_10_14
   ) %>% 
   unique() %>% 
  dplyr::arrange(
    cz
  ) 

data_cz_establishments_all_ippann_share <-
  cbind(
    id_1,
    data_cz_establishments_all_ippann_share
  )
 
data_cz_establishments_all_ippann_share <-
  data_cz_establishments_all_ippann_share %>% 
  dplyr::mutate(
    cz_bin = cut(id_1, 
                 breaks = 30)
  ) %>% 
  dplyr::group_by(
    cz_bin
  ) %>% 
  dplyr::mutate(
    log_diff_10_14_avr = mean(log_diff_10_14),
    share_cz_2010_avr = mean(share_cz_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_cz_establishments_all_ippann_share_avr <- 
   data_cz_establishments_all_ippann_share %>% 
   dplyr::select(
     share_cz_2010_avr,
     log_diff_10_14_avr
   ) %>% 
   dplyr::distinct()
   

 g13 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_share,
     mapping = aes(x = share_cz_2010, y = log_diff_10_14),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("y") 
 
 print(g13)
 
 
```

## binscatter plot for first stage 

```{r}

 g23 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_share_avr,
     mapping = aes(x = share_cz_2010_avr, y = log_diff_10_14_avr),
     size = 0.3
   ) +
   stat_smooth(
   method = "lm",
   data = data_cz_establishments_all_ippann_share_avr,
   mapping = aes(x = share_cz_2010_avr, y = log_diff_10_14_avr),
    se = FALSE,
    size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("y") 
 
 print(g23)
 
 
```

## Reduced form (cz)

Regress first order difference of the natural logarithm of the average wage and the average fee(log_diffwage_14_10 / flog_difffee_14_10) on the percentage of tokutei establishments at the initial period(share_cz_2010). The natural logarithm of the average wage and average fee are calculated by creating panel data by making the average of each cz level year by year.
log_diffwage_14_10 / flog_difffee_14_10 is log(average wage / fee in 2014) - log(average wage / fee in 2010).

### wage (log_diffwage_14_10)

log_diffwage_14_10

```{r}

### wage

results_growth_cz <- list()

results_growth_cz[[1]] <- 
  lm(formula = log_diffwage_14_10 ~  share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_wage
    )

result_growthcz <- 
  list(
    "log_diffwage_14_10" = results_growth_cz[[1]]
  )

modelsummary::modelsummary(
  result_growthcz,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```
### wage (wage_growth_14_10)

wage_growth_14_10 = (wage_2014-wage_2010)/wage_2010

```{r}

### wage

results_growth_cza <- list()

results_growth_cza[[1]] <- 
  lm(formula = wage_growth_14_10 ~  share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_wage
    )

result_growthcza <- 
  list(
    "wage_growth_14_10" = results_growth_cza[[1]]
  )

modelsummary::modelsummary(
  result_growthcza,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### wage(weighted / log_diffwage_14_10)

```{r}

### wage

results_growth_cz_w <- list()

results_growth_cz_w[[1]] <- 
  lm(formula = log_diffwage_14_10 ~  share_cz_2010,
     data = data_cz_establishments_all_ippann_unique_wage,
     weights = weights
     )

result_growthczw <- 
  list(
    "log_diffwage_14_10(weighted)" = results_growth_cz_w[[1]]
  )

modelsummary::modelsummary(
  result_growthczw,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### wage(weighted / wage_growth_14_10)

```{r}

### wage

results_growth_cz_wa <- list()

results_growth_cz_wa[[1]] <- 
  lm(formula = wage_growth_14_10 ~  share_cz_2010,
     data = data_cz_establishments_all_ippann_unique_wage,
     weights = weights
     )

result_growthczwa <- 
  list(
    "wage_growth_14_10(weighted)" = results_growth_cz_wa[[1]]
  )

modelsummary::modelsummary(
  result_growthczwa,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### Plot for reduced form (wage)

```{r}

id_2 <- c(1:198)

data_cz_establishments_all_ippann_wage <-
   data_cz_establishments_all_ippann_unique_wage %>% 
   dplyr::select(
     cz,
     share_cz_2010,
     log_diffwage_14_10
   ) %>% 
   unique() %>% 
  dplyr::arrange(
    cz
  ) 
 
data_cz_establishments_all_ippann_wage <-
  data_cz_establishments_all_ippann_wage %>% 
  dplyr::mutate(
    cz_bin = cut(id_2, 
                 breaks = 20)
  ) %>% 
  dplyr::group_by(
    cz_bin
  ) %>% 
  dplyr::mutate(
    log_diffwage_14_10_avr = mean(log_diffwage_14_10),
    share_cz_2010_med = median(share_cz_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_cz_establishments_all_ippann_wage_avr <- 
   data_cz_establishments_all_ippann_wage %>% 
   dplyr::select(
     share_cz_2010_med,
     log_diffwage_14_10_avr
   ) %>% 
   dplyr::distinct()
   
 

 g14 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_wage,
     mapping = aes(x = share_cz_2010, y = log_diffwage_14_10),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average wage)") 
 
 print(g14)

```

### binscatter plot for reduced form (wage)

```{r}

 g24 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_wage_avr,
     mapping = aes(x = share_cz_2010_med, y = log_diffwage_14_10_avr),
     size = 0.5
   ) +
   stat_smooth(
     data = data_cz_establishments_all_ippann_wage_avr,
     method = "lm",
     mapping = aes(x = share_cz_2010_med, y = log_diffwage_14_10_avr),
     se = FALSE,
     size = 0.5
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average wage)")
 
 print(g24)

```

### fee (log_difffee_14_10)

```{r}

### fee

results_feegrowth_cz <- list()

results_feegrowth_cz[[1]] <- 
  lm(formula = log_difffee_14_10 ~  share_cz_2010,
     data = data_cz_establishments_all_ippann_unique_fee
     )


result_feegrowthcz <- 
  list(
    "log_difffee_14_10" = results_feegrowth_cz[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthcz,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### fee (fee_growth_14_10)

```{r}

### fee

results_feegrowth_cza <- list()

results_feegrowth_cza[[1]] <- 
  lm(formula = fee_growth_14_10 ~  share_cz_2010,
     data = data_cz_establishments_all_ippann_unique_fee
     )


result_feegrowthcza <- 
  list(
    "fee_growth_14_10" = results_feegrowth_cza[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthcza,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### fee(log_difffee_14_10 / weighted)

```{r}

### fee

results_feegrowth_cz_w <- list()

results_feegrowth_cz_w[[1]] <- 
  lm(formula = log_difffee_14_10 ~  share_cz_2010,
     data = data_cz_establishments_all_ippann_unique_fee,
     weights = weights
     )


result_feegrowthczw <- 
  list(
    "log_difffee_14_10(weighted)" = results_feegrowth_cz_w[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthczw,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### fee(fee_growth_14_10 / weighted)

```{r}

### fee

results_feegrowth_cz_wa <- list()

results_feegrowth_cz_wa[[1]] <- 
  lm(formula = fee_growth_14_10 ~  share_cz_2010,
     data = data_cz_establishments_all_ippann_unique_fee,
     weights = weights
     )


result_feegrowthczwa <- 
  list(
    "log_difffee_14_10(weighted)" = results_feegrowth_cz_wa[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthczwa,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```


### Plot for reduced form (fee)

```{r}

id_3 <- c(1:220)

data_cz_establishments_all_ippann_fee <-
   data_cz_establishments_all_ippann %>% 
   dplyr::select(
     cz,
     share_cz_2010,
     log_difffee_14_10
   ) %>% 
   unique() %>% 
  dplyr::arrange(
    cz
  ) 
 
data_cz_establishments_all_ippann_fee <-
  data_cz_establishments_all_ippann_fee %>% 
  dplyr::mutate(
    cz_bin = cut(id_3, 
                 breaks = 20)
  ) %>% 
  dplyr::group_by(
    cz_bin
  ) %>% 
  dplyr::mutate(
    log_difffee_14_10_avr = mean(log_difffee_14_10),
    share_cz_2010_med = median(share_cz_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_cz_establishments_all_ippann_fee_avr <- 
   data_cz_establishments_all_ippann_fee %>% 
   dplyr::select(
     share_cz_2010_med,
     log_difffee_14_10_avr
   ) %>% 
   dplyr::distinct()
   
 

 g15 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_fee,
     mapping = aes(x = share_cz_2010, y = log_difffee_14_10),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average fee)")
 
 print(g15)


```

### binscatter plot for reduced form (fee)

```{r}

 g25 <- ggplot() +
   geom_point(
     data = data_cz_establishments_all_ippann_fee_avr,
     mapping = aes(x = share_cz_2010_med, y = log_difffee_14_10_avr),
     size = 0.5
   ) +
   stat_smooth(
     method = "lm",
     data = data_cz_establishments_all_ippann_fee_avr,
     mapping = aes(x = share_cz_2010_med, y = log_difffee_14_10_avr),
     se = FALSE,
     size = 0.5
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average fee)")
 
 print(g25)


```

## Structural form (cz)

Regress the difference between the natural logarithm of average wages and average rates on the difference between 2014 and 2010 in the number of general establishments (log_diffwage/fee_14_10). We use the ratio of tokutei establishments at the initial periods as the instrument variable for the difference between the natural logarithm of average wages and average rates on the difference between 2014 and 2010 in the number of general establishments (log_diff_10_14).

### 2nd stage (wage / log_diffwage_14_10)

```{r}

results_s_wage_cz <- list()

results_s_wage_cz[[1]] <- 
  lfe::felm(
    formula = log_diffwage_14_10 ~ 1 | 0 | (log_diff_10_14 ~ share_cz_2010) | 0,
    data = data_cz_establishments_all_ippann_unique_wage
  )

result_swagegrowthcz <- 
  list(
    "log_diffwage_14_10" = results_s_wage_cz[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthcz,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (wage / wage_growth_14_10)

```{r}

results_s_wage_cz_a <- list()

results_s_wage_cz_a[[1]] <- 
  lfe::felm(
    formula = wage_growth_14_10 ~ 1 | 0 | (diff_14_10_1000 ~ share_cz_2010) | 0,
    data = data_cz_establishments_all_ippann_unique_wage
  )

result_swagegrowthcza <- 
  list(
    "log_diffwage_14_10" = results_s_wage_cz_a[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthcza,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (wage / log_diffwage_14_10 / weighted)

```{r}

results_s_wage_cz_2nd <- list()

results_s_wage_cz_2nd[[1]] <- 
  fixest::feols(
    fml = log_diffwage_14_10 ~ 1 | log_diff_10_14 ~ share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_wage,
    weights = ~ weights
  )


result_swagegrowthcz2nd <- 
  list(
    "log_diffwage_14_10(weighted)" = results_s_wage_cz_2nd[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthcz2nd,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```
### 2nd stage (wage / wage_growth_14_10 / weighted)

```{r}

results_s_wage_cz_2nd_a <- list()

results_s_wage_cz_2nd_a[[1]] <- 
  fixest::feols(
    fml = wage_growth_14_10 ~ 1 | diff_14_10_1000 ~ share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_wage,
    weights = ~ weights
  )


result_swagegrowthcz2nda <- 
  list(
    "wage_growth_14_10(weighted)" = results_s_wage_cz_2nd_a[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthcz2nda,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 1st stage (wage / log_diff_10_14)

```{r}


resultsb3 <- 
  list(
    "log_diff_10_14(1st stage)" = results_s_wage_cz[[1]]$stage1
  )

modelsummary::modelsummary(
  resultsb3,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)

```

### 1st stage (wage / wage_growth_14_10)

```{r}


resultsbb3 <- 
  list(
    "wage_growth_14_10(1st stage)" = results_s_wage_cz_a[[1]]$stage1
  )

modelsummary::modelsummary(
  resultsbb3,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)

```

### 1st stage (wage / log_diff_10_14 / weighted )

```{r}

modelsummary::modelsummary(
  results_s_wage_cz_2nd[[1]]$iv_first_stage,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)


```

### 1st stage (wage / wage_growth_14_10 / weighted)

```{r}

modelsummary::modelsummary(
  results_s_wage_cz_2nd_a[[1]]$iv_first_stage,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)


```

### 2nd stage (fee / log_difffee_14_10)

```{r}

results_s_fee_cz <- list()

results_s_fee_cz[[1]] <- 
  lfe::felm(
    formula = log_difffee_14_10 ~ 1 | 0 | (log_diff_10_14 ~ share_cz_2010) | 0 ,
    data = data_cz_establishments_all_ippann_unique_fee
  )


result_sfeegrowthcz <- 
  list(
    "log_difffee_14_10" = results_s_fee_cz[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthcz,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (fee / fee_growth_14_10)

```{r}

results_s_fee_cz_a <- list()

results_s_fee_cz_a[[1]] <- 
  lfe::felm(
    formula = fee_growth_14_10 ~ 1 | 0 | (diff_14_10_1000 ~ share_cz_2010) | 0 ,
    data = data_cz_establishments_all_ippann_unique_fee
  )


result_sfeegrowthcza <- 
  list(
    "fee_growth_14_10" = results_s_fee_cz_a[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthcza,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (fee / log_difffee_14_10 / weighted)

```{r}

results_s_fee_cz_2nd <- list()

results_s_fee_cz_2nd[[1]] <- 
  fixest::feols(
    fml = log_difffee_14_10 ~ 1 | log_diff_10_14 ~ share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_fee,
    weights = ~ weights
  )


result_sfeegrowthcz2nd <- 
  list(
    "log_difffee_14_10(weighted)" = results_s_fee_cz_2nd[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthcz2nd,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (fee / fee_growth_14_10 / weighted)

```{r}

results_s_fee_cz_2nd_a <- list()

results_s_fee_cz_2nd_a[[1]] <- 
  fixest::feols(
    fml = fee_growth_14_10 ~ 1 | diff_14_10_1000 ~ share_cz_2010,
    data = data_cz_establishments_all_ippann_unique_fee,
    weights = ~ weights
  )


result_sfeegrowthcz2nda <- 
  list(
    "fee_growth_14_10(weighted)" = results_s_fee_cz_2nd_a[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthcz2nda,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 1st stage (fee / log_difffee_14_10)

```{r}

resultsb4 <- 
  list(
    "log_difffee_14_10(1st stage)" = results_s_fee_cz[[1]]$stage1
  )

modelsummary::modelsummary(
  resultsb4,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)

```

### 1st stage (fee / fee_growth_14_10)

```{r}

resultsbb4 <- 
  list(
    "fee_growth_14_10(1st stage)" = results_s_fee_cz_a[[1]]$stage1
  )

modelsummary::modelsummary(
  resultsbb4,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)

```

### 1st stage (fee / log_difffee_14_10 / weighted )

```{r}

modelsummary::modelsummary(
  results_s_fee_cz_2nd[[1]]$iv_first_stage,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)

```

### 1st stage (fee / fee_growth_14_10 / weighted )

```{r}

modelsummary::modelsummary(
  results_s_fee_cz_2nd_a[[1]]$iv_first_stage,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)

```

# zip data

## First stage (zip)
Regress the difference between 2014 and 2010 in the number of general establishments (log_diff_10_14) on the percentage of tokutei establishments at the initial period(share_cz_2010). "log_diff_10_14" is the natural logarithm of the number of general establishments in 2014 minus the natural logarithm of the number of general establishments in 2010.

### log_diff_10_14

taking log difference (ln(X_2014) - ln(X_2010))


```{r}
results_diff_zip <- list()

results_diff_zip[[1]] <- 
  lm(formula = log_diff_10_14 ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique
  )

result_diffzip <- 
  list(
    "log_diff_10_14" = results_diff_zip[[1]]
  )

modelsummary::modelsummary(
  result_diffzip,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### diff_14_10

```{r}

results_diff_zip_a <- list()

summary(data_zip_establishments_all_ippann_unique$diff_14_10)


 results_diff_zip_a[[1]] <- 
   lm(formula = diff_14_10 ~  share_zip_2010 ,
      data = data_zip_establishments_all_ippann_unique
   )
 
 result_diffzipa <- 
   list(
     "diff_14_10" = results_diff_zip_a[[1]]
   )
 
 modelsummary::modelsummary(
   result_diffzipa,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

## First stage (weighted by the number of general establishments in 2010)

### log_diff_10_14

```{r}

results_diff_zip_w <- list()
 
 
 results_diff_zip_w[[1]] <- 
   lm(formula = log_diff_10_14 ~  share_zip_2010 ,
     data = data_zip_establishments_all_ippann_unique,
     weights = weights
   )
 
 result_diffzipw <- 
   list(
     "log_diff_10_14" = results_diff_zip_w[[1]]
   )
 
 modelsummary::modelsummary(
   result_diffzipw,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

### diff_14_10

```{r}

results_diff_zip_w_a <- list()
 
 
 results_diff_zip_w_a[[1]] <- 
   lm(formula = diff_14_10 ~  share_zip_2010 ,
     data = data_zip_establishments_all_ippann_unique,
     weights = weights
   )
 
 result_diffzipwa <- 
   list(
     "diff_14_10" = results_diff_zip_w_a[[1]]
   )
 
 modelsummary::modelsummary(
   result_diffzipwa,
   stars = TRUE,
   statistic = 'conf.int',
   conf_level = .95 ,
   gof_omit = "AIC|BIC"
 ) 

```

## Plot for first stage

"estab." represents establishments. y represents "log(#general establishments in 2014) - log(#general establishments in 2010)".

```{r}

id_4 <- c(1:778)

data_zip_establishments_all_ippann_share <-
   data_zip_establishments_all_ippann_unique %>% 
   dplyr::select(
     zip_three,
     share_zip_2010,
     log_diff_10_14
   ) %>% 
  dplyr::distinct() %>% 
  dplyr::arrange(
    zip_three
  ) 

data_zip_establishments_all_ippann_share <-
  cbind(
    id_4,
    data_zip_establishments_all_ippann_share
  )
 
data_zip_establishments_all_ippann_share <-
  data_zip_establishments_all_ippann_share %>% 
  dplyr::mutate(
    zip_bin = cut(id_4, 
                 breaks = 50)
  ) %>% 
  dplyr::group_by(
    zip_bin
  ) %>% 
  dplyr::mutate(
    log_diff_10_14_avr = mean(log_diff_10_14),
    share_zip_2010_med = median(share_zip_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_zip_establishments_all_ippann_share_avr <- 
   data_zip_establishments_all_ippann_share %>% 
   dplyr::select(
     share_zip_2010_med,
     log_diff_10_14_avr
   ) %>% 
   dplyr::distinct()
   

 g16 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_share,
     mapping = aes(x = share_zip_2010, y = log_diff_10_14),
     size = 0.3
     ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("y") 
 
 print(g16)
 
 
```

## binscatter plot for first stage

```{r}

 g26 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_share_avr,
     mapping = aes(x = share_zip_2010_med, y = log_diff_10_14_avr),
     size = 0.3
   ) +
   stat_smooth(
     method = "lm",
     data = data_zip_establishments_all_ippann_share_avr,
     mapping = aes(x = share_zip_2010_med, y = log_diff_10_14_avr),
     se = FALSE,
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("y") 
 
 print(g26)
 
 
```

## Reduced form (zip)

Regress first order difference of the natural logarithm of the average wage and the average fee(log_diffwage_14_10 / flog_difffee_14_10) on the percentage of tokutei establishments at the initial period(share_zip_2010). The natural logarithm of the average wage and average fee are calculated by creating panel data by making the average of each zip code level year by year.
log_diffwage_14_10 / flog_difffee_14_10 is log(average wage / fee in 2014) - log(average wage / fee in 2010).

### wage(log_diffwage_14_10)

```{r}

### wage

results_growth_zip <- list()

results_growth_zip[[1]] <- 
  lm(formula = log_diffwage_14_10 ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique_wage
     )

result_growthzip <- 
  list(
    "log_diffwage_14_10" = results_growth_zip[[1]]
  )

modelsummary::modelsummary(
  result_growthzip,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### wage(wage_growth_14_10)

```{r}

### wage

results_growth_zip_a <- list()

results_growth_zip_a[[1]] <- 
  lm(formula = wage_growth_14_10 ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique_wage
     )

result_growthzipa <- 
  list(
    "wage_growth_14_10" = results_growth_zip_a[[1]]
  )

modelsummary::modelsummary(
  result_growthzipa,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```


### wage(weighted / log_diffwage_14_10)

```{r}

### wage

results_growth_zip_w <- list()

results_growth_zip_w[[1]] <- 
  lm(formula = log_diffwage_14_10 ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique_wage,
     weights = weights
     )

result_growthzipw <- 
  list(
    "log_diffwage_14_10(weighted)" = results_growth_zip_w[[1]]
  )

modelsummary::modelsummary(
  result_growthzipw,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### wage(weighted / wage_growth_14_10)

```{r}

### wage

results_growth_zip_w_a <- list()

results_growth_zip_w_a[[1]] <- 
  lm(formula = wage_growth_14_10 ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique_wage,
     weights = weights
     )

result_growthzipwa <- 
  list(
    "wage_growth_14_10(weighted)" = results_growth_zip_w_a[[1]]
  )

modelsummary::modelsummary(
  result_growthzipwa,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### Plot for reduced form (wage)

```{r}

id_5 <- c(1:778)

data_zip_establishments_all_ippann_wage <-
   data_zip_establishments_all_ippann_unique_wage %>% 
   dplyr::select(
     zip_three,
     share_zip_2010,
     log_diffwage_14_10
   ) %>% 
   dplyr::distinct() %>% 
  dplyr::arrange(
    zip_three
  ) 
 
data_zip_establishments_all_ippann_wage <-
  data_zip_establishments_all_ippann_wage %>% 
  dplyr::mutate(
    zip_bin = cut(id_5, 
                 breaks = 50)
  ) %>% 
  dplyr::group_by(
    zip_bin
  ) %>% 
  dplyr::mutate(
    log_diffwage_14_10_avr = mean(log_diffwage_14_10),
    share_zip_2010_med = median(share_zip_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_zip_establishments_all_ippann_wage_avr <- 
   data_zip_establishments_all_ippann_wage %>% 
   dplyr::select(
     share_zip_2010_med,
     log_diffwage_14_10_avr
   ) %>% 
   dplyr::distinct()
   
 

 g17 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_wage,
     mapping = aes(x = share_zip_2010, y = log_diffwage_14_10),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average wage)")
 
 print(g17)
 
```

### binscatter plot for reduced form (wage)

```{r}

 g27 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_wage_avr,
     mapping = aes(x = share_zip_2010_med, y = log_diffwage_14_10_avr),
     size = 0.5
   ) +
   stat_smooth(
     data = data_zip_establishments_all_ippann_wage_avr,
     method = "lm",
     mapping = aes(x = share_zip_2010_med, y = log_diffwage_14_10_avr),
     se = FALSE,
     size = 0.5
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average wage)")
 
 print(g27)
 
```

### fee(log_difffee_14_10)

```{r}

### fee

results_feegrowth_zip <- list()

results_feegrowth_zip[[1]] <- 
  lm(formula = log_difffee_14_10 ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique_fee
     )

result_feegrowthzip <- 
  list(
    "log_difffee_14_10" = results_feegrowth_zip[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthzip,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### fee(fee_growth_14_10)

```{r}

### fee

results_feegrowth_zip_a <- list()

results_feegrowth_zip_a[[1]] <- 
  lm(formula = fee_growth_14_10 ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique_fee
     )

result_feegrowthzipa <- 
  list(
    "fee_growth_14_10" = results_feegrowth_zip_a[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthzipa,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### fee(log_difffee_14_10 / weighted )

```{r}

### fee

results_feegrowth_zip_w <- list()

results_feegrowth_zip_w[[1]] <- 
  lm(formula = log_difffee_14_10 ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique_fee,
     weights = weights
     )

result_feegrowthzipw <- 
  list(
    "log_difffee_14_10(weighted)" = results_feegrowth_zip_w[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthzipw,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### fee(fee_growth_14_10/ weighted )

```{r}

### fee

results_feegrowth_zip_w_a <- list()

results_feegrowth_zip_w_a[[1]] <- 
  lm(formula = fee_growth_14_10 ~  share_zip_2010,
     data = data_zip_establishments_all_ippann_unique_fee,
     weights = weights
     )

result_feegrowthzipawa <- 
  list(
    "fee_growth_14_10(weighted)" = results_feegrowth_zip_w_a[[1]]
  )

modelsummary::modelsummary(
  result_feegrowthzipawa,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### Plot for reduced form (fee)

```{r}

id_6 <- c(1:778)

data_zip_establishments_all_ippann_fee <-
   data_zip_establishments_all_ippann_unique_fee %>% 
   dplyr::select(
     zip_three,
     share_zip_2010,
     log_difffee_14_10
   ) %>% 
   dplyr::distinct() %>% 
  dplyr::arrange(
    zip_three
  ) 
 
data_zip_establishments_all_ippann_fee <-
  data_zip_establishments_all_ippann_fee %>% 
  dplyr::mutate(
    zip_bin = cut(id_6, 
                 breaks = 50)
  ) %>% 
  dplyr::group_by(
    zip_bin
  ) %>% 
  dplyr::mutate(
    log_difffee_14_10_avr = mean(log_difffee_14_10),
    share_zip_2010_med = median(share_zip_2010)
  ) %>% 
  dplyr::ungroup()
 
 data_zip_establishments_all_ippann_fee_avr <- 
   data_zip_establishments_all_ippann_fee %>% 
   dplyr::select(
     share_zip_2010_med,
     log_difffee_14_10_avr
   ) %>% 
   dplyr::distinct()
   

 g18 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_fee,
     mapping = aes(x = share_zip_2010, y = log_difffee_14_10),
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average fee)")
 
 print(g18)
 
```

### binscatter plot for reduced form (fee)

```{r}

 g28 <- ggplot() +
   geom_point(
     data = data_zip_establishments_all_ippann_fee_avr,
     mapping = aes(x = share_zip_2010_med, y = log_difffee_14_10_avr),
     size = 0.3
   ) +
   stat_smooth(
     data = data_zip_establishments_all_ippann_fee_avr,
     method = "lm",
     mapping = aes(x = share_zip_2010_med, y = log_difffee_14_10_avr),
     se = FALSE,
     size = 0.3
   ) +
   xlab("Ratio of # tokutei estab. to # total estab. in 2010") +
   ylab("Difference of log(the average fee)")
 
 print(g28)
 
```

## Structural form (zip)

Regress the difference between the natural logarithm of average wages and average rates on the difference between 2014 and 2010 in the number of general establishments (log_diffwage/fee_14_10). We use the ratio of tokutei establishments at the initial periods as the instrument variable for the difference between the natural logarithm of average wages and average rates on the difference between 2014 and 2010 in the number of general establishments (log_diff_10_14).

### 2nd stage (wage / log_diffwage_14_10)

```{r}
results_s_wage_zip <- list()

results_s_wage_zip[[1]] <- 
  lfe::felm(
    formula = log_diffwage_14_10 ~  1 | 0 | (log_diff_10_14 ~ share_zip_2010) | 0 ,
    data = data_zip_establishments_all_ippann_unique_wage
  )


result_swagegrowthzip <- 
  list(
    "log_diffwage_14_10" = results_s_wage_zip[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthzip,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 2nd stage (wage / wage_growth_14_10)

```{r}
results_s_wage_zip_a <- list()

results_s_wage_zip_a[[1]] <- 
  lfe::felm(
    formula = wage_growth_14_10 ~  1 | 0 | (diff_14_10 ~ share_zip_2010) | 0 ,
    data = data_zip_establishments_all_ippann_unique_wage
  )


result_swagegrowthzipa <- 
  list(
    "wage_growth_14_10" = results_s_wage_zip_a[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthzipa,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 
```

### 2nd stage (wage / log_diffwage_14_10 / weighted)

```{r}

results_s_wage_zip_2nd <- list()

results_s_wage_zip_2nd[[1]] <- 
  fixest::feols(
    fml = log_diffwage_14_10 ~ 1 | log_diff_10_14 ~ share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_wage,
    weights = ~ weights
  )

result_swagegrowthzip2nd <- 
  list(
    "log_diffwage_14_10(weighted)" = results_s_wage_zip_2nd[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthzip2nd,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (wage / wage_growth_14_10 / weighted)

```{r}

results_s_wage_zip_2nd_a <- list()

results_s_wage_zip_2nd_a[[1]] <- 
  fixest::feols(
    fml = wage_growth_14_10 ~ 1 | diff_14_10 ~ share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_wage,
    weights = ~ weights
  )

result_swagegrowthzip2nda <- 
  list(
    "wage_growth_14_10(weighted)" = results_s_wage_zip_2nd_a[[1]]
  )

modelsummary::modelsummary(
  result_swagegrowthzip2nda,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 1st stage (wage / log_diffwage_14_10)

```{r}

resultsb5 <- 
  list(
    "log_diff_10_14(1st stage)" = results_s_wage_zip[[1]]$stage1
  )

modelsummary::modelsummary(
  resultsb5,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)

```

### 1st stage (wage / wage_growth_14_10 )

```{r}

resultsbb5 <- 
  list(
    "wage_growth_14_10(1st stage)" = results_s_wage_zip_a[[1]]$stage1
  )

modelsummary::modelsummary(
  resultsbb5,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)


```
### 1st stage (wage / log_diff_10_14 / weighted )

```{r}

modelsummary::modelsummary(
  results_s_wage_zip_2nd[[1]]$iv_first_stage,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)


```

### 1st stage (wage / results_s_wage_zip_2nd_a[[1]] / weighted )

```{r}

modelsummary::modelsummary(
  results_s_wage_zip_2nd_a[[1]]$iv_first_stage,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)


```

### 2nd stage (fee / log_difffee_14_10)

```{r}

results_s_fee_zip <- list()

results_s_fee_zip[[1]] <- 
  lfe::felm(
    formula = log_difffee_14_10 ~ 1 | 0 | (log_diff_10_14 ~ share_zip_2010) | 0 ,
    data = data_zip_establishments_all_ippann_unique_fee
  )


result_sfeegrowthzip <- 
  list(
    "log_difffee_14_10" = results_s_fee_zip[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthzip,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (fee / fee_growth_14_10)

```{r}

results_s_fee_zip_a <- list()

results_s_fee_zip_a[[1]] <- 
  lfe::felm(
    formula = fee_growth_14_10 ~ 1 | 0 | (diff_14_10 ~ share_zip_2010) | 0 ,
    data = data_zip_establishments_all_ippann_unique_fee
  )


result_sfeegrowthzipa <- 
  list(
    "fee_growth_14_10" = results_s_fee_zip_a[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthzipa,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (fee / log_difffee_14_10 / weighted)

```{r}

results_s_fee_zip_2nd <- list()

results_s_fee_zip_2nd[[1]] <- 
  fixest::feols(
    fml = log_difffee_14_10 ~ 1 | log_diff_10_14 ~ share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_fee,
    weights = ~ weights
  )

result_sfeegrowthzip2nd <- 
  list(
    "log_difffee_14_10" = results_s_fee_zip_2nd[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthzip2nd,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 2nd stage (fee / fee_growth_14_10 / weighted)

```{r}

results_s_fee_zip_2nd_a <- list()

results_s_fee_zip_2nd_a[[1]] <- 
  fixest::feols(
    fml = fee_growth_14_10 ~ 1 | diff_14_10 ~ share_zip_2010,
    data = data_zip_establishments_all_ippann_unique_fee,
    weights = ~ weights
  )

result_sfeegrowthzip2nda <- 
  list(
    "log_difffee_14_10" = results_s_fee_zip_2nd_a[[1]]
  )

modelsummary::modelsummary(
  result_sfeegrowthzip2nda,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95 ,
  gof_omit = "AIC|BIC"
) 

```

### 1st stage (fee / log_diff_10_14)

```{r}

resultsb6 <- 
  list(
    "log_diff_10_14(1st stage)" = results_s_fee_zip[[1]]$stage1
  )

modelsummary::modelsummary(
  resultsb6,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)

```

### 1st stage (fee / fee_growth_14_10)

```{r}

resultsbb6 <- 
  list(
    "fee_growth_14_10(1st stage)" = results_s_fee_zip_a[[1]]$stage1
  )

modelsummary::modelsummary(
  resultsbb6,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)

```

### 1st stage (fee / log_difffee_14_10 / weighted)

```{r}

modelsummary::modelsummary(
  results_s_fee_zip_2nd[[1]]$iv_first_stage,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)


```

### 1st stage (fee / fee_growth_14_10 / weighted)

```{r}

modelsummary::modelsummary(
  results_s_fee_zip_2nd_a[[1]]$iv_first_stage,
  stars = TRUE,
  statistic = 'conf.int',
  conf_level = .95
)


```

