---
title: "Testing Simulation: Monopoly"
output: html_document
date: "2022-11-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = "hide"
  )
rm(list = ls())
library(Dispatching)
library(foreach)
library(magrittr)
library(codetools)
library(ggplot2)
library(kableExtra)
```

# Set constant

```{r}
seed <- 1
set.seed(seed)
n_ths <- 2
n_market <- 1
n_zone <- 1
t <- 1
j <- 1
multistart <- 20
solver <- "nleqslv"
use_rcpp <- TRUE
```


# Generate the baseline equilibrium

```{r}
equilibrium <-
  generate_equilibrium(
    n_ths = n_ths,
    n_market = n_market,
    n_zone = n_zone,
    seed = seed
  )
```

# Comparative statics {.tabset}

## Setting

```{r, results = "asis"}
equilibrium
```

## Check the foc at the baseline

```{r, results = "asis"}
baseline <- 
  evaluate_equilibrium_tj(
    x = equilibrium$parameter$m_w,
    target = "m_w",
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
baseline %>%
  kbl() %>%
  kable_styling()
```

## Parameter {.tabset}

### m_w (Matching coefficient of worker) {.tabset}

```{r}
target <- "m_w"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```


```{r, results='hide'}

df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )
    
df_old <- 
  df[
  index,
  1:ncol(df)
  ]

```

### beta_w (Worker's utility) {.tabset}

```{r}
target <- "beta_w"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### beta_f (Client firm's utility) {.tabset}

```{r}
target <- "beta_f"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### gamma_w (Cost for handling workers) {.tabset}

```{r}
target <- "gamma_w"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### gamma_f (Cost for handling client firms) {.tabset}

```{r}
target <- "gamma_f"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results = "asis"}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### lambda_w (Wage coefficient) {.tabset}

```{r}
target <- "lambda_w"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### lambda_f (fee coefficient) {.tabset}

```{r}
target <- "lambda_f"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### mu (Matching efficiency of THS) {.tabset}

```{r}
target <- "mu"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### size_w (number of workers) {.tabset}

```{r}
target <- "size_w"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### size_f (number of firms) {.tabset}

```{r}
target <- "size_f"
comparative <- 
  evaluate_comparative_tj(
    target = target,
    t = t,
    j = j,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart,
    use_rcpp = use_rcpp
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

## Summary table{.tabset}

```{r, results ='asis'}
df_old %>%
  kbl() %>%
  kable_styling()
```