---
title: "Data Codebook"
author: "Katsuhiro Komatsu"
date: "`r Sys.Date()`"
output: 
  html_document:
    # toc: true
    # toc_float: true
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 6, fig.width = 12)
```

```{r}
library(magrittr)
library(psych)
```

# Read data

```{r}
data_establishments <- readRDS(here::here("cleaned/data_establishments.RDS"))
data_area_year_num_firms <- readRDS(here::here("cleaned/data_area_year_num_firms.RDS"))
data_area_year_num_establishments <- readRDS(here::here("cleaned/data_area_year_num_establishments.RDS"))
data_area_year_num_labor <- readRDS(here::here("cleaned/data_area_year_num_labor.RDS"))
data_area_year_num_emp <- readRDS(here::here("cleaned/data_area_year_num_emp.RDS"))
data_area_year_num_parttemp <- readRDS(here::here("cleaned/data_area_year_num_parttemp.RDS"))
data_area_year_partwage <- readRDS(here::here("cleaned/data_area_year_partwage.RDS"))
data_pref_year_partwage <- readRDS(here::here("cleaned/data_pref_year_partwage.RDS"))
data_pref_year_minimum_wage <- readRDS(here::here("cleaned/data_pref_year_minimum_wage.RDS"))
data_area <- readRDS(here::here("cleaned/data_area.RDS"))
data_zipcode <- readRDS(here::here("cleaned/data_zipcode.RDS"))
data_year <- readRDS(here::here("cleaned/data_year.RDS"))
data_area_adjacent_municipalities <- readRDS(here::here("cleaned/data_area_adjacent_municipalities.RDS"))
data_area_area_distance <- readRDS(here::here("cleaned/data_area_area_distance.RDS"))
```

# Describe data {.tabset}

## Establishment

- File name: `cleaned/data_establishments.RDS`
- Key: `id_unique`
- The data is at the zipcode, year, and establishment level. However, the establishment id is not assigned because this is not a panel. Within zipcode and year, a row represents an establishment.
- The `id_unique` is assigned to each row.

```{r}
ds <-
  data_establishments %>% 
  dplyr::mutate(
    id_unique = as.character(id_unique),
    firm_id = as.character(firm_id)
  ) %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- c("Unique ID for each observation",
         "Firm ID",
         "Year",
         "Tokutei (=1) or Ippan (=0)",
         "Zipcode",
         "Prefecture code",
         "Number of permanent workers",
         "Number of non-permanent workers",
         "Number of daily workers (full-time equivalent)",
         "Number of permanent temp workers (full-time equivalent)",
         "Number of non-permanent temp workers (full-time equivalent)",
         "Number of registered people who worked at least one in the previous year",
         "Number of daily workers",
         "Number of permanent temp workers",
         "Number of non-pearmanent temp workers",
         "Number of client firms",
         "Fee (10K Yen/ 8H)",
         "Fee (10K Yen/ 8H) for daily workers",
         "Fee (10K Yen/ 8H) for workers with skills in ソフトウェア開発",
         "Fee (10K Yen/ 8H) for workers with skills in 機械設計",
         "Fee (10K Yen/ 8H) for workers with skills in 放送機器等操作",
         "Fee (10K Yen/ 8H) for workers with skills in 放送番組等演出",
         "Fee (10K Yen/ 8H) for workers with skills in 事務用機器操作",
         "Fee (10K Yen/ 8H) for workers with skills in 通訳、翻訳、速記",
         "Fee (10K Yen/ 8H) for workers with skills in 秘書",
         "Fee (10K Yen/ 8H) for workers with skills in ファイリング",
         "Fee (10K Yen/ 8H) for workers with skills in 調査",
         "Fee (10K Yen/ 8H) for workers with skills in 財務処理",
         "Fee (10K Yen/ 8H) for workers with skills in 取引文書作成",
         "Fee (10K Yen/ 8H) for workers with skills in デモンストレーション",
         "Fee (10K Yen/ 8H) for workers with skills in 添乗",
         "Fee (10K Yen/ 8H) for workers with skills in 建築物清掃",
         "Fee (10K Yen/ 8H) for workers with skills in 建築設備運転、点検、整備",
         "Fee (10K Yen/ 8H) for workers with skills in 案内・受付、駐車場管理等",
         "Fee (10K Yen/ 8H) for workers with skills in 研究開発",
         "Fee (10K Yen/ 8H) for workers with skills in 事業の実施体制の企画、立案",
         "Fee (10K Yen/ 8H) for workers with skills in 書籍等の制作・編集",
         "Fee (10K Yen/ 8H) for workers with skills in 広告・デザイン",
         "Fee (10K Yen/ 8H) for workers with skills in インテリアコーディネーター",
         "Fee (10K Yen/ 8H) for workers with skills in アナウンサー",
         "Fee (10K Yen/ 8H) for workers with skills in OAインストラクション",
         "Fee (10K Yen/ 8H) for workers with skills in テレマーケティングの営業",
         "Fee (10K Yen/ 8H) for workers with skills in セールスエンジニアの営業、金融商品の営業",
         "Fee (10K Yen/ 8H) for workers with skills in 放送番組等における大道具・小道具",
         "Wage (10K Yen/ 8H)",
         "Wage (10K Yen/ 8H) for daily workers",
         "Wage (10K Yen/ 8H) for workers with skills in ソフトウェア開発",
         "Wage (10K Yen/ 8H) for workers with skills in 機械設計",
         "Wage (10K Yen/ 8H) for workers with skills in 放送機器等操作",
         "Wage (10K Yen/ 8H) for workers with skills in 放送番組等演出",
         "Wage (10K Yen/ 8H) for workers with skills in 事務用機器操作",
         "Wage (10K Yen/ 8H) for workers with skills in 通訳、翻訳、速記",
         "Wage (10K Yen/ 8H) for workers with skills in 秘書",
         "Wage (10K Yen/ 8H) for workers with skills in ファイリング",
         "Wage (10K Yen/ 8H) for workers with skills in 調査",
         "Wage (10K Yen/ 8H) for workers with skills in 財務処理",
         "Wage (10K Yen/ 8H) for workers with skills in 取引文書作成",
         "Wage (10K Yen/ 8H) for workers with skills in デモンストレーション",
         "Wage (10K Yen/ 8H) for workers with skills in 添乗",
         "Wage (10K Yen/ 8H) for workers with skills in 建築物清掃",
         "Wage (10K Yen/ 8H) for workers with skills in 建築設備運転、点検、整備",
         "Wage (10K Yen/ 8H) for workers with skills in 案内・受付、駐車場管理等",
         "Wage (10K Yen/ 8H) for workers with skills in 研究開発",
         "Wage (10K Yen/ 8H) for workers with skills in 事業の実施体制の企画、立案",
         "Wage (10K Yen/ 8H) for workers with skills in 書籍等の制作・編集",
         "Wage (10K Yen/ 8H) for workers with skills in 広告・デザイン",
         "Wage (10K Yen/ 8H) for workers with skills in インテリアコーディネーター",
         "Wage (10K Yen/ 8H) for workers with skills in アナウンサー",
         "Wage (10K Yen/ 8H) for workers with skills in OAインストラクション",
         "Wage (10K Yen/ 8H) for workers with skills in テレマーケティングの営業",
         "Wage (10K Yen/ 8H) for workers with skills in セールスエンジニアの営業、金融商品の営業",
         "Wage (10K Yen/ 8H) for workers with skills in 放送番組等における大道具・小道具",
         "Sales (10K Yen / Year)",
         "Indicator for dispatching workers oversea",
         "Number of workers dispatched to oversea",
         "Indicator for providing temp-to-perm hiring offer",
         "Number of applications to temp-to-perm offer",
         "Number of actual temp-to-perm offers",
         "Number of ?",
         "Number of temp-to-perm offer cases leading to direct employment",
         "Number of contracts: not longer than 1 day",
         "Number of contracts: longer than 1 day and not longer than 7 days",
         "Number of contracts: longer than 7 days and not longer than 1 month",
         "Number of contracts: longer than 1 month and not longer than 2 months",
         "Number of contracts: longer than 2 months and not longer than 3 months",
         "Number of contracts: longer than 3 months and not longer than 6 months",
         "Number of contracts: longer than 6 months and not longer than 1 year",
         "Number of contracts: longer than 1 year and not longer than 3 year",
         "Number of contracts: others",
         "Number of contracts: total",
         "type of training",
         "Number of trained workers",
         "Indicator for on-the-job training",
         "Indicator for off-the-job training",
         "Indicator for whether workers are paid for training",
         "Indicator for whether workers are not paid for training",
         "Indicator for whether the establishment provided training by itself",
         "Indicator for whether the establishment turned to a training center for training its workers",
         "Indicator for whether the establishment turned to other institutions for training its workers",
         "Number of days for training",
         "Number of months for training",
         "Number of hours for training",
         "Indicator for whether workers co-paid for training",
         "Indicator for whether workers did not co-pay for training",
         "note",
         "Indicator for whether the establishment offers employment placement services")

knitr::kable(ds)
```



## Area-year

- File name: `cleaned/data_area_year_num_firms.RDS`
- Key: `area_code`, `year`

```{r}
data_area_year_num_firms <- 
  data_area_year_num_firms %>% 
  dplyr::select(
    area_code, 
    year, 
    dplyr::everything()
    )

ds <- 
  data_area_year_num_firms %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- c("Municipality code",
                   "Year", 
                   "Number of firms",
                   "Number of firms (鉱業，採石業，砂利採取業)",
                   "Number of firms (建設業)",
                   "Number of firms (製造業)",
                   "Number of firms (電気・ガス・熱供給・水道業)",
                   "Number of firms (情報通信業)",
                   "Number of firms (運輸業，郵便業)",
                   "Number of firms (卸売業，小売業)",
                   "Number of firms (金融業，保険業)",
                   "Number of firms (不動産業，物品賃貸業)",
                   "Number of firms (学術研究，専門・技術サービス業)",
                   "Number of firms (宿泊業，飲食サービス業)",
                   "Number of firms (生活関連サービス業，娯楽業)",
                   "Number of firms (教育，学習支援業)",
                   "Number of firms (医療，福祉)",
                   "Number of firms (複合サービス事業)",
                   "Number of firms (サービス業 他に分類されないもの)",
                   "Number of firms (農林漁業)")

knitr::kable(ds)
```


- File name: `cleaned/data_area_year_num_establishments.RDS`
- Key: `area_code`, `year`

```{r}
data_area_year_num_establishments <- 
  data_area_year_num_establishments %>% 
  dplyr::select(
    area_code, 
    year, 
    dplyr::everything()
    )

ds <- 
  data_area_year_num_establishments %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- c("Municipality code",
                   "Year", 
                   "Number of establishments",
                   "Number of establishments (鉱業，採石業，砂利採取業)",
                   "Number of establishments (建設業)",
                   "Number of establishments (製造業)",
                   "Number of establishments (電気・ガス・熱供給・水道業)",
                   "Number of establishments (情報通信業)",
                   "Number of establishments (運輸業，郵便業)",
                   "Number of establishments (卸売業，小売業)",
                   "Number of establishments (金融業，保険業)",
                   "Number of establishments (不動産業，物品賃貸業)",
                   "Number of establishments (学術研究，専門・技術サービス業)",
                   "Number of establishments (宿泊業，飲食サービス業)",
                   "Number of establishments (生活関連サービス業，娯楽業)",
                   "Number of establishments (教育，学習支援業)",
                   "Number of establishments (医療，福祉)",
                   "Number of establishments (複合サービス事業)",
                   "Number of establishments (サービス業 他に分類されないもの)",
                   "Number of establishments (農林漁業)")

knitr::kable(ds)
```



- File name: `cleaned/data_area_year_num_labor.RDS`
- Key: `area_code`, `year`

```{r, results = "asis"}
data_area_year_num_labor <- 
  data_area_year_num_labor %>% 
  dplyr::select(
    area_code, 
    year, 
    dplyr::everything()
    )


ds <- 
  data_area_year_num_labor %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- c("Municipality code",
                   "Year", 
                   "Labor force",
                   "Labor force (Age 15-19)",
                   "Labor force (Age 20-24)",
                   "Labor force (Age 25-29)",
                   "Labor force (Age 30-34)",
                   "Labor force (Age 35-39)",
                   "Labor force (Age 40-44)",
                   "Labor force (Age 45-49)",
                   "Labor force (Age 50-54)",
                   "Labor force (Age 55-59)",
                   "Labor force (Age 60-64)",
                   "Labor force (Age 65-69)",
                   "Labor force (Age 70-74)",
                   "Labor force (Age 75-79)",
                   "Labor force (Age 80-84)",
                   "Labor force (Age 85-)"
                   )


knitr::kable(ds)



```




- File name: `cleaned/data_area_year_num_emp.RDS`
- Key: `area_code`, `year`

```{r, results = "asis"}
data_area_year_num_emp <- 
  data_area_year_num_emp %>% 
  dplyr::select(
    area_code, 
    year, 
    dplyr::everything()
    )


ds <- 
  data_area_year_num_emp %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- c("Municipality code",
                   "Year", 
                   "Number of employed people"
                   )


knitr::kable(ds)



```



- File name: `cleaned/data_area_year_num_parttemp.RDS`
- Key: `area_code`, `year`

```{r, results = "asis"}
data_area_year_num_parttemp <- 
  data_area_year_num_parttemp %>% 
  dplyr::select(
    area_code, 
    year, 
    dplyr::everything()
    )

ds <- 
  data_area_year_num_parttemp %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- 
  c(
    "Municipality code",
    "Year", 
    "Number of part-time workers",
    "Number of temp workers"
  )


knitr::kable(ds)



```

- File name: `cleaned/data_area_year_partwage.RDS`
- Key: `area_code`, `year`

```{r, results = "asis"}
ds <- 
  data_area_year_partwage %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- 
  c(
    "Year", 
    "Municipality code",
    "Part-time wage", 
    "Number of observations used for calculating part-time wages"
    )

knitr::kable(ds)
```


## Prefecture-year 

- File name: `cleaned/data_pref_year_minimum_wage.RDS`
- Key: `pref`, `year`

```{r}
ds <- 
  data_pref_year_minimum_wage %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- 
  c(
    "Prefecture code", 
    "Year",
    "Minum wage (10K Yen/ 8H)"
    )

knitr::kable(ds)
```

- File name: `cleaned/data_pref_year_partwage.RDS`
- Key: `pref`, `year`

```{r}
ds <- 
  data_pref_year_partwage %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- 
  c(
    "Prefecture code", 
    "Year",
    "Part-time wage (10K Yen/ 8H)",
    "Number of observations used for calculating part-time wages"
    )

knitr::kable(ds)
```



## Area

- File name: `cleaned/data_area.RDS`
- Key: `area_code`

```{r}
ds <- 
  data_area %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- 
  c(
    "Municipality code",
    "Commuting zone code"
    )

knitr::kable(ds)
```

## Zipcode

- File name: `cleaned/data_zipcode.RDS`
- Key: `zipcode`

```{r}
ds <- 
  data_zipcode %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- 
  c(
    "Zip code",
    "Municipality code"
    )

knitr::kable(ds)
```

## Year

- File name: `cleaned/data_year.RDS`
- Key: `year`

```{r}
ds <- 
  data_year %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- 
  c(
    "Year",
    "CPI (100 = 1998/3/1)"
    )

knitr::kable(ds)
```


## Area-adjacent area

- File name: `cleaned/data_area_adjacent_municipalities.RDS`
- Key: `area_code`, `adj`

```{r}
ds <- 
  data_area_adjacent_municipalities %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- 
  c(
    "Municipality code",
    "Adjacent municipality code"
    )

knitr::kable(ds)
```

## Area-Area

- File name: `cleaned/data_area_adjacent_municipalities.RDS`
- Key: `area_code_1`, `area_code_2`

```{r}
ds <- 
  data_area_area_distance %>% 
  describe(
    skew = F,
    ranges = F,
    trim = 0,
    quant = c(.05, .25, .5, .75, .95)
    )

ds$vars <- NULL
ds$se <- NULL

ds <- round(ds, digits = 2)

ds$definition <- 
  c(
    "Municipality code 1",
    "Municipality code 2",
    "Distance (m)"
    )

knitr::kable(ds)
```


