---
title: "Reduced Form Estimtion of Demand Function"
author: "Katsuhiro Komatsu"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---


```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 4, fig.width = 8)

library(magrittr)
```

```{css, echo = FALSE}

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

```


```{r}
# Read data
result_OLS <- readRDS(here::here("output/estimate_demand_reduced_form/OLS.RDS"))
result_firmFE <- readRDS(here::here("output/estimate_demand_reduced_form/2SLS_firmFE.RDS"))
result_estFE <- readRDS(here::here("output/estimate_demand_reduced_form/2SLS_establishmentFE.RDS"))
result_GMM <- readRDS(here::here("output/estimate_demand_reduced_form/GMM_firmFE.RDS"))

result_1st_dist <- readRDS(here::here("output/estimate_demand_reduced_form/dist_IV_first_stage.RDS"))
result_1st_dist_agg <- readRDS(here::here("output/estimate_demand_reduced_form/dist_aggregate_IV_first_stage.RDS"))
result_1st_rival <- readRDS(here::here("output/estimate_demand_reduced_form/rivals_IV_first_stage.RDS"))
result_1st_hausman <- readRDS(here::here("output/estimate_demand_reduced_form/hausman_IV_first_stage.RDS"))


```


The model implies the following reduced-form demand functions:
$$
\log{(s^W_{i,m,t}/s^W_{0,m,t})} = \beta^{WW} (w_{i,m,t} - w_{0,m,t}) + \beta^{WF} (f_{i,m,t} - f_{0,m,t}) + x_{i,m,t}^{W\prime} \gamma^W + \lambda_i^W + \eta_t^W + \epsilon_{i,t}^W, \\
\log{(s^F_{i,m,t}/s^F_{0,m,t})} = \beta^{FF} (f_{i,m,t} - f_{0,m,t}) + \beta^{FW} (w_{i,m,t} - w_{0,m,t}) + x_{i,m,t}^{F\prime} \gamma^F + \lambda_i^F + \eta_t^F + \epsilon_{i,t}^F.
$$

$i$: Establishment, $m$: Commuting zone, $t$: Year


Three set of instruments:

- Differentiation IV: For each establishment $i$ and characteristic $k$, calculate the mean and the s.d. of the empirical distribution of $|x^k_{i,m,t}-x^k_{j,m,t}|$.
  1. Use the mean and the s.d. for each characteristic $k$.
  2. Use only characteristics that are significant in the first stage (p-val < 0.1).
  3. Use the mean and the s.d. of the distribution of one-dimensional distance.
- Number of rivals IV: For each establishment $i$, count the number of other establishments in the same market that are within distance $d$ for various $d$.
- Hausman IV: For each establishment, use the average wage and fee of the establishments belonging to the same firm but in other commuting zones. For establishments that do not have other establishments belonging to the same firm, assume that all of them belong to the same firm.


```{r}
gm <- tibble::tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "Obs.", 0,
  "r.squared", "R-sq.", 3)


```

# 1. OLS


```{r}

var_name <- c("wage_net" = "Net Wage", "fee_net" = "Net Fee")

rows <- c("FE", rep("Firm", 2), rep("Estab.", 2)) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()
colnames(rows) <- c("term", paste("Model", as.character(1:4), sep = " "))

names(result_OLS) <- paste("(", 1:length(result_OLS), ")", sep = "")

modelsummary::modelsummary(result_OLS, 
                           output = "html",
                           stars = c("*" = .1, "**" = .05, "***" = .01),
                           gof_map = gm,
                           escape = T,
                           coef_map = var_name,
                           add_rows = rows) %>% 
  kableExtra::add_header_above(c(" ", "Worker" = 1, "Client Firm" = 1, "Worker" = 1, "Client Firm" = 1)) 


```


# 2. 2SLS

## Firm FE

```{r}
var_name <- c("`wage_net(fit)`" = "Net Wage", "`fee_net(fit)`" = "Net Fee")

rows <- c("IV", rep("Dist", 2), rep("Dist Selected", 2), rep("Dist Agg.", 2), rep("Num Rivals", 2), rep("Hausman", 2)) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()

colnames(rows) <- c("term", paste("Model", as.character(1:length(result_firmFE)), sep = " "))

names(result_firmFE) <- paste("(", 1:length(result_firmFE), ")", sep = "")

modelsummary::modelsummary(result_firmFE, 
                           output = "html",
                           stars = c("*" = .1, "**" = .05, "***" = .01),
                           gof_map = gm,
                           escape = T,
                           coef_map = var_name,
                           add_rows = rows) 


```



```{r}
# Latex output

var_name <- c("`wage_net(fit)`" = "Net Wage", "`fee_net(fit)`" = "Net Fee")

out <- list(
  "(1)" = result_firmFE[[1]],
  "(2)" = result_firmFE[[2]],
  "(3)" = result_firmFE[[7]],
  "(4)" = result_firmFE[[8]]
)


row1 <- c("IV", rep("Dist", 2), rep("Num Rivals", 2)) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()

row2 <- c("Wage elast.", 
           round(result_firmFE[[1]]$wage_elasticity, 3),
           round(result_firmFE[[2]]$wage_elasticity, 3),
           round(result_firmFE[[7]]$wage_elasticity, 3),
           round(result_firmFE[[8]]$wage_elasticity, 3)
           ) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()

row3 <- c("Fee elast.", 
           round(result_firmFE[[1]]$fee_elasticity, 3),
           round(result_firmFE[[2]]$fee_elasticity, 3),
           round(result_firmFE[[7]]$fee_elasticity, 3),
           round(result_firmFE[[8]]$fee_elasticity, 3)
           ) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame() 

rows <- rbind(row1, row2, row3)


colnames(rows) <- c("term", paste("Model", as.character(1:length(out)), sep = " "))


modelsummary::modelsummary(out, 
                      		 booktabs = TRUE,
                           stars = c("$^{*}$" = .1, "$^{**}$" = .05, "$^{***}$" = .01),
                           output = "latex_tabular",
                      		 escape = T,
                      		 fmt = 3,
                           coef_map = var_name,
                           gof_map = gm,
                      		 add_rows = rows) %>%
  kableExtra::add_header_above(c(" ", "Worker" = 1, "Firm" = 1, "Worker" = 1, "Firm" = 1)) %>% 
  kableExtra::save_kable(
    file = here::here("figuretable/estimate_demand_reduced_form/2SLS_firmFE.tex")
  )

```



## Establishment FE

```{r}
var_name <- c("`wage_net(fit)`" = "Net Wage", "`fee_net(fit)`" = "Net Fee")

rows <- c("IV", rep("Dist", 2), rep("Dist Selected", 2), rep("Dist Agg.", 2), rep("Num Rivals", 2), rep("Hausman", 2)) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()

colnames(rows) <- c("term", paste("Model", as.character(1:length(result_firmFE)), sep = " "))

names(result_estFE) <- paste("(", 1:length(result_estFE), ")", sep = "")

modelsummary::modelsummary(result_estFE, 
                           output = "html",
                           stars = c("*" = .1, "**" = .05, "***" = .01),
                           gof_map = gm,
                           escape = T,
                           coef_map = var_name,
                           add_rows = rows) 
```



# 3. Two-Step GMM

## Firm FE

```{r}

var_name <- c("wage_net" = "Net Wage", "fee_net" = "Net Fee")

rows <- c("IV", rep("Dist", 2), rep("Dist Selected", 2), rep("Dist Agg.", 2), rep("Num Rivals", 2), rep("Hausman", 2)) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()

colnames(rows) <- c("term", paste("Model", as.character(1:length(result_firmFE)), sep = " "))

names(result_GMM) <- paste("(", 1:length(result_GMM), ")", sep = "")

modelsummary::modelsummary(result_GMM, 
                           output = "html",
                           stars = c("*" = .1, "**" = .05, "***" = .01),
                           gof_map = gm,
                           escape = T,
                           coef_map = var_name,
                           add_rows = rows) 

```


# 4. First Stage {.tabset}



## Distance IV

```{r}


var_name <- rep("", times = 60)
names(var_name) <- rownames(result_1st_dist[[1]]$coefficients)[1:60]
var_name[1:26] <- paste("Dist Avg: worktype ", 1:26, sep = "")
var_name[27:30] <- paste("Dist Avg: ", c("Daily", "Temp to perm", "Oversea", "Cocurrent"), sep = "")
var_name[31:56] <- paste("Dist SD: worktype ", 1:26, sep = "")
var_name[57:60] <- paste("Dist SD: ", c("Daily", "Temp to perm", "Oversea", "Cocurrent"), sep = "")

rows <- c("FE", rep("Firm", 4), rep("Estab.", 4)) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()
colnames(rows) <- c("term", paste("Model", as.character(1:8), sep = " "))


header <- c(" ", "Wage" = 1, "Fee" = 1, "Wage" = 1, "Fee" = 1,
            "Wage" = 1, "Fee" = 1, "Wage" = 1, "Fee" = 1)

names(result_1st_dist) <- paste("(", 1:length(result_1st_dist), ")", sep = "")
modelsummary::modelsummary(result_1st_dist, 
                           output = "html",
                           stars = c("*" = .1, "**" = .05, "***" = .01),
                           gof_map = gm,
                           coef_map = var_name,
                           escape = T,
                           add_rows = rows) %>% 
  kableExtra::add_header_above(header) 

```


## Distance IV (each)

```{r}

var_name <- c("dist_mean" = "Distance: Mean",
              "dist_sd" = "Distance: S.D.")

rows <- c("FE", rep("Firm", 2), rep("Estab.", 2)) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()
colnames(rows) <- c("term", paste("Model", as.character(1:4), sep = " "))

header <- c(" ", "Wage" = 1, "Fee" = 1, "Wage" = 1, "Fee" = 1)

names(result_1st_dist_agg) <- paste("(", 1:length(result_1st_dist_agg), ")", sep = "")
modelsummary::modelsummary(result_1st_dist_agg, 
                           output = "html",
                           stars = c("*" = .1, "**" = .05, "***" = .01),
                           gof_map = gm,
                           coef_map = var_name,
                           escape = T,
                           add_rows = rows) %>% 
  kableExtra::add_header_above(header) 
```



## Number of rivals 

```{r}
var_name <- c("num_rivals_1" = "Log number of rivals: distance 0",
              "num_rivals_2" = "Log number of rivals: distance 1-4",
              "num_rivals_3" = "Log number of rivals: distance 5-8",
              "num_rivals_4" = "Log number of rivals: distance 9-12",
              "num_rivals_5" = "Log number of rivals: distance 13-16",
              "num_rivals_6" = "Log number of rivals: distance 17+"
              )

rows <- c("FE", rep("Firm", 2), rep("Estab.", 2)) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()
colnames(rows) <- c("term", paste("Model", as.character(1:4), sep = " "))

header <- c(" ", "Wage" = 1, "Fee" = 1, "Wage" = 1, "Fee" = 1)

names(result_1st_rival) <- paste("(", 1:length(result_1st_rival), ")", sep = "")
modelsummary::modelsummary(result_1st_rival, 
                           output = "html",
                           stars = c("*" = .1, "**" = .05, "***" = .01),
                           gof_map = gm,
                           coef_map = var_name,
                           escape = T,
                           add_rows = rows) %>% 
  kableExtra::add_header_above(header) 

```



## Hausman IV

```{r}

var_name <- c("wage_iv" = "Wage",
            "fee_iv"  = "Fee")

rows <- c("FE", rep("Firm", 2), rep("Estab.", 2)) %>% 
  matrix(nrow = 1) %>% 
  as.data.frame()
colnames(rows) <- c("term", paste("Model", as.character(1:4), sep = " "))

header <- c(" ", "Wage" = 1, "Fee" = 1, "Wage" = 1, "Fee" = 1)

names(result_1st_hausman) <- paste("(", 1:length(result_1st_hausman), ")", sep = "")
modelsummary::modelsummary(result_1st_hausman, 
                           output = "html",
                           stars = c("*" = .1, "**" = .05, "***" = .01),
                           gof_map = gm,
                           coef_map = var_name,
                           escape = T,
                           add_rows = rows) %>% 
  kableExtra::add_header_above(header) 
```






