---
title: "check_variation"
author: "Katsuhiro Komatsu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F, include = F}
rm(list = ls())
gc()

library(magrittr)
library(ggplot2)
library(stargazer)
library(lfe)
library(gtools)
library(knitr)
library(psych)
```


```{r, include = F}
load("../data/data_2010_2014_cleaned.RData")
load("../data/num_platforms.RData")
```

# Variations across commuting zones


```{r, include = F}

num_platforms <- num_platforms %>% 
  dplyr::arrange(cz, year) %>% 
  dplyr::group_by(cz) %>% 
  dplyr::mutate(N_ldif = log(N) - log(N_lag),
                N_tokutei_ldif = log(N_tokutei) - log(N_tokutei_lag),
                N_ippan_ldif = log(N_ippan) - log(N_ippan_lag)) %>% 
  dplyr::ungroup()

```

- Left: Histogram of the number of ippan platforms
- Right: Histogram of the growth of the number of ippan platforms
```{r, warning = FALSE, message = FALSE, echo = FALSE}
# g1 <- ggplot(num_platforms, aes(x = log(N))) +
#   geom_histogram()
# 
# g2 <- ggplot(num_platforms, aes(x = log(N_tokutei))) +
#   geom_histogram()


g3 <- ggplot(num_platforms, aes(x = log(N_ippan))) +
  geom_histogram() + xlab("log(N)")

g4 <- ggplot(num_platforms, aes(x = N_ippan_ldif)) +
  geom_histogram() + xlab("Dif in log(N)")

gridExtra::grid.arrange(g3, g4, nrow = 1)
```


```{r, include = F}
data <- data %>% 
  dplyr::filter(tokutei == 0)  # restricted to ippan

data_cz <- data %>% 
  dplyr::mutate() %>% 
  dplyr::group_by(cz, year) %>% 
  dplyr::summarize(client = mean(client),
                   fee = mean(fee),
                   wage = mean(wage),
                   margin = mean(margin),
                   sales = mean(sales),
                   oversea = mean(oversea),
                   shokai = mean(shokai),
                   training = mean(training),
                   register = mean(register),
                   staff = mean(staff),
                   tempperm = mean(tempperm),
                   tempdaily = mean(tempdaily),
                   tempfixed = mean(tempfixed),
                   N_ippan = mean(N_ippan)) %>% 
  dplyr::ungroup()
```


```{r, include = F}
ds <- data_cz %>% 
  dplyr::select(-(cz:year)) %>% 
  describe(skew = F,
           ranges = F,
           trim = 0,
         quant = c(.05, .25, .5, .75, .95))

ds$vars <- NULL
ds$se <- NULL

```


```{r, include = F}

compute_r2 <- function(y, xmat){
  
  formula1 <- as.formula(paste(yvar, "~ 1 | 0 ", sep = ""))
  formula2 <- as.formula(paste(yvar, "~ 1 | cz_year ", sep = ""))
  formula3 <- as.formula(paste(yvar, "~ 1 | cz + year "))
  resid1 <- felm(formula1, data = data)$residuals
  resid2 <- felm(formula2, data = data)$residuals
  resid3 <- felm(formula3, data = data)$residuals

  r2_1 <- 1 - sum(resid2 ^ 2) / sum(resid1 ^ 2)
  r2_2 <- 1 - sum(resid3 ^ 2) / sum(resid1 ^ 2)
  
  # formula1 <- as.formula(paste(yvar, "~ as.factor(cz_year) ", sep = ""))
  # formula2 <- as.formula(paste(yvar, "~ as.factor(cz) + as.factor(year)", sep = ""))
  # r2_1 <- summary(lm(formula1, data = data))$r.squared
  # r2_2 <- summary(lm(formula2, data = data))$r.squared
  
  
  return(c(r2_1, r2_2))
}

```




```{r, include = F}


data$cz_year <- dplyr::group_indices(data, cz, year)
yvars <- rownames(ds)
r2_vec_1 <- c()
r2_vec_2 <- c()
for (yvar in yvars){
  
  r2 <- compute_r2(yvar, data)
  r2_vec_1 <- c(r2_vec_1, r2[1])
  r2_vec_2 <- c(r2_vec_2, r2[2])
}

ds$R2_prod <- r2_vec_1
ds$R2_sum <- r2_vec_2


```

### Descriptives of variables averaged within each location
- 一般事業所のみ
- R2_prod: 各変数を地域x年のダミーに回帰したときのR-squared
- R2_sum: 各変数を地域ダミーと年ダミーに回帰したときのR-squared
- oversea: 海外派遣の有無
- shokai: 紹介予定派遣の有無
- training: 教育訓練の有無
- staff: 労働者の総数-派遣労働者の数
```{r, echo = F, results = "asis"}
kable(ds, digits = 3)
```

