---
title: "Regression on Number of Platforms"
author: "Katsuhiro Komatsu"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

- Regress wages, fees, etc. on the number of platforms in each commuting zone (CZ).
- Restrict sample to ippan establishments.
- Use the number of platforms in the previous year.
- Year FE + Firm FE + Commuting zone FE are controlled.
- IV is the sum of $N$ in adjacent commuting zones.
- Standard errors are clustered at community zone level.
- Other control variables are
  - Number of firms in each industry (major classification)
  - Labor force in each age range (15-19, 20-24, ...)
  - Indicator variables that takes 1 if a establishment paid wages for a particular type of work
  - Indicator for hiring daily workers
  - Indicator for providing temp-to-perm hiring offers
  - Indicator for overasea dispatching
  - Indicator for employment placement services


```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
      x)
  } else x
}
```


```{r, include = F}

type = "html" # regression output

source("../R/temp.R")
library(magrittr)
library(ggplot2);  theme_set(theme_classic())
library(stargazer)
library(knitr)
library(lfe)
# library(gtools)
# library(grid)
library(gridExtra)
# library(gtable)
```


```{r, include = F}
# load("../data/data_2010_2014_cleaned.RData")
# load("../data/num_platforms.RData")
# load("../data/num_platforms_adjacent.RData")
# data <- dplyr::filter(data,
#                       year <= 2014)

# data <- readRDS("../output/data_establishments.RDS")
data <- readRDS("../output/share_data_two_shares.RDS")
num_labor <- readRDS("../output/num_labor_cz.RDS")
num_firms <- readRDS("../output/num_firms_cz.RDS")
num_platforms <- readRDS("../output/num_platforms.RDS")

data <- data %>% 
  dplyr::left_join(num_labor, by = c("cz", "year")) %>% 
  dplyr::left_join(num_firms, by = c("cz", "year")) %>% 
  dplyr::mutate(
    margin = log(fee) - log(wage)
  ) %>% 
  dplyr::group_by(cz, year) %>% 
  dplyr::mutate(
    s_W_sum = sum(s_W),
    s_F_sum = sum(s_F)
  ) %>% 
  dplyr::ungroup()

```


```{r, include = F}
# data <- data %>% 
#   dplyr::filter(
#     is.finite(staff_ratio),
#     !is.na(ptwage),
#     staff_ratio > 0,
#     to_use == 1
#   ) 

```


```{r, include = F}
# Control variables
ctr_vars_names <- data %>% 
  dplyr::select(dplyr::starts_with("firms"),
                dplyr::starts_with("labor")) %>%
  dplyr::select(!dplyr::ends_with("_all"),
                !dplyr::ends_with("_all")) %>% 
  colnames()

ctr_vars_names <- paste("log(1 + ", ctr_vars_names, ")", sep = "")

temp <- data %>% 
  dplyr::select(dplyr::starts_with("type_")) %>% 
  colnames()

ctr_vars_names <- c(ctr_vars_names,
                    temp,
                    # "log(staff_ratio)",
                    # "log(ptwage)",
                    "daily",
                    "shokai",
                    "oversea",
                    "cocurrent")

ctr_vars <- paste(ctr_vars_names, sep = "", collapse = " + ")

```


```{r, eval = F}

# linear regression
reg_linear <- function(data, N_data, N_iv){
  
  data_reg <- data %>% 
    dplyr::left_join(N_data, by = c("year", "cz")) %>% 
    dplyr::left_join(N_iv, by = c("year", "cz")) %>% 
    dplyr::filter(N > 0)

  data_iv <- dplyr::filter(data_reg, N_adj > 0)
  N_adj <- data_iv %>%
    dplyr::pull(N_adj) %>%
    unique() %>%
    sort()

  for (i in 1:length(N_adj)){
    j <- N_adj[i]
    varname <- paste("N_adj", j, sep = "_")
    data_iv <- data_iv %>%
      dplyr::mutate(!!varname := dplyr::if_else(N_adj == j, 1, 0))
  }


  temp <- paste("N_adj", N_adj, sep = "_", collapse = " + ")
  N_iv_formula <- paste("log(N) ", temp, sep = " ~ ")
  
  result <- list()
  formula <- list()

  formula[[1]] <- paste("log(wage) ~ log(N) + ", ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")
  formula[[2]] <- paste("log(wage) ~ log(N) + ", ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")
  formula[[3]] <- paste("log(wage) ~ ", ctr_vars, " | year + cz + firm_id | (log(N) ~ log(N_adj)) | cz", sep = "")
  formula[[4]] <- paste("log(wage) ~ ", ctr_vars, " | year + cz + firm_id | (", N_iv_formula, ") | cz", sep = "")
  
  formula[[5]] <- paste("log(fee) ~ log(N) + ", ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")
  formula[[6]] <- paste("log(fee) ~ log(N) + ", ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")
  formula[[7]] <- paste("log(fee) ~ ", ctr_vars, " | year + cz + firm_id | (log(N) ~ log(N_adj)) | cz", sep = "")
  formula[[8]] <- paste("log(fee) ~ ", ctr_vars, " | year + cz + firm_id | (", N_iv_formula, ") | cz", sep = "")
  
  
  formula[[9]] <- paste("margin ~ log(N) + ", ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")
  formula[[10]] <- paste("margin ~ log(N) + ", ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")
  formula[[11]] <- paste("margin ~ ", ctr_vars, " | year + cz + firm_id | (log(N) ~ log(N_adj)) | cz", sep = "")
  formula[[12]] <- paste("margin ~ ", ctr_vars, " | year + cz + firm_id | (", N_iv_formula, ") | cz", sep = "")
  
  
  formula[[13]] <- paste("log(N) ~ log(N_adj) + ", ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")
  
  
  nspec <- length(formula)
  for (i in 1:nspec){
    
    if (i %in% c(1, 5, 9)){
      data_touse <- data_reg
    } else {
      data_touse <- data_iv
    }
    
    result[[i]] <- felm(
      data = data_touse,
      formula = as.formula(formula[[i]])
    )
    
  }
  
  # tidy up the expression
  i <- 1 + length(ctr_vars_names)
  coef_order <- c(i, 1:(i-1))
  
  for (j in c(3, 4, 7, 8, 11, 12)){
  
  	# change label
  	rownames(result[[j]]$coefficients)[i] <- "log(N)"
  	rownames(result[[j]]$beta)[i] <- "log(N)"
  	names(result[[j]]$cse)[i] <- "log(N)"
  
  	result[[j]]$coefficients <- result[[j]]$coefficients[coef_order, 1, drop = F]
  	result[[j]]$beta <- result[[j]]$beta[coef_order, 1, drop = F]
  	result[[j]]$cse <- result[[j]]$cse[coef_order]
  	result[[j]]$cpval <- result[[j]]$cpval[coef_order]
  
  }

  return(result)
  
}

# show results of the linear regression
show_result <- function(result){
  nspec = length(result)  
  nyvar = 3
  stargazer(result,
            type = type,
            keep.stat = c("n", "rsq"),
            dep.var.labels.include = FALSE,
            column.separate = c(4, 4, 4, 1),
            column.labels = c("log(wage)", "log(fee)", "margin", "log(N)"),
            keep = c(1, 2),
            align = TRUE,
            add.lines = list(c("IV (Log-linear)",
                               c(rep(c("No", "No", "Yes", "No"), 3), " ")),
                             c("IV (Dummies)",
                               c(rep(c("No", "No", "No", "Yes"), 3), " "))),
            notes.align = "l")  
}


# plot coefficients
plot_func <- function(data_reg, N_vars, N_vec, ref_lev = 1, N_iv_formula = NULL, x_label = NULL){
  
  result = list()
  formula = list()
  coef = list()
  se = list()

  if (is.null(N_iv_formula)){
    formula[[1]] <- paste("log(wage) ~ ", N_vars, " + ",  ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")
    formula[[2]] <- paste("log(fee) ~ ", N_vars, " + ",  ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")
    formula[[3]] <- paste("margin ~ ", N_vars, " + ",  ctr_vars, " | year + cz + firm_id | 0 | cz", sep = "")  
    
    for (i in 1:3){
    result[[i]] <- felm(
      formula = as.formula(formula[[i]]),
      data = data_reg
    )
    temp <- dim(summary(result[[i]])$coefficients)[1]
    coef[[i]] <- summary(result[[i]])$coefficients[1:length(N_vec), 1]
    coef[[i]] <- c(0, coef[[i]])
    se[[i]] <- summary(result[[i]])$coefficients[1:length(N_vec), 2]
    se[[i]] <- c(0, se[[i]])
  }  
    
  } else {
    formula[[1]] <- paste("log(wage) ~ ",   ctr_vars, " | year + cz + firm_id | (", N_iv_formula, ") | cz", sep = "")
    formula[[2]] <- paste("log(fee) ~ ",  ctr_vars, " | year + cz + firm_id | (", N_iv_formula, ") | cz", sep = "")
    formula[[3]] <- paste("margin ~ ",  ctr_vars, " | year + cz + firm_id | (", N_iv_formula, ") | cz", sep = "")     
    
    for (i in 1:3){
      result[[i]] <- felm(
        formula = as.formula(formula[[i]]),
        data = data_reg
      )
      temp <- dim(summary(result[[i]])$coefficients)[1]
      coef[[i]] <- summary(result[[i]])$coefficients[(temp - length(N_vec) + 1):temp, 1]
      coef[[i]] <- c(0, coef[[i]])
      se[[i]] <- summary(result[[i]])$coefficients[(temp - length(N_vec) + 1):temp, 2]
      se[[i]] <- c(0, se[[i]])
    }    
  }


  x_axis <- c(ref_lev, N_vec)
  if (is.null(x_label)){
    x_label <- "Number of Platforms"
  }

  g1 <- data.frame(N = x_axis, coef = coef[[1]], se = se[[1]]) %>%
    ggplot(aes(x = N, y = coef)) +
    geom_point() + geom_line() +
    geom_ribbon(aes(ymax = coef + 1.645 * se, ymin = coef - 1.645 * se), alpha = 0.1, width = 0.1) +
    xlab(x_label) + ylab("Impact on Wage") #+
    #scale_x_continuous(breaks = x_breaks)
  
  g2 <- data.frame(N = x_axis, coef = coef[[2]], se = se[[2]]) %>%
    ggplot(aes(x = N, y = coef)) +
    geom_point() + geom_line() +
    geom_ribbon(aes(ymax = coef + 1.645 * se, ymin = coef - 1.645 * se), alpha = 0.1, width = 0.1) +
    xlab(x_label) + ylab("Impact on Fee") #+
    #scale_x_continuous(breaks = x_breaks)
  
  g3 <- data.frame(N = x_axis, coef = coef[[3]], se = se[[3]]) %>%
    ggplot(aes(x = N, y = coef)) +
    geom_point() + geom_line() +
    geom_ribbon(aes(ymax = coef + 1.645 * se, ymin = coef - 1.645 * se), alpha = 0.1, width = 0.1) +
    xlab(x_label) + ylab("Impact on Margin") #+
    #scale_x_continuous(breaks = x_breaks)
  

  gridExtra::grid.arrange(g1, g2, g3, nrow = 2)
    
  
}


reg_nonlinear <- function(data, N_data, N_iv){

  # Merge the number of platforms
  data_reg <- data %>% 
    dplyr::left_join(N_data, by = c("year", "cz")) %>% 
    dplyr::left_join(N_iv, by = c("year", "cz")) %>% 
    dplyr::filter(N > 0)
  
  # Distribution of N
  N_dist <- data_reg %>% 
    dplyr::select(cz, year, N) %>% 
    dplyr::distinct() %>% 
    dplyr::pull(N)
  
  N_vec <- unique(N_dist) %>% 
    sort()
    
  #----------------------------------------
  # 1. Regress on 1{N=2}, 1{N=3}, ...
  #----------------------------------------
  
  # truncate at F(N) = 0.5
  N_max <- floor(quantile(N_dist, 0.5))
  N_vec <- N_vec[N_vec <= N_max]
  N_vec <- N_vec[2:length(N_vec)] # remove reference level (N=1)

  for (i in 1:(length(N_vec) - 1)){
    j <- N_vec[i]
    varname <- paste("N", j, sep = "_")
    data_reg <- data_reg %>%
    dplyr::mutate(!!varname := dplyr::if_else(N == j, 1, 0))
  }
  
  varname <- paste("N", N_max, sep = "_")
  data_reg <- data_reg %>%
    dplyr::mutate(!!varname := dplyr::if_else(N >= N_max, 1, 0))
  
  N_vars <- paste("N", N_vec, sep = "_", collapse = " + ")
  
  title <- "1.1 Regression on the indicators for each $N$"
  cat(paste("##### ", colorize(title, "blue"), sep = ""))
  cat("\n\n")
  plot_func(data_reg, N_vars, N_vec)
  cat("\n\n")
  
  # IV
  N_adj <- data_reg %>%
    dplyr::pull(N_adj) %>%
    unique() %>%
    sort()

  for (i in 1:length(N_adj)){
    j <- N_adj[i]
    varname <- paste("N_adj", j, sep = "_")
    data_reg <- data_reg %>%
      dplyr::mutate(!!varname := dplyr::if_else(N_adj == j, 1, 0))
  }

  temp1 <- paste("N", N_vec, sep = "_", collapse = " | ")
  temp2 <- paste("N_adj", N_adj, sep = "_", collapse = " + ")
  N_iv_formula <- paste(temp1, temp2, sep = " ~ ")

  title <- "1.2 Using IV"
  cat(paste("##### ", colorize(title, "blue"), sep = ""))
  cat("\n\n")
  plot_func(data_reg, N_vars, N_vec, ref_lev = 1, N_iv_formula)
  cat("\n\n")

  #-----------------------------------------------
  # 2. Regress on 1{N=4,5,6}, 1{N=7,8,9}, ...
  #-----------------------------------------------
  
  N_vec <- c(4, 7, 10, 13, 16, 19)
  N_size <- length(N_vec) + 1

  for (i in 2:(N_size - 1)){
    varname <- paste("N", i, sep = "_")
    data_reg <- data_reg %>%
      dplyr::mutate(!!varname := dplyr::if_else(N >= N_vec[i-1] & N < N_vec[i], 1, 0))
  }

  varname <- paste("N", N_size, sep = "_")
  data_reg <- data_reg %>%
    dplyr::mutate(!!varname := dplyr::if_else(N >= N_vec[length(N_vec)], 1, 0))

  N_vars <- paste("N", 2:N_size, sep = "_", collapse = " + ")
  
  title <- "2.1 Regression on the indicators for each range of $N$"
  cat(paste("##### ", colorize(title, "blue"), sep = ""))
  cat("\n\n")
  plot_func(data_reg, N_vars, (N_vec + 1), ref_lev = 2)
  cat("\n\n")
  
  # IV
  temp1 <- paste("N", 2:N_size, sep = "_", collapse = " | ")
  temp2 <- paste("N_adj", N_adj, sep = "_", collapse = " + ")
  N_iv_formula <- paste(temp1, temp2, sep = " ~ ")

  title <- "2.2 Using IV"
  cat(paste("##### ", colorize(title, "blue"), sep = ""))
  cat("\n\n")
  plot_func(data_reg, N_vars, (N_vec + 1), ref_lev = 2, N_iv_formula)
  cat("\n\n")

  
  #----------------------------------------------------
  # 3. Regress on indicators for deciles
  #----------------------------------------------------
  N_qntl <- quantile(N_dist, c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))
  N_size <- length(N_qntl) + 1

  for (i in 2:(N_size - 1)){
    varname <- paste("N", i, sep = "_")
    data_reg <- data_reg %>%
      dplyr::mutate(!!varname := dplyr::if_else(N >= N_qntl[i-1] & N < N_qntl[i], 1, 0))
  }

  data_reg <- data_reg %>%
    dplyr::mutate(N_10 = dplyr::if_else(N >= N_qntl[9], 1, 0))

  N_vars <- paste("N", 2:N_size, sep = "_") %>%
    paste(sep = "", collapse = " + ")

  if (length(N_qntl) == length(unique(N_qntl))){
    N_vec <- 2:10 * 0.1
    title <- "3.1 Regression on the indicators for deciles of $N$"
    cat(paste("##### ", colorize(title, "blue"), sep = ""))
    cat("\n\n")
    plot_func(data_reg, N_vars, N_vec, ref_lev = 0.1, N_iv_formula = NULL, x_label = "Num Platforms Decile")
    cat("\n\n")
  }
  
  # IV
  temp1 <- paste("N", 2:10, sep = "_", collapse = " | ")
  temp2 <- paste("N_adj", N_adj, sep = "_", collapse = " + ")
  N_iv_formula <- paste(temp1, temp2, sep = " ~ ")

  if (length(N_qntl) == length(unique(N_qntl))){
    N_vec <- 2:10 * 0.1
    title <- "3.2 Using IV"
    cat(paste("##### ", colorize(title, "blue"), sep = ""))
    cat("\n\n")
  plot_func(data_reg, N_vars, N_vec, ref_lev = 0.1, N_iv_formula, x_label = "Num Platforms Decile")
    cat("\n\n")
  }
  
}


show_deciles <- function(N_data){
  N_data %>%
    dplyr::filter(N > 0, !is.na(N)) %>% 
    dplyr::pull(N) %>%
    quantile(c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)) %>%
    t() %>% 
    kable()
}


reg_np <- function(data, N_data){
  
  
  
  
}

```


```{r, eval = F}
titles <- c("1. All platforms",
            "2. Active platforms",
            "3. General platforms",
            "4. Platforms of large firms",
            "5. All firms",
            "6. Active firms")

descriptions <- c("Using the number of all platforms",
                  "Using the number of platforms reporting wages and fees",
                  "Using the number of platforms that did not report worktype-specific wages and fees",
                  "Using the number of platforms belonging to large firms in terms of sales in the previous year",
                  "Using the number of firms",
                  "Using the number of firms whose platforms reported wages and fees")

N_data_list <- list()
N_data_list[[1]] <- num_platforms
N_data_list[[2]] <- num_platforms_active
N_data_list[[3]] <- num_platforms_general
N_data_list[[4]] <- num_platforms_large
N_data_list[[5]] <- num_firms
N_data_list[[6]] <- num_firms_active

N_iv_list <- list()
N_iv_list[[1]] <- num_platforms_adjacent
N_iv_list[[2]] <- num_platforms_active_adjacent
N_iv_list[[3]] <- num_platforms_general_adjacent
N_iv_list[[4]] <- num_platforms_large_adjacent
N_iv_list[[5]] <- num_firms_adjacent
N_iv_list[[6]] <- num_firms_active_adjacent

```

```{r, results = "asis", eval = F}

for (i in 1:6){
  cat(paste("### ", colorize(titles[i], "blue"), sep = ""))
  cat("\n\n")
  cat(descriptions[i])
  cat("\n\n")
  cat("***")
  cat("\n\n")

  # title <- "Linear regression"
  # cat(paste("#### ", colorize(title, "blue"), sep = ""))
  # cat("\n\n")
  # reg_linear(data, N_data_list[[i]], N_iv_list[[i]]) %>% 
  #   show_result()
  
  # title <- "Distribution of N"
  # cat(paste("#### ", colorize(title, "blue"), sep = ""))
  # cat("\n\n")
  # print(show_deciles(N_data_list[[i]]))
  # cat("\n\n")
  
  reg_nonlinear(data, N_data_list[[i]], N_iv_list[[i]])  

  cat("\n\n")
}


```




```{r}
ylab_vec <- c("Wage", "Fee", "Margin", "Worker Share", "Firm Share")
yvar_vec <- c("log(wage)", "log(fee)", "margin", "log(s_W_sum)", "log(s_F_sum)")
```

```{r, results = "asis"}
N_data <- num_platforms %>% 
  dplyr::mutate(year = year + 1) %>% 
  dplyr::select(year, cz, N)

N_iv <- num_platforms %>% 
  dplyr::mutate(year = year + 1) %>% 
  dplyr::select(year, cz, N_adj) %>% 
  na.omit()

cat("### OLS")

reg_nonlinear(data,
              N_data,
              N_iv,
              yvar_vec,
              ylab_vec,
              dir_name = "all_platforms")
```



```{r, results = "asis", eval = F}
N_data <- num_platforms %>% 
  dplyr::select(year, cz, N)

N_iv <- num_platforms %>% 
  dplyr::select(year, cz, N_adj) %>% 
  na.omit()

# Merge the number of platforms
data_reg <- data %>% 
  dplyr::left_join(N_data, by = c("year", "cz")) %>% 
  dplyr::left_join(N_iv, by = c("year", "cz")) %>% 
  dplyr::filter(N > 0)
  
# Distribution of N
N_dist <- data_reg %>% 
  dplyr::select(cz, year, N) %>% 
  dplyr::distinct() %>% 
  dplyr::pull(N)
  
N_vec <- unique(N_dist) %>% 
  sort()  
  
# truncate at F(N) = 0.5
N_max <- floor(quantile(N_dist, 0.5))
N_vec <- N_vec[N_vec <= N_max]
N_vec <- N_vec[2:length(N_vec)] # remove reference level (N=1)
  
for (i in 1:(length(N_vec) - 1)){
  j <- N_vec[i]
  varname <- paste("N", j, sep = "_")
  data_reg <- data_reg %>%
    dplyr::mutate(!!varname := dplyr::if_else(N == j, 1, 0))
}
  
varname <- paste("N", N_max, sep = "_")
data_reg <- data_reg %>%
  dplyr::mutate(!!varname := dplyr::if_else(N >= N_max, 1, 0))
  
N_vars <- paste("N", N_vec, sep = "_", collapse = " + ")
  
title <- "1.1 Regression on the indicators for each $N$"
cat(paste("##### ", colorize(title, "blue"), sep = ""))
cat("\n\n")
g_list <- plot_func(data_reg, N_vars, N_vec, yvar_vec, ylab_vec)
do.call("grid.arrange", c(g_list, nrow = 2))
cat("\n\n")

# save
for (i in 1:length(ylab_vec)){
  filename <- paste("figuretable/competition_regression/each_N/competition_OLS_", ylab_vec[i], ".png", sep = "")
  ggsave(
    g_list[[i]],
    filename = here::here(filename),
    width = 4,
    height = 3
  )  
}

  
# IV
N_adj <- data_reg %>%
  dplyr::pull(N_adj) %>%
  unique() %>%
  sort()
  
for (i in 1:length(N_adj)){
  j <- N_adj[i]
  varname <- paste("N_adj", j, sep = "_")
  data_reg <- data_reg %>%
    dplyr::mutate(!!varname := dplyr::if_else(N_adj == j, 1, 0))
}
  
temp1 <- paste("N", N_vec, sep = "_", collapse = " | ")
temp2 <- paste("N_adj", N_adj, sep = "_", collapse = " + ")
N_iv_formula <- paste(temp1, temp2, sep = " ~ ")
  
title <- "1.2 Using IV"
cat(paste("##### ", colorize(title, "blue"), sep = ""))
cat("\n\n")
g_list <- plot_func(data_reg, N_vars, N_vec, yvar_vec, ylab_vec, ref_lev = 1, N_iv_formula)
do.call("grid.arrange", c(g_list, nrow = 2))
cat("\n\n")

# save

for (i in 1:length(ylab_vec)){
  filename <- paste("figuretable/competition_regression/each_N/competition_IV_", ylab_vec[i], ".png", sep = "")
  ggsave(
    g_list[[i]],
    filename = here::here(filename),
    width = 4,
    height = 3
  )  
}

```





