---
title: "Estimate first stage using shift share"
author: "Katsuhiro Komatsu"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{css, echo = FALSE}

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

```



- Construct the predicted growth of the number of THS establishments by Bartik type instrument:
$$
z_{m,t} = \sum_{i} s_{i,m,t-1} \times (\log{N_{i, -m, t}} - \log{N_{i,-m, t-1}})
$$
where 
- $s_{i,t-1}$ is the share of firm $i$ in market $m$ in year $t-1$.
  1. Weight based on the number of establishments of firms in market $m$
      - E.g. In market $m$, firm A has 2 establishments while firm B has 1 establishment -> $s_A=2/3$, $s_B=1/3$.
  2. Weight based on the number of establishments of firms in market $m$ and its adjacent markets.
      - To put a positive weight on firms that newly enter in year $t$
- $N_{i,-m,t}$ is the number of establishments of firm $i$ in year $t$ located in markets other than $m$.
      - For case 2, I exclude adjacent markets when calculating $N_{i,-m,t}$.



### First stage regression
$$
  y_{m,t} = \beta \tilde z_{m,t} + x_{m,t}'\gamma + \lambda_m + \eta_t + \epsilon_{m,t}
$$
where 

- $y_{m,t}$: (i) $\Delta \log{N_{m,t}}$ or (ii)  $\log{N_{m,t}}$
- $\tilde z_{m,t}$: (i) $z_{m,t}$ or (ii) $N_{m, t-1} (1 + z_{m,t})$
- $x_{m,t}$: Log of labor force in each age category, log of number of firms in each industry


```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 4, fig.width = 8)
```


#### Log difference

```{r}
htmltools::includeHTML(here::here("figuretable/first_stage/first_stage_logdif_logdif.html"))
```


#### Log

```{r}
htmltools::includeHTML(here::here("figuretable/first_stage/first_stage_log_log.html"))
```





