---
title: "Large_platforms"
author: "Katsuhiro Komatsu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F, include = F}
rm(list = ls())
gc()

library(magrittr)
library(ggplot2); theme_set(theme_bw())
library(plotly)
library(leaflet)
library(knitr)

# Map
library(sf)
library(jpndistrict)
```


```{r, include = F}
# load("../data/data_2010_2014_cleaned.RData")

# use data before clearning
data <- haven::read_dta("../data/data_2010_2015_old_numeric.dta") %>% 
  dplyr::filter(
    year <= 2014,
    tokutei == 0
  ) %>% 
  dplyr::mutate(sales = dplyr::if_else(is.na(sales), 0, sales))

# municipality
zipcode_city <- haven::read_dta("../data/zipcode_municipality.dta")
data <- dplyr::left_join(data, zipcode_city, by = "zipcode")
mun_list <- unique(zipcode_city$mun)

# community zone
community_zone <- read.csv("../data/CZ_2005_original.csv")
colnames(community_zone) <- c("mun", "cz")
data <- dplyr::left_join(data, community_zone, by = "mun")

data <- data %>% 
  dplyr::filter(!is.na(cz))


```


# Ranking in terms of sales
  - Define "large firms" as firms that are in the top5 in terms of sales at least one year during 2010-2014
```{r, include = F, message = F}

data_firms <- data %>% 
  dplyr::group_by(firm_id, year) %>% 
  dplyr::summarise(sales = sum(sales),
                   N = dplyr::n()) %>% 
  dplyr::arrange(year, dplyr::desc(sales)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(year) %>% 
  dplyr::mutate(share = sales / sum(sales),
                cdf = cumsum(sales) / sum(sales),
                temp = 1,
                rank = cumsum(temp),
                top5 = dplyr::if_else(rank <= 5, 1, 0),
                top10 = dplyr::if_else(rank <= 10, 1, 0)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(firm_id) %>% 
  dplyr::mutate(top5_ever = max(top5))

large_firms <- data_firms %>% 
  dplyr::filter(top5_ever == 1) %>% 
  dplyr::select(year, firm_id, rank)

save(large_firms, file = "../data/large_firms.RData")


```


```{r, include = F}

data %>% 
  dplyr::left_join(large_firms) %>% 
  dplyr::filter(!is.na(rank)) %>% 
  dplyr::arrange(year, firm_id, dplyr::desc(sales)) %>% 
  dplyr::group_by(year, firm_id) %>% 
  dplyr::mutate(temp = 1,
                rank = cumsum(temp)) %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(rank == 1, year == 2010) %>% 
  dplyr::select(firm_id, zipcode)

```


```{r, echo = F, message = F, fig.width = 12, fig.height = 6}
g1 <- data_firms %>% 
  dplyr::filter(top5_ever == 1) %>% 
  dplyr::arrange(year, share) %>% 
  ggplot(aes(x = year, y = share, fill = firm_id)) +
  geom_bar(stat = "identity")

g2 <- data_firms %>% 
  dplyr::filter(top5_ever == 1) %>% 
  dplyr::arrange(year, share) %>% 
  ggplot(aes(x = year, y = sales / 1e+9, color = firm_id)) + geom_line() + geom_point() +
  ylab("Sales (Billion Yen)")
  

g3 <- data_firms %>% 
  dplyr::filter(top5_ever == 1) %>% 
  dplyr::arrange(year, share) %>% 
  ggplot(aes(x = year, y = N, color = firm_id)) + geom_line() + geom_point()

gridExtra::grid.arrange(g1, g2, g3, nrow = 1)

```

### Why does firm_id=3351414 have so small sales in year 2010?
```{r, echo = F, warning = F, message = F, results = "asis"}
# Why firm_id=3351414 has so small sales in year 2010?
temp <- data %>% 
  dplyr::filter(firm_id == 3351414) %>% 
  dplyr::arrange(year, dplyr::desc(sales))


temp %>% 
  dplyr::group_by(year) %>% 
  dplyr::summarise(wage = mean(wage, na.rm = T),
                   fee = mean(fee, na.rm = T),
                   sales = mean(sales, na.rm = T),
                   client = mean(client, na.rm = T),
                   tempperm = mean(tempperm, na.rm = T),
                   tempfixed = mean(tempfixed, na.rm = T),
                   tempdaily = mean(tempdaily, na.rm = T),
                   N = dplyr::n()) %>% 
  kable(digits = 1)




```



```{r, echo = F, message = F}

data_local <- data %>% 
  dplyr::group_by(firm_id, cz, year) %>% 
  dplyr::summarise(sales = sum(sales)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(cz, year) %>% 
  dplyr::mutate(share = sales / sum(sales)) %>% 
  dplyr::ungroup() %>% 
  dplyr::left_join(large_firms, by = c("firm_id", "year")) %>% 
  dplyr::mutate(large = dplyr::if_else(!is.na(rank), 1, 0)) %>% 
  dplyr::group_by(cz, year) %>% 
  dplyr::summarise(share = sum(share * large),
                   N = dplyr::n()) %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(!is.nan(share))

# In some areas, share = NaN because sum(sales) = 0.

data_local <- dplyr::left_join(community_zone, data_local, by = c("cz"))
```


### Market size and shares by large firms
```{r, echo = F, message = F, warning = F}

g1 <- data_local %>% 
  ggplot(aes(x = N, y = share)) +
  geom_point() + ylab("Share of Large Firms")

g2 <- data_local %>% 
  ggplot(aes(x = log(N), y = share)) +
  geom_point() + ylab("Share of Large Firms")


gridExtra::grid.arrange(g1, g2, nrow = 1)

```




## Sales share of large firms in community zones {.tabset}


```{r, include = F}
jpmap <- jpn_pref(1, district = T)
for (i in 2:47){
  jpmap <- dplyr::bind_rows(jpmap, jpn_pref(i, district = T))
}
```




### Year 2010
```{r, echo = F}

temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2010), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)


g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 


g

```

### Year 2011
```{r, echo = F}

temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2011), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)

g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 


g

```


### Year 2012
```{r, echo = F}

temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2012), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)

g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 

g

```


### Year 2013
```{r, echo = F}


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2013), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)

g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 


g

```



### Year 2014
```{r, echo = F}

temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)


g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 

g

```



## Location of establishments at 2014 {.tabset}

```{r, include = F}
jpmap <- jpn_pref(1, district = T)
for (i in 2:47){
  jpmap <- dplyr::bind_rows(jpmap, jpn_pref(i, district = T))
}

```


### ID 110011

```{r, echo = F}
locations <- data %>% 
  dplyr::filter(firm_id == 110011) %>% 
  dplyr::select(firm_id, year, zipcode, mun)


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code)) %>% 
  dplyr::left_join(dplyr::filter(locations, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421) %>% 
  dplyr::mutate(ishere = !is.na(firm_id))


g <- temp %>% 
  ggplot(aes(fill = ishere)) + geom_sf(color = NA, show.legend = F) + 
  coord_sf(datum = NA) + scale_fill_manual(values = c("FALSE" = "gray90", "TRUE" = "blue"))

g

```

### ID 110286 (テンプスタッフ?)

```{r, echo = F}
locations <- data %>% 
  dplyr::filter(firm_id == 110286) %>% 
  dplyr::select(firm_id, year, zipcode, mun)


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code)) %>% 
  dplyr::left_join(dplyr::filter(locations, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421) %>% 
  dplyr::mutate(ishere = !is.na(firm_id))


g <- temp %>% 
  ggplot(aes(fill = ishere)) + geom_sf(color = NA, show.legend = F) + 
  coord_sf(datum = NA) + scale_fill_manual(values = c("FALSE" = "gray90", "TRUE" = "blue"))

g

```



### ID 115841

```{r, echo = F}
locations <- data %>% 
  dplyr::filter(firm_id == 115841) %>% 
  dplyr::select(firm_id, year, zipcode, mun)


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code)) %>% 
  dplyr::left_join(dplyr::filter(locations, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421) %>% 
  dplyr::mutate(ishere = !is.na(firm_id))


g <- temp %>% 
  ggplot(aes(fill = ishere)) + geom_sf(color = NA, show.legend = F) + 
  coord_sf(datum = NA) + scale_fill_manual(values = c("FALSE" = "gray90", "TRUE" = "blue"))

g

```



### ID 116193 (リクルート)

```{r, echo = F}
locations <- data %>% 
  dplyr::filter(firm_id == 116193) %>% 
  dplyr::select(firm_id, year, zipcode, mun)


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code)) %>% 
  dplyr::left_join(dplyr::filter(locations, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421) %>% 
  dplyr::mutate(ishere = !is.na(firm_id))


g <- temp %>% 
  ggplot(aes(fill = ishere)) + geom_sf(color = NA, show.legend = F) + 
  coord_sf(datum = NA) + scale_fill_manual(values = c("FALSE" = "gray90", "TRUE" = "blue"))

g

```





### ID 121671

```{r, echo = F}
locations <- data %>% 
  dplyr::filter(firm_id == 121671) %>% 
  dplyr::select(firm_id, year, zipcode, mun)


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code)) %>% 
  dplyr::left_join(dplyr::filter(locations, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421) %>% 
  dplyr::mutate(ishere = !is.na(firm_id))


g <- temp %>% 
  ggplot(aes(fill = ishere)) + geom_sf(color = NA, show.legend = F) + 
  coord_sf(datum = NA) + scale_fill_manual(values = c("FALSE" = "gray90", "TRUE" = "blue"))

g

```



### ID 3351414 (パソナ)

```{r, echo = F}
locations <- data %>% 
  dplyr::filter(firm_id == 3351414) %>% 
  dplyr::select(firm_id, year, zipcode, mun)


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code)) %>% 
  dplyr::left_join(dplyr::filter(locations, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421) %>% 
  dplyr::mutate(ishere = !is.na(firm_id))


g <- temp %>% 
  ggplot(aes(fill = ishere)) + geom_sf(color = NA, show.legend = F) + 
  coord_sf(datum = NA) + scale_fill_manual(values = c("FALSE" = "gray90", "TRUE" = "blue"))

g

```




# Ranking in terms of the number of platforms
  - Define "large firms" as firms that are in the top5 in terms of the number of platforms at least one year during 2010-2014
```{r, include = F, message = F}

data_firms <- data %>% 
  dplyr::group_by(firm_id, year) %>% 
  dplyr::summarise(N = dplyr::n(),
                   sales = sum(sales)) %>% 
  dplyr::arrange(year, dplyr::desc(N)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(year) %>% 
  dplyr::mutate(share = N / sum(N),
                cdf = cumsum(N) / sum(N),
                temp = 1,
                rank = cumsum(temp),
                top5 = dplyr::if_else(rank <= 5, 1, 0),
                top10 = dplyr::if_else(rank <= 10, 1, 0)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(firm_id) %>% 
  dplyr::mutate(top5_ever = max(top5))

large_firms <- data_firms %>% 
  dplyr::filter(top5_ever == 1) %>% 
  dplyr::select(year, firm_id, rank)


```




```{r, echo = F, message = F, fig.width = 12, fig.height = 6}
g1 <- data_firms %>% 
  dplyr::filter(top5_ever == 1) %>% 
  dplyr::arrange(year, N) %>% 
  ggplot(aes(x = year, y = share, fill = firm_id)) +
  geom_bar(stat = "identity")

g2 <- data_firms %>% 
  dplyr::filter(top5_ever == 1) %>% 
  dplyr::arrange(year, N) %>% 
  ggplot(aes(x = year, y = sales / 1e+9, color = firm_id)) + geom_line() + geom_point() +
  ylab("Sales (Billion Yen)")
  

g3 <- data_firms %>% 
  dplyr::filter(top5_ever == 1) %>% 
  dplyr::arrange(year, N) %>% 
  ggplot(aes(x = year, y = N, color = firm_id)) + geom_line() + geom_point()

gridExtra::grid.arrange(g1, g2, g3, nrow = 1)

```




```{r, echo = F, message = F}

data_local <- data %>% 
  dplyr::group_by(firm_id, cz, year) %>% 
  dplyr::summarise(sales = sum(sales)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(cz, year) %>% 
  dplyr::mutate(share = sales / sum(sales)) %>% 
  dplyr::ungroup() %>% 
  dplyr::left_join(large_firms, by = c("firm_id", "year")) %>% 
  dplyr::mutate(large = dplyr::if_else(!is.na(rank), 1, 0)) %>% 
  dplyr::group_by(cz, year) %>% 
  dplyr::summarise(share = sum(share * large),
                   N = dplyr::n()) %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(!is.nan(share))

# In some areas, share = NaN because sum(sales) = 0.

data_local <- dplyr::left_join(community_zone, data_local, by = c("cz"))
```


### Market size and shares by large firms
```{r, echo = F, message = F, warning = F}

g1 <- data_local %>% 
  ggplot(aes(x = N, y = share)) +
  geom_point() + ylab("Share of Large Firms")

g2 <- data_local %>% 
  ggplot(aes(x = log(N), y = share)) +
  geom_point() + ylab("Share of Large Firms")


gridExtra::grid.arrange(g1, g2, nrow = 1)

```




## Sales share of large firms in community zones {.tabset}


```{r, include = F}
jpmap <- jpn_pref(1, district = T)
for (i in 2:47){
  jpmap <- dplyr::bind_rows(jpmap, jpn_pref(i, district = T))
}
```




### Year 2010
```{r, echo = F}

temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2010), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)


g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 


g

```

### Year 2011
```{r, echo = F}

temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2011), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)

g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 


g

```


### Year 2012
```{r, echo = F}

temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2012), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)

g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 

g

```


### Year 2013
```{r, echo = F}


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2013), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)

g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 


g

```



### Year 2014
```{r, echo = F}

temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code),
                pref_code = as.numeric(pref_code)) %>% 
  dplyr::left_join(dplyr::filter(data_local, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421)


g <- temp %>% 
  ggplot(aes(fill = share)) + geom_sf(color = NA) + 
  coord_sf(datum = NA) +
  scale_fill_continuous(low = "wheat",
                        high = "orangered4",
                        na.value = "gray80",
                        limits = c(0, 0.5)) 

g

```


## Location of establishments at 2014 {.tabset}

```{r, include = F}
jpmap <- jpn_pref(1, district = T)
for (i in 2:47){
  jpmap <- dplyr::bind_rows(jpmap, jpn_pref(i, district = T))
}

```


### ID 112233

```{r, echo = F}
locations <- data %>% 
  dplyr::filter(firm_id == 112233) %>% 
  dplyr::select(firm_id, year, zipcode, mun)


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code)) %>% 
  dplyr::left_join(dplyr::filter(locations, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421) %>% 
  dplyr::mutate(ishere = !is.na(firm_id))


g <- temp %>% 
  ggplot(aes(fill = ishere)) + geom_sf(color = NA, show.legend = F) + 
  coord_sf(datum = NA) + scale_fill_manual(values = c("FALSE" = "gray90", "TRUE" = "blue"))

g

```


### ID 113410

```{r, echo = F}
locations <- data %>% 
  dplyr::filter(firm_id == 113410) %>% 
  dplyr::select(firm_id, year, zipcode, mun)


temp <- jpmap %>% 
  dplyr::select(pref_code, city_code, geometry) %>% 
  dplyr::mutate(city_code = as.numeric(city_code)) %>% 
  dplyr::left_join(dplyr::filter(locations, year == 2014), by = c("city_code" = "mun")) %>% 
  dplyr::filter(city_code != 13421) %>% 
  dplyr::mutate(ishere = !is.na(firm_id))


g <- temp %>% 
  ggplot(aes(fill = ishere)) + geom_sf(color = NA, show.legend = F) + 
  coord_sf(datum = NA) + scale_fill_manual(values = c("FALSE" = "gray90", "TRUE" = "blue"))

g

```


