---
title: "Model Estimation"
author: "Katsuhiro Komatsu"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 4, fig.width = 8)
```

```{r, include = F}

type = "html" # regression output

library(magrittr)
library(ggplot2); theme_set(theme_bw())
library(stargazer)
library(lfe)
library(gmm)
library(nleqslv)

```


```{r}
load("../output/share_data.RData")
```

```{r}
x_names <- share_data %>% 
  dplyr::select(
    daily,
    shokai,
    oversea,
    cocurrent,
    dplyr::starts_with("type_")
  ) %>% 
  colnames()

iv_names <- share_data %>% 
  dplyr::select(
    dplyr::starts_with("d_mean_"),
    dplyr::starts_with("d_sd_")
  ) %>% 
  colnames()


fe_names <- share_data %>% 
  dplyr::select(
    year_cz,
    firm_id
  ) %>% 
  colnames()

var_names <- list(
  x_names = x_names,
  iv_names = iv_names,
  fe_names = fe_names
)

```


<!-- ### Distribution of Net Wages and Net Fees -->
```{r, eval = F}
g1 <- share_data %>% 
  ggplot(aes(x = wage_net)) + stat_ecdf() +
  xlab("Wage - Parttime Wage") + ylab("Fraction")

g2 <- share_data %>% 
  ggplot(aes(x = fee_net)) + stat_ecdf() +
  xlab("Fee - Parttime Wage") + ylab("Fraction")

gridExtra::grid.arrange(g1, g2, nrow = 1)

```


- Year x CZ fixed effects and firm fixed effects are controlled.
- Covariates: Type of work, daily (dummy), shokai, oversea, coccurent
- Differentiation IV: For each THS establishment $i$, compute $d_{i,k}=|x_i - x_k|$ for all $k\neq i$ and use the average and the standard deviation of $d_{i,k}$ as instruments for wages and fees.

```{r, results="asis", eval = F}

reg_data <- share_data %>% 
  dplyr::select(
    y_W,
    y_F,
    dplyr::starts_with("type_"),
    daily,
    shokai,
    oversea,
    cocurrent,
    staff_decile,
    dplyr::starts_with("d_mean_"),
    dplyr::starts_with("d_sd_"),
    year_cz,
    firm_id,
    wage_net,
    fee_net,
    cz,
    wage_hiv,
    fee_hiv,
    fee,
    wage,
    share_W,
    share_F,
    year,
    id_unique
  ) %>% 
  dplyr::mutate(firm_id = as.numeric(firm_id)) %>% 
  na.omit()

formula_list <- list()
formula_list[[1]] <- paste("y_W ~ ", ctr_vars, " + wage_net + fee_net | year_cz + firm_id | 0 | cz ")
formula_list[[2]] <- paste("y_W ~ ", ctr_vars, " + 1 | year_cz + firm_id | (wage_net | fee_net ~ ", iv_dif,  ") | cz ")
formula_list[[3]] <- paste("y_W ~ ", ctr_vars, " + 1 | year_cz + firm_id | (wage_net | fee_net ~ wage_hiv + fee_hiv + I(wage_hiv ^ 2) + I(fee_hiv ^ 2) + wage_hiv:fee_hiv) | cz ")
formula_list[[4]] <- paste("y_W ~ ", ctr_vars, " + 1 | year_cz + firm_id | (wage_net | fee_net ~ ", iv_dif,  " + wage_hiv + fee_hiv) | cz ")
formula_list[[5]] <- paste("y_F ~ ", ctr_vars, " + wage_net + fee_net | year_cz + firm_id | 0 | cz ")
formula_list[[6]] <- paste("y_F ~ ", ctr_vars, " + 1 | year_cz + firm_id | (wage_net | fee_net ~ ", iv_dif,  ") | cz ")
formula_list[[7]] <- paste("y_F ~ ", ctr_vars, " + 1 | year_cz + firm_id | (wage_net | fee_net ~ wage_hiv + fee_hiv + I(wage_hiv ^ 2) + I(fee_hiv ^ 2) + wage_hiv:fee_hiv) | cz ")
formula_list[[8]] <- paste("y_F ~ ", ctr_vars, " + 1 | year_cz + firm_id | (wage_net | fee_net ~ ", iv_dif,  " + wage_hiv + fee_hiv) | cz ")


result <- list()
for (i in 1:8){
  result[[i]] <- reg_data %>% 
    felm(data = .,
      formula = as.formula(formula_list[[i]])) 
}


# tidy up the expression
i_w <- 1 + length(ctr_vars_names) # Because X includes the decile of staff members
i_f <- 2 + length(ctr_vars_names)

coef_order <- c(i_w, i_f, 1:(i_w-1))

for (j in 2:4){

  # change label
  rownames(result[[j]]$coefficients)[i_w] <- "wage_net"
  rownames(result[[j]]$beta)[i_w] <- "wage_net"
  names(result[[j]]$cse)[i_w] <- "wage_net"

  rownames(result[[j]]$coefficients)[i_f] <- "fee_net"
  rownames(result[[j]]$beta)[i_f] <- "fee_net"
  names(result[[j]]$cse)[i_f] <- "fee_net"

  # result[[j]]$coefficients <- result[[j]]$coefficients[coef_order, 1, drop = F]
  # result[[j]]$beta <- result[[j]]$beta[coef_order, 1, drop = F]
  # result[[j]]$cse <- result[[j]]$cse[coef_order]
  # result[[j]]$cpval <- result[[j]]$cpval[coef_order]

}

for (j in 6:8){

  # change label
  rownames(result[[j]]$coefficients)[i_w] <- "wage_net"
  rownames(result[[j]]$beta)[i_w] <- "wage_net"
  names(result[[j]]$cse)[i_w] <- "wage_net"

  rownames(result[[j]]$coefficients)[i_f] <- "fee_net"
  rownames(result[[j]]$beta)[i_f] <- "fee_net"
  names(result[[j]]$cse)[i_f] <- "fee_net"

  # result[[j]]$coefficients <- result[[j]]$coefficients[coef_order, 1, drop = F]
  # result[[j]]$beta <- result[[j]]$beta[coef_order, 1, drop = F]
  # result[[j]]$cse <- result[[j]]$cse[coef_order]
  # result[[j]]$cpval <- result[[j]]$cpval[coef_order]

}

stargazer(result, 
          type = "html",
          dep.var.labels.include = FALSE,
          column.separate = c(4, 4),
          column.labels = c("Worker", "Firm"),
          keep.stat = c("n", "rsq"),
          order = c("wage_net", "fee_net", "daily", "shokai", "oversea", "cocurrent"),
          # keep = c("wage", "fee"),
          covariate.labels = c("Net Wage", "Net Fee", "Daily", "Shokai", "Oversea", "Cocurrent", worktype_description$description_jp),
          add.lines = list(c("Dif IV", c("", "X", "", "X", "", "X", "", "X")),
                           c("Hausman IV", c("", "", "X", "X", "", "", "X", "X"))))

```

#### 1. OLS
```{r, results="asis"}

ctr_vars <- paste(x_names, sep = "", collapse = " + ")

result_w <- lfe::felm(
  formula = as.formula(paste("y_W ~ ", ctr_vars, " + wage_net + fee_net | year_cz + firm_id ")),
  data = share_data
)

result_f <- lfe::felm(
  formula = as.formula(paste("y_F ~ ", ctr_vars, " + wage_net + fee_net | year_cz + firm_id ")),
  data = share_data
)

stargazer(result_w, result_f, 
          type = "html",
          keep.stat = c("n", "rsq"),
          dep.var.labels.include = FALSE,
          dep.var.caption = "",
          column.labels = c("Worker", "Firm"),
          keep = c("wage_net", "fee_net", "daily", "shokai", "oversea", "cocurrent"),
          order = c("wage_net", "fee_net", "daily", "shokai", "oversea", "cocurrent"),
          covariate.labels = c("Net Wage", "Net Fee", "Daily", "Shokai", "Oversea", "Cocurrent"),
          omit = c("Constant"))

```


#### 2. GMM Separate Estimation 
  - Two-Step GMM without Optimal Instruments
```{r, results="asis"}
# GMM
vars <- c(x_names, iv_names, "y_W", "y_F", "wage_net", "fee_net")

fe_vars <- fe_names %>% 
  paste(sep = "", collapse = " + ")
  
# Partial out FE
data_list <- list()
for (i in 1:length(vars)){
    
  v <- vars[i]
  fml <- paste(v, " ~ 1 | ", fe_vars)
  data_list[[v]] <- fixest::feols(fml = as.formula(fml), data = share_data)$residuals
}

data_transformed <- as.data.frame(data_list)

ctr_vars <- paste(x_names, sep = "", collapse = " + ")
iv_vars <- paste(iv_names, sep = "", collapse = " + ")

fml_w <- paste("y_W ~ ", ctr_vars, " + wage_net + fee_net")
fml_f <- paste("y_F ~ ", ctr_vars, " + wage_net + fee_net")
fml_z <- paste(" ~ ", iv_vars, " + ", ctr_vars)

# result_w <- gmm(
#   g = as.formula(fml_w),
#   x = as.formula(fml_z),
#   data = data_transformed,
#   type = "twoStep"
# )
# 
# result_f <- gmm(
#   g = as.formula(fml_f),
#   x = as.formula(fml_z),
#   data = data_transformed,
#   type = "twoStep"
# )
# 
# save(result_w, result_f, file = "../output/gmm_result_separate.RData")

load("../output/gmm_result_separate.RData")

stargazer(result_w, result_f, 
          type = "html",
          keep.stat = c("n", "rsq"),
          dep.var.labels.include = FALSE,
          dep.var.caption = "",
          column.labels = c("Worker", "Firm"),
          keep = c("wage_net", "fee_net", "daily", "shokai", "oversea", "cocurrent"),
          order = c("wage_net", "fee_net", "daily", "shokai", "oversea", "cocurrent"),
          covariate.labels = c("Net Wage", "Net Fee", "Daily", "Shokai", "Oversea", "Cocurrent"),
          omit = c("Constant"))
```



#### GMM Joint Estimation 
  - Two-Step GMM without Optimal Instruments
```{r, results="asis"}
x_names <- share_data %>% 
  dplyr::select(
    daily,
    shokai,
    oversea,
    cocurrent,
    dplyr::starts_with("type_")
  ) %>% 
  colnames()

iv_names <- share_data %>% 
  dplyr::select(
    dplyr::starts_with("d_mean_"),
    dplyr::starts_with("d_sd_")
  ) %>% 
  colnames()


fe_names <- share_data %>% 
  dplyr::select(
    year_cz,
    firm_id
  ) %>% 
  colnames()

var_names <- list(
  x_names = x_names,
  iv_names = iv_names,
  fe_names = fe_names
)

# result <- estimate_parameters_all(share_data, var_names)
# save(result, file = "../output/gmm_not_optimal_iv.RData")

load("../output/gmm_not_optimal_iv.RData")

varname <- c("net wage", "net fee",
              names(result$params_linear_W)[1:4],
              "net wage", "net fee",
              names(result$params_linear_F[1:4]),
              names(result$params_linear_MC[1:4]))

coef <- c(result$params_nonlinear[1],
           -result$params_nonlinear[2],
           result$params_linear_W[1:4],
           result$params_nonlinear[4],
           -result$params_nonlinear[3],
           result$params_linear_F[1:4], 
           result$params_linear_MC[1:4])
names(coef) <- varname

se <- c(result$se_nonlinear[1:2], 
         result$se_linear_W[1:4], 
         result$se_nonlinear[4:3],
         result$se_linear_F[1:4], 
         result$se_linear_MC[1:4])
names(se) <- varname

# df <- data.frame(
#   Varname = c("net wage", "net fee",
#               names(result$params_linear_W)[1:4],
#               "net wage", "net fee",
#               names(result$params_linear_F[1:4]),
#               names(result$params_linear_MC[1:4])),
#   Coef = c(result$params_nonlinear[1],
#            -result$params_nonlinear[2],
#            result$params_linear_W[1:4],
#            result$params_nonlinear[4],
#            -result$params_nonlinear[3],
#            result$params_linear_F[1:4], 
#            result$params_linear_MC[1:4]),
#   SE = c(result$se_nonlinear[1:2], 
#          result$se_linear_W[1:4], 
#          result$se_nonlinear[3:4],
#          result$se_linear_F[1:4], 
#          result$se_linear_MC[1:4])
# )
# 
# df$Coef <- round(df$Coef, 3)
# df$SE <- round(df$SE, 3)
# tbl <- xtable::xtable(df)

# This regression has no meaning. Just to use stargazer. 
result_W <- lm(y_W ~ wage_net + fee_net + daily + shokai + oversea + cocurrent, 
               data = share_data)

# result_W$residuals <- NULL
# result_W$effects <- NULL
# result_W$rank <- NULL
# result_W$fitted.values <- NULL
# result_W$assign <- NULL
# result_W$call <- NULL

result_F <- result_W
result_MC <- result_W


w_idx <- 1:6
f_idx <- 7:12
mc_idx <- 13:16

result_W$coefficients <- coef[w_idx]
result_F$coefficients <- coef[f_idx]
result_MC$coefficients <- coef[mc_idx]

stargazer(result_W, result_F, result_MC,
          type = "html",
          dep.var.caption = "",
          dep.var.labels.include = FALSE,
          column.labels = c("Worker", "Firm", "MC"),
          se = list(se[w_idx], se[f_idx], se[mc_idx]),
          covariate.labels = c("Net Wage", "Net Fee", "Daily", "Shokai", "Oversea", "Cocurrent"),
          keep.stat = c("N"))

# knitr::kable(tbl, format = "html", caption = "", booktabs = T) %>%
#   kableExtra::kable_styling() %>%
#   kableExtra::group_rows("Worker Demand", 1, 6) %>%
#   kableExtra::group_rows("Firm Demand", 7, 12) %>% 
#   kableExtra::group_rows("Supply Side", 13, 16)
```







<!-- ### Residuals $\hat \xi_{i,m,t}$ -->
<!-- ```{r, eval=F} -->

<!-- result_W <- result[[2]] -->
<!-- result_F <- result[[6]] -->
<!-- reg_data$resid_W <- result_W$residuals -->
<!-- reg_data$resid_F <- result_F$residuals -->

<!-- figdata <- data %>%  -->
<!--   dplyr::filter(to_use == 1) %>%  -->
<!--   dplyr::left_join(dplyr::select(reg_data, id_unique, resid_W, resid_F), by = "id_unique") %>%  -->
<!--   dplyr::group_by(year, firm_id) %>%  -->
<!--   dplyr::mutate(firmsize = dplyr::n()) %>%  -->
<!--   dplyr::ungroup() -->

<!-- figdata$sales_qntl <- gtools::quantcut(figdata$sales, q = 4, na.rm = T) -->
<!-- levels(figdata$sales_qntl) <- c("Q1", "Q2", "Q3", "Q4") -->

<!-- figdata$firmsize_qntl <- gtools::quantcut(figdata$firmsize, q = 4, na.rm = T) -->
<!-- levels(figdata$firmsize_qntl) <- c("Q1", "Q2", "Q3", "Q4") -->

<!-- # Sales -->
<!-- g1 <- figdata %>%  -->
<!--   ggplot(aes(x = resid_W, color = sales_qntl, linetype = sales_qntl)) + -->
<!--   stat_ecdf() + xlab("Worker Side Residual") + ylab("Fraction") + ggtitle("Distribution of Worker Side Residuals") + -->
<!--   scale_color_discrete(name = "Sales") + -->
<!--   scale_linetype_discrete(name = "Sales") + -->
<!--   xlim(-5, 5) + theme(legend.position = "bottom") -->

<!-- g2 <- figdata %>%  -->
<!--   ggplot(aes(x = resid_F, color = sales_qntl, linetype = sales_qntl)) + -->
<!--   stat_ecdf() + xlab("Firm Side Residual") + ylab("Fraction") + ggtitle("Distribution of Firm Side Residuals") + -->
<!--   scale_color_discrete(name = "Sales") + -->
<!--   scale_linetype_discrete(name = "Sales") + -->
<!--   xlim(-5, 5) + theme(legend.position = "bottom") -->

<!-- gridExtra::grid.arrange(g1, g2, nrow = 1) -->

<!-- # Firm size (number of establishments) -->
<!-- g1 <- figdata %>%  -->
<!--   ggplot(aes(x = resid_W, color = firmsize_qntl, linetype = firmsize_qntl)) + -->
<!--   stat_ecdf() + xlab("Worker Side Residual") + ylab("Fraction") + ggtitle("Distribution of Worker Side Residuals") + -->
<!--   scale_color_discrete(name = "Num Establishments") + -->
<!--   scale_linetype_discrete(name = "Num Establishments") + -->
<!--   xlim(-5, 5) + theme(legend.position = "bottom") -->

<!-- g2 <- figdata %>%  -->
<!--   ggplot(aes(x = resid_F, color = firmsize_qntl, linetype = firmsize_qntl)) + -->
<!--   stat_ecdf() + xlab("Firm Side Residual") + ylab("Fraction") + ggtitle("Distribution of Firm Side Residuals") + -->
<!--   scale_color_discrete(name = "Num Establishments") + -->
<!--   scale_linetype_discrete(name = "Num Establishments")   + -->
<!--   xlim(-5, 5) + theme(legend.position = "bottom") -->

<!-- gridExtra::grid.arrange(g1, g2, nrow = 1) -->


<!-- ``` -->


<!-- ### GMM -->
<!-- ```{r} -->

<!-- fml_1 <- paste("y_W ~ wage_net + fee_net + factor(year_cz) + ", ctr_vars) -->
<!-- fml_2 <- paste(" ~ ", iv_dif, " + factor(year_cz) + ", ctr_vars) -->

<!-- foo <- gmm::gmm( -->
<!--   as.formula(fml_1), as.formula(fml_2), -->
<!--   data = reg_data, -->
<!--   type = "twoStep" -->
<!-- ) -->

<!-- summary(foo) -->

<!-- ``` -->



<!-- ### First Stage -->
<!-- ```{r, results="asis"} -->

<!-- formula_list <- list() -->
<!-- formula_list[[1]] <- paste("wage_net ~ ", ctr_vars, " + wage_hiv + fee_hiv | year_cz + firm_id | 0 | cz ") -->
<!-- formula_list[[2]] <- paste("wage_net ~ ", ctr_vars, "+", iv_dif, " | year_cz + firm_id | 0 | cz ") -->
<!-- formula_list[[3]] <- paste("fee_net ~ ", ctr_vars, " + wage_hiv + fee_hiv | year_cz + firm_id | 0 | cz ") -->
<!-- formula_list[[4]] <- paste("fee_net ~ ", ctr_vars, "+", iv_dif, "  | year_cz + firm_id | 0 | cz ") -->

<!-- result <- list() -->
<!-- for (i in 1:4){ -->
<!--   result[[i]] <- share_data %>%  -->
<!--     felm(data = ., -->
<!--       formula = as.formula(formula_list[[i]]))  -->
<!-- } -->

<!-- stargazer(result,  -->
<!--           type = "html", -->
<!--           dep.var.labels.include = FALSE, -->
<!--           column.separate = c(2, 2), -->
<!--           column.labels = c("Net Wage", "Net Fee"), -->
<!--           keep.stat = c("n", "rsq"), -->
<!--           order = c("wage_hiv", "fee_hiv")) -->

<!-- ``` -->


<!-- ### Implied Marginal Costs -->

<!-- ```{r, eval=F} -->

<!-- fn_param <- function(x, param){ -->

<!--   alpha = x[1] -->
<!--   beta = x[2] -->
<!--   lambda_W = x[3] -->
<!--   lambda_F = x[4] -->

<!--   out = rep(0, 4) -->
<!--   out[1] = -param[1] + (1 + (beta + 2 * (alpha - 1)) / 2 / (2 - alpha - beta)) / lambda_W -->
<!--   out[2] = -param[2] + beta / 2 / (2 - alpha - beta) -->
<!--   out[3] = -param[3] + (1 + (alpha + 2 * (beta - 1)) / 2 / (2 - alpha - beta)) / lambda_F -->
<!--   out[4] = -param[4] + alpha / 2 / (2 - alpha - beta) -->

<!--   return(out) -->
<!-- } -->

<!-- param <- c(1.789, 1.865, 1.203, 0.944) -->

<!-- fn <- function(x){ return (fn_param(x, param))} -->
<!-- result <- nleqslv(rep(0.5, 4), fn) -->
<!-- alpha = result$x[1] -->
<!-- beta = result$x[2] -->


<!-- beta_W_1 = param[1] -->
<!-- beta_W_2 = param[2] -->
<!-- beta_F_1 = param[3] -->
<!-- beta_F_2 = param[4] -->

<!-- # Worker side -->
<!-- temp <- share_data %>%  -->
<!--   dplyr::mutate( -->
<!--     mu_W = fee - 1 / (alpha * beta_W_1 * (1 - share_W) + beta * beta_F_2 * (1 - share_F)), -->
<!--     mu_F = wage + 1 / (beta * beta_F_1 * (1 - share_F) + alpha * beta_W_2 * (1 - share_W)), -->
<!--     c_W = mu_W - wage, -->
<!--     c_F = fee - mu_F -->
<!--   ) %>%  -->
<!--   dplyr::select(year, cz, wage, fee, mu_W, mu_F, c_W, c_F, share_W, share_F) -->

<!-- # g1 <- data.frame(mc = temp$c_F, type = "by FOC for Fee") %>%  -->
<!-- #   dplyr::bind_rows(data.frame(mc = temp$c_W, type = "by FOC for Wage")) %>%  -->
<!-- #   ggplot(aes(x = mc)) + geom_point() + xlab("Marginal Cost (10K Yen)") + -->
<!-- #   theme(legend.title = element_blank(), legend.position = "bottom") -->

<!-- g1 <- temp %>%  -->
<!--   ggplot(aes(x = c_W, y = c_F)) + geom_point() + -->
<!--   xlab("MC implied by FOC for wage (10K Yen)") + ylab("MC implied by FOC for fee (10K Yen)") -->

<!-- g2 <- temp %>%  -->
<!--   ggplot(aes(x = fee - wage)) + geom_histogram() + xlab("Fee - Wage (10K Yen)") -->


<!-- g3 <- data.frame(mc = temp$c_F, type = "by FOC for Fee") %>%  -->
<!--   dplyr::bind_rows(data.frame(mc = temp$c_W, type = "by FOC for Wage")) %>%  -->
<!--   ggplot(aes(x = mc, color = type, fill = type)) + stat_ecdf() + xlab("Marginal Cost (10K Yen)") + ylab("Fraction") + -->
<!--   theme(legend.title = element_blank(), legend.position = "bottom") -->

<!-- g4 <- temp %>%  -->
<!--   ggplot(aes(x = fee - wage)) + stat_ecdf() + xlab("Fee - Wage (10K Yen)") + ylab("Fraction") -->

<!-- gridExtra::grid.arrange(g1, g3, g4, nrow = 2) -->

<!-- ``` -->




<!-- ### Implied Parameters -->
<!-- ```{r, eval = F} -->

<!-- fn_param <- function(x, param){ -->

<!--   alpha = x[1] -->
<!--   beta = x[2] -->
<!--   lambda_W = x[3] -->
<!--   lambda_F = x[4] -->

<!--   out = rep(0, 4) -->
<!--   out[1] = -param[1] + (1 + (beta + 2 * (alpha - 1)) / 2 / (2 - alpha - beta)) / lambda_W -->
<!--   out[2] = -param[2] + beta / 2 / (2 - alpha - beta) -->
<!--   out[3] = -param[3] + (1 + (alpha + 2 * (beta - 1)) / 2 / (2 - alpha - beta)) / lambda_F -->
<!--   out[4] = -param[4] + alpha / 2 / (2 - alpha - beta) -->

<!--   return(out) -->
<!-- } -->

<!-- param <- c(3.033, 2.556, 1.314, 1.409) -->
<!-- fn <- function(x){ return (fn_param(x, param))} -->
<!-- result <- nleqslv(rep(0.5, 4), fn) -->
<!-- print(result) -->

<!-- ``` -->



<!-- ### Numerically check how $a_i$ affects $\mu_i^W$ and $\mu_i^F$ -->
<!-- ```{r, eval = F} -->


<!-- fn_a <- function(x, a){ -->

<!--   mu_W = x[1] -->
<!--   mu_F = x[2] -->

<!--   H_W = 1 -->
<!--   H_F = 1 -->
<!--   c = 1 -->
<!--   alpha = 0.350 -->
<!--   beta = 0.486 -->
<!--   lambda_W = 1 -->
<!--   lambda_F = 1 -->

<!--   p_W_1 = 1 + (beta + 2 * (alpha - 1)) / (2 * (2 - alpha - beta)) -->
<!--   p_W_2 = beta / (2 * (2 - alpha - beta)) -->
<!--   p_F_1 = 1 + (alpha + 2 * (beta - 1)) / (2 * (2 - alpha - beta)) -->
<!--   p_F_2 = alpha / (2 * (2 - alpha - beta)) -->

<!--   n_W = H_W * exp((a - c + mu_W) / lambda_W) ^ p_W_1 * exp((a - c - mu_F) / lambda_F) ^ p_W_2 -->
<!--   n_F = H_F * exp((a - c - mu_F) / lambda_F) ^ p_F_1 * exp((a - c + mu_W) / lambda_W) ^ p_F_2 -->

<!--   out = c(0, 0) -->
<!--   out[1] = -mu_W + c + mu_F + lambda_W * p_W_1 * (1 - n_W) - lambda_W * p_W_2 * (1 - n_F) -->
<!--   out[2] = -mu_F - c + mu_W - lambda_F * p_F_1 * (1 - n_F) + lambda_F * p_F_2 * (1 - n_W) -->

<!--   return(out) -->
<!-- } -->

<!-- a <- 1.5 -->
<!-- fn <- function(x){ return (fn_a(x, a))} -->
<!-- result <- nleqslv(c(1, 1), fn) -->

<!-- mu_W_vec <- c() -->
<!-- mu_F_vec <- c() -->
<!-- a_vec <- 1:10 * 0.1 -->

<!-- for (i in 1:10){ -->
<!--   fn <- function(x){ return (fn_a(x, a_vec[i]))} -->
<!--   result <- nleqslv(c(1, 1), fn) -->
<!--   mu_W_vec <- c(mu_W_vec, result$x[1]) -->
<!--   mu_F_vec <- c(mu_F_vec, result$x[2]) -->
<!-- } -->


<!-- g1 <- data.frame(a = a_vec, mu = mu_W_vec) %>%  -->
<!--   ggplot(aes(x = a, y = mu)) + geom_point() + xlab("a") + ylab("m_W") -->

<!-- g2 <- data.frame(a = a_vec, mu = mu_F_vec) %>%  -->
<!--   ggplot(aes(x = a, y = mu)) + geom_point() + xlab("a") + ylab("m_F") -->

<!-- gridExtra::grid.arrange(g1, g2, nrow = 1) -->


<!-- ``` -->

