---
title: "Margin Distribution"
author: "Katsuhiro Komatsu"
date: "2020/8/3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F, include = F}
rm(list = ls())
gc()

library(magrittr)
library(ggplot2); theme_set(theme_bw())
library(stargazer)
library(tidyverse)
library(gtools)
library(knitr)
library(psych)
```

```{r, include = F}
load("../data/data_2010_2014_cleaned.RData")
data <- dplyr::filter(data, tokutei == 0)
```


### Margin
```{r, echo = F}
ds <- data %>% 
  dplyr::select(year, margin) %>% 
  dplyr::group_by(year) %>% 
  dplyr::mutate(temp = 1,
                id = cumsum(temp)) %>% 
  spread(year, margin) %>% 
  dplyr::select(!(temp:id)) %>% 
  describe(skew = F,
           ranges = F,
           trim = 0,
           quant = c(.01, .05, .25, .5, .75, .95, .99))

ds$vars <- NULL
ds$se <- NULL
```

```{r, echo = F, results = "asis"}
kable(ds, digits = 3)
```




### Wage
```{r, echo = F}
ds <- data %>% 
  dplyr::select(year, wage) %>% 
  dplyr::group_by(year) %>% 
  dplyr::mutate(temp = 1,
                id = cumsum(temp)) %>% 
  spread(year, wage) %>% 
  dplyr::select(!(temp:id)) %>% 
  describe(skew = F,
           ranges = F,
           trim = 0,
           quant = c(.01, .05, .25, .5, .75, .95, .99))

ds$vars <- NULL
ds$se <- NULL
```

```{r, echo = F, results = "asis"}
kable(ds, digits = 2)
```

### Fee
```{r, echo = F}
ds <- data %>% 
  dplyr::select(year, fee) %>% 
  dplyr::group_by(year) %>% 
  dplyr::mutate(temp = 1,
                id = cumsum(temp)) %>% 
  spread(year, fee) %>% 
  dplyr::select(!(temp:id)) %>% 
  describe(skew = F,
           ranges = F,
           trim = 0,
           quant = c(.01, .05, .25, .5, .75, .95, .99))

ds$vars <- NULL
ds$se <- NULL
```

```{r, echo = F, results = "asis"}
kable(ds, digits = 2)
```


### CDF of Margins
```{r, echo = F}

g <- data %>% 
  dplyr::filter(year == 2010 | year == 2012 | year == 2014) %>% 
  dplyr::mutate(year = as.factor(year)) %>% 
  ggplot(aes(x = margin)) +
  stat_ecdf(aes(color = year)) +
  labs(y = "CDF") + 
  coord_cartesian(xlim = c(0.2, 1))

g
```

- Compute the dispersion of margin in each commuting zone (95%tile - 5%tile, 90%tile - 10%tile etc.)
- Plot the dispersion in year 2010 on x-axis and the change of the dispersion on y-axis.
```{r, echo = F, message = F}

data_cz <- data %>% 
  dplyr::group_by(year, cz) %>% 
  dplyr::summarise(margin_p05 = quantile(margin, c(0.05)),
                   margin_p10 = quantile(margin, c(0.1)),
                   margin_p25 = quantile(margin, c(0.25)),
                   margin_p75 = quantile(margin, c(0.75)),
                   margin_p90 = quantile(margin, c(0.9)),
                   margin_p95 = quantile(margin, c(0.95)),
                   N = dplyr::n()) %>% 
  dplyr::ungroup()

# data_cz <- data_cz %>% 
#   dplyr::filter(N >= 10)

```
### 1. Change of the dispersion between 2010-2014 (After the policy change)
```{r, echo = F, warning = F, message = F, fig.width = 12, fig.height = 6}

g1 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p75 - margin_p25) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2014 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p75 - p25") + ylab("Change in margin p75 - p25")


g2 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p90 - margin_p10) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2014 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p90 - p10") + ylab("Change in margin p90 - p10")
  

g3 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p95 - margin_p05) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2014 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p95 - p5") + ylab("Change in margin p95 - p5")

gridExtra::grid.arrange(g1, g2, g3, nrow = 1)

```


### 2. Change between 2010-2013 (After the policy change)
```{r, echo = F, warning = F, message = F, fig.width = 12, fig.height = 6}

g1 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p75 - margin_p25) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2013 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p75 - p25") + ylab("Change in margin p75 - p25")


g2 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p90 - margin_p10) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2013 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p90 - p10") + ylab("Change in margin p90 - p10")
  

g3 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p95 - margin_p05) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2013 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p95 - p5") + ylab("Change in margin p95 - p5")

gridExtra::grid.arrange(g1, g2, g3, nrow = 1)

```



### 3. Change between 2010-2012 (Before the policy change)
```{r, echo = F, warning = F, message = F, fig.width = 12, fig.height = 6}

g1 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p75 - margin_p25) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2012 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p75 - p25") + ylab("Change in margin p75 - p25")


g2 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p90 - margin_p10) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2012 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p90 - p10") + ylab("Change in margin p90 - p10")
  

g3 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p95 - margin_p05) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2012 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p95 - p5") + ylab("Change in margin p95 - p5")

gridExtra::grid.arrange(g1, g2, g3, nrow = 1)
```


### 4. Change between 2010-2011 (Before the policy change)
```{r, echo = F, warning = F, message = F, fig.width = 12, fig.height = 6}

g1 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p75 - margin_p25) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2011 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p75 - p25") + ylab("Change in margin p75 - p25")


g2 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p90 - margin_p10) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2011 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p90 - p10") + ylab("Change in margin p90 - p10")
  

g3 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p95 - margin_p05) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2011 - year_2010))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p95 - p5") + ylab("Change in margin p95 - p5")

gridExtra::grid.arrange(g1, g2, g3, nrow = 1)
```


### 5. Change between 2012-2013
```{r, echo = F, warning = F, message = F, fig.width = 12, fig.height = 6}

g1 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p75 - margin_p25) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2013 - year_2012))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p75 - p25") + ylab("Change in margin p75 - p25")


g2 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p90 - margin_p10) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2013 - year_2012))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p90 - p10") + ylab("Change in margin p90 - p10")
  

g3 <- data_cz %>% 
  dplyr::mutate(margin_disp = margin_p95 - margin_p05) %>% 
  dplyr::select(year, margin_disp, cz) %>% 
  tidyr::spread(key = year, value = margin_disp, sep = "_") %>% 
  ggplot(aes(x = year_2010, y = (year_2013 - year_2012))) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  xlab("Margin p95 - p5") + ylab("Change in margin p95 - p5")

gridExtra::grid.arrange(g1, g2, g3, nrow = 1)
```